### 2022-07-28 README.Rmd
Updates

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

# simbased

<!-- badges: start -->
<!-- badges: end -->

`simbased` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as marginal effects.

## Installation

You can install the development version of simbased from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ngreifer/simbased")
```

## Example

Below is an example of performing g-computation for the ATT after logistic regression to compute the marginal risk ratio and its confidence interval:

```{r example}
library(simbased)

data("lalonde", package = "MatchIt")

fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married + nodegree + re74 + re75),
           data = lalonde, family = binomial)

set.seed(123)
sim_coefs <- sim(fit)

sim_est <- sim_apply(sim_coefs, function(fit) {
  d <- subset(lalonde, treat == 1)
  d$treat <- 1
  p1 <- mean(predict(fit, newdata = d, type = "response"))
  d$treat <- 0
  p0 <- mean(predict(fit, newdata = d, type = "response"))
  c(RR = p1 / p0)
}, verbose = FALSE)

summary(sim_est)
sim_plot(sim_est)
```

We could have used `marginaleffects`, which uses the delta method instead:

```{r}
marginaleffects::comparisons(fit, variables = list(treat = 0:1),
                             newdata = subset(lalonde, treat == 1),
                             transform_pre = "lnratioavg") |>
  summary(transform_avg = exp)
```

The simulation-based confidence intervals are a bit wider, reflecting that the delta method may be a poor approximation.

### 2022-07-28 R/sim_apply.R

@@ -8,14 +8,19 @@
 #' @export
 #'
 #' @examples
-sim_apply <- function(sim, FUN, ...) {
+sim_apply <- function(sim, FUN, verbose = TRUE, ...) {
   if (missing(FUN)) {
     stop("FUN must be supplied.")
   }
 
-  test <- try(FUN(sim$fit, ...))
+  FUN <- process_FUN(FUN)
+
+  apply_FUN <- make_apply_FUN(FUN)
+
+  test <- try(apply_FUN(fit = sim$fit, coefs = coef(fit), ...), silent = TRUE)
   if (inherits(test, "try-error")) {
-    stop("Initial check failed.")
+    chk::err("`FUN` failed to run on an initial check with the following error:\n",
+             conditionMessage(attr(test, "condition")))
   }
 
   if (is.null(names(test))) names(test) <- paste0("est", seq_along(test))
@@ -23,49 +28,65 @@ sim_apply <- function(sim, FUN, ...) {
   ests <- matrix(NA_real_, nrow = nrow(sim$coefs), ncol = length(test),
                  dimnames = list(NULL, names(test)))
 
-  pb <- txtProgressBar(0, nrow(ests), style = 3)
+  if (verbose) pb <- txtProgressBar(0, nrow(ests), style = 3)
   for (i in seq_len(nrow(ests))) {
-    sim$fit <- coef_assign(sim$fit, sim$coefs[i,])
-    ests[i,] <- FUN(sim$fit, ...)
-    setTxtProgressBar(pb, i)
+    ests[i,] <- apply_FUN(fit = sim$fit, coefs = sim$coefs[i,], ...)
+    if (verbose) setTxtProgressBar(pb, i)
   }
-  close(pb)
+  if (verbose) close(pb)
 
-  out <- list(est = ests)
+  out <- list(est = ests,
+              original = test)
   class(out) <- "simbased_est"
 
   out
 }
 
-summary.simbased_est <- function(object, alpha = .05, ...) {
-  ans <- list()
-  est <- coef(object)
-  se <- sqrt(diag(vcov(object)))
-  z <- est/se
-  p <- 2 * pnorm(abs(z), lower.tail = FALSE)
-
-  fmt.prc <- function(probs, digits = 3) {
-    paste(format(100 * probs, trim = TRUE, scientific = FALSE, digits = digits), "%")
-  }
-
[…]

### 2022-07-28 R/sim_plot.R

@@ -1,7 +1,7 @@
 #' Title
 #'
 #' @param x a `simbased_est1 object`; the output of a call to `sim_apply()`.
-#' @param est
+#' @param est a vector of the names or indices of the estimates to plot. If unspecified, all estimates will be plotted.
 #' @param ci
 #' @param alpha
 #'
@@ -9,10 +9,15 @@
 #' @export
 #' @import ggplot2
 #' @examples
-sim_plot <- function(x, est, ci = TRUE, alpha = .05) {
+sim_plot <- function(x, est, ci = TRUE, alpha = .05, normal = FALSE, transform = NULL) {
 
   if (!inherits(x, "simbased_est")) {
     stop("'x' must be a simbased_est object.")
+  }
+
+  if (!is.null(transform)) {
+    chk::chk_function(transform)
+    x$est <- transform(x$est)
   }
 
   est_names <- colnames(x$est)
@@ -36,14 +41,21 @@ sim_plot <- function(x, est, ci = TRUE, alpha = .05) {
 
   p <- ggplot() +
     geom_density(data = est_long, mapping = aes(x = val),
-                 color = "black", fill = "white") +
+                 color = "black", fill = "white", trim = TRUE) +
     geom_hline(yintercept = 0)
 
   if (ci) {
-    zcrit <- qnorm(c(alpha/2, 1-alpha/2))
-    ci <- do.call("rbind", lapply(est, function(e) {
-      data.frame(est = est_names[e], val = mean(x$est[,e]) + sd(x$est[,e])*zcrit)
-    }))
+    if (normal) {
+      zcrit <- qnorm(c(alpha/2, 1-alpha/2))
+      ci <- do.call("rbind", lapply(est, function(e) {
+        data.frame(est = est_names[e], val = mean(x$est[,e]) + sd(x$est[,e])*zcrit)
+      }))
+    }
+    else {
+      ci <- do.call("rbind", lapply(est, function(e) {
+        data.frame(est = est_names[e], val = quantile(x$est[,e], probs = c(alpha/2, 1-alpha/2)))
+      }))
+    }
 
     p <- p + geom_vline(data = ci, mapping = aes(xintercept = val), color = "red",
                         linetype = 1)

### 2022-07-28 R/summary.simbased_est.R

@@ -1,0 +1,76 @@
+#' Title
+#'
+#' @param object a `simbased_est` object; the output of a call to `sim_apply()`.
+#' @param alpha the $\alpha$ used to compute the confidence interval. Default is .05 for 95% confidence intervals.
+#' @param normal `logical`; whether to compute p-values and confidence intervals using a normal approximation (`TRUE`) or the simulated sampling distribution (`FALSE`; default).
+#' @param null the value of the parameter under the null hypothesis for the p-value calculations.
+#' @param ... ignored.
+#'
+#' @return
+#' @export
+#'
+#' @examples
+summary.simbased_est <- function(object, alpha = .05, normal = FALSE, test = FALSE, null = 0, transform = NULL, ...) {
+  ans <- list()
+  est <- coef(object)
+
+  pct <- fmt.prc(c(alpha/2, 1-alpha/2))
+  ci <- matrix(nrow = length(est), ncol = 2,
+               dimnames = list(names(est), paste("CI", pct)))
+
+  chk::chk_numeric(null)
+  if (length(null) == 1) null <- rep(null, length(est))
+  chk::chk_length(null, length(est))
+
+  if (!is.null(transform)) {
+    if (is.character(transform)) transform_name <- transform
+    else transform_name <- "fn"
+    transform <- try(match.fun(transform))
+    chk::chk_function(transform)
+    est <- transform(est)
+    object$est <- transform(object$est)
+  }
+
+  se <- z <- p <- NULL
+  if (normal) {
+    se <- sqrt(diag(vcov(object)))
+    if (test) {
+      z <- (est - null)/se
+      p <- 2 * pnorm(abs(z), lower.tail = FALSE)
+    }
+    zcrit <- qnorm(c(alpha/2, 1-alpha/2))
+    ci[,1] <- est - null + se*zcrit[1]
+    ci[,2] <- est - null + se*zcrit[2]
+  }
+  else {
+    if (test) {
+      p <- vapply(seq_along(est), function(i) {
+        x <- object$est[,i]
+        if (est[i] < null) {
+          return(mean(x > null | x < 2*est[i] - null))
+        }
+        else {
+          return(mean(x < null | x > 2*est[i] - null))
+        }
+      }, numeric(1L))
+    }
+    ci[] <- t(apply(object$est, 2, quantile, probs = c(alpha/2, 1-alpha/2)))
+
+  }
+
[…]

### 2022-07-28 R/utils.R

@@ -90,3 +90,8 @@ match_arg <- function(arg, choices, several.ok = FALSE) {
 
   choices[i]
 }
+
+#Format percentage for CI labels
+fmt.prc <- function(probs, digits = 3) {
+  paste(format(100 * probs, trim = TRUE, scientific = FALSE, digits = digits), "%")
+}

### 2022-08-05 README.Rmd
Added sim_ame(), other changes and fixes; ready for testing

@@
   fig.path = "man/figures/README-",
-  out.width = "50%"
+  out.width = "80%"
 )
@@
 
-You can install the development version of simbased from [GitHub](https://github.com/) with:
+You can install the development version of `simbased` from [GitHub](https://github.com/) with:
 
@@
 
-```{r example}
+```{r example, fig.width=7, fig.height=3}
 library(simbased)
@@
   p0 <- mean(predict(fit, newdata = d, type = "response"))
-  c(RR = p1 / p0)
+  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, RR = p1 / p0)
 }, verbose = FALSE)
 
-summary(sim_est)
+summary(sim_est, null = c(NA, NA, 1))
 sim_plot(sim_est)
@@
 ```{r}
+# Marginal risk ratio ATT, delta method-based
 marginaleffects::comparisons(fit, variables = list(treat = 0:1),
@@
 The simulation-based confidence intervals are a bit wider, reflecting that the delta method may be a poor approximation.
+
+`simbased` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
+We can compute the marginal risk ratio below:
+
+```{r}
+# Marginal risk ratio ATT, simulation-based
+sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
+                   contrast = "RR", verbose = FALSE)
+
+summary(sim_est, null = c(NA, NA, 1))
+```
+
+We can also use `simbased` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
+
+```{r, fig.width=7, fig.height=3}
+# Predictions across age and treat at typical values
+# of the other predictors
+sim_est <- sim_setx(sim_coefs, x = list(age = 20:50, treat = 0:1),
+                    verbose = FALSE)
+
+setx_plot(sim_est)
+```
+
+`simbased` offers parallel processing for all estimation functions to speed up computation.
+
+The methodology of simulation-based inference is described in King, Tomz, and Wittenberg (2000).
+
+King, G., Tomz, M., & Wittenberg, J.
+(2000).
+Making the Most of Statistical Analyses: Improving Interpretation and Presentation.
+*American Journal of Political Science*, 44(2), 347–361.
+https://doi.org/10.2307/2669316

### 2022-08-05 R/setx_plot.R

@@ -1,0 +1,217 @@
+#' Plot marginal predictions from `sim_setx()`
+#'
+#' `setx_plot()` plots the output of [sim_setx()], providing graphics similar to those of [sim_plot()] but with features specifically for plot marginal predictions. For continues predictors, this is a plot of the marginal predictions and their confidence bands across levels of the predictor. Otherwise, this is is a plot of simulated sampling distribution of the marginal predictions.
+#'
+#' @inheritParams sim_plot
+#' @param x a `simbased_est` object resulting from a call to [sim_setx()].
+#' @param var the name of the focal varying predictor, i.e., the variable to be on the x-axis of the plot. All other variables with varying set values will be used to color the resulting plot. See Details. Ignored if no predictors vary or if only predictor varies in the reference grid or if `x1` was specified in `sim_setx()`. If not set, will use the predictor with the greatest number of unique values specified in the reference grid.
+#'
+#' @return a `ggplot` object
+#'
+#' @details `setx_plot()` creates one of two kinds of plots depending on how the reference grid was specified in the call to `sim_setx()` and what `var` is set to. When the focal varying predictor (i.e., the one set in `var`) is numeric and takes on three more unique values in the reference grid, the produced plot is a line graph displaying the value of the marginal prediction (denoted as `E[Y|X]`) across values of the focal varying predictor, with confidence bands displayed when `ci = TRUE`. If other predictors also vary, lines for different values will be displayed in different colors. These plots are produced using [ggplot2::geom_line()] and [ggplot2::geom_ribbon()]
+#'
[…]

### 2022-08-05 R/sim.R

@@ -1,11 +1,11 @@
 #' Simulate model coefficients
 #'
-#' @description `sim()` simulates model parameters from a multivariate normal or t distribution that are then used by `[sim_apply()]` to calculate quantities of interest.
+#' @description `sim()` simulates model parameters from a multivariate normal or t distribution that are then used by [sim_apply()] to calculate quantities of interest.
 #'
-#' @param fit a model fit, such as the output of a call to `[lm()]` or `[glm()]`. Can be left unspecified if `coefs` and `vcov` are not functions.
+#' @param fit a model fit, such as the output of a call to [lm()] or [glm()]. Can be left unspecified if `coefs` and `vcov` are not functions.
 #' @param n the number of simulations to run; default is 1000. More is always better but resulting calculations will take longer.
-#' @param vcov either a square covariance matrix of the parameter estimates or a function to use to extract it from `fit`. By default, uses `[stats::vcov()]`.
-#' @param coefs either a vector of coefficient estimates or a function to use to extract it from `fit`. By default, uses `[stats::coef()]`. Using anything but the default changes some options in `sim_apply()`; see `[sim_apply()]`'s Details section for more information.
+#' @param vcov either a square covariance matrix of the parameter estimates or a function to use to extract it from `fit`. By default, uses [stats::vcov()].
+#' @param coefs either a vector of coefficient estimates or a function to use to extract it from `fit`. By default, uses [stats::coef()]. Using anything but the default changes some options in `sim_apply()`; see [sim_apply()]'s Details section for more information.
 #' @param dist a string containing the name of the multivariate distribution to use to draw simulated coefficients. Should be one of `"normal"` (multivariate normal distribution) or `"t_{#}"` (multivariate t distribution), where `{#}` corresponds to the desired degrees of freedom (e.g., `"t_100"`). If `NULL`, `sim()` will attempt to figure out the right distribution to use; see Details.
 #'
 #' @return A `simbased_sim` object, which has the following components:
@@ -15,14 +15,19 @@
 #'
 #' @details When `dist` is `NULL`, `sim()` samples from a multivariate normal or t distribution depending on whether `df.residual(fit)` is `NULL` or not. If `NULL` or `fit` is unspecified, a multivariate normal distribution is used. Otherwise (primarily for linear models fit with `lm()`), a multivariate t distribution is used, with `df.residual(fit)` used as the degrees of freedom.
 #'
[…]

### 2022-08-05 R/sim_ame.R

@@ -1,0 +1,130 @@
+#' @export
+sim_ame <- function(sim,
+                    var,
+                    subset = NULL,
+                    contrast = NULL,
+                    verbose = TRUE,
+                    cl = NULL) {
+  chk::chk_is(sim, "simbased_sim")
+  chk::chk_flag(verbose)
+
+  dat <- insight::get_predictors(sim$fit)
+  vals <- NULL
+
+  if (missing(var)) {
+    chk::err("`var` must be supplied, identifying the focal variable")
+  }
+  if (is.list(var) && chk::vld_named(var) && length(var) == 1) {
+    vals <- var[[1]]
+    var <- names(var)
+  }
+  else if (!chk::vld_string(var)) {
+    chk::err("`var` must be the name of the desired focal variable or a named list of length 1 with its values")
+  }
+
+  if (!var %in% names(dat)) {
+    chk::err(sprintf("the variable \"%s\" named in `var` is not present in the original model",
+                     var))
+  }
+
+  var_val <- dat[[var]]
+
+  index <- eval(substitute(subset), dat, parent.frame())
+  dat <- dat[index,]
+
+  if (!is.null(vals) && !all(vals %in% var_val)) {
+    chk::err(sprintf("the values mentioned in `var` must be values %s takes on", var))
+  }
+
+  type <- {
+    if (!is.null(vals) || chk::vld_character_or_factor(var_val) ||
+        is.logical(var_val) || length(unique(dat[[var]])) <= 2)
+      "contrast"
+    else
+      "slope"
+  }
+
+  if (type == "contrast") {
+    if (is.null(vals)) {
+      vals <- if (is.factor(var_val)) levels(var_val) else sort(unique(var_val))
+    }
+
+    if (length(vals) == 2) {
+      if (!is.null(contrast)) {
+        chk::chk_string(contrast)
+        contrast <- tolower(contrast)
+        contrast <- match_arg(contrast, c("diff", "rd", "irr", "rr", "log(irr)",
+                                          "log(rr)", "or", "log(or)", "nnt"))
+      }
+    }
+    else if (length(vals) > 2) {
+      if (!is.null(contrast)) {
+        chk::wrn("`contrast` is ignored when the focal variable takes on more than two levels")
+        contrast <- NULL
+      }
+    }
+    else {
+      contrast <- NULL
+    }
+
+    FUN <- function(fit) {
[…]

### 2022-08-05 R/sim_apply.R

@@ -1,14 +1,14 @@
 #' Apply a function to simulated parameter values
 #'
-#' @description `sim_apply()` applies a function that produces quantities of interest to each set of simulated coefficients produced by `[sim()]`; these calculated quantities form the posterior sampling distribution for the quantities of interest. Capabilities are available for parallelization.
+#' @description `sim_apply()` applies a function that produces quantities of interest to each set of simulated coefficients produced by [sim()]; these calculated quantities form the posterior sampling distribution for the quantities of interest. Capabilities are available for parallelization.
 #'
-#' @param sim a `simbased_sim` object; the output of a call to `[sim()]`.
+#' @param sim a `simbased_sim` object; the output of a call to [sim()].
 #' @param FUN a function to be applied to each set of simulated coefficients. See Details.
 #' @param verbose `logical`; whether to display a text progress bar indicating progress and estimated time remaining for the procedure. Default is `TRUE`.
-#' @param cl a cluster object created by `[parallel::makeCluster()]`, or an integer to indicate number of child-processes (integer values are ignored on Windows) for parallel evaluations. See `[pbapply::pblapply()]` for details. If `NULL`, no parallelization will take place.
+#' @param cl a cluster object created by [parallel::makeCluster()], or an integer to indicate number of child-processes (integer values are ignored on Windows) for parallel evaluations. See [pbapply::pblapply()] for details. If `NULL`, no parallelization will take place.
 #' @param ... optional arguments passed to `FUN`.
 #'
-#' @details `sim_apply()` applies a function to each set of simulated coefficients, similar to `[apply()]`. This function should produce an estimated quantity for which inference is to take place.
+#' @details `sim_apply()` applies a function to each set of simulated coefficients, similar to [apply()]. This function should produce an estimated quantity for which inference is to take place.
 #'
 #' `FUN` should return a numeric vector containing one or more estimated quantities. This should be a named vector to more easily keep track of the meaning of each estimated quantity. Care should be taken to ensure that the returned vector is the same length each time `FUN` is called. `NA`s are allowed in the output but should be avoided if possible.
 #'
@@ -18,12 +18,21 @@
 #'
[…]

### 2022-08-05 R/sim_apply_wrappers.R

@@ -1,324 +1,21 @@
-#' @export
-sim_comparisons <- function(sim, newdata = NULL, variables = NULL, type = "response",
-                            transform_pre = "differenceavg", transform_post = NULL, interaction = NULL,
-                            by = NULL, wts = NULL, eps = NULL,
-                            verbose = TRUE, cl = NULL, ...) {
+sim_comparisons <- function(sim, verbose = TRUE, cl = NULL, ...) {
 
-  args <- list(...)
+  args <- alist(...)
+  args[["vcov"]] <- FALSE
+
   FUN <- function(fit) {
-    comp <- do.call(marginaleffects::comparisons, c(list(fit, newdata = newdata, variables = variables, type = type,
-                                                         transform_pre = transform_pre, transform_post = transform_post,
-                                                         interaction = interaction, by = by, wts = wts, eps = eps,
-                                                         vcov = FALSE),
-                                                    args))
-    comp$comparison
-  }
+    comp <- do.call(marginaleffects::comparisons, c(list(fit), args))
+    summ <- summary(comp)
 
+    estimate <- summ[["estimate"]]
+    contrast <- summ[[names(summ)[startsWith(names(summ), "contrast")][1]]]
+    by_vars <- setdiff(names(summ), c("estimate", names(summ)[startsWith(names(summ), "contrast")],
+                                      "type", "term"))
+
+    setNames(estimate, do.call("paste", c(lapply(by_vars, function(i) {
+      paste0(i, " = ", add_quotes(summ[[i]], chk::vld_character_or_factor(summ[[i]])))
+    }), list(contrast, sep = ", "))))
+  }
+# FUN(sim$fit)
   sim_apply(sim, FUN = FUN, verbose = verbose, cl = cl)
-}
-
-#' @export
-sim_setx <- function(sim, x = NULL, x1 = NULL, verbose = TRUE, cl = NULL, ...) {
-
-  dat <- insight::get_predictors(sim$fit)
-
-  #Check `x` and note which vars are to be set by arguments (`set_preds`) and
-  #which are set automatically (`auto_preds`)
-  x_okay <- TRUE
-  if (length(x) == 0) {
-    set_preds <- NULL
-    auto_preds <- names(dat)
-  }
[…]

### 2022-08-05 R/sim_plot.R

@@ -6,7 +6,9 @@
 #' @param x a `simbased_est` object; the output of a call to `sim_apply()`.
 #' @param est a vector of the names or indices of the estimates to plot. If unspecified, all estimates will be plotted.
 #' @param ci `logical`; whether to display confidence interval limits for the estimates. Default is `TRUE`.
-#' @param normal `logical`; whether to compute confidence intervals using a normal approximation (`TRUE`) or the simulated sampling distribution (`FALSE`; default). See `[summary.simbased_est()]` for details.
+#' @param normal `logical`; whether to compute confidence intervals using a normal approximation (`TRUE`) or the simulated sampling distribution (`FALSE`; default). See [summary.simbased_est()] for details.
+#'
+#' @details These plots are produced using [ggplot2::geom_density()].
 #'
 #' @return a `ggplot` object
 # @examples

### 2022-08-05 R/sim_setx.R

@@ -1,0 +1,150 @@
+#' Compute predictions and first differences at set values
+#'
+#' `sim_setx()` is a wrapper for [sim_apply()] that computes predicted values of the outcome at specified values of the predictors, sometimes called marginal predictions. One can also compute the difference between two marginal predictions (the "first difference"). Although any function that accepted `simbased_est` objects can be used with `sim_setx()` output objects, a special plotting function, [setx_plot()], can be used to plot marginal predictions.
+#'
+#' @inheritParams sim_apply
+#' @param x a named list of values each predictor should take defining a reference grid of predictor values, e.g., `list(v1 = 1:4, v2 = c("A", "B"))`. Any omitted predictors are fixed at a "typical" value. See Details. When `x1` is specified, `x` should identify a single reference unit.
+#' @param x1 a named list of the value each predictor should take to compute the first difference from the predictor combination specified in `x`. `x1` can only identify a single unit. See Details.
+#'
+#' @return a `simbased_est` object, similar to the output of `sim_apply()`, with the following additional attributes:
+#' * `"setx"` - a data frame containing the values at which predictions are to be made
+#' * `"fd"` - whether or not the first difference is to be computed; set to `TRUE` if `x1` is specified and `FALSE` otherwise
+#'
+#' @details `x` should be a named list of predictor values that will be crossed to form a reference grid for the marginal predictions. Any predictors not set in `x` are assigned their "typical" value, which, for factor, character, logical, and binary variables is the mode, for numeric variables is the mean, and for ordered variables is the median. These values can be seen in the `"setx"` attribute of the output object. If `x` is empty, a prediction will be made at a point corresponding to the typical value of every predictor. Estimates are identified (in `summary()`, etc.) only by the variables that differ across predictions.
+#'
[…]

### 2022-08-05 R/simbased_est_methods.R

@@ -1,9 +1,11 @@
-#' @export
+#' @importFrom stats coef
+#' @exportS3Method coef simbased_est
 coef.simbased_est <- function(object, ...) {
   attr(object, "original")
 }
 
-#' @export
+#' @importFrom stats vcov
+#' @exportS3Method vcov simbased_est
 vcov.simbased_est <- function(object, ...) {
   class(object) <- setdiff(class(object), "simbased_est")
   cov(object)
@@ -69,4 +71,28 @@ transform.simbased_est <- function(`_data`, ...) {
   else {
     return(`_data`)
   }
+}
+
+#' @export
+names.simbased_est <- function(x) {
+  colnames(x)
+}
+
+#' @export
+`names<-.simbased_est` <- function(x, value) {
+  original_names <- names(x)
+  colnames(x) <- value
+  names(attr(x, "original")) <- value
+  for (i in names(attributes(x))) {
+    if (identical(names(attr(x, i)), original_names)) {
+      names(attr(x, i)) <- value
+    }
+    if (identical(rownames(attr(x, i)), original_names)) {
+      rownames(attr(x, i)) <- value
+    }
+    if (identical(colnames(attr(x, i)), original_names)) {
+      colnames(attr(x, i)) <- value
+    }
+  }
+  x
 }

### 2022-08-05 R/summary.simbased_est.R

@@ -2,8 +2,8 @@
 #'
 #' `summary()` tabulates the estimates and simulation-based confidence intervals and (optionally) p-values from a `simbased_est` object.
 #'
-#' @param object a `simbased_est` object; the output of a call to `sim_apply()`.
-#' @param alpha the $\alpha$ used to compute the confidence interval. Default is .05 for 95% confidence intervals.
+#' @param object a `simbased_est` object; the output of a call to [sim_apply()].
+#' @param alpha the \eqn{\alpha} used to compute the confidence interval. Default is .05 for 95% confidence intervals.
 #' @param normal `logical`; whether to compute p-values and confidence intervals using a normal approximation (`TRUE`) or the simulated sampling distribution (`FALSE`; default). See Details.
 #' @param null the values of the parameters under the null hypothesis for the p-value calculations. Should have length equal to the number of quantities estimated, or one, in which case it will be recycled. Set values to `NA` to omit p-values for those quantities. When all values are `NA`, the default, no p-values are produced.
 #' @param ... ignored.
@@ -12,7 +12,7 @@
 #' \item{coefficients}{a matrix containing the coefficient estimates, standard errors, test statistics, p-values, and confidence intervals. Not all columns will be present depending on the arguments supplied to `summary()`.}
 #'
 #'
-#' @details `summary()` uses the estimates computed from the original model as its estimates and uses the simulated parameters for inference only. When `normal = TRUE`, the standard deviation of the simulation estimates is used as the standard error, which is used in the t- or z- statistic and the confidence interval. The p-values and confidence intervals are valid only when the sampling distribution of the resulting statistic is normal (which can be assessed using `[sim_plot()]`. When `normal = FALSE`, the confidence interval is calculated using the `alpha/2` and `1 - alpha/2` quantiles of the simulation estimates, and the p-value is calculated as twice the proportion of simulation estimates less than or greater than `null`, whichever is smaller. Using `normal = FALSE` (the default) is recommended because the confidence intervals and p-values will be valid even if the sampling distribution is not normally distributed. The precision of the p-values and confidence intervals depends on the number of simulation requested (the value of `n` supplied to `[sim()]`).
[…]

### 2022-08-05 R/utils.R

@@ -108,3 +108,29 @@ try_chk <- function(expr) {
            error = function(e) chk::err(conditionMessage(e)),
            warning = function(w) chk::err(conditionMessage(w)))
 }
+
+#mode
+Mode <- function(v, na.rm = TRUE) {
+  if (anyNA(v)) {
+    if (na.rm) v <- v[!is.na(v)]
+    else {
+      #Return NA, keeping type of `v`
+      v <- v[1]
+      is.na(v) <- TRUE
+      return(v)
+    }
+  }
+
+  if (length(v) == 0) return(v)
+  if (is.factor(v)) {
+    if (nlevels(v) == 1) return(levels(v)[1])
+    mode <- levels(v)[which.max(tabulate(v, nbins = nlevels(v)))]
+    mode <- factor(mode, levels = levels(v))
+  }
+  else {
+    uv <- unique(v)
+    if (length(uv) == 1) return(uv)
+    mode <- uv[which.max(tabulate(match(v, uv)))]
+  }
+  mode
+}

### 2022-08-10 README.Rmd
Updates

@@
 <!-- badges: start -->
+[![CRAN status](https://www.r-pkg.org/badges/version/simbased)](https://CRAN.R-project.org/package=simbased)
 <!-- badges: end -->
 
-`simbased` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as marginal effects.
+`simbased` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
 
@@
 ```
+## Introduction
+
+Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters.
+The delta method involves multiple assumptions: 1) the regression coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance.
+When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate.
+Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference; however, it is computationally intensive since the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.
+
+Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3), and it is faster and more stable than bootstrapping because the model only needs to be fit once.
+Simulation-based inference involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution.
+Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals.
+Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory confidence intervals and p-values can be computed.
+
+The `simbased` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
+The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `sim_plot()`.
+These work together to create a simple workflow for simulation-based inference.
+
+* `sim()` simulates model parameters from a fitted model
+* `sim_apply()` applies an estimator to the simulated coefficients, or to the original object but with the new coefficients inserted
+* `summary()` produces confidence intervals and p-values for the resulting estimates
+* `sim_plot()` produces plots of the simulated sampling distribution of the resulting estimates
+
+There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; and `sim_setx()` computes predicted values at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`.
 
@@
 
-Below is an example of performing g-computation for the ATT after logistic regression to compute the marginal risk ratio and its confidence interval:
+Below is an example of performing g-computation for the ATT after logistic regression to compute the marginal log risk ratio and its confidence interval:
 
@@
 
+#Fit the model
 fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married + nodegree + re74 + re75),
@@
 
+#Simulate coefficients from a multivariate normal distribution
 set.seed(123)
@@
 
+#Apply a function that estimate the g-computation estimate for the ATT
+#to models with the estimated coefficients replaced by the simulated ones
 sim_est <- sim_apply(sim_coefs, function(fit) {
@@
   p0 <- mean(predict(fit, newdata = d, type = "response"))
-  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, RR = p1 / p0)
+  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, `log(RR)` = log(p1 / p0))
 }, verbose = FALSE)
 
-summary(sim_est, null = c(NA, NA, 1))
+sim_est
+
+#View the estimates, confidence intervals, and p-values
+summary(sim_est, null = c(NA, NA, 0))
+
+#Plot the resulting sampling distributions
 sim_plot(sim_est)
+```
+
+`simbased` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
+We can compute the log marginal risk ratio below:
+
+```{r}
+# Marginal risk ratio ATT, simulation-based
+sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
+                   contrast = "log(RR)", verbose = FALSE)
+
+sim_est
+
+summary(sim_est, null = c(NA, NA, 0))
 ```
@@
                              transform_pre = "lnratioavg") |>
-  summary(transform_avg = exp)
+  summary()
 ```
 
-The simulation-based confidence intervals are a bit wider, reflecting that the delta method may be a poor approximation.
+The plot of the simulated sampling distribution indicates that the sampling distribution for the log risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid.
 
-`simbased` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
-We can compute the marginal risk ratio below:
+If we want to compute the marginal risk ratio, we can do that using `transform()` on the already-produced output:
 
 ```{r}
-# Marginal risk ratio ATT, simulation-based
-sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
-                   contrast = "RR", verbose = FALSE)
-
-summary(sim_est, null = c(NA, NA, 1))
+#Transform estimates into new quantities of interest
+sim_est <- transform(sim_est, `RR` = exp(`log(RR)`))
+summary(sim_est, null = c(NA, NA, 0, 1))
 ```
@@
 
+#Plot of predicted values across age for each value of treat
 setx_plot(sim_est)

### 2022-08-10 R/checks.R

@@ -67,10 +67,10 @@ check_ests <- function(ests) {
 
 #Edits to stats::.checkMFClasses
 check_classes <- function(olddata, newdata) {
-  new <- vapply(newdata, .MFclass, character(1L))
-  old <- vapply(olddata, .MFclass, character(1L))
+  new <- vapply(newdata, stats::.MFclass, character(1L))
+  old <- vapply(olddata, stats::.MFclass, character(1L))
   new <- new[names(new) %in% names(old)]
-  if (length(new) == 0L) return(invisible())
+  if (length(new) == 0L) return(invisible(NULL))
   old <- old[names(new)]
   old[old == "ordered"] <- "factor"
   new[new == "ordered"] <- "factor"
@@ -84,5 +84,5 @@ check_classes <- function(olddata, newdata) {
     else chk::err(sprintf("variables %s were specified with different types from the original model fit",
                           word_list(names(old)[wrong], quotes = TRUE)))
   }
-  else invisible()
+  else invisible(NULL)
 }

### 2022-08-10 R/setx_plot.R

@@ -17,6 +17,7 @@
 #' @seealso [sim_plot()] for a another way to plot estimates; [summary.simbased_est()] for computing p-values and confidence intervals for the estimated quantities.
 #'
 #' @examples
+#' ## See help("sim_sext") for examples
 #'
 #' @export
 setx_plot <- function(x, var = NULL, ci = TRUE, alpha = .05, normal = FALSE) {
@@ -64,7 +65,7 @@ setx_plot <- function(x, var = NULL, ci = TRUE, alpha = .05, normal = FALSE) {
   else {
     chk::chk_string(var)
     if (!var %in% varying) {
-      chk::err("`var` must be the name of a predictor set to be varying. Allowable options include ", word_list(varying, quote = TRUE))
+      chk::err("`var` must be the name of a predictor set to be varying. Allowable options include ", word_list(varying, quotes = TRUE))
     }
   }
 
@@ -89,14 +90,14 @@ setx_sim_plot <- function(x, var, non_var_varying = NULL, ci = TRUE, alpha = .05
   original_est <- coef(x)
   est_names <- rownames(newdata)
 
-  est_long <- setNames(stack(as.data.frame(x[,est_names, drop = FALSE])),
+  est_long <- setNames(utils::stack(as.data.frame(x[,est_names, drop = FALSE])),
                        c("val", "est"))
   est_long <- merge(est_long,
                     newdata[c(var, non_var_varying)],
                     by.x = "est", by.y = 0)
   est_long[[var]] <- paste0(var, " = ", add_quotes(est_long[[var]], chk::vld_character_or_factor(est_long[[var]])))
 
-  original_est_long <- setNames(stack(original_est[est_names]),
+  original_est_long <- setNames(utils::stack(original_est[est_names]),
                                 c("val", "est"))
   original_est_long <- merge(original_est_long,
                              newdata[c(var, non_var_varying)],
@@ -146,7 +147,7 @@ setx_sim_plot <- function(x, var, non_var_varying = NULL, ci = TRUE, alpha = .05
       })), est_names)
     }
 
-    ci_long <- setNames(stack(ci), c("val", "est"))
+    ci_long <- setNames(utils::stack(ci), c("val", "est"))
     ci_long <- merge(ci_long,
                      newdata[c(var, non_var_varying)],
                      by.x = "est", by.y = 0)
[…]

### 2022-08-10 R/sim.R

@@ -20,7 +20,23 @@
 #' @seealso
 #' * [sim_apply()] for applying a function to each set of simulated coefficients.
 #'
-# @examples
+#' @examples
+#'
+#' data("lalonde", package = "MatchIt")
+#' fit <- lm(re78 ~ treat * (age + race + nodegree + re74), data = lalonde)
+#'
+#' # Simulate coefficients
+#' s <- sim(fit)
+#' s
+#'
+#' ## Could also use a robust covariance matrix, e.g.,
+#' # s <- sim(fit, vcov = sandwich::vcovHC)
+#'
+#' # Simulated coefficients assuming a normal distribution
+#' # for coefficients; default for `lm` objects is a t-
+#' # distribution
+#' s <- sim(fit, dist = "normal")
+#' s
 #'
 #' @export
 sim <- function(fit,
@@ -106,7 +122,7 @@ get_sampling_dist <- function(fit = NULL, dist = NULL) {
       df <- as.numeric(df)
       dist <- "t"
     }
-    else if (anyNA(pmatch(dist, "normal"))) {
+    else if (!anyNA(pmatch(dist, "normal"))) {
       dist <- "normal"
     }
     else {
@@ -119,7 +135,7 @@ get_sampling_dist <- function(fit = NULL, dist = NULL) {
   else {
     if (inherits(fit, "glm")) df <- NULL
     else {
-      df <- try(df.residual(fit), silent = TRUE)
+      df <- try(stats::df.residual(fit), silent = TRUE)
       if (inherits(df, "try-error")) df <- NULL
     }
 

### 2022-08-10 R/sim_ame.R

@@ -1,3 +1,64 @@
+#' Compute average marginal effects
+#'
+#' @description
+#' `sim_ame()` is a wrapper for [sim_apply()] that computes average marginal effects, the average effect of changing a single variable from one value to another (i.e., from one category to another for categorical variables or a tiny change for continuous variables).
+#'
+#' @inheritParams sim_apply
+#' @param var either the name of a variable for which marginal effects are to be computed or a named list of length one containing the values the variable should take. If a list is supplied or the named variables is categorical (factor, character, or having two values), categorical calculations will be triggered. Otherwise, continuous calculations will be triggered. See Details.
+#' @param subset optional; a vector used to subset the data used to compute the marginal effects. This will be evaluated within the original dataset used to fit the model using [subset()], so nonstandard evaluation is allowed.
+#' @param contrast a string containing the name of a contrast between the average marginal means when the variable named in `var` is categorical and takes on two values. Allowed options include `"diff"` for the difference in means (also `"rd"`), `"rr"` for the risk ratio (also `"irr"`), `"log(rr):` for the log risk ratio (also `"log(irr)"`), `"or"` for the odds ratio, `"log(or)"` for the log odds ratio, and `"nnt"` for the number needed to treat. These options are not case sensitive, but the parentheses must be included if present.
+#'
+#' @details
+#' `sim_ame()` operates differently depending on whether continuous or categorical calculations are trigger. To trigger categorical calculations, `var` should be a string naming a factor, character, or binary variable or a named list with specific values given (e.g., `var = list(x1 = c(1, 2 ,3))`). Otherwise, continuous calculations are triggered.
+#'
[…]

### 2022-08-10 R/sim_apply.R

@@ -5,7 +5,7 @@
 #' @param sim a `simbased_sim` object; the output of a call to [sim()].
 #' @param FUN a function to be applied to each set of simulated coefficients. See Details.
 #' @param verbose `logical`; whether to display a text progress bar indicating progress and estimated time remaining for the procedure. Default is `TRUE`.
-#' @param cl a cluster object created by [parallel::makeCluster()], or an integer to indicate number of child-processes (integer values are ignored on Windows) for parallel evaluations. See [pbapply::pblapply()] for details. If `NULL`, no parallelization will take place.
+#' @param cl a cluster object created by [parallel::makeCluster()], or an integer to indicate the number of child-processes (integer values are ignored on Windows) for parallel evaluations. See [pbapply::pblapply()] for details. If `NULL`, no parallelization will take place.
 #' @param ... optional arguments passed to `FUN`.
 #'
 #' @details `sim_apply()` applies a function to each set of simulated coefficients, similar to [apply()]. This function should produce an estimated quantity for which inference is to take place.
@@ -20,11 +20,46 @@
 #'
 #' @seealso
 #' * [sim()] for generating the simulated coefficients
-#' * [cbind.simbased_est()] and [transform.simbased_est()] for combining and transforming `simbased_est` objects
 #' * [summary.simbased_est()] for computing p-values and confidence intervals for the estimated quantities
 #' * [sim_plot()] for plotting estimated quantities and their simulated posterior sampling distribution.
 #'
-# @examples
+#' @examples
+#'
+#' data("lalonde", package = "MatchIt")
+#' fit <- lm(re78 ~ treat + age + race + nodegree + re74,
+#'           data = lalonde)
+#' coef(fit)
+#'
+#' set.seed(123)
+#' s <- sim(fit, n = 100)
+#'
+#' # Function to compare predicted values for two units
+#' # using `fit` argument
+#' sim_fun <- function(fit) {
+#'   pred1 <- unname(predict(fit, newdata = lalonde[1,]))
+#'   pred2 <- unname(predict(fit, newdata = lalonde[2,]))
+#'   c(pred1 = pred1, pred2 = pred2)
+#' }
+#'
+#' est <- sim_apply(s, sim_fun, verbose = FALSE)
+#'
[…]

### 2022-08-10 R/sim_apply_wrappers.R

@@ -1,21 +1,21 @@
-sim_comparisons <- function(sim, verbose = TRUE, cl = NULL, ...) {
-
-  args <- alist(...)
-  args[["vcov"]] <- FALSE
-
-  FUN <- function(fit) {
-    comp <- do.call(marginaleffects::comparisons, c(list(fit), args))
-    summ <- summary(comp)
-
-    estimate <- summ[["estimate"]]
-    contrast <- summ[[names(summ)[startsWith(names(summ), "contrast")][1]]]
-    by_vars <- setdiff(names(summ), c("estimate", names(summ)[startsWith(names(summ), "contrast")],
-                                      "type", "term"))
-
-    setNames(estimate, do.call("paste", c(lapply(by_vars, function(i) {
-      paste0(i, " = ", add_quotes(summ[[i]], chk::vld_character_or_factor(summ[[i]])))
-    }), list(contrast, sep = ", "))))
-  }
-# FUN(sim$fit)
-  sim_apply(sim, FUN = FUN, verbose = verbose, cl = cl)
-}
+# sim_comparisons <- function(sim, verbose = TRUE, cl = NULL, ...) {
+#
+#   args <- alist(...)
+#   args[["vcov"]] <- FALSE
+#
+#   FUN <- function(fit) {
+#     comp <- do.call(marginaleffects::comparisons, c(list(fit), args))
+#     summ <- summary(comp)
+#
+#     estimate <- summ[["estimate"]]
+#     contrast <- summ[[names(summ)[startsWith(names(summ), "contrast")][1]]]
+#     by_vars <- setdiff(names(summ), c("estimate", names(summ)[startsWith(names(summ), "contrast")],
+#                                       "type", "term"))
+#
+#     setNames(estimate, do.call("paste", c(lapply(by_vars, function(i) {
+#       paste0(i, " = ", add_quotes(summ[[i]], chk::vld_character_or_factor(summ[[i]])))
+#     }), list(contrast, sep = ", "))))
+#   }
+# # FUN(sim$fit)
+#   sim_apply(sim, FUN = FUN, verbose = verbose, cl = cl)
+# }

### 2022-08-10 R/sim_plot.R

@@ -4,7 +4,6 @@
 #'
 #' @inheritParams summary.simbased_est
 #' @param x a `simbased_est` object; the output of a call to `sim_apply()`.
-#' @param est a vector of the names or indices of the estimates to plot. If unspecified, all estimates will be plotted.
 #' @param ci `logical`; whether to display confidence interval limits for the estimates. Default is `TRUE`.
 #' @param normal `logical`; whether to compute confidence intervals using a normal approximation (`TRUE`) or the simulated sampling distribution (`FALSE`; default). See [summary.simbased_est()] for details.
 #'
@@ -50,9 +49,9 @@ sim_plot <- function(x, est, ci = TRUE, alpha = .05, normal = FALSE) {
 
   est_names <- colnames(x)[est]
 
-  est_long <- setNames(stack(as.data.frame(x[,est_names, drop = FALSE])),
+  est_long <- setNames(utils::stack(as.data.frame(x[,est_names, drop = FALSE])),
                        c("val", "est"))
-  original_est_long <- setNames(stack(original_est[est_names]),
+  original_est_long <- setNames(utils::stack(original_est[est_names]),
                                 c("val", "est"))
 
   p <- ggplot() +
@@ -81,7 +80,7 @@ sim_plot <- function(x, est, ci = TRUE, alpha = .05, normal = FALSE) {
       })), est_names)
     }
 
-    ci_long <- setNames(stack(ci), c("val", "est"))
+    ci_long <- setNames(utils::stack(ci), c("val", "est"))
     p <- p + geom_vline(data = ci_long, mapping = aes(xintercept = .data$val),
                         linetype = 2)
   }

### 2022-08-10 R/sim_setx.R

@@ -1,22 +1,81 @@
 #' Compute predictions and first differences at set values
 #'
-#' `sim_setx()` is a wrapper for [sim_apply()] that computes predicted values of the outcome at specified values of the predictors, sometimes called marginal predictions. One can also compute the difference between two marginal predictions (the "first difference"). Although any function that accepted `simbased_est` objects can be used with `sim_setx()` output objects, a special plotting function, [setx_plot()], can be used to plot marginal predictions.
+#' `sim_setx()` is a wrapper for [sim_apply()] that computes predicted values of
+#' the outcome at specified values of the predictors, sometimes called marginal
+#' predictions. One can also compute the difference between two marginal
+#' predictions (the "first difference"). Although any function that accepted
+#' `simbased_est` objects can be used with `sim_setx()` output objects, a
+#' special plotting function, [setx_plot()], can be used to plot marginal
+#' predictions.
 #'
 #' @inheritParams sim_apply
-#' @param x a named list of values each predictor should take defining a reference grid of predictor values, e.g., `list(v1 = 1:4, v2 = c("A", "B"))`. Any omitted predictors are fixed at a "typical" value. See Details. When `x1` is specified, `x` should identify a single reference unit.
-#' @param x1 a named list of the value each predictor should take to compute the first difference from the predictor combination specified in `x`. `x1` can only identify a single unit. See Details.
+#' @param x a named list of values each predictor should take defining a
+#'   reference grid of predictor values, e.g., `list(v1 = 1:4, v2 = c("A",
+#'   "B"))`. Any omitted predictors are fixed at a "typical" value. See Details.
+#'   When `x1` is specified, `x` should identify a single reference unit.
+#' @param x1 a named list of the value each predictor should take to compute the
+#'   first difference from the predictor combination specified in `x`. `x1` can
+#'   only identify a single unit. See Details.
 #'
-#' @return a `simbased_est` object, similar to the output of `sim_apply()`, with the following additional attributes:
-#' * `"setx"` - a data frame containing the values at which predictions are to be made
-#' * `"fd"` - whether or not the first difference is to be computed; set to `TRUE` if `x1` is specified and `FALSE` otherwise
+#' @return a `simbased_est` object, similar to the output of `sim_apply()`, with
+#'   the following additional attributes: * `"setx"` - a data frame containing
[…]

### 2022-08-10 R/simbased-package.R

@@ -1,0 +1,9 @@
+#' @keywords internal
+"_PACKAGE"
+
+## usethis namespace: start
+#' @import stats
+#' @import ggplot2
+## usethis namespace: end
+NULL
+

### 2022-08-10 R/simbased_est_methods.R

@@ -1,10 +1,8 @@
-#' @importFrom stats coef
 #' @exportS3Method coef simbased_est
 coef.simbased_est <- function(object, ...) {
   attr(object, "original")
 }
 
-#' @importFrom stats vcov
 #' @exportS3Method vcov simbased_est
 vcov.simbased_est <- function(object, ...) {
   class(object) <- setdiff(class(object), "simbased_est")
@@ -17,7 +15,7 @@ cbind.simbased_est <- function(..., deparse.level = 1) {
 
   for (i in seq_len(...length())) {
     if (!inherits(...elt(i), "simbased_est")) {
-      chk::err("all supplied objects must be `simbased_est` objects, the output of calls to `sim_apply()`")
+      chk::err("all supplied objects must be `simbased_est` objects, the output of calls to `sim_apply()` or its wrappers")
     }
   }
 
@@ -28,7 +26,7 @@ cbind.simbased_est <- function(..., deparse.level = 1) {
     chk::err("all supplied objects must be unmodified `simbased_est` objects")
   }
   if (!all_the_same(unlist(hashes)) || !all_the_same(unlist(lapply(obj, nrow)))) {
-    chk::err("all supplied objects must be calls of `sim_apply()` on the same `simbased_sim` object")
+    chk::err("all supplied objects must be calls of `sim_apply()` or its wrappers on the same `simbased_sim` object")
   }
 
   out <- do.call("cbind", lapply(obj, function(x) {
@@ -47,30 +45,45 @@ cbind.simbased_est <- function(..., deparse.level = 1) {
 transform.simbased_est <- function(`_data`, ...) {
   e <- eval(substitute(list(...)), as.data.frame(`_data`), parent.frame())
 
-  if (any(lengths(e) != nrow(`_data`)) || any(!vapply(e, is.numeric, logical(1L)))) {
-    chk::err("all transformations must produce numeric vectors with the same length as the number of rows in the original object")
+  n <- nrow(`_data`)
+  if (!all(vapply(e, function(e.) length(e.) == 0 || (length(e.) == n && is.numeric(e.)), logical(1L)))) {
+    chk::err("all transformations must be vector operations of the variables in the original `simbased_est` object")
   }
 
[…]

### 2022-08-10 R/summary.simbased_est.R

@@ -3,6 +3,7 @@
 #' `summary()` tabulates the estimates and simulation-based confidence intervals and (optionally) p-values from a `simbased_est` object.
 #'
 #' @param object a `simbased_est` object; the output of a call to [sim_apply()].
+#' @param est a vector of the names or indices of the estimates to plot. If unspecified, all estimates will be plotted.
 #' @param alpha the \eqn{\alpha} used to compute the confidence interval. Default is .05 for 95% confidence intervals.
 #' @param normal `logical`; whether to compute p-values and confidence intervals using a normal approximation (`TRUE`) or the simulated sampling distribution (`FALSE`; default). See Details.
 #' @param null the values of the parameters under the null hypothesis for the p-value calculations. Should have length equal to the number of quantities estimated, or one, in which case it will be recycled. Set values to `NA` to omit p-values for those quantities. When all values are `NA`, the default, no p-values are produced.
@@ -12,83 +13,139 @@
 #' \item{coefficients}{a matrix containing the coefficient estimates, standard errors, test statistics, p-values, and confidence intervals. Not all columns will be present depending on the arguments supplied to `summary()`.}
 #'
 #'
-#' @details `summary()` uses the estimates computed from the original model as its estimates and uses the simulated parameters for inference only. When `normal = TRUE`, the standard deviation of the simulation estimates is used as the standard error, which is used in the t- or z- statistic and the confidence interval. The p-values and confidence intervals are valid only when the sampling distribution of the resulting statistic is normal (which can be assessed using [sim_plot()]. When `normal = FALSE`, the confidence interval is calculated using the `alpha/2` and `1 - alpha/2` quantiles of the simulation estimates, and the p-value is calculated as twice the proportion of simulation estimates less than or greater than `null`, whichever is smaller. Using `normal = FALSE` (the default) is recommended because the confidence intervals and p-values will be valid even if the sampling distribution is not normally distributed. The precision of the p-values and confidence intervals depends on the number of simulation requested (the value of `n` supplied to [sim()]).
[…]

### 2022-08-10 R/utils.R

@@ -134,3 +134,16 @@ Mode <- function(v, na.rm = TRUE) {
   }
   mode
 }
+
+#Shortcut for predicting from models to avoid slow insight::get_predicted()
+#for simple models (GLMs)
+simbased_predict <- function(x, newdata = NULL) {
+  if (inherits(x, "lm") || inherits(x, "glm")) {
+    predict(x, newdata = newdata, type = "response")
+  }
+  else {
+    setNames(as.numeric(insight::get_predicted(x, data = newdata, predict = "expectation",
+                           verbose = FALSE)),
+             rownames(newdata))
+  }
+}

### 2022-08-10 tests/testthat.R

@@ -1,4 +1,4 @@
 library(testthat)
 library(simbased)
 
-test_check("simbased")
+# test_check("simbased")

### 2022-09-08 _dev/supported_models.Rmd
Roxygen updates

---
title: "Model Support"
author: "Noah Greifer"
date: "2022-08-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Supported models

* `stats::lm()`

For `mlm` models (multiple outcomes), coefficients are named `y1:x1` and `y2:x1` as they are in the covariance matrix when supplied through `coefs` argument of `FUN` in `sim_apply()`; when extracted from `fit`, they are in a matrix as usual.

* `stats::glm()`

* `MASS::glm.nb()`

* `survey::svyglm()`

* `estimatr::lm_robust()`

See `lm()` about multiple outcomes.

* `fixest::feols()`, `fixest::feglm()`, `fixest::femlm()`, etc.

Cannot accept `fixest.multi` models, i.e., resulting from multiple models being fit in the same `feols()` call. In IV, only second stage coefficients and covariance are extracted.

* `betareg::betareg()`

* `logistf` models (`logistf::logistf()`, `logistf::flic()`, `logistf::flac()`)

* `geepack::geeglm()`

* `rms::ols()`, `rms::lrm()`

* Multiply imputed data (fit list or `mids`)

Need to add tests and examples

## Models to add

* `survival` models (incl. `rms::cph()`)

* `ivreg` models

* `gam` models

* `estimatr::iv_robust()`

Only operates on second stage model. NOTE: bug in `estimatr` preventing full use.

### Way down the road

* Mixed effects models (`nlme`, `lme4`, `glmmTMB`)

* Multinomial regression (`nnet::multinom()`, `mlogit::mlogit()`, `mclogit::mblogit()`)

* Ordinal regression (`MASS::polr()`, `rms::olr()`, `geepack::ordgee()`)

* `brms::brms()`

Probably want an `as.sim()` method to use posterior as simulated values. May also want to trigger a Bayesian pipeline.

* `ordbetareg::ordbetareg()`

Returns a `brms` object.

## Adding new models

* Add `transform_coefs()` (probably okay unless `coef()` doesn't return a vector)
* Add `get_vcov()` (probably okay)
* Add `get_df()` (probably set to `Inf` unless model is a linear model fit with OLS)
* Add `get_coef_template()` (probably okay unless coefficients stored in unusual way)
* Add `untransform_coefs()` (probably okay unless coefficients stored in unusual way)
* Add `get_coef_location()` (probably `"coefficients"`)
* Add `simbased_predict()` (probably okay unless multivariate)
* Add test to `test-sim.R` and `test-sim_ame.R`

### 2022-09-08 README.Rmd
Updates
Readme updates

@@
 
-# simbased
+# `simbased`: Simulation-Based Inference for Regression Models
 
@@
 The `simbased` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
-The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `sim_plot()`.
+The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
 These work together to create a simple workflow for simulation-based inference.
@@
 * `summary()` produces confidence intervals and p-values for the resulting estimates
-* `sim_plot()` produces plots of the simulated sampling distribution of the resulting estimates
+* `plot()` produces plots of the simulated sampling distribution of the resulting estimates
 
@@
 #Plot the resulting sampling distributions
-sim_plot(sim_est)
+plot(sim_est)
 ```
@@
 #Plot of predicted values across age for each value of treat
-setx_plot(sim_est)
+plot(sim_est)
 ```

### 2022-09-08 tests/testthat/test-sim.R
fix

@@ -14,7 +14,7 @@ test_that("sim() works with coefs and vcov", {
   expect_equal(colnames(s$sim.coefs),
                c("(Intercept)", "treat", "age", "educ", "racehispan", "racewhite", "re74"))
   expect_equal(attr(s, "dist"), "normal")
-  expect_false(attr(s, "use.fit"))
+  expect_false(attr(s, "use_fit"))
 
   s <- sim(coefs = coef(fit), vcov = sandwich::vcovHC(fit),
            n = 5, dist = "t_100")
@@ -103,7 +103,7 @@ test_that("sim() works with lm()", {
 
   s <- sim(n = 5, coefs = coef(fit), vcov = vcov(fit))
   expect_good_simbased_sim(s)
-  expect_false(attr(s, "use.fit"))
+  expect_false(attr(s, "use_fit"))
 })
 
 test_that("sim() works with glm()", {
@@ -155,7 +155,7 @@ test_that("sim() works with glm()", {
 
   s <- sim(n = 5, coefs = coef(fit), vcov = vcov(fit))
   expect_good_simbased_sim(s)
-  expect_false(attr(s, "use.fit"))
+  expect_false(attr(s, "use_fit"))
 })
 
 test_that("sim() works with MASS::glm.nb()", {
@@ -207,7 +207,7 @@ test_that("sim() works with MASS::glm.nb()", {
 
   s <- sim(n = 5, coefs = coef(fit), vcov = vcov(fit))
   expect_good_simbased_sim(s)
-  expect_false(attr(s, "use.fit"))
+  expect_false(attr(s, "use_fit"))
 })
 
 test_that("sim() works with betareg::betareg()", {
@@ -261,7 +261,7 @@ test_that("sim() works with betareg::betareg()", {
 
   s <- sim(n = 5, coefs = coef(fit), vcov = vcov(fit))
   expect_good_simbased_sim(s)
-  expect_false(attr(s, "use.fit"))
+  expect_false(attr(s, "use_fit"))
 })
 
 test_that("sim() works with survey::svyglm()", {
@@ -313,7 +313,7 @@ test_that("sim() works with survey::svyglm()", {
 
   s <- sim(n = 5, coefs = coef(fit), vcov = vcov(fit))
   expect_good_simbased_sim(s)
-  expect_false(attr(s, "use.fit"))
+  expect_false(attr(s, "use_fit"))
 })
 
[…]

### 2022-12-14 R/_defunct-versions.R
Defunct versions of old functions

@@ -1,0 +1,237 @@
+# #Defunct functions that have been replaced by versions that rely on `marginaleffects`
+# get_coefs <- function(fit) {
+#
+#   b <- try(coef(fit), silent = TRUE)
+#
+#   if (!is_error(b)) {
+#     b <- try(transform_coefs(b), silent = TRUE)
+#   }
+#
+#   if (!check_valid_coef(b)) {
+#     if (insight::is_model_supported(fit)) {
+#       b <- insight::get_parameters(fit, summary = TRUE, component = "all")
+#       b <- try(transform_coefs(b, insight_used = TRUE), silent = TRUE)
+#     }
+#   }
+#
+#   if (!check_valid_coef(b)) {
+#     .err("`sim()` was unable to extract a valid set of coefficients from the model fit; please supply coefficients to the `coefs` argument and a covariance matrix to the `vcov` argument")
+#   }
+#
+#   return(b)
+# }
+#
+# get_vcov <- function(fit) {
+#   check <- TRUE
+#   if (!inherits(fit, "tobit") &&
+#       check_valid_vcov(v <- try(vcov(fit), silent = TRUE))) {
+#     check <- FALSE
+#     #v already extracted
+#   }
+#   else if (insight::is_model_supported(fit)) {
+#     v <- try(insight::get_varcov(fit, component = "all"), silent = TRUE)
+#   }
+#
+#   if (check && !check_valid_vcov(v)) {
+#     .err("`sim()` was unable to extract a valid covariance matrix from the model fit; please supply a covariance matrix to the `vcov` argument")
+#   }
+#
+#   return(v)
+# }
+#
+# make_apply_FUN <- function(FUN, coef_location = NULL, template = NULL) {
+#   if (is.null(coef_location) && isTRUE(attr(FUN, "use_fit"))) {
+#     if (isTRUE(attr(FUN, "use_coefs"))) {
+#       .err("the location of the coefficients in the model object cannot found, so `FUN` cannot have a `fit` argument")
+#     }
+#     else {
+#       .err("the location of the coefficients in the model object cannot found, so `FUN` must have a `coefs` argument")
+#     }
+#   }
+#
+#   if (isTRUE(attr(FUN, "use_coefs")) && isTRUE(attr(FUN, "use_fit"))) {
+#     apply_FUN <- function(fit, coefs, ...) {
+#       fit <- coef_assign(fit, coefs, coef_location, template)
+#       FUN(fit = fit, coefs = coefs, ...)
+#     }
+#   }
[…]

### 2022-12-14 README.Rmd
Updates

@@
 
-# `simbased`: Simulation-Based Inference for Regression Models
+# `{simbased}`: Simulation-Based Inference for Regression Models
 
@@
 
-`simbased` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
+`{simbased}` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
 
@@
 
-You can install the development version of `simbased` from [GitHub](https://github.com/) with:
+You can install the development version of `{simbased}` from [GitHub](https://github.com/) with:
 
@@
 
-The `simbased` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
-The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
+The `{simbased}` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
+The primary functions of `{simbased}` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
 These work together to create a simple workflow for simulation-based inference.
@@
 
-`simbased` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
+`{simbased}` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
 We can compute the log marginal risk ratio below:
@@
 
-We can also use `simbased` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
+We can also use `{simbased}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
 
@@
 
-`simbased` offers parallel processing for all estimation functions to speed up computation.
+`{simbased}` offers parallel processing for all estimation functions to speed up computation.
 

### 2022-12-14 R/sim_apply_wrappers.R

@@ -1,21 +1,0 @@
-# sim_comparisons <- function(sim, verbose = TRUE, cl = NULL, ...) {
-#
-#   args <- alist(...)
-#   args[["vcov"]] <- FALSE
-#
-#   FUN <- function(fit) {
-#     comp <- do.call(marginaleffects::comparisons, c(list(fit), args))
-#     summ <- summary(comp)
-#
-#     estimate <- summ[["estimate"]]
-#     contrast <- summ[[names(summ)[startsWith(names(summ), "contrast")][1]]]
-#     by_vars <- setdiff(names(summ), c("estimate", names(summ)[startsWith(names(summ), "contrast")],
-#                                       "type", "term"))
-#
-#     setNames(estimate, do.call("paste", c(lapply(by_vars, function(i) {
-#       paste0(i, " = ", add_quotes(summ[[i]], chk::vld_character_or_factor(summ[[i]])))
-#     }), list(contrast, sep = ", "))))
-#   }
-# # FUN(sim$fit)
-#   sim_apply(sim, FUN = FUN, verbose = verbose, cl = cl)
-# }

### 2022-12-14 R/summary.simbased_est.R

@@ -32,7 +32,7 @@
 #' s <- sim(fit, n = 100)
 #'
 #' # Compute average marginal means for `treat`
-#' est <- sim_ame(s, var = "treat")
+#' est <- sim_ame(s, var = "treat", verbose = FALSE)
 #' coef(est)
 #'
 #' # Compute average marginal effects on risk difference

### 2022-12-21 README.Rmd
changed package name to clarify and simmi to misim

--- 2022-09-08 README.Rmd
@@
 
-# `simbased`: Simulation-Based Inference for Regression Models
+# `{clarify}`: Simulation-Based Inference for Regression Models
 
 <!-- badges: start -->
-[![CRAN status](https://www.r-pkg.org/badges/version/simbased)](https://CRAN.R-project.org/package=simbased)
+[![CRAN status](https://www.r-pkg.org/badges/version/clarify)](https://CRAN.R-project.org/package=clarify)
 <!-- badges: end -->
 
-`simbased` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
+`{clarify}` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
 
@@
 
-You can install the development version of `simbased` from [GitHub](https://github.com/) with:
+You can install the development version of `{clarify}` from [GitHub](https://github.com/) with:
 
@@
 # install.packages("devtools")
-devtools::install_github("ngreifer/simbased")
+devtools::install_github("ngreifer/clarify")
 ```
@@
 
-The `simbased` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
-The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
+The `{clarify}` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
+The primary functions of `{clarify}` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
 These work together to create a simple workflow for simulation-based inference.
@@
 ```{r example, fig.width=7, fig.height=3}
-library(simbased)
+library(clarify)
 
@@
 
-`simbased` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
+`{clarify}` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
 We can compute the log marginal risk ratio below:
@@
 
-We can also use `simbased` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
+We can also use `{clarify}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
 
@@
 
-`simbased` offers parallel processing for all estimation functions to speed up computation.
+`{clarify}` offers parallel processing for all estimation functions to speed up computation.
 

### 2022-12-21 _dev/demo2.Rmd
changed package name to clarify and simmi to misim

---
title: "clarify demo"
author: "Noah Greifer"
date: "2022-10-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.width = 7,
                      fig.height = 3.5,
                      fig.align = "center",
                      message = FALSE)
```

This is a demo of `clarify`, a general-purpose package for simulation-based inference of post-estimation quantities from regression models.

We'll load in the `lalonde` dataset that comes with `MatchIt`.

```{r}
#Loading in lalonde dataset
data("lalonde", package = "MatchIt")

#Attaching `clarify`
library(clarify)
```

We can fit a regression model and estimate derived quantities, using simulation to approximate their sampling distribution without relying on delta-method approximations.

```{r}
#Fitting treatment effect model on binary outcome
fit <- glm(I(re78 > 0) ~ treat + age + educ + race + 
             married + nodegree + re74 + re75,
           data = lalonde, family = binomial)
```

## Simulate coefficients with `sim()`

The first step is simulate the model coefficients from a multivariate normal or t-distribution using `sim()`. Users can supply their own covariance matrix or a function for extracting them:

```{r}
set.seed(543)

#Simulate 1000 coefficients, use robust SE
s <- sim(fit, n = 1e3, vcov = sandwich::vcovHC)
s
```

## Computing arbitrary quantities using `sim_apply()`

`clarify` provides a general-purpose interface for estimating any derived quantity (`sim_apply()`) as well as two convenience functions for estimating commonly estimated quantities, namely `sim_ame()` for estimating average marginal effects and `sim_setx()` for estimating marginal predictions and first differences at representative values.

We'll use `sim_apply()` to manually estimate a derived quantity, the product of two coefficients:

```{r}
est_fun <- function(fit) {
  prod <- coef(fit)["racewhite"] * coef(fit)["racehispan"]
  return(c(`w * h` = unname(prod)))
}
e <- sim_apply(s, est_fun)
e
summary(e)
plot(e)
```

`summary()` has options to display a p-value by specifying the null value of a hypothesis test for the estimated quantity:

```{r}
summary(e, null = 1)
```

One can also set `normal = TRUE` to compute Wald-style confidence intervals and p-values using the standard deviation of the estimates. Below we compare this with delta-method estimates.

```{r}
summary(e, null = 1, normal = TRUE)

#Using delta method
marginaleffects::deltamethod(fit, FUN = est_fun, vcov = "HC3")
```

## Compute average marginal effects using `sim_ame()`

Next we'll use `sim_ame()` to estimate an average marginal effect. For binary and categorical variables, this involves computing the expected potential outcomes, and, optionally, computing an effect measure to contrast them. For continuous variables, this involves computing the average of the derivatives with respect to that variable.

```{r}
#Estimating ATE of treat
e <- sim_ame(s, var = "treat", contrast = "rd")
e
summary(e)
```

If we want a different effect measure, we can use `transform()` to compute a new quantity from the estimated quantities:

```{r}
#Computing risk ratio from expected POs
summary(e |> transform(`RR` = `E[Y(1)]` / `E[Y(0)]`))
```

Next we'll look at a continuous variable:

```{r}
#Computing AME of age
e <- sim_ame(s, var = "age")
e
summary(e)
```

## Computing average dose-response functions using `sim_adrf()`

We'll use `sim_adrf()` to estimate the average does-response function (ADRF) for `age`, which estimates the average marginal means at each level of `age`.

```{r}
e <- sim_adrf(s, var = "age")
e
plot(e)
```

We can also estimate the average marginal effect function, which is the derivative of the (ADRF):

```{r}
e <- sim_adrf(s, var = "age", contrast = "amef")
e
plot(e)
```

## Computing predictions at representative values using `sim_setx()`

Next we'll use `sim_setx()` to estimate marginal predictions at representative values of the predictors.

```{r}
#Predicted values at cross of treat levels and race levels
e <- sim_setx(s, x = list(treat = 0:1, race = c("black", "hispan", "white")),
              verbose = FALSE)
e
summary(e)
plot(e)
```

We can compute first differences using the `x1` argument, like in `Zelig`:

```{r}
#Difference between Black and white with college and typical values
#of other covariates
e <- sim_setx(s, x = list(race = "white", educ = 16),
              x1 = list(race = "black", educ = 16))
e
summary(e)
```

When looking at predictions across levels of a continuous variable, we get different kind of plot:

```{r}
#Predicted values at treat levels and wide range of re74 values
e <- sim_setx(s, x = list(treat = 0:1, re74 = seq(0, 100000, len = 101)))
e
plot(e)
```

Notice that the confidence intervals never exceed the bounds of the variable, which would not be the case for delta method-based intervals.

## Simulating coefficients for multiply imputed data using `simmi()`

`clarify` is compatible with models fit in multiply imputed data. The function `simmi()` simulates coefficients from each imputation and appends them (i.e., "mixes the draws"). Here we use a complicated example that involves propensity score matching using the `MatchThem` package.

```{r}
#Load dataset with missingness
data("lalonde_mis", package = "cobalt")

#Multiple imputation, 20 imputations
imp <- mice::mice(lalonde_mis, m = 20, print = FALSE)

#Matching within each imputed dataset
m.out <- MatchThem::matchthem(treat ~ age + educ + race + married +
                                nodegree + re74 + re75,
                              datasets = imp)

#Fitting outcome model with a few covariates
library(survey)
fits <- with(m.out, svyglm(I(re78 > 0) ~ treat * (married + re74 + re75),
                           family = quasibinomial))

#Simulating coefficients from each imputation
s <- simmi(fits, n = 100)
s
```

We can estimate the ATT on the risk difference scale using `sim_ame()`, which is compatible with `simmi()`:

```{r}
#Estimating ATT of treat across imputations
e <- sim_ame(s, "treat", subset = treat == 1, contrast = "rd",
             verbose = TRUE, cl = 4)
e
summary(e)
plot(e)
```

Same as above but using `Amelia`.

```{r}
#Load dataset with missingness
data("lalonde_mis", package = "cobalt")

#Multiple imputation, 20 imputations
imp <- Amelia::amelia(lalonde_mis, m = 20, noms = c("race"),
                      ords = c("married", "nodegree"))

#Fitting outcome model with a few covariates
fits <- lapply(imp$imputations, function(d) {
  glm(I(re78 > 0) ~ treat + age + educ + race + 
             married + nodegree + re74 + re75,
           data = d, family = binomial)
})

#Simulating coefficients from each imputation
s <- simmi(fits, n = 100)
s
```

We can estimate the ATT on the risk difference scale using `sim_ame()`, which is compatible with `simmi()`:

```{r}
#Estimating ATT of treat across imputations
e <- sim_ame(s, "treat", subset = treat == 1, contrast = "rd",
             verbose = TRUE, cl = 4)
e
summary(e)
plot(e)
```
## Notes

### Models supported and tested:

* `stats::lm()`
* `stats::glm()`
* `MASS::glm.nb()`
* `survey::svyglm()`
* `estimatr::lm_robust()`
* `fixest::feols()`, `fixest::feglm()`, `fixest::femlm()`, etc.
* `betareg::betareg()`
* `logistf` models (`logistf::logistf()`, `logistf::flic()`, `logistf::flac()`)
* `geepack::geeglm()`
* `rms::ols()`, `rms::lrm()`
* `robustbase::lmrob()`, `robustbase::glmrob()`
* `robust::lmRob()`, `robust::glmRob()`
* `AER::tobit()`

### Models in progress:

* Survival models (`survival::coxph()`, `survival::survreg()`, `rms::cph()`)
* GAM models (`mgcv::gam()`)
* `ivreg` models
* Quantile regression (`quantreg::rq()`)

### Future models:

* Bayesian models (`brms::brm()`)
* Multinomial regression (`nnet::multinom()`, `mlogit::mlogit()`, `mclogit::mblogit()`)
* Ordinal regression (`MASS::polr()`, `rms::olr()`, `geepack::ordgee()`)
* SEM (`lavaan`)
* Mixed models (`lme4::lmer()`, `lme4::glmer()`, `nlme::lme()`, `glmmTMB::glmmTMB()`)

### Comparison to `simluate` package:

* `simulate` only computes predictions at representative values; `clarify` is a general-purpose tools for simulation-based inference, providing shortcuts for predictions at representative values and average marginal effects.
* `simulate` only provides support for `glm`, `lm`, and `betareg` models; `clarify` provides support for these and many other related models, including unit tests for each class.
* `simulate` uses the standard variance of the coefficients; `clarify` allows custom variances.
* `simulate` use sequential computation; `clarify` supports parallel computation.

### 2022-12-21 _dev/supported_models.Rmd
changed package name to clarify and simmi to misim

@@
 
+* `robustbase::lmrob()`, `robustbase::glmrob()`
+
+* `robust::lmRob()`, `robust::glmRob()`
+
+* `AER::tobit()`
+
 * Multiply imputed data (fit list or `mids`)
 
-Need to add tests and examples
+Need to add examples
+
+* `ivreg` models
 
@@
 * `survival` models (incl. `rms::cph()`)
-
-* `ivreg` models
 
@@
 Only operates on second stage model. NOTE: bug in `estimatr` preventing full use.
+
+* Quantile regression (`quantreg::rq()`)
 
@@
 
+* SEM (`lavaan`)
+
 ## Adding new models
@@
 * Add `get_df()` (probably set to `Inf` unless model is a linear model fit with OLS)
+* Add `get_coef_location()` (probably `"coefficients"`)
 * Add `get_coef_template()` (probably okay unless coefficients stored in unusual way)
 * Add `untransform_coefs()` (probably okay unless coefficients stored in unusual way)
-* Add `get_coef_location()` (probably `"coefficients"`)
-* Add `simbased_predict()` (probably okay unless multivariate)
+* Add `simbased_predict()`
 * Add test to `test-sim.R` and `test-sim_ame.R`

### 2022-12-21 R/checks.R

@@ -268,7 +268,7 @@ check_sim_apply_wrapper_ready <- function(sim) {
     .err(sprintf("`%s()` can only be used when a model fit was supplied to the original call to `sim()`",
                  fun))
   }
-  if (inherits(sim, "simbased_simmi")) {
+  if (inherits(sim, "simbased_misim")) {
     if (any(!vapply(sim$fit, insight::is_regression_model, logical(1L)))) {
       .err(sprintf("`%s()` can only be used with regression models",
                    fun))

### 2022-12-21 R/misim.R

@@ -1,6 +1,6 @@
 #' @title Simulate model coefficients after multiple imputation
 #'
-#' @description `simmi()` simulates model parameters from multivariate normal or t distributions after multiple imputation that are then used by [sim_apply()] to calculate quantities of interest.
+#' @description `misim()` simulates model parameters from multivariate normal or t distributions after multiple imputation that are then used by [sim_apply()] to calculate quantities of interest.
 #'
 #' @param fitlist a list of model fits, one for each imputed dataset, or a `mira` object (the output of a call to `with()` applied to a `mids` object in `mice`).
 #' @param n the number of simulations to run for each imputed dataset; default is 1000. More is always better but resulting calculations will take longer.
@@ -9,7 +9,7 @@
 #' @param dist a character vector containing the name of the multivariate distribution(s) to use to draw simulated coefficients. Should be one of `"normal"` (multivariate normal distribution) or `"t_{#}"` (multivariate t distribution), where `{#}` corresponds to the desired degrees of freedom (e.g., `"t_100"`). If `NULL`, the right distributions to use will be determined based on heuristics; see [sim()] for details.
 #'
 #' @return
-#' A `simbased_simmi` object, which inherits from `simbased_sim` and has the following components:
+#' A `simbased_misim` object, which inherits from `simbased_sim` and has the following components:
 #'  \item{sim.coefs}{a matrix containing the simulated coefficients with a column for each coefficient and a row for each simulation for each imputation}
 #'  \item{coefs}{a matrix containing the original coefficients extracted from `fitlist` or supplied to `coefs`, with a row per imputation.}
 #'  \item{fit}{the list of model fits supplied to `fitlist`}
@@ -17,7 +17,7 @@
 #' The `"dist"` attribute contains `"normal"` if the coefficients were sampled from a multivariate normal distribution and `"t({df})"` if sampled from a multivariate t distribution. The `"simbased_hash"` attribute contains a unique hash generated by [rlang::hash()].
 #'
 #' @details
-#' `simmi()` essentially combines multiple `sim()` calls applied to a list of model fits, each fit in an imputed dataset, into a single combined pool of simulated coefficients. When simulation-based inference is to be used with multiply imputed data, many imputations are required; see Zhou and Reiter (2010).
[…]

### 2022-12-21 R/sim.R

@@ -21,7 +21,7 @@
 #' When a multivariate normal is used, it is sampled from with means equal to the estimated coefficients and the parameter covariance matrix as the covariance matrix using [mvnfast::rmvn()]. When a multivariate t distribution is used, it is sampled from with means equal to the estimated coefficients and scaling matrix equal to `cov*(df - 2)/df`, where `cov` is the parameter covariance matrix and `df` is the residual degrees of freedom for the model, using [mvnfast::rmvt()].
 #'
 #' @seealso
-#' * [simmi()] for simulating model coefficients after multiple imputation
+#' * [misim()] for simulating model coefficients after multiple imputation
 #' * [sim_apply()] for applying a function to each set of simulated coefficients
 #' * [sim_ame()] for computing average marginal effects in each simulation draw
 #' * [sim_setx()] for computing marginal predictions and first differences at typical values in each simulation draw

### 2022-12-21 R/sim_adrf.R

@@ -73,7 +73,7 @@ sim_adrf <- function(sim,
   check_sim_apply_wrapper_ready(sim)
 
   chk::chk_flag(verbose)
-  is_simmi <- inherits(sim, "simbased_simmi")
+  is_misim <- inherits(sim, "simbased_misim")
 
   if (missing(var)) {
     .err("`var` must be supplied, identifying the focal variable")
@@ -86,7 +86,7 @@ sim_adrf <- function(sim,
   contrast <- tolower(contrast)
   contrast <- match_arg(contrast, c("adrf", "amef"))
 
-  if (is_simmi) {
+  if (is_misim) {
     dat <- do.call("rbind", lapply(sim$fit, insight::get_predictors))
   }
   else {
@@ -108,10 +108,10 @@ sim_adrf <- function(sim,
 
   index.sub <- substitute(subset)
   sim$fit <- attach_pred_data_to_fit(sim$fit, index.sub = index.sub,
-                                     is_fitlist = is_simmi)
+                                     is_fitlist = is_misim)
 
   #Test to make sure compatible
-  if (is_simmi) {
+  if (is_misim) {
     test_dat <- get_pred_data_from_fit(sim$fit[[1]])
     test_predict <- simbased_predict(sim$fit[[1]], newdata = test_dat, group = NULL, type = type)
   }

### 2022-12-21 R/sim_ame.R

@@ -90,7 +90,7 @@ sim_ame <- function(sim,
   check_sim_apply_wrapper_ready(sim)
 
   chk::chk_flag(verbose)
-  is_simmi <- inherits(sim, "simbased_simmi")
+  is_misim <- inherits(sim, "simbased_misim")
 
   vals <- NULL
 
@@ -105,7 +105,7 @@ sim_ame <- function(sim,
     .err("`var` must be the name of the desired focal variable or a named list of length 1 with its values")
   }
 
-  if (is_simmi) {
+  if (is_misim) {
     dat <- do.call("rbind", lapply(sim$fit, insight::get_predictors))
   }
   else {
@@ -134,10 +134,10 @@ sim_ame <- function(sim,
 
   index.sub <- substitute(subset)
   sim$fit <- attach_pred_data_to_fit(sim$fit, index.sub = index.sub,
-                                     is_fitlist = is_simmi)
+                                     is_fitlist = is_misim)
 
   #Test to make sure compatible
-  if (is_simmi) {
+  if (is_misim) {
     test_dat <- get_pred_data_from_fit(sim$fit[[1]])
     test_predict <- simbased_predict(sim$fit[[1]], newdata = test_dat, group = NULL, type = type)
   }

### 2022-12-21 R/sim_apply.R

@@ -6,7 +6,7 @@
 #'   quantities of interest. Capabilities are available for parallelization.
 #'
 #' @param sim a `simbased_sim` object; the output of a call to [sim()] or
-#'   [simmi()].
+#'   [misim()].
 #' @param FUN a function to be applied to each set of simulated coefficients.
 #'   See Details.
 #' @param verbose `logical`; whether to display a text progress bar indicating
@@ -49,7 +49,7 @@
 #'
 #'   ## `sim_apply()` with multiply imputed data
 #'
-#'   When using [simmi()] and `sim_apply()` with multiply imputed data, the
+#'   When using [misim()] and `sim_apply()` with multiply imputed data, the
 #'   coefficients are supplied to the model fit corresponding to the imputation
 #'   identifier associated with each set of coefficients, which means if `FUN`
 #'   uses a dataset extracted from a model, it will do so from the model fit in
@@ -135,7 +135,7 @@ sim_apply <- function(sim,
     }
 
     ests <- sim$sim.coefs
-    if (inherits(sim, "simbased_simmi")) {
+    if (inherits(sim, "simbased_misim")) {
       attr(ests, "original") <- colMeans(sim$coefs)
     }
     else {
@@ -152,7 +152,7 @@ sim_apply <- function(sim,
   opb <- pbapply::pboptions(type = if (verbose) "timer" else "none")
   on.exit(pbapply::pboptions(opb))
 
-  if (inherits(sim, "simbased_simmi")) {
+  if (inherits(sim, "simbased_misim")) {
     nimp <- nrow(sim$coefs)
 
     apply_FUN <- make_apply_FUN_mi(FUN)

### 2022-12-21 R/sim_setx.R

@@ -91,21 +91,21 @@ sim_setx <- function(sim,
   check_sim_apply_wrapper_ready(sim)
 
   chk::chk_flag(verbose)
-  is_simmi <- inherits(sim, "simbased_simmi")
+  is_misim <- inherits(sim, "simbased_misim")
 
-  if (is_simmi) {
+  if (is_misim) {
     dat <- do.call("rbind", lapply(sim$fit, insight::get_predictors))
   }
   else {
     dat <- insight::get_predictors(sim$fit)
   }
 
-  sim$fit <- attach_pred_data_to_fit(sim$fit, is_fitlist = is_simmi)
+  sim$fit <- attach_pred_data_to_fit(sim$fit, is_fitlist = is_misim)
 
   x <- process_x(x, dat, "x")
 
   #Test to make sure compatible
-  if (is_simmi) {
+  if (is_misim) {
     test_dat <- get_pred_data_from_fit(sim$fit[[1]])[1,, drop = FALSE]
     test_predict <- simbased_predict(sim$fit[[1]], newdata = test_dat, group = NULL, type = type)
   }

### 2022-12-21 R/simbased_est_methods.R

@@ -124,7 +124,7 @@ Ops.simbased_est <- function(e1, e2 = NULL) {
     }
 
     if (!identical(attr(e1, "hash"), attr(e2, "hash"))) {
-      .err(sprintf("`%s` can only be used on `simbased_est` objects originating from calls applied to the same `simbased-sim` object",
+      .err(sprintf("`%s` can only be used on `simbased_est` objects originating from calls applied to the same `clarify-sim` object",
                    .Generic))
     }
 

### 2022-12-21 _dev/demo.R

@@ -1,5 +1,5 @@
 data("lalonde", package = "MatchIt")
-library(simbased)
+library(clarify)
 
 lalonde$re78_0 <- as.numeric(lalonde$re78 == 0)
 

### 2022-12-21 tests/testthat.R

@@ -7,6 +7,6 @@
 # * https://testthat.r-lib.org/reference/test_package.html#special-files
 
 library(testthat)
-library(simbased)
+library(clarify)
 
-test_check("simbased")
+test_check("clarify")

### 2022-12-21 tests/testthat/helper.R

@@ -38,8 +38,8 @@ expect_good_simbased_est <- function(e) {
   expect_false(any(apply(e, 2, all_the_same)))
 }
 
-expect_good_simbased_simmi <- function(s) {
-  expect_s3_class(s, "simbased_simmi")
+expect_good_simbased_misim <- function(s) {
+  expect_s3_class(s, "simbased_misim")
   expect_s3_class(s, "simbased_sim")
   expect_true(all(c("sim.coefs", "coefs", "imp") %in% names(s)))
 

### 2022-12-21 tests/testthat/test-sim.R

@@ -218,7 +218,7 @@ test_that("sim() works with betareg::betareg()", {
                           data = mdata, weights = weights)
 
   if (length(marginaleffects::get_coef(fit)) != 10L) {
-    skip("disagreement between `marginaleffects` and `simbased` treatment of `betareg` obejcts")
+    skip("disagreement between `marginaleffects` and `clarify` treatment of `betareg` obejcts")
   }
 
   s <- sim(fit, n = 5)

### 2022-12-21 tests/testthat/test-simmi.R

@@ -1,185 +1,185 @@
-test_that("simmi() works with lists of regressions", {
+test_that("misim() works with lists of regressions", {
   m <- readRDS(test_path("fixtures", "model_list.rds"))
 
-  s <- simmi(m, n = 5)
+  s <- misim(m, n = 5)
 
-  expect_good_simbased_simmi(s)
+  expect_good_simbased_misim(s)
 
   expect_equal(dim(s$sim.coefs), c(5L * length(s$fit), 7L))
   expect_equal(colnames(s$sim.coefs),
                c("(Intercept)", "treat", "age", "educ", "racehispan", "racewhite", "re74"))
   expect_equal(attr(s, "dist"), "normal")
 
-  s <- simmi(m, n = 5, dist = "t(100)")
-  expect_good_simbased_simmi(s)
+  s <- misim(m, n = 5, dist = "t(100)")
+  expect_good_simbased_misim(s)
   expect_equal(attr(s, "dist"), "t(100)")
 
-  expect_error(simmi(m, n = 5, dist = "t"))
+  expect_error(misim(m, n = 5, dist = "t"))
 
   set.seed(987)
-  s1 <- simmi(m, n = 5)
-  expect_good_simbased_simmi(s1)
+  s1 <- misim(m, n = 5)
+  expect_good_simbased_misim(s1)
   set.seed(987)
-  s2 <- simmi(m, n = 5)
-  expect_good_simbased_simmi(s2)
+  s2 <- misim(m, n = 5)
+  expect_good_simbased_misim(s2)
 
   expect_identical(s1$sim.coefs, s2$sim.coefs)
 
   #Different seed
   set.seed(123)
-  s3 <- simmi(m, n = 5)
-  expect_good_simbased_simmi(s3)
+  s3 <- misim(m, n = 5)
+  expect_good_simbased_misim(s3)
   expect_false(identical(s1$sim.coefs, s3$sim.coefs))
 
   #Using custom variances
-  expect_good_simbased_simmi(simmi(m, n = 5, vcov = sandwich::vcovHC))
-  expect_good_simbased_simmi(simmi(m, n = 5, vcov = sandwich::vcovHC(m[[1]])))
-  expect_good_simbased_simmi(simmi(m, n = 5, vcov = lapply(1:10, function(i) sandwich::vcovHC)))
[…]

### 2022-12-21 R/checks.R
Renamed from simbased to clarify

@@ -262,13 +262,13 @@ check_classes <- function(olddata, newdata) {
 check_sim_apply_wrapper_ready <- function(sim) {
   fun <- deparse1(pkg_caller_call()[[1]])
 
-  chk::chk_is(sim, "simbased_sim")
+  chk::chk_is(sim, "clarify_sim")
 
   if (!isTRUE(attr(sim, "use_fit"))) {
     .err(sprintf("`%s()` can only be used when a model fit was supplied to the original call to `sim()`",
                  fun))
   }
-  if (inherits(sim, "simbased_misim")) {
+  if (inherits(sim, "clarify_misim")) {
     if (any(!vapply(sim$fit, insight::is_regression_model, logical(1L)))) {
       .err(sprintf("`%s()` can only be used with regression models",
                    fun))

### 2022-12-21 R/misim.R

@@ -9,12 +9,12 @@
 #' @param dist a character vector containing the name of the multivariate distribution(s) to use to draw simulated coefficients. Should be one of `"normal"` (multivariate normal distribution) or `"t_{#}"` (multivariate t distribution), where `{#}` corresponds to the desired degrees of freedom (e.g., `"t_100"`). If `NULL`, the right distributions to use will be determined based on heuristics; see [sim()] for details.
 #'
 #' @return
-#' A `simbased_misim` object, which inherits from `simbased_sim` and has the following components:
+#' A `clarify_misim` object, which inherits from `clarify_sim` and has the following components:
 #'  \item{sim.coefs}{a matrix containing the simulated coefficients with a column for each coefficient and a row for each simulation for each imputation}
 #'  \item{coefs}{a matrix containing the original coefficients extracted from `fitlist` or supplied to `coefs`, with a row per imputation.}
 #'  \item{fit}{the list of model fits supplied to `fitlist`}
 #'  \item{imp}{a identifier of which imputed dataset each set of simulated coefficients corresponds to.}
-#' The `"dist"` attribute contains `"normal"` if the coefficients were sampled from a multivariate normal distribution and `"t({df})"` if sampled from a multivariate t distribution. The `"simbased_hash"` attribute contains a unique hash generated by [rlang::hash()].
+#' The `"dist"` attribute contains `"normal"` if the coefficients were sampled from a multivariate normal distribution and `"t({df})"` if sampled from a multivariate t distribution. The `"clarify_hash"` attribute contains a unique hash generated by [rlang::hash()].
 #'
 #' @details
 #' `misim()` essentially combines multiple `sim()` calls applied to a list of model fits, each fit in an imputed dataset, into a single combined pool of simulated coefficients. When simulation-based inference is to be used with multiply imputed data, many imputations are required; see Zhou and Reiter (2010).
@@ -141,15 +141,15 @@ misim <- function(fitlist,
   attr(out, "dist") <- dists
   attr(out, "use_fit") <- !is.null(fitlist)
   attr(out, "sim_hash") <- rlang::hash(out$sim.coefs)
-  class(out) <- c("simbased_misim", "simbased_sim")
+  class(out) <- c("clarify_misim", "clarify_sim")
 
   out
 }
 
 #' @export
-print.simbased_misim <- function(x, ...) {
[…]

### 2022-12-21 R/plot.simbased_adrf.R

@@ -1,11 +1,11 @@
 #' Plot marginal predictions from `sim_adrf()`
 #'
-#' `plot.simbased_adrf()` plots the output of [sim_adrf()]. For the average dose-response function (ADRF, requested with `contrast = "adrf"` in `sim_adrf()`), this is a plot of the average marginal mean of the outcome against the requested values of the focal predictor; for the average marginal effects function (AMEF, requested with `contrast = "amef"` in `sim_adrf()`), this is a plot of the instantaneous average marginal effect of the focal predictor on the outcome against the requested values of the focal predictor.
+#' `plot.clarify_adrf()` plots the output of [sim_adrf()]. For the average dose-response function (ADRF, requested with `contrast = "adrf"` in `sim_adrf()`), this is a plot of the average marginal mean of the outcome against the requested values of the focal predictor; for the average marginal effects function (AMEF, requested with `contrast = "amef"` in `sim_adrf()`), this is a plot of the instantaneous average marginal effect of the focal predictor on the outcome against the requested values of the focal predictor.
 #'
-#' @inheritParams plot.simbased_est
-#' @param x a `simbased_adrf` object resulting from a call to [sim_adrf()].
+#' @inheritParams plot.clarify_est
+#' @param x a `clarify_adrf` object resulting from a call to [sim_adrf()].
 #' @param ci `logical`; whether to display confidence bands for the estimates. Default is `TRUE`.
-#' @param method the method used to compute confidence bands. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See [summary.simbased_est()] for details. Abbreviations allowed.
+#' @param method the method used to compute confidence bands. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See [summary.clarify_est()] for details. Abbreviations allowed.
 #' @param baseline `logical`; whether to include a horizontal line at `y = 0` on the plot. Default is `FALSE` for the ADRF (since 0 might not be in the range of the outcome) and `TRUE` for the AMEF.
 #' @param color the color of the line and confidence band in the plot.
 #'
@@ -13,13 +13,13 @@
 #'
 #' @details These plots are produced using [ggplot2::geom_line()] and [ggplot2::geom_ribbon()]. The confidence bands should be interpreted pointwise (i.e., they do not account for simultaneous inference).
 #'
[…]

### 2022-12-21 R/plot.simbased_est.R

@@ -1,6 +1,6 @@
-#' @exportS3Method plot simbased_est
-#' @rdname summary.simbased_est
-plot.simbased_est <- function(x, parm, ci = TRUE, level = .95, method = "quantile", ...) {
+#' @exportS3Method plot clarify_est
+#' @rdname summary.clarify_est
+plot.clarify_est <- function(x, parm, ci = TRUE, level = .95, method = "quantile", ...) {
 
   original_est <- coef(x)
   est_names <- names(x)

### 2022-12-21 R/plot.simbased_setx.R

@@ -1,28 +1,28 @@
 #' Plot marginal predictions from `sim_setx()`
 #'
-#' `plot.simbased_sext()` plots the output of [sim_setx()], providing graphics similar to those of [plot.simbased_est()] but with features specifically for plot marginal predictions. For continues predictors, this is a plot of the marginal predictions and their confidence bands across levels of the predictor. Otherwise, this is is a plot of simulated sampling distribution of the marginal predictions.
+#' `plot.clarify_sext()` plots the output of [sim_setx()], providing graphics similar to those of [plot.clarify_est()] but with features specifically for plot marginal predictions. For continues predictors, this is a plot of the marginal predictions and their confidence bands across levels of the predictor. Otherwise, this is is a plot of simulated sampling distribution of the marginal predictions.
 #'
-#' @inheritParams plot.simbased_est
-#' @param x a `simbased_est` object resulting from a call to [sim_setx()].
+#' @inheritParams plot.clarify_est
+#' @param x a `clarify_est` object resulting from a call to [sim_setx()].
 #' @param var the name of the focal varying predictor, i.e., the variable to be on the x-axis of the plot. All other variables with varying set values will be used to color the resulting plot. See Details. Ignored if no predictors vary or if only one predictor varies in the reference grid or if `x1` was specified in `sim_setx()`. If not set, will use the predictor with the greatest number of unique values specified in the reference grid.
 #' @param ci `logical`; whether to display confidence intervals or bands for the estimates. Default is `TRUE`.
-#' @param method the method used to compute confidence intervals or bands. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See [summary.simbased_est()] for details. Abbreviations allowed.
+#' @param method the method used to compute confidence intervals or bands. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See [summary.clarify_est()] for details. Abbreviations allowed.
 #'
 #' @return A `ggplot` object.
 #'
[…]

### 2022-12-21 R/sim.R

@@ -9,12 +9,12 @@
 #' @param dist a string containing the name of the multivariate distribution to use to draw simulated coefficients. Should be one of `"normal"` (multivariate normal distribution) or `"t({#})"` (multivariate t distribution), where `{#}` corresponds to the desired degrees of freedom (e.g., `"t(100)"`). If `NULL`, the right distribution to use will be determined based on heuristics; see Details.
 #'
 #' @return
-#' A `simbased_sim` object, which has the following components:
+#' A `clarify_sim` object, which has the following components:
 #'  \item{sim.coefs}{a matrix containing the simulated coefficients with a column for each coefficient and a row for each simulation}
 #'  \item{coefs}{the original coefficients extracted from `fit` or supplied to `coefs`.}
 #'  \item{vcov}{the covariance matrix of the coefficients extracted from `fit` or supplied to `vcov`}
 #'  \item{fit}{the original model fit supplied to `fit`}
-#' The `"dist"` attribute contains `"normal"` if the coefficients were sampled from a multivariate normal distribution and `"t(df)"` if sampled from a multivariate t distribution. The `"simbased_hash"` attribute contains a unique hash generated by [rlang::hash()].
+#' The `"dist"` attribute contains `"normal"` if the coefficients were sampled from a multivariate normal distribution and `"t(df)"` if sampled from a multivariate t distribution. The `"clarify_hash"` attribute contains a unique hash generated by [rlang::hash()].
 #'
 #' @details When `dist` is `NULL`, `sim()` samples from a multivariate normal or t distribution depending on whether `df.residual(fit)` is `NULL` or not. If `NULL` or `fit` is unspecified, a multivariate normal distribution is used. Otherwise (primarily for linear models fit with `lm()`), a multivariate t distribution is used, with `df.residual(fit)` used as the degrees of freedom.
 #'
@@ -95,14 +95,14 @@ sim <- function(fit,
   attr(out, "dist") <- attr(sampler, "dist")
   attr(out, "use_fit") <- !is.null(fit)
   attr(out, "sim_hash") <- rlang::hash(out$sim.coefs)
-  class(out) <- "simbased_sim"
+  class(out) <- "clarify_sim"
 
   out
 }
 
 #' @export
-print.simbased_sim <- function(x, ...) {
-  cat("A `simbased_sim` object\n")
+print.clarify_sim <- function(x, ...) {
[…]

### 2022-12-21 R/sim_adrf.R

@@ -14,21 +14,21 @@
 #' @param eps when `contrast = "amef"`, the value by which to shift the value of `var` to approximate the derivative. See Details.
 #'
 #' @details
-#' The ADRF is composed of average marginal means across levels of the focal predictor. For each level of the focal predictor, predicted values of the outcome are computed after setting the value of the predictor to that level, and those values of the outcome are averaged across all units in the sample to arrive at an average marginal mean. Thus, the ADRF represent the relationship between the "dose" (i.e., the level of the focal predictor) and the average "response" (i.e., the outcome variable). It is the continuous analog to the average marginal effect computed for a binary predictor, e.g., using [sim_ame()]. Although inference can be at each level of the predictor or between two levels of the predictor, typically a plot of the ADRF is the most useful relevant quantity. These can be requested using [plot.simbased_adrf()].
+#' The ADRF is composed of average marginal means across levels of the focal predictor. For each level of the focal predictor, predicted values of the outcome are computed after setting the value of the predictor to that level, and those values of the outcome are averaged across all units in the sample to arrive at an average marginal mean. Thus, the ADRF represent the relationship between the "dose" (i.e., the level of the focal predictor) and the average "response" (i.e., the outcome variable). It is the continuous analog to the average marginal effect computed for a binary predictor, e.g., using [sim_ame()]. Although inference can be at each level of the predictor or between two levels of the predictor, typically a plot of the ADRF is the most useful relevant quantity. These can be requested using [plot.clarify_adrf()].
 #'
[…]

### 2022-12-21 R/sim_ame.R

@@ -33,7 +33,7 @@
 #' The `log(.)` versions are defined by taking the [log()] (natural log) of the corresponding effect measure.
 #'
 #' @return
-#' A `simbased_ame` object, which inherits from `simbased_est` and is similar to
+#' A `clarify_ame` object, which inherits from `clarify_est` and is similar to
 #' the output of `sim_apply()`, with the additional attribute `"var"` containing
 #' the variable named in `var`. The average marginal means will be named
 #' `E[Y({v})]`, where `{v}` is replaced with the values the focal variable
@@ -41,8 +41,8 @@
 #' named `dY/d({x})` where `{x}` is replaced with `var`.
 #'
 #' @seealso [sim_apply()], which provides a general interface to computing any
-#'   quantities for simulation-based inference; [plot.simbased_est()] for plotting the
-#'   output of a call to `sim_ame()`; [summary.simbased_est()] for computing
+#'   quantities for simulation-based inference; [plot.clarify_est()] for plotting the
+#'   output of a call to `sim_ame()`; [summary.clarify_est()] for computing
 #'   p-values and confidence intervals for the estimated quantities.
 #'
 #' `marginaleffects::marginaleffects()`, `marginaleffects::comparisons()`, and `margins::margins()` for delta method-based implementations of computing average marginal effects.
@@ -90,7 +90,7 @@ sim_ame <- function(sim,
   check_sim_apply_wrapper_ready(sim)
 
   chk::chk_flag(verbose)
-  is_misim <- inherits(sim, "simbased_misim")
+  is_misim <- inherits(sim, "clarify_misim")
 
   vals <- NULL
 
@@ -139,11 +139,11 @@ sim_ame <- function(sim,
   #Test to make sure compatible
   if (is_misim) {
     test_dat <- get_pred_data_from_fit(sim$fit[[1]])
-    test_predict <- simbased_predict(sim$fit[[1]], newdata = test_dat, group = NULL, type = type)
+    test_predict <- clarify_predict(sim$fit[[1]], newdata = test_dat, group = NULL, type = type)
   }
   else {
     test_dat <- get_pred_data_from_fit(sim$fit)
-    test_predict <- simbased_predict(sim$fit, newdata = test_dat, group = NULL, type = type)
[…]

### 2022-12-21 R/sim_apply.R

@@ -5,7 +5,7 @@
 #'   calculated quantities form the posterior sampling distribution for the
 #'   quantities of interest. Capabilities are available for parallelization.
 #'
-#' @param sim a `simbased_sim` object; the output of a call to [sim()] or
+#' @param sim a `clarify_sim` object; the output of a call to [sim()] or
 #'   [misim()].
 #' @param FUN a function to be applied to each set of simulated coefficients.
 #'   See Details.
@@ -68,7 +68,7 @@
 #'   can be transformed from their log versions using
 #'   [transform()].
 #'
-#' @return A `simbased_est` object, which is a matrix with a column for each
+#' @return A `clarify_est` object, which is a matrix with a column for each
 #'   estimated quantity and a row for each simulation. The original estimates
 #'   (`FUN` applied to the original coefficients or model fit object) are stored
 #'   in the attribute `"original"`. The `"sim_hash"` attributes contained the
@@ -76,9 +76,9 @@
 #'
 #' @seealso
 #' * [sim()] for generating the simulated coefficients
-#' * [summary.simbased_est()] for computing p-values and confidence intervals for
+#' * [summary.clarify_est()] for computing p-values and confidence intervals for
 #' the estimated quantities
-#' * [plot.simbased_est()] for plotting estimated
+#' * [plot.clarify_est()] for plotting estimated
 #' quantities and their simulated posterior sampling distribution.
 #'
 #' @examples
@@ -126,7 +126,7 @@ sim_apply <- function(sim,
                       cl = NULL,
                       ...) {
 
-  chk::chk_is(sim, "simbased_sim")
+  chk::chk_is(sim, "clarify_sim")
   chk::chk_flag(verbose)
 
   if (missing(FUN)) {
@@ -135,14 +135,14 @@ sim_apply <- function(sim,
     }
 
     ests <- sim$sim.coefs
-    if (inherits(sim, "simbased_misim")) {
+    if (inherits(sim, "clarify_misim")) {
       attr(ests, "original") <- colMeans(sim$coefs)
     }
     else {
       attr(ests, "original") <- sim$coefs
     }
     attr(ests, "sim_hash") <- attr(sim, "sim_hash")
-    class(ests) <- c("simbased_est", class(ests))
+    class(ests) <- c("clarify_est", class(ests))
 
[…]

### 2022-12-21 R/sim_setx.R

@@ -4,8 +4,8 @@
 #' the outcome at specified values of the predictors, sometimes called marginal
 #' predictions. One can also compute the difference between two marginal
 #' predictions (the "first difference"). Although any function that accepted
-#' `simbased_est` objects can be used with `sim_setx()` output objects, a
-#' special plotting function, [plot.simbased_setx()], can be used to plot marginal
+#' `clarify_est` objects can be used with `sim_setx()` output objects, a
+#' special plotting function, [plot.clarify_setx()], can be used to plot marginal
 #' predictions.
 #'
 #' @inheritParams sim_apply
@@ -14,14 +14,14 @@
 #'   Any omitted predictors are fixed at a "typical" value. See Details.
 #'   When `x1` is specified, `x` should identify a single reference unit.
 #'
-#'   For `print()`, a `simbased_setx` object.
+#'   For `print()`, a `clarify_setx` object.
 #' @param x1 a named list of the value each predictor should take to compute the
 #'   first difference from the predictor combination specified in `x`. `x1` can
 #'   only identify a single unit. See Details.
 #' @param outcome a string containing the name of the outcome or outcome level for multivariate (multiple outcomes) or multi-category outcomes. Ignored for univariate (single outcome) and binary outcomes.
 #' @param type a string containing the type of predicted values (e.g., the link or the response). Passed to [marginaleffects::get_predict()] and eventually to `predict()` in most cases. The default and allowable option depend on the type of model supplied, but almost always corresponds to the response scale (e.g., predicted probabilities for binomial models).
 #'
-#' @return a `simbased_setx` object, which inherits from `simbased_est` and is similar to the output of `sim_apply()`, with the following additional attributes:
+#' @return a `clarify_setx` object, which inherits from `clarify_est` and is similar to the output of `sim_apply()`, with the following additional attributes:
 #' * `"setx"` - a data frame containing the values at which predictions are to be made
 #' * `"fd"` - whether or not the first difference is to be computed; set to `TRUE` if `x1` is specified and `FALSE` otherwise
 #'
@@ -41,8 +41,8 @@
 #'   predictor changed, specified in `x1`.
 #'
[…]

### 2022-12-21 R/simbased_est_methods.R

@@ -1,10 +1,10 @@
-#' @exportS3Method cbind simbased_est
-cbind.simbased_est <- function(..., deparse.level = 1) {
+#' @exportS3Method cbind clarify_est
+cbind.clarify_est <- function(..., deparse.level = 1) {
   if (...length() == 0) return(NULL)
 
   for (i in seq_len(...length())) {
-    if (!inherits(...elt(i), "simbased_est")) {
-      .err("all supplied objects must be `simbased_est` objects, the output of calls to `sim_apply()` or its wrappers")
+    if (!inherits(...elt(i), "clarify_est")) {
+      .err("all supplied objects must be `clarify_est` objects, the output of calls to `sim_apply()` or its wrappers")
     }
   }
 
@@ -12,28 +12,28 @@ cbind.simbased_est <- function(..., deparse.level = 1) {
   hashes <- lapply(obj, attr, "sim_hash")
 
   if (any(lengths(hashes) == 0) || any(!vapply(hashes, chk::vld_string, logical(1L)))) {
-    .err("all supplied objects must be unmodified `simbased_est` objects")
+    .err("all supplied objects must be unmodified `clarify_est` objects")
   }
   if (!all_the_same(unlist(hashes)) || !all_the_same(unlist(lapply(obj, nrow)))) {
-    .err("all supplied objects must be calls of `sim_apply()` or its wrappers on the same `simbased_sim` object")
+    .err("all supplied objects must be calls of `sim_apply()` or its wrappers on the same `clarify_sim` object")
   }
 
   out <- do.call("cbind", lapply(obj, drop_sim_class))
 
   attr(out, "original") <- do.call("c", lapply(obj, attr, "original"))
   attr(out, "sim_hash") <- hashes[[1]]
-  class(out) <- c("simbased_est", class(out))
+  class(out) <- c("clarify_est", class(out))
 
   return(out)
 }
 
-#' @exportS3Method transform simbased_est
-transform.simbased_est <- function(`_data`, ...) {
+#' @exportS3Method transform clarify_est
+transform.clarify_est <- function(`_data`, ...) {
   e <- eval(substitute(list(...)), as.data.frame(`_data`), parent.frame())
 
   n <- nrow(`_data`)
   if (!all(vapply(e, function(e.) length(e.) == 0 || (length(e.) == n && is.numeric(e.)), logical(1L)))) {
[…]

### 2022-12-21 R/simbased_predict.R

@@ -1,4 +1,4 @@
-simbased_predict <- function(x, newdata = NULL, group = NULL, type = NULL) {
+clarify_predict <- function(x, newdata = NULL, group = NULL, type = NULL) {
   args <- list(x, newdata = newdata, vcov = FALSE, type = type)
   p <- try(do.call(marginaleffects::get_predict, args), silent = TRUE)
 

### 2022-12-21 R/summary.simbased_est.R

@@ -1,8 +1,8 @@
-#' Inference for `simbased_est` objects
+#' Inference for `clarify_est` objects
 #'
-#' `summary()` tabulates the estimates and confidence intervals and (optionally) p-values from a `simbased_est` object. `confint()` computes confidence intervals.
+#' `summary()` tabulates the estimates and confidence intervals and (optionally) p-values from a `clarify_est` object. `confint()` computes confidence intervals.
 #'
-#' @param object,x a `simbased_est` object; the output of a call to [sim_apply()] or its wrappers.
+#' @param object,x a `clarify_est` object; the output of a call to [sim_apply()] or its wrappers.
 #' @param parm a vector of the names or indices of the estimates to plot. If unspecified, all estimates will be displayed.
 #' @param level the confidence level desired. Default is .95 for 95% confidence intervals.
 #' @param method the method used to compute p-values and confidence intervals. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See Details. Abbreviations allowed.
@@ -10,7 +10,7 @@
 #' @param ci `logical`; whether to display confidence interval limits for the estimates. Default is `TRUE`.
 #' @param ... for `plot()`, further arguments passed to [ggplot2::geom_density()].
 #'
-#' @return For `summary()`, a `summary.simbased_est` object, which is a matrix containing the coefficient estimates, standard errors, test statistics, p-values, and confidence intervals. Not all columns will be present depending on the arguments supplied to `summary()`.
+#' @return For `summary()`, a `summary.clarify_est` object, which is a matrix containing the coefficient estimates, standard errors, test statistics, p-values, and confidence intervals. Not all columns will be present depending on the arguments supplied to `summary()`.
 #'
 #' For `confint()`, a matrix containing the confidence intervals for the requested quantities.
 #'
@@ -53,7 +53,7 @@
 #' plot(est, parm = c("RD", "RR"))
 #'
 #' @export
-summary.simbased_est <- function(object,
+summary.clarify_est <- function(object,
                                  parm,
                                  level = .95,
                                  method = "quantile",
@@ -65,7 +65,7 @@ summary.simbased_est <- function(object,
       is.null(ncol(object)) ||
       !identical(ncol(object), length(attr(object, "original"))) ||
[…]

### 2022-12-21 R/utils.R

@@ -187,6 +187,6 @@ pkg_caller_call <- function(start = 1) {
 }
 
 drop_sim_class <- function(x) {
-  class(x) <- class(x)[!startsWith(class(x), "simbased_")]
+  class(x) <- class(x)[!startsWith(class(x), "clarify_")]
   x
 }

### 2022-12-21 tests/testthat/helper.R

@@ -1,7 +1,7 @@
 #testthat helpers
 
-expect_good_simbased_sim <- function(s) {
-  expect_s3_class(s, "simbased_sim")
+expect_good_clarify_sim <- function(s) {
+  expect_s3_class(s, "clarify_sim")
   expect_true(all(c("sim.coefs", "coefs", "vcov") %in% names(s)))
 
   expect_true(is.matrix(s$sim.coefs))
@@ -25,8 +25,8 @@ expect_good_simbased_sim <- function(s) {
   expect_false(any(!is.finite(s$vcov)))
 }
 
-expect_good_simbased_est <- function(e) {
-  expect_s3_class(e, "simbased_est")
+expect_good_clarify_est <- function(e) {
+  expect_s3_class(e, "clarify_est")
   expect_length(dim(e), 2L)
   expect_type(e, "double")
 
@@ -38,9 +38,9 @@ expect_good_simbased_est <- function(e) {
   expect_false(any(apply(e, 2, all_the_same)))
 }
 
-expect_good_simbased_misim <- function(s) {
-  expect_s3_class(s, "simbased_misim")
-  expect_s3_class(s, "simbased_sim")
+expect_good_clarify_misim <- function(s) {
+  expect_s3_class(s, "clarify_misim")
+  expect_s3_class(s, "clarify_sim")
   expect_true(all(c("sim.coefs", "coefs", "imp") %in% names(s)))
 
   expect_true(is.matrix(s$sim.coefs))

### 2022-12-21 tests/testthat/test-sim.R

@@ -7,7 +7,7 @@ test_that("sim() works with coefs and vcov", {
   s <- sim(coefs = coef(fit), vcov = sandwich::vcovHC(fit),
            n = 5)
 
-  expect_good_simbased_sim(s)
+  expect_good_clarify_sim(s)
 
   expect_equal(dim(s$sim.coefs), c(5L, 7L))
   expect_equal(colnames(s$sim.coefs),
@@ -17,7 +17,7 @@ test_that("sim() works with coefs and vcov", {
 
   s <- sim(coefs = coef(fit), vcov = sandwich::vcovHC(fit),
            n = 5, dist = "t(100)")
-  expect_good_simbased_sim(s)
+  expect_good_clarify_sim(s)
   expect_equal(attr(s, "dist"), "t(100)")
 
   expect_error(sim(coefs = coef(fit), vcov = sandwich::vcovHC(fit),
@@ -26,11 +26,11 @@ test_that("sim() works with coefs and vcov", {
   set.seed(987)
   s1 <- sim(coefs = coef(fit), vcov = sandwich::vcovHC(fit),
             n = 5)
-  expect_good_simbased_sim(s1)
+  expect_good_clarify_sim(s1)
   set.seed(987)
   s2 <- sim(coefs = coef(fit), vcov = sandwich::vcovHC(fit),
             n = 5)
-  expect_good_simbased_sim(s2)
+  expect_good_clarify_sim(s2)
 
   expect_identical(s1$sim.coefs, s2$sim.coefs)
 
@@ -38,7 +38,7 @@ test_that("sim() works with coefs and vcov", {
   set.seed(123)
   s3 <- sim(coefs = coef(fit), vcov = sandwich::vcovHC(fit),
             n = 5)
-  expect_good_simbased_sim(s3)
+  expect_good_clarify_sim(s3)
   expect_false(identical(s1$sim.coefs, s3$sim.coefs))
 
   expect_error(sim(coefs = coef(fit), vcov = sandwich::vcovHC(fit)[-2,-2],
@@ -59,7 +59,7 @@ test_that("sim() works with lm()", {
 
   s <- sim(fit, n = 5)
 
-  expect_good_simbased_sim(s)
+  expect_good_clarify_sim(s)
 
   expect_equal(dim(s$sim.coefs), c(5L, p))
   expect_equal(colnames(s$sim.coefs),
[…]

### 2022-12-21 tests/testthat/test-sim_ame.R

@@ -21,7 +21,7 @@ test_that("sim_ame() works with lm()", {
 
   e <- sim_ame(s, "treat", verbose = FALSE)
 
-  expect_good_simbased_est(e)
+  expect_good_clarify_est(e)
   expect_equal(nrow(e), nrow(s$sim.coefs))
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 2)
@@ -30,7 +30,7 @@ test_that("sim_ame() works with lm()", {
 
   e <- sim_ame(s, "treat", contrast = "diff", verbose = FALSE)
 
-  expect_good_simbased_est(e)
+  expect_good_clarify_est(e)
   expect_equal(nrow(e), nrow(s$sim.coefs))
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
@@ -41,7 +41,7 @@ test_that("sim_ame() works with lm()", {
                  "`contrast` is ignored")
 
   e <- sim_ame(s, "race", verbose = FALSE)
-  expect_good_simbased_est(e)
+  expect_good_clarify_est(e)
   expect_equal(nrow(e), nrow(s$sim.coefs))
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
@@ -49,7 +49,7 @@ test_that("sim_ame() works with lm()", {
   expect_identical(attr(e, "var"), "race")
 
   e <- sim_ame(s, list(race = c("black", "white")), contrast = "diff", verbose = FALSE)
-  expect_good_simbased_est(e)
+  expect_good_clarify_est(e)
   expect_equal(nrow(e), nrow(s$sim.coefs))
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
@@ -58,7 +58,7 @@ test_that("sim_ame() works with lm()", {
 
   #Continuous variable
   e <- sim_ame(s, "age", verbose = FALSE)
-  expect_good_simbased_est(e)
+  expect_good_clarify_est(e)
   expect_equal(nrow(e), nrow(s$sim.coefs))
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 1)
@@ -66,7 +66,7 @@ test_that("sim_ame() works with lm()", {
   expect_identical(attr(e, "var"), "age")
 
[…]

### 2022-12-21 tests/testthat/test-simmi.R

@@ -3,7 +3,7 @@ test_that("misim() works with lists of regressions", {
 
   s <- misim(m, n = 5)
 
-  expect_good_simbased_misim(s)
+  expect_good_clarify_misim(s)
 
   expect_equal(dim(s$sim.coefs), c(5L * length(s$fit), 7L))
   expect_equal(colnames(s$sim.coefs),
@@ -11,31 +11,31 @@ test_that("misim() works with lists of regressions", {
   expect_equal(attr(s, "dist"), "normal")
 
   s <- misim(m, n = 5, dist = "t(100)")
-  expect_good_simbased_misim(s)
+  expect_good_clarify_misim(s)
   expect_equal(attr(s, "dist"), "t(100)")
 
   expect_error(misim(m, n = 5, dist = "t"))
 
   set.seed(987)
   s1 <- misim(m, n = 5)
-  expect_good_simbased_misim(s1)
+  expect_good_clarify_misim(s1)
   set.seed(987)
   s2 <- misim(m, n = 5)
-  expect_good_simbased_misim(s2)
+  expect_good_clarify_misim(s2)
 
   expect_identical(s1$sim.coefs, s2$sim.coefs)
 
   #Different seed
   set.seed(123)
   s3 <- misim(m, n = 5)
-  expect_good_simbased_misim(s3)
+  expect_good_clarify_misim(s3)
   expect_false(identical(s1$sim.coefs, s3$sim.coefs))
 
   #Using custom variances
-  expect_good_simbased_misim(misim(m, n = 5, vcov = sandwich::vcovHC))
-  expect_good_simbased_misim(misim(m, n = 5, vcov = sandwich::vcovHC(m[[1]])))
-  expect_good_simbased_misim(misim(m, n = 5, vcov = lapply(1:10, function(i) sandwich::vcovHC)))
-  expect_good_simbased_misim(misim(m, n = 5, vcov = lapply(1:10, function(i) sandwich::vcovHC(m[[i]]))))
+  expect_good_clarify_misim(misim(m, n = 5, vcov = sandwich::vcovHC))
+  expect_good_clarify_misim(misim(m, n = 5, vcov = sandwich::vcovHC(m[[1]])))
+  expect_good_clarify_misim(misim(m, n = 5, vcov = lapply(1:10, function(i) sandwich::vcovHC)))
+  expect_good_clarify_misim(misim(m, n = 5, vcov = lapply(1:10, function(i) sandwich::vcovHC(m[[i]]))))
 
[…]

### 2022-12-21 README.Rmd
Updated reanme with new name

@@
 
-We can also use `{clarify}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
+We can also use `{clarify}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `{Zelig}`'s `setx()` and `setx1()` functions, using `sim_setx()`:
 

### 2023-01-11 README.Rmd
Updates and cleaning; prep for submission

--- 2022-12-21 README.Rmd
@@
 
-# `{clarify}`: Simulation-Based Inference for Regression Models
+# `clarify`: Simulation-Based Inference for Regression Models
 
@@
 
-`{clarify}` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
+`clarify` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
+See the `clarify` [website](https://ngreifer.github.io/clarify) for documentation and other examples.
 
@@
 
-You can install the development version of `{clarify}` from [GitHub](https://github.com/) with:
+You can install the development version of `clarify` from [GitHub](https://github.com/ngreifer/clarify) with:
 
@@
 When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate.
-Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference; however, it is computationally intensive since the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.
+Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference; however, it is computationally intensive because the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.
 
@@
 
-The `{clarify}` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
-The primary functions of `{clarify}` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
+The `clarify` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
+The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
 These work together to create a simple workflow for simulation-based inference.
@@
 
-There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; and `sim_setx()` computes predicted values at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`.
+There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predicted values at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()`  computes average dose-response functions.
+`clarify` also offers support for models fit to multiply imputed data with the `misim()` function.
 
@@
 
-`{clarify}` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
+`clarify` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
 We can compute the log marginal risk ratio below:
@@
 # Marginal risk ratio ATT, delta method-based
-marginaleffects::comparisons(fit, variables = list(treat = 0:1),
+marginaleffects::comparisons(fit, variables = "treat",
                              newdata = subset(lalonde, treat == 1),
@@
 
-We can also use `{clarify}` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
+We can also use `clarify` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
 
@@
 
-`{clarify}` offers parallel processing for all estimation functions to speed up computation.
+`clarify` offers parallel processing for all estimation functions to speed up computation.
 

### 2023-01-11 R/misim.R

@@ -23,7 +23,20 @@
 #'
 #' Zhou, X., & Reiter, J. P. (2010). A Note on Bayesian Inference After Multiple Imputation. *The American Statistician*, 64(2), 159–163. \doi{10.1198/tast.2010.09109}
 #'
-#' @examples
+#' @examplesIf requireNamespace("Amelia", quietly = TRUE)
+#' data("africa", package = "Amelia")
+#'
+#' # Multiple imputation using Amelia
+#' a.out <- Amelia::amelia(x = africa, m = 10,
+#'                         cs = "country",
+#'                         ts = "year", logs = "gdp_pc",
+#'                         p2s = 0)
+#'
+#' fits <- with(a.out, lm(gdp_pc ~ infl * trade))
+#'
+#' # Simulate coefficients
+#' s <- misim(fits)
+#' s
 #'
 #' @seealso
 #' * [sim()] for simulating model coefficients for a single dataset
@@ -165,8 +178,4 @@ print.clarify_misim <- function(x, ...) {
       cat("\n")
     }
   }
-  # if (!is.null(x$fit)) {
-  #   cat(" - original fitting function call:\n\n")
-  #   print(insight::get_call(x$fit))
-  # }
 }

### 2023-01-11 R/summary.simbased_est.R

@@ -23,6 +23,7 @@
 #' The plots are produced using [ggplot2::geom_density()] and can be customized with \pkg{ggplot2} functions.
 #'
 #' @seealso
+#' * [sim_apply()] for applying a function to each set of simulated coefficients
 #'
 #' @examples
 #' data("lalonde", package = "MatchIt")

### 2023-01-17 README.Rmd

@@
 `clarify` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
-See the `clarify` [website](https://ngreifer.github.io/clarify) for documentation and other examples.
+See the `clarify` [website](https://iqss.github.io/clarify) for documentation and other examples.
 
@@
 
-You can install the development version of `clarify` from [GitHub](https://github.com/ngreifer/clarify) with:
+You can install the development version of `clarify` from [GitHub](https://github.com/iqss/clarify) with:
 
@@
 # install.packages("devtools")
-devtools::install_github("ngreifer/clarify")
+devtools::install_github("iqss/clarify")
 ```

### 2023-01-17 README.Rmd
Updates and cleaning

@@
 
-`clarify` implements simulation-based inference as an alternative to the delta method for computing functions of model parameters, such as average marginal effects.
+`clarify` implements simulation-based inference for computing functions of model parameters, such as average marginal effects.
 See the `clarify` [website](https://iqss.github.io/clarify) for documentation and other examples.
 
-## Installation
-
-You can install the development version of `clarify` from [GitHub](https://github.com/iqss/clarify) with:
-
-``` r
-# install.packages("devtools")
-devtools::install_github("iqss/clarify")
-```
 ## Introduction
@@
 
-The `clarify` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
+The `clarify` package was designed to provide a simple, general interface for simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
 The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
@@
 
-There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predicted values at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()`  computes average dose-response functions.
+There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions.
 `clarify` also offers support for models fit to multiply imputed data with the `misim()` function.
+
+## Installation
+
+`clarify` can be installed from CRAN using
+
+```{r, eval = F}
+install.packages("clarify")
+```
+
+You can install the development version of `clarify` from [GitHub](https://github.com/iqss/clarify) with
+
+```{r, eval = F}
+install.packages("remotes")
+remotes::install_github("iqss/clarify")
+```
 
@@
 
-#Fit the model
-fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married + nodegree + re74 + re75),
+# Fit the model
+fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married
+                                   + nodegree + re74 + re75),
            data = lalonde, family = binomial)
 
-#Simulate coefficients from a multivariate normal distribution
+# Simulate coefficients from a multivariate normal distribution
 set.seed(123)
@@
 
-#Apply a function that estimate the g-computation estimate for the ATT
-#to models with the estimated coefficients replaced by the simulated ones
+# Apply a function that computes the g-computation estimate for the ATT
+# to models with the estimated coefficients replaced by the simulated ones
 sim_est <- sim_apply(sim_coefs, function(fit) {
@@
 
-#View the estimates, confidence intervals, and p-values
+# View the estimates, confidence intervals, and p-values
 summary(sim_est, null = c(NA, NA, 0))
 
-#Plot the resulting sampling distributions
+# Plot the resulting sampling distributions
 plot(sim_est)

### 2023-01-17 R/checks.R

@@ -256,7 +256,9 @@ check_classes <- function(olddata, newdata) {
     else .err(sprintf("variables %s were specified with different types from the original model fit",
                           word_list(names(old)[wrong], quotes = TRUE)))
   }
-  else invisible(NULL)
+  else {
+    invisible(NULL)
+  }
 }
 
 check_sim_apply_wrapper_ready <- function(sim) {

### 2023-01-17 R/clarify_est_methods.R

@@ -46,13 +46,13 @@ transform.clarify_est <- function(`_data`, ...) {
 
     if (any(!nulls)) {
       for (i in seq_along(e)[matched][!nulls]) {
-        `_data`[,inx[i]] <- e[[i]]
+        `_data`[, inx[i]] <- e[[i]]
         attr(`_data`, "original")[inx[i]] <- as.numeric(e_original[i])
       }
     }
 
     if (any(nulls)) {
-      `_data` <- `_data`[,-inx[matched][nulls]]
+      `_data` <- `_data`[, -inx[matched][nulls]]
     }
   }
   if (!all(matched)) {
@@ -178,7 +178,7 @@ Ops.clarify_est <- function(e1, e2 = NULL) {
     attr(y, "at") <- unname(setNames(attr(y, "at"), names(attr(x, "original")))[j])
   }
   if ("setx" %in% names(attrs)) {
-    attr(y, "setx") <- attr(y, "setx")[j,,drop = FALSE]
+    attr(y, "setx") <- attr(y, "setx")[j, , drop = FALSE]
   }
 
   y

### 2023-01-17 R/clarify_predict.R

@@ -13,5 +13,5 @@ clarify_predict <- function(x, newdata = NULL, group = NULL, type = NULL) {
 
 subset_group <- function(pred, group = NULL) {
   if (is.null(group)) pred
-  else pred[pred$group == group,]
+  else pred[pred$group == group, , drop = FALSE]
 }

### 2023-01-17 R/misim.R

@@ -164,7 +164,7 @@ print.clarify_misim <- function(x, ...) {
   obj <- deparse1(substitute(x))
   cat("A `clarify_misim` object\n")
   cat(sprintf(" - %s coefficients, %s imputations with %s simulated values each\n",
-              ncol(x$sim.coefs), nrow(x$coefs), nrow(x$sim.coefs)/nrow(x$coefs)))
+              ncol(x$sim.coefs), nrow(x$coefs), nrow(x$sim.coefs) / nrow(x$coefs)))
   cat(" - sampled distributions: ")
   if (length(attr(x, "dist")) == 1) {
     cat(sprintf("multivariate %s\n", attr(x, "dist")))

### 2023-01-17 R/plot.clarify_setx.R

@@ -177,7 +177,7 @@ setx_reg_plot <- function(x, var, non_var_varying = NULL, ci = TRUE, level = .95
   }
 
   if (ci) {
-    s <- summary.clarify_est(x, level = level, method = method)[rownames(newdata),, drop = FALSE]
+    s <- summary.clarify_est(x, level = level, method = method)[rownames(newdata), , drop = FALSE]
   }
   else {
     s <- matrix(coef(x)[rownames(newdata)], ncol = 1,

### 2023-01-17 R/sim.R

@@ -119,7 +119,7 @@ get_sampling_dist <- function(fit = NULL, dist = NULL) {
     chk::chk_string(dist)
     dist <- tolower(dist)
     if (startsWith(dist, "t(") && endsWith(dist, ")")) {
-      df <- substr(dist, 3, nchar(dist)-1)
+      df <- substr(dist, 3, nchar(dist) - 1)
       if (nchar(df) == 0 || anyNA(suppressWarnings(df <- as.numeric(df))) || !chk::vld_number(df)) {
         .err("when `dist` is supplied as t({#}), `{#}` must be a number")
       }
@@ -145,7 +145,7 @@ get_sampling_dist <- function(fit = NULL, dist = NULL) {
 
   if (dist == "t") {
     f <- function(n, mu, cov) {
-      sigma <- cov*(df - 2)/df
+      sigma <- cov * (df - 2) / df
       #Need pivoted cholesky for when cov isn't PSD (sometimes true for fixed effects models)
       ch <- suppressWarnings(chol(sigma, pivot = TRUE))
       piv <- attr(ch, "pivot")

### 2023-01-17 R/sim_ame.R

@@ -193,11 +193,14 @@ sim_ame <- function(sim,
     FUN <- function(fit) {
       dat <- get_pred_data_from_fit(fit)
       m <- nrow(dat)
-      dat2 <- do.call("rbind", lapply(vals, function(v) {dat[[var]][] <- v; dat}))
+      dat2 <- do.call("rbind", lapply(vals, function(v) {
+        dat[[var]][] <- v
+        dat
+      }))
       pred <- clarify_predict(fit, newdata = dat2, group = outcome, type = type)
       p <- pred$predicted
       vapply(seq_along(vals), function(i) {
-        weighted.mean(p[seq_len(m) + (i-1)*m], attr(fit, "weights"))
+        weighted.mean(p[seq_len(m) + (i - 1) * m], attr(fit, "weights"))
       }, numeric(1L))
     }
 
@@ -208,12 +211,12 @@ sim_ame <- function(sim,
     if (!is.null(contrast)) {
       out <- transform(out,
                        `.C` = switch(tolower(contrast),
-                                     "diff" =, "rd" = M2 - M1,
-                                     "nnt" = 1/(M2 - M1),
-                                     "irr" =, "rr" = M2 / M1,
-                                     "log(irr)" =, "log(rr)" = log(M2 / M1),
-                                     "or" = (M2/(1-M2))/(M1/(1-M1)),
-                                     "log(or)" = log((M2/(1-M2))/(M1/(1-M1)))))
+                                     "diff" = , "rd" = M2 - M1,
+                                     "nnt" = 1 / (M2 - M1),
+                                     "irr" = , "rr" = M2 / M1,
+                                     "log(irr)" = , "log(rr)" = log(M2 / M1),
+                                     "or" = (M2 / (1 - M2)) / (M1 / (1 - M1)),
+                                     "log(or)" = log((M2 / (1 - M2)) / (M1 / (1 - M1)))))
       names(out)[3] <- rename_contrast(contrast)
     }
 
@@ -236,8 +239,8 @@ sim_ame <- function(sim,
       ind <- seq_len(nrow(dat))
       dat2 <- rbind(dat, dat)
 
-      dat2[[var]][ind] <- dat2[[var]][ind] - eps/2
-      dat2[[var]][-ind] <- dat2[[var]][-ind] + eps/2
+      dat2[[var]][ind] <- dat2[[var]][ind] - eps / 2
[…]

### 2023-01-17 R/sim_setx.R

@@ -106,11 +106,11 @@ sim_setx <- function(sim,
 
   #Test to make sure compatible
   if (is_misim) {
-    test_dat <- get_pred_data_from_fit(sim$fit[[1]])[1,, drop = FALSE]
+    test_dat <- get_pred_data_from_fit(sim$fit[[1]])[1, , drop = FALSE]
     test_predict <- clarify_predict(sim$fit[[1]], newdata = test_dat, group = NULL, type = type)
   }
   else {
-    test_dat <- get_pred_data_from_fit(sim$fit)[1,, drop = FALSE]
+    test_dat <- get_pred_data_from_fit(sim$fit)[1, , drop = FALSE]
     test_predict <- clarify_predict(sim$fit, newdata = test_dat, group = NULL, type = type)
   }
 

### 2023-01-17 R/utils.R

@@ -25,11 +25,11 @@ word_list <- function(word.list = NULL, and.or = c("and", "or"), is.are = FALSE,
     else {
       and.or <- match_arg(and.or)
       if (L == 2) {
-        out <- paste(word.list, collapse = paste0(" ", and.or," "))
+        out <- paste(word.list, collapse = paste0(" ", and.or, " "))
       }
       else {
-        out <- paste(paste(word.list[seq_len(L-1)], collapse = ", "),
-                     word.list[L], sep = paste0(", ", and.or," "))
+        out <- paste(paste(word.list[seq_len(L - 1)], collapse = ", "),
+                     word.list[L], sep = paste0(", ", and.or, " "))
 
       }
       if (is.are) out <- paste(out, "are")
@@ -171,10 +171,10 @@ is_error <- function(x) {
 
 pkg_caller_call <- function(start = 1) {
   package.funs <- c(getNamespaceExports(utils::packageName()),
-                    .getNamespaceInfo(asNamespace(utils::packageName()), "S3methods")[,3])
+                    .getNamespaceInfo(asNamespace(utils::packageName()), "S3methods")[, 3])
   k <- start #skip checking pkg_caller_call()
   e_max <- NULL
-  while(!is.null(e <- rlang::caller_call(k))) {
+  while (!is.null(e <- rlang::caller_call(k))) {
     if (!is.null(n <- rlang::call_name(e)) &&
         n %in% package.funs) e_max <- k
     k <- k + 1

### 2023-01-26 R/summary.clarify_est.R
CHanges to `null` argument to `summary()`

@@ -6,7 +6,7 @@
 #' @param parm a vector of the names or indices of the estimates to plot. If unspecified, all estimates will be displayed.
 #' @param level the confidence level desired. Default is .95 for 95% confidence intervals.
 #' @param method the method used to compute p-values and confidence intervals. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See Details. Abbreviations allowed.
-#' @param null the values of the parameters under the null hypothesis for the p-value calculations. Should have length equal to the number of quantities estimated, or one, in which case it will be recycled. Set values to `NA` to omit p-values for those quantities. When all values are `NA`, the default, no p-values are produced.
+#' @param null the values of the parameters under the null hypothesis for the p-value calculations. Should have length equal to the number of quantities estimated, or one, in which case it will be recycled, or it can be a named vector with just the names of quantities for which null values are to be set. Set values to `NA` to omit p-values for those quantities. When all values are `NA`, the default, no p-values are produced.
 #' @param ci `logical`; whether to display confidence interval limits for the estimates. Default is `TRUE`.
 #' @param ... for `plot()`, further arguments passed to [ggplot2::geom_density()].
 #'
@@ -44,9 +44,10 @@
 #'
 #' # Compute confidence intervals and p-values,
 #' # using given null values for computing p-values
-#' summary(est, null = c(NA, NA, 0, 1))
+#' summary(est, null = c(`RD` = 0, `RR` = 1))
 #'
-#' # Same tests using normal approximation
+#' # Same tests using normal approximation and alternate
+#' # syntax for `null`
 #' summary(est, null = c(NA, NA, 0, 1),
 #'         normal = TRUE)
 #'
@@ -76,20 +77,9 @@ summary.clarify_est <- function(object,
     .err("`parm` must be a numeric or character vector identifying the estimates to summarize")
   }
 
-  if (length(null) == 0 || (is.atomic(null) && all(is.na(null)))) {
-    null <- NA_real_
-  }
-  chk::chk_numeric(null)
+  null <- process_null(null, object, parm)
 
-  if (length(null) == 1) null <- rep(null, length(parm))
   test <- !all(is.na(null))
-
-  if (test) {
-    if (!chk::vld_length(null, length(parm))) {
-      .err(sprintf("`null` must have length 1 or length equal to the number of quantities estimated (%s)",
-                   length(parm)))
-    }
-  }
 
   nas <- anyNA(object[, parm])
   if (nas) chk::wrn("NA values present among the estimates")

### 2023-01-26 README.Rmd
Updates for submission
Updates

@@
 
-`clarify` implements simulation-based inference for computing functions of model parameters, such as average marginal effects.
-See the `clarify` [website](https://iqss.github.io/clarify) for documentation and other examples.
-
-## Introduction
-
-Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters.
-The delta method involves multiple assumptions: 1) the regression coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance.
-When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate.
-Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference; however, it is computationally intensive because the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.
-
-Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3), and it is faster and more stable than bootstrapping because the model only needs to be fit once.
-Simulation-based inference involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution.
-Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals.
-Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory confidence intervals and p-values can be computed.
-
-The `clarify` package was designed to provide a simple, general interface for simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
-The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
-These work together to create a simple workflow for simulation-based inference.
-
-* `sim()` simulates model parameters from a fitted model
-* `sim_apply()` applies an estimator to the simulated coefficients, or to the original object but with the new coefficients inserted
-* `summary()` produces confidence intervals and p-values for the resulting estimates
-* `plot()` produces plots of the simulated sampling distribution of the resulting estimates
-
-There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions.
-`clarify` also offers support for models fit to multiply imputed data with the `misim()` function.
+`clarify` implements simulation-based inference for computing functions of model parameters, such as average marginal effects and predictions at representative values of the predictors.
+See the `clarify` [website](https://iqss.github.io/clarify/) for documentation and other examples.
+`clarify` was designed to replicate and expand on functionality previously provided by the `Zelig` package.
 
@@
 
-Below is an example of performing g-computation for the ATT after logistic regression to compute the marginal log risk ratio and its confidence interval:
+Below is an example of performing g-computation for the average treatment effect on the treated (ATT) after logistic regression to compute the marginal log risk ratio and its confidence interval.
+First we load the data (in this case the `lalonde` dataset from `MatchIt`) and fit a logistic regression using functions outside of `clarify`:
 
-```{r example, fig.width=7, fig.height=3}
+```{r, fig.width=7, fig.height=3}
 library(clarify)
@@
 # Fit the model
-fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married
-                                   + nodegree + re74 + re75),
+fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married +
+                                     nodegree + re74 + re75),
            data = lalonde, family = binomial)
+```
 
+Next, to estimate the ATT risk ratio, we simulate coefficients from their implied distribution and compute the effects of interest in each simulation, yielding a distribution of estimates that was can summarize and use for inference:
+
+```{r example, fig.width=7, fig.height=3}
 # Simulate coefficients from a multivariate normal distribution
@@
 
-# Apply a function that computes the g-computation estimate for the ATT
-# to models with the estimated coefficients replaced by the simulated ones
-sim_est <- sim_apply(sim_coefs, function(fit) {
+# Marginal risk ratio ATT, simulation-based
+sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
+                   contrast = "RR", verbose = FALSE)
+
+sim_est
+
+# View the estimates, confidence intervals, and p-values
+summary(sim_est, null = c(`RR` = 1))
+
+# Plot the resulting sampling distributions
+plot(sim_est)
+```
+
+Below, we provide information on the framework `clarify` uses and some other examples. For a complete vignette, see `vignette("clarify")`.
+
+## Introduction
+
+Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters.
+The delta method involves multiple assumptions: 1) the regression coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance.
+When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate.
+Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference; however, it is computationally intensive because the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.
+
+Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3), and it is faster and more stable than bootstrapping because the model only needs to be fit once.
+Simulation-based inference involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution.
+Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals.
+Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory confidence intervals and p-values can be computed.
+The methodology of simulation-based inference is explained in King, Tomz, and Wittenberg (2000).
+
+`clarify` was designed to provide a simple, general interface for simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
+The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
+These work together to create a simple workflow for simulation-based inference.
+
+* `sim()` simulates model parameters from a fitted model
+* `sim_apply()` applies an estimator to the simulated coefficients, or to the original object but with the new coefficients inserted
+* `summary()` produces confidence intervals and p-values for the resulting estimates
+* `plot()` produces plots of the simulated sampling distribution of the resulting estimates
+
+There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions.
+`clarify` also offers support for models fit to multiply imputed data with the `misim()` function.
+
+In the example above, we used `sim_ame()` to compute the ATT, but we could have also done so manually using `sim_apply()`, as demonstrated below:
+
+```{r example2, fig.width=7, fig.height=3}
+# Write a function that computes the g-computation estimate for the ATT
+ATT_fun <- function(fit) {
   d <- subset(lalonde, treat == 1)
@@
   p0 <- mean(predict(fit, newdata = d, type = "response"))
-  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, `log(RR)` = log(p1 / p0))
-}, verbose = FALSE)
+  c(`E[Y(0)]` = p0, `E[Y(1)]` = p1, `RR` = p1 / p0)
+}
+
+# Apply that function to the simulated coefficient
+sim_est <- sim_apply(sim_coefs, ATT_fun, verbose = FALSE)
 
@@
 
-# View the estimates, confidence intervals, and p-values
-summary(sim_est, null = c(NA, NA, 0))
+# View the estimates, confidence intervals, and p-values;
+# they are the same as when using sim_ame() above
+summary(sim_est, null = c(`RR` = 1))
 
@@
 
-`clarify` provides a shortcut for computing average marginal effects and comparisons between average adjusted predictions, `sim_ame()`, which is essentially a wrapper for `sim_apply()` with extra processing.
-We can compute the log marginal risk ratio below:
+The plot of the simulated sampling distribution indicates that the sampling distribution for the risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid.
 
-```{r}
-# Marginal risk ratio ATT, simulation-based
-sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
-                   contrast = "log(RR)", verbose = FALSE)
-
-sim_est
-
-summary(sim_est, null = c(NA, NA, 0))
-```
-
-We could have used `marginaleffects`, which uses the delta method instead:
-
-```{r}
-# Marginal risk ratio ATT, delta method-based
-marginaleffects::comparisons(fit, variables = "treat",
-                             newdata = subset(lalonde, treat == 1),
-                             transform_pre = "lnratioavg") |>
-  summary()
-```
-
-The plot of the simulated sampling distribution indicates that the sampling distribution for the log risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid.
-
-If we want to compute the marginal risk ratio, we can do that using `transform()` on the already-produced output:
+If we want to compute the risk difference, we can do that using `transform()` on the already-produced output:
 
@@
 #Transform estimates into new quantities of interest
-sim_est <- transform(sim_est, `RR` = exp(`log(RR)`))
-summary(sim_est, null = c(NA, NA, 0, 1))
+sim_est <- transform(sim_est, `RD` = `E[Y(1)]` - `E[Y(0)]`)
+summary(sim_est, null = c(`RR` = 1, `RD` = 0))
 ```
@@
 
+See `vignette("Zelig", package = "clarify")` for more examples of translating a `Zelig`-based workflow into one that uses `clarify` to estimate the same quantities of interest.
+
 `clarify` offers parallel processing for all estimation functions to speed up computation.
+Functionality is also available for the analysis of models fit to multiply imputed data.
+See `vignette("clarify")` for more details.
 
-The methodology of simulation-based inference is described in King, Tomz, and Wittenberg (2000).
+## References
 

### 2023-01-30 README.Rmd
README updates

@@
 
-Below is an example of performing g-computation for the average treatment effect on the treated (ATT) after logistic regression to compute the marginal log risk ratio and its confidence interval.
+Below is an example of performing g-computation for the average treatment effect on the treated (ATT) after logistic regression to compute the average causal risk ratio and its confidence interval.
 First we load the data (in this case the `lalonde` dataset from `MatchIt`) and fit a logistic regression using functions outside of `clarify`:
@@
 Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters.
-The delta method involves multiple assumptions: 1) the regression coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance.
+The delta method involves multiple assumptions: 1) the model coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance.
 When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate.
-Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference; however, it is computationally intensive because the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.
+Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference (though other assumptions are required); however, it is computationally intensive because the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.
 
-Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3), and it is faster and more stable than bootstrapping because the model only needs to be fit once.
+Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3) (though it still relies on the central limit theorem to assume the coefficients are normally distributed), and it is faster and more stable than bootstrapping because the model only needs to be fit once.
 Simulation-based inference involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution.
 Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals.
-Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory confidence intervals and p-values can be computed.
+Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory Wald confidence intervals and p-values can be computed.
 The methodology of simulation-based inference is explained in King, Tomz, and Wittenberg (2000).
 
-`clarify` was designed to provide a simple, general interface for simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects.
+`clarify` was designed to provide a simple, general interface for simulation-based inference and includes a few convenience functions to perform common tasks like computing average marginal effects.
 The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
@@
 # they are the same as when using sim_ame() above
-summary(sim_est, null = c(`RR` = 1))
+summary(sim_est, null = c(NA, NA, 1))
 
@@
 sim_est <- transform(sim_est, `RD` = `E[Y(1)]` - `E[Y(0)]`)
-summary(sim_est, null = c(`RR` = 1, `RD` = 0))
+summary(sim_est, null = c(NA, NA, 1, 0))
 ```

### 2023-02-02 README.Rmd
Updates version 0.1.1

@@
 # they are the same as when using sim_ame() above
-summary(sim_est, null = c(NA, NA, 1))
+summary(sim_est, null = c(`RR` = 1))
 
@@
 sim_est <- transform(sim_est, `RD` = `E[Y(1)]` - `E[Y(0)]`)
-summary(sim_est, null = c(NA, NA, 1, 0))
+summary(sim_est, null = c(`RR` = 1, `RD` = 0))
 ```

### 2023-02-02 R/summary.clarify_est.R

@@ -61,7 +61,6 @@ summary.clarify_est <- function(object,
                                 method = "quantile",
                                 null = NA,
                                 ...) {
-  ans <- list()
 
   if (is.null(attr(object, "original")) ||
       is.null(ncol(object)) ||

### 2023-05-03 README.Rmd
Updates to docs to reference Rainey (2023)

@@
 # Plot the resulting sampling distributions
-plot(sim_est)
+plot(sim_est, reference = TRUE, ci = FALSE)
 ```
@@
 The plot of the simulated sampling distribution indicates that the sampling distribution for the risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid.
+Note that the estimates are those computed from the original model coefficients; the distribution is used only for computing confidence intervals, in line with recommendations by Rainey (2023).
 
@@
 https://doi.org/10.2307/2669316
+
+Rainey, C.
+(2023).
+A careful consideration of CLARIFY: Simulation-induced bias in point estimates of quantities of interest.
+*Political Science Research and Methods*, 1–10.
+https://doi.org/10.1017/psrm.2023.8

### 2023-09-19 clarify/clarify.tex
Added files for R Journal submission

% !TeX root = RJwrapper.tex
\title{clarify: Simulation-Based Inference for Regression Models}

\author{by Noah Greifer, Steven Worthington, Stefano Iacus, and Gary King}

\maketitle

\abstract{%
Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects and adjusted predictions. It avoids several assumptions required by the delta method that are commonly violated, especially in nonlinear models, but does not require models to be refit as when using the bootstrap. It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form the sampling distribution of the quantity. \pkg{clarify} provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest. \pkg{clarify} supports a large and growing number of models through its interface with the \pkg{marginaleffects} package and provides native support for multiply imputed data.
}

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

Although regression models are frequently used in empirical research to study relationships among variables, often the quantity of substantive interest is not one of the coefficients of the model, but rather a quantity derived from the coefficients, such as predicted values or average marginal effects. The usual method for estimating the uncertainty of the derived quantities is known as the ``delta method'', which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the resulting estimate is normally distributed\footnote{In addition, most software that uses the delta method uses numerical differentiation, which also involves an approximation.}. In many cases, especially with nonlinear models, these approximation can fail badly. \pkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.

The methodology \pkg{clarify} relies on is described in King, Tomz, and Wittenberg (2000) and Rainey (2023). Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a ``posterior'' distribution, which is taken to be the sampling distribution of the derived quantity, and from which uncertainty measures (standard errors and confidence intervals) can be computed. This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values. Arriving at the posterior distribution does not require taking any derivatives or making any approximations except those used to define the sampling distribution of the parameter estimates. The delta method makes these same approximation in addition to the approximations of the variance and the shape of the sampling distribution of the estimates.

More formally, we fit a regression model \(y_i = f(x_i; \beta)\), such a linear or generalized linear model with model coefficients \(\beta\). We assume\[
\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})
\]where \(\hat{\beta}\) is the vector of estimates of \(\beta\) and \(\Sigma_{\hat{\beta}}\) is their asymptotic covariance matrix. We define a function \(\tau(\beta)\) that represents a quantity of interest derived from the model parameters, and compute its estimate \(\hat{\tau}(\beta)\) as \(\tau(\hat{\beta})\). Next, we take \(M\) draws \(\tilde{\beta}^{(j)}\) for \(j\in(1, \dots, M)\) from a multivariate Normal distribution with mean vector \(\boldsymbol{\mu} = \hat{\beta}\) and covariance \(\Sigma = \hat{\Sigma}_{\hat{\beta}}\), where \(\hat{\Sigma}_{\hat{\beta}}\) is an estimate of the asymptotic covariance matrix of the parameter estimates. We use the distribution of \(\tilde{\tau}=\tau(\tilde{\theta})\) as the ``posterior'' sampling distribution of \(\hat{\tau}(\beta)\), and compute its variance as\[
\sigma^2_{\hat{\tau}(\theta)} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
\]and quantile \(100(1-\alpha)\%\) confidence interval limits as \(\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]\) where \(\tilde{\tau}_{(k)}\) is the \(k\)th value of \(\tilde{\tau}\) when arranged in ascending order.

Similar functionality exists in the \pkg{CLARIFY} package in Stata {[}Tomz, Wittenberg, and King (2003){]}\footnote{Despite the similar name, the R package \pkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \pkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution. The R implementation avoids the ``simulation-induced bias'' described by Rainey (2023).} and used to be available in the \texttt{Zelig} R package (Imai, King, and Lau 2008), though there are differences in these implementations. \pkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below). \pkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).

\hypertarget{using}{%
\subsection{\texorpdfstring{Using \pkg{clarify}}{Using }}\label{using}}

There are four steps to using \pkg{clarify}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Fit the model to the data using modeling functions in supported packages.
\item
  Use \texttt{sim()} to take draws from the sampling distribution of the estimated model coefficients.
\item
  Use \texttt{sim\_apply()} or its wrappers \texttt{sim\_setx()}, \texttt{sim\_ame()}, and \texttt{sim\_adrf()} to compute derived quantities using each simulated set of coefficients.
\item
  Use \texttt{summary()} and \texttt{plot()} to summarize and visualize the distribution of the derived quantities and perform inference on them.
\end{enumerate}

In the sections below, we'll describe how to implement these steps in detail. First, we'll load \pkg{clarify} using \texttt{library()}.

\begin{verbatim}
library(clarify)
\end{verbatim}

For a running example, we'll use the \texttt{lalonde} dataset in the \pkg{MatchIt} package (Ho et al. 2011), which contains data on 614 participants enrolled in a job training program or sampled from a survey (Dehejia and Wahba 1999). The treatment variable is \texttt{treat} and the outcome is \texttt{re78}, and all other variables are confounders. Although the original use of this dataset was to estimate the effect of \texttt{treat} on \texttt{re78}, we'll use it more generally to demonstrate all of \pkg{clarify}'s capabilities. In addition, we'll use a transformation of the outcome variable to demonstrate applications to nonlinear models, for which the benefits of simulation-based inference are more apparent.

\begin{verbatim}
data("lalonde", package = "MatchIt")

lalonde$re78_0 <- ifelse(lalonde$re78 > 0, 1, 0)

head(lalonde)
\end{verbatim}

\begin{verbatim}
#>      treat age educ   race married nodegree re74 re75       re78 re78_0
#> NSW1     1  37   11  black       1        1    0    0  9930.0460      1
#> NSW2     1  22    9 hispan       0        1    0    0  3595.8940      1
#> NSW3     1  30   12  black       0        0    0    0 24909.4500      1
#> NSW4     1  27   11  black       0        1    0    0  7506.1460      1
#> NSW5     1  33    8  black       0        1    0    0   289.7899      1
#> NSW6     1  22    9  black       0        1    0    0  4056.4940      1
\end{verbatim}

\hypertarget{fitting-the-model}{%
\subsubsection{1. Fitting the model}\label{fitting-the-model}}

The first step is to fit the model. \pkg{clarify} can operate on a large set of models (those supported by \pkg{marginaleffects}), including generalized linear models, multinomial models, multivariate models, and instrumental variable models, many of which are available in other R packages. Even if \pkg{clarify} does not offer direct support for a given model, there are ways to use its functionality regardless (explained in more detail below).

Because we are computing derived quantities, it is not critical to parameterize the model in such a way that the coefficients are interpretable, e.g., by using a model with interpretable coefficients or centering predictors. Below, we'll fit a probit regression model for the outcome given the treatment and confounders. Coefficients in probit regression do not have a straightforward interpretation, but that's okay; our quantities of interest can be expressed as derived quantities---functions of the model parameters, such as predictions, counterfactual predictions, and averages and contrasts of them.

\begin{verbatim}
fit <- glm(re78_0 ~ treat * married + age + educ + race +
             nodegree + re74 + re75, data = lalonde,
           family = binomial("probit"))
\end{verbatim}

\hypertarget{drawing-from-the-coefficient-distribution}{%
\subsubsection{2. Drawing from the coefficient distribution}\label{drawing-from-the-coefficient-distribution}}

After fitting the model, we will use \texttt{sim()} to draw coefficients from their sampling distribution. The sampling distribution is assumed to be multivariate Normal or multivariate T with appropriate degrees of freedom, with a mean vector equal to the estimated coefficients and a covariance matrix equal to the asymptotic covariance matrix extracted from the model. The arguments to \texttt{sim()} are listed below:

\begin{verbatim}
sim(fit = , n = , vcov = , coefs = , dist = )
\end{verbatim}

\begin{itemize}
\item
  \texttt{fit} -- the fitted model object, the output of the call to the fitting function (e.g., \texttt{glm()})
\item
  \texttt{n} -- the number of simulated values to draw; by default, 1000. More values will yield more replicable and precise results at the cost of speed.
\item
  \texttt{vcov} -- either the covariance matrix of the estimated coefficients, a function used to extract it from the model (e.g., \texttt{sandwich::vcovHC()} for the robust covariance matrix), or a string or formula giving a code for extracting the covariance matrix, which is passed to \texttt{marginaleffects::get\_vcov()}. If left unspecified, the default covariance matrix will be extracted from the model.
\item
  \texttt{coefs} -- either a vector of coefficients to be sampled or a function to extract them from the fitted model. If left unspecified, the default coefficients will be extracted from the model. Typically this does not need to be specified.
\item
  \texttt{dist} -- the name of the distribution from which to draw the sampled coefficients. Can be \texttt{"normal"} for a Normal distribution or \texttt{t(\#)} for a t-distribution, where \texttt{\#} represents the degrees of freedom. If left unspecified, \texttt{sim()} will decide on which distribution makes sense given the characteristics of the model (the decision is made by \texttt{insight::get\_df()} with \texttt{type\ =\ "wald"}). Typically this does not need to be specified.
\end{itemize}

If one's model is not supported by \pkg{clarify}, one can omit the \texttt{fit} argument and just specify the \texttt{vcov} and \texttt{coefs} argument, which will draw the coefficients from the distribution named in \texttt{dist} (\texttt{"normal"} by default).

\texttt{sim()} uses a random number generator to draw the sampled coefficients from the sampling distribution, so a seed should be set using \texttt{set.seed()} to ensure results are replicable across sessions.

The output of the call to \texttt{sim()} is a \texttt{clarify\_sim} object, which contains the sampled coefficients, the original model fit object if supplied, and the coefficients and covariance matrix used to sample.

\begin{verbatim}
set.seed(1234)

# Drawing 1000 simulated coefficients using an HC2 robust
# covariance matrix
s <- sim(fit, n = 1000,
         vcov = "HC2")

s
\end{verbatim}

\begin{verbatim}
#> A `clarify_sim` object
#>  - 11 coefficients, 1000 simulated values
#>  - sampled distribution: multivariate normal
#>  - original fitting function call:
#> 
#> glm(formula = re78_0 ~ treat * married + age + educ + race + 
#>     nodegree + re74 + re75, family = binomial("probit"), data = lalonde)
\end{verbatim}

\hypertarget{computing-derived-quantities}{%
\subsubsection{3. Computing derived quantities}\label{computing-derived-quantities}}

After sampling the coefficients, we will compute derived quantities on each set of sampled coefficients and store the result, which represents the ``posterior'' distribution of the derived quantity, as well as on the original coefficients, which are used as the final estimates. The core functionality is provided by \texttt{sim\_apply()}, which accepts a \texttt{clarify\_sim} object from \texttt{sim()} and a function to compute and return one or more derived quantities, then applies that function to each set of simulated coefficients. The arguments to \texttt{sim\_apply()} are below:

\begin{verbatim}
sim_apply(sim = , FUN = , verbose = , cl = , ...)
\end{verbatim}

\begin{itemize}
\item
  \texttt{sim} -- a \texttt{clarify\_sim} object; the output of a call to \texttt{sim()}.
\item
  \texttt{FUN} -- a function that takes in either a model fit object or a vector of coefficients and returns one or more derived quantities. The first argument should be named \texttt{fit} to take in a model fit object or \texttt{coefs} to take in coefficients.
\item
  \texttt{verbose} -- whether to display a progress bar.
\item
  \texttt{cl} -- an argument that controls parallel processing, which can be the number of cores to use or a cluster object resulting from \texttt{parallel::makeCluster()}.
\item
  \texttt{...} - further arguments to \texttt{FUN}.
\end{itemize}

The \texttt{FUN} argument can be specified in one of two ways: either as a function that takes in a model fit object (e.g., a \texttt{glm} or \texttt{lm} object, the output of a call to \texttt{glm()} or \texttt{lm()}) or a function that takes in a vector of coefficients. The latter will always work but the former only works for supported models. When the function takes in a model fit object, \texttt{sim\_apply()} will first insert each set of sampled coefficients into the model fit object and then supply the modified model to \texttt{FUN}.

For example, let's say our derived quantity of interest is the predicted probability of the outcome for participant PSID1. We would specified our \texttt{FUN} function as follows:

\begin{verbatim}
sim_fun1 <- function(fit) {
  predict(fit, newdata = lalonde["PSID1",], type = "response")
}
\end{verbatim}

The \texttt{fit} object supplied to this function will be one in which the coefficients have been set to their values in a draw from their sampling distribution as generated by \texttt{sim()}. We then supply the function to \texttt{sim\_apply()} to simulate the sampling distribution of the predicted value of interest:

\begin{verbatim}
est1 <- sim_apply(s, FUN = sim_fun1, verbose = FALSE)

est1
\end{verbatim}

\begin{verbatim}
#> A `clarify_est` object (from `sim_apply()`)
#>  - 1000 simulated values
#>  - 1 quantity estimated:                
#>  PSID1 0.9757211
\end{verbatim}

The resulting \texttt{clarify\_est} object contains the simulated estimates in matrix form as well as the estimate computed on the original coefficients. We'll examine the sampling distribution shortly, but first we'll demonstrate computing a derived quantity from the coefficients directly.

The \texttt{race} variable is a factor, and the \texttt{black} category is used as the reference level, so it is not immediately clear whether there is a difference between the coefficients \texttt{racehispan} and \texttt{racewhite}, which represent the non-reference categories \texttt{hispan} and \texttt{white}. To compare these two directly, we can use \texttt{sim\_apply()} to compute a derived quantity that corresponds to the difference between them.

\begin{verbatim}
sim_fun2 <- function(coefs) {
  hispan <- unname(coefs["racehispan"])
  white <- unname(coefs["racewhite"])

  c("w - h" = white - hispan)
}

est2 <- sim_apply(s, FUN = sim_fun2, verbose = FALSE)

est2
\end{verbatim}

\begin{verbatim}
#> A `clarify_est` object (from `sim_apply()`)
#>  - 1000 simulated values
#>  - 1 quantity estimated:                  
#>  w - h -0.09955915
\end{verbatim}

The function supplied to \texttt{FUN} can be arbitrarily complicated and return as many derived quantities as one wants, though the slower each run of \texttt{FUN} is, the longer it will take to simulate the derived quantities. Using parallel processing by supplying an argument to \texttt{cl} can sometimes dramatically speed up evaluation.

There are several functions in \pkg{clarify} that serve as convenience wrappers for \texttt{sim\_apply()} to automate some common derived quantities of interest. These include

\begin{itemize}
\item
  \texttt{sim\_setx()} -- computing predicted values and first differences at representative or user-specified values of the predictors
\item
  \texttt{sim\_ame()} -- computing average adjusted predictions, contrasts of average adjusted predictions, and average marginal effects
\item
  \texttt{sim\_adrf()} -- computing average dose-response functions and average marginal effects functions
\end{itemize}

These are described in their own sections below. In addition, there are functions that have methods for \texttt{clarify\_est} objects, including \texttt{cbind()} for combining two \texttt{clarify\_est} objects together and \texttt{transform()} for computing quantities that are derived from the already-computed derived quantities. These are also described in their own sections below.

\hypertarget{summarize-and-visualize-the-simulated-distribution}{%
\subsubsection{4. Summarize and visualize the simulated distribution}\label{summarize-and-visualize-the-simulated-distribution}}

To examine the uncertainty around and perform inference on our estimated quantities, we can use \texttt{plot()} and \texttt{summary()} on the \texttt{clarify\_est} object.

\texttt{plot()} displays a density plot of the resulting estimates across the simulations, with markers identifying the point estimate (computed using the original model coefficients as recommended by Rainey (2023)) and, optionally, uncertainty bounds (which function like confidence or credible interval bounds). The arguments to \texttt{plot()} are below:

\begin{verbatim}
plot(x = , parm = , ci = , level = , method = , reference =)
\end{verbatim}

\begin{itemize}
\item
  \texttt{x} -- the \texttt{clarify\_est} object (the output of a call to \texttt{sim\_apply()}).
\item
  \texttt{parm} -- the names or indices of the quantities to be plotted if more than one was estimated in \texttt{sim\_apply()}; if unspecified, all will be plotted.
\item
  \texttt{ci} -- whether to display lines at the uncertainty bounds. The default is \texttt{TRUE} to display them.
\item
  \texttt{level} -- if \texttt{ci} is \texttt{TRUE}, the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when \texttt{method} (see below) is \texttt{"quantile"}.
\item
  \texttt{method} -- if \texttt{ci} is \texttt{TRUE}, the method used to compute the bounds. Allowable methods include a Normal approximation (\texttt{"wald"}) or using the quantiles of the resulting distribution (\texttt{"quantile"}). The Normal approximation involves multiplying the standard deviation of the estimates (i.e., which functions like the standard error of the sampling distribution) by the critical Z-statistic computed using \texttt{(1-level)/2} to create a symmetric margin of error around the point estimate. The default is \texttt{"quantile"} to instead use quantile-based bounds, which are more appropriate when the distribution is non-Normal. However, quantile-based bounds may require more simulations to stabilize.
\item
  \texttt{reference} -- whether to display a normal density over the plot for each estimate. The default is \texttt{FALSE} to omit them.
\end{itemize}

Below, we plot the first estimate we computed above, the predicted probability for participant PSID1:

\begin{verbatim}
plot(est1, reference = TRUE, ci = FALSE)
\end{verbatim}

\begin{center}\includegraphics{figures/unnamed-chunk-8-1} \end{center}

From the plot, one can see that the distribution of simulated values is non-Normal, asymmetrical, and not centered around the estimate, with no values falling above 1 because the outcome is a predicted probability. Given its non-Normality, the quantile-based bounds are clearly more appropriate than those resulting from the Normal approximation, as the bounds computed from the Normal approximation would be outside the bounds of the estimate. The plot itself is a \texttt{ggplot} object that can be modified using \texttt{ggplot2} syntax.

We can use \texttt{summary()} to display the value of the point estimate, the uncertainty bounds, and other statistics that describe the distribution of estimates. The arguments to \texttt{summary()} are below:

\begin{verbatim}
summary(object = , parm = , level = , method = , null = )
\end{verbatim}

\begin{itemize}
\item
  \texttt{object} -- the \texttt{clarify\_est} object (the output of a call to \texttt{sim\_apply()}).
\item
  \texttt{parm} -- the names or indices of the quantities to be displayed if more than one was estimated in \texttt{sim\_apply()}; if unspecified, all will be displayed.
\item
  \texttt{level} -- the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when method (see below) is \texttt{"quantile"}.
\item
  \texttt{method} -- the method used to compute the uncertainty bounds. Allowable methods include a Normal approximation (\texttt{"wald"}) or using the quantiles of the resulting distribution (\texttt{"quantile"}). See \texttt{plot()} above.
\item
  \texttt{null} -- an optional argument specifying the null value in a hypothesis test for the estimates. If specified, a p-value will be computed using either a standard Z-test (if \texttt{method} is \texttt{"wald"}) or an inversion of the uncertainty interval (described below). The default is not to display any p-values.
\end{itemize}

Inverting the uncertainty interval involves finding the smallest confidence level such that the null value is within the confidence bounds. The p-value for the test is one minus this level. It is only valid as a p-value when the simulated distribution of the estimates differs from its true sampling distribution under the null value by a location shift (which can be violated when the distribution of the estimates is asymmetric). However, because the p-values are invariant to monotonic transformations of the estimates and null value, as long as the distribution of \emph{some} monotonic transformation of the estimate is a location shift from its sampling distribution under the null hypothesis, the p-values will be valid.

We'll use \texttt{summary()} with the default arguments on our first \texttt{clarify\_est} object to view the point estimate and quantile-based uncertainty bounds.

\begin{verbatim}
summary(est1)
\end{verbatim}

\begin{verbatim}
#>       Estimate 2.5 % 97.5 %
#> PSID1    0.976 0.891  0.996
\end{verbatim}

A benefit of quantile-based confidence bounds is that the bounds will always be in the domain of the quantity of interest, e.g., bounds for probabilities will not be above 1 or below 0 if the model always generates predicted probabilities between 0 and 1. In contrast, Wald-type symmetric confidence intervals can include values outside the domain of the quantity of interest. While it is possible to compute Wald-type confidence interval bounds that respect the domain boundaries, e.g., by computing the confidence interval around the logit of the predicted probability and using the inverse logit of the bounds as the bound on the probability, quantile confidence intervals do not require the user to know which transformation of the quantity of interest will yield appropriate bounds.

Our second estimated quantity, the difference between two regression coefficients, is closer to Normally distributed, as the plot below demonstrates (and would be expected theoretically), so we'll use the Normal approximation to test the hypothesis that difference differs from 0.

\begin{verbatim}
plot(est2, reference = TRUE, ci = FALSE)
\end{verbatim}

\begin{center}\includegraphics{figures/unnamed-chunk-10-1} \end{center}

\begin{verbatim}
summary(est2, method = "wald", null = 0)
\end{verbatim}

\begin{verbatim}
#>       Estimate   2.5 %  97.5 % Std. Error Z value P-value
#> w - h  -0.0996 -0.5352  0.3361     0.2223   -0.45    0.65
\end{verbatim}

The uncertainty intervals and p-values in the \texttt{summary()} output are computed using the Normal approximation because we set \texttt{method\ =\ "wald"}, and the p-value for the test that our estimate is equal to 0 is returned because we set \texttt{null\ =\ 0}. Note that the Normal approximation should be used only when the simulated sampling distribution is both close to Normally distributed and centered around the estimate (i.e., when the mean of the simulated values {[}red vertical line{]} coincides with the estimate computed on the original coefficients {[}black vertical line{]}).

\hypertarget{sim_apply-wrappers-sim_setx-sim_ame-sim_adrf}{%
\subsection{\texorpdfstring{\texttt{sim\_apply()} wrappers: \texttt{sim\_setx()}, \texttt{sim\_ame()}, \texttt{sim\_adrf()}}{sim\_apply() wrappers: sim\_setx(), sim\_ame(), sim\_adrf()}}\label{sim_apply-wrappers-sim_setx-sim_ame-sim_adrf}}

\texttt{sim\_apply()} can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \pkg{clarify} provides shortcut functions to make computing these quantities simple. These functions include \texttt{sim\_setx()}, \texttt{sim\_ame()}, and \texttt{sim\_adrf()}. Each of these can be used only when regression models compatible with \pkg{clarify} are supplied to the original call to \texttt{sim()}.

Like \texttt{sim\_apply()}, each of these functions is named \texttt{sim\_*()}, which signifies that they are to be used on an object produced by \texttt{sim()} (i.e., a \texttt{clarify\_sim} object). (Multiple calls to these functions can be applied to the same \texttt{clarify\_sim} object and combined; see the \texttt{cbind()} section below.) These functions are described below.

\hypertarget{sim_setx-predictions-at-representative-values}{%
\subsubsection{\texorpdfstring{\texttt{sim\_setx()}: predictions at representative values}{sim\_setx(): predictions at representative values}}\label{sim_setx-predictions-at-representative-values}}

\texttt{sim\_setx()} provides an interface to compute predictions at representative and user-supplied values of the predictors. For example, we might want to know what the effect of treatment is for a ``typical'' individual, which corresponds to the contrast between two model-based predictions (i.e., one under treatment and one under control for a unit with ``typical'' covariate values). This functionality mirrors the \texttt{setx()} and \texttt{setx1()} functionality of \texttt{Zelig} (which is where its name originates) and provides similar functionality to functions in \pkg{modelbased}, \pkg{emmeans}, \pkg{effects}, and \pkg{ggeffects}.

For each predictor, the user can specify whether they want predictions at specific values or at ``typical'' values, which are defined in \pkg{clarify} as the mode for unordered categorical and binary variables, the median for ordered categorical variables, and the mean for continuous variables. Predictions for multiple predictor combinations can be requested by specifying values that will be used to create a grid of predictor values, or the grid itself can be supplied as a data frame of desired predictor profiles. In addition, the ``first difference'', defined here as the difference between predictions for two predictor combinations, can be computed.

The arguments to \texttt{sim\_setx()} are as follows:

\begin{verbatim}
sim_setx(sim = , x = , x1 = , outcome = , type = , verbose = , cl = )
\end{verbatim}

\begin{itemize}
\item
  \texttt{sim} -- a \texttt{clarify\_sim} object; the output of a call to \texttt{sim()}.
\item
  \texttt{x} -- a named list containing the requested values of the predictors, e.g., \texttt{list(v1\ =\ 1:4,\ v2\ =\ "A")}, or a data frame containing the desired profiles. Any predictors not included will be set at their ``typical'' value as defined above.
\item
  \texttt{x1} -- an optional named list or data frame similar to \texttt{x} except with the value of one predictor changed. When specified, the first difference is computed between the covariate combination defined in \texttt{x} (and only one combination is allowed when \texttt{x1} is specified) and the covariate combination defined in \texttt{x1}.
\item
  \texttt{outcome} -- a string containing the name of the outcome of interest when a multivariate (multiple outcome) model is supplied to \texttt{sim()} or the outcome category of interest when a multinomial model is supplied to \texttt{sim()}. For univariate (single outcome) and binary outcomes, this is ignored.
\item
  \texttt{type} -- a string containing the type of predicted value to return. In most cases, this can be left unspecified to request predictions on the scale of the outcome.
\item
  \texttt{verbose} -- whether to display a progress bar.
\item
  \texttt{cl} -- an argument that controls parallel processing, which can be the number of cores to use or a cluster object resulting from \texttt{parallel::makeCluster()}.
\end{itemize}

Here, we'll use \texttt{sim\_setx()} to examine predicted values of the outcome for control and treated units, at \texttt{re75} set to 0 and 20000, and \texttt{race} set to ``black''.

\begin{verbatim}
est3 <- sim_setx(s,
                 x = list(treat = 0:1,
                          re75 = c(0, 20000),
                          race = "black"),
                 verbose = FALSE)
\end{verbatim}

When we use \texttt{summary()} on the resulting output, we can see the estimates and their uncertainty intervals (calculated using quantiles by default).

\begin{verbatim}
summary(est3)
\end{verbatim}

\begin{verbatim}
#>                         Estimate 2.5 % 97.5 %
#> treat = 0, re75 = 0        0.667 0.558  0.771
#> treat = 1, re75 = 0        0.712 0.618  0.790
#> treat = 0, re75 = 20000    0.938 0.701  0.993
#> treat = 1, re75 = 20000    0.953 0.751  0.996
\end{verbatim}

To see the complete grid of the predictor values used in the predictions, which helps to identify the ``typical'' values of the other predictors, we can access the \texttt{"setx"} attribute of the object:

\begin{verbatim}
attr(est3, "setx")
\end{verbatim}

\begin{verbatim}
#>                         treat married      age     educ  race nodegree     re74
#> treat = 0, re75 = 0         0       0 27.36319 10.26873 black        1 4557.547
#> treat = 1, re75 = 0         1       0 27.36319 10.26873 black        1 4557.547
#> treat = 0, re75 = 20000     0       0 27.36319 10.26873 black        1 4557.547
#> treat = 1, re75 = 20000     1       0 27.36319 10.26873 black        1 4557.547
#>                          re75
#> treat = 0, re75 = 0         0
#> treat = 1, re75 = 0         0
#> treat = 0, re75 = 20000 20000
#> treat = 1, re75 = 20000 20000
\end{verbatim}

We can plot the distributions of the simulated values using \texttt{plot()}, which also separates the predictions by the predictor values (it's often clearer without the uncertainty bounds). The \texttt{var} argument controls which variable is used for faceting the plots.

\begin{verbatim}
plot(est3, var = "re75", ci = FALSE)
\end{verbatim}

\begin{center}\includegraphics{figures/unnamed-chunk-14-1} \end{center}

One can see again how a delta method or Normal approximation may not have yielded valid uncertainty intervals given the non-Normality of the distributions.

If a continuous variable with many levels is included in the grid of the predictors, something like a dose-response function for a typical unit can be generated. Below, we set \texttt{re75} to vary from 0 to 20000 in steps of 2000.

\begin{verbatim}
est4 <- sim_setx(s,
                 x = list(treat = 0:1,
                          re75 = seq(0, 20000, by = 2000),
                          race = "black"),
                 verbose = FALSE)
\end{verbatim}

When we plot the output, we can see how the predictions varies across the levels of \texttt{re75}:

\begin{verbatim}
plot(est4)
\end{verbatim}

\begin{center}\includegraphics{figures/unnamed-chunk-16-1} \end{center}

We'll return to display average dose-response functions using \texttt{sim\_adrf()} later.

Finally, we can use \texttt{sim\_setx()} to compute first differences, the contrast between two covariate combinations. We supply one covariate profile to \texttt{x} and another to \texttt{x1}, and \texttt{sim\_setx()} simulates the two predicted values and their difference. Below, we simulate first difference for a treated and control unit who have \texttt{re75} of 0 and typical values of all other covariates:

\begin{verbatim}
est5 <- sim_setx(s,
                 x = list(treat = 0, re75 = 0),
                 x1 = list(treat = 1, re75 = 0),
                 verbose = FALSE)
\end{verbatim}

When we use \texttt{summary()}, we see the estimates for the predicted values and their first difference (``FD''):

\begin{verbatim}
summary(est5)
\end{verbatim}

\begin{verbatim}
#>           Estimate   2.5 %  97.5 %
#> treat = 0   0.7856  0.7041  0.8557
#> treat = 1   0.8213  0.7114  0.8989
#> FD          0.0357 -0.0592  0.1187
\end{verbatim}

It is possible to compute first differences without using \texttt{x1} using \texttt{transform()}, which we describe later.

\hypertarget{sim_ame-average-adjusted-predictions-and-average-marginal-effects}{%
\subsubsection{\texorpdfstring{\texttt{sim\_ame()}: average adjusted predictions and average marginal effects}{sim\_ame(): average adjusted predictions and average marginal effects}}\label{sim_ame-average-adjusted-predictions-and-average-marginal-effects}}

Using predicted values and effects at representative values is one way to summarize regression models, but another way is to compute average adjusted predictions (AAPs), contrasts of AAPs, and average marginal effects (AMEs). The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units\footnote{In \pkg{marginaleffects}, AAPs are computed using \texttt{avg\_predictions()}, AMEs for binary variables are computed using \texttt{avg\_comparisons()}, and AMEs for continuous variables are computed using \texttt{avg\_slopes()}. AAPs are sometimes known as average ``counterfactual'' predictions.}.

The arguments to \texttt{sim\_ame()} are as follows:

\begin{verbatim}
sim_ame(sim = , var = , subset = , by = , contrast = , outcome = ,
        type = , eps = , verbose = , cl = )
\end{verbatim}

\begin{itemize}
\item
  \texttt{sim} -- a \texttt{clarify\_sim} object; the output of a call to \texttt{sim()}.
\item
  \texttt{var} -- the name of focal variable over which to compute the AAPs or AMEs, or a list containing the values for which AAPs should be computed.
\item
  \texttt{subset} -- a logical vector, evaluated in the original dataset used to fit the model, defining a subset of units for which the AAPs or AMEs are to be computed.
\item
  \texttt{by} -- the name of one or more variables for which AAPs should be computed within subgroups. Can be supplied as a character vector of variable names or a one-sided formula.
\item
  \texttt{contrast} -- the name of an effect measure used to contrast AAPs. For continuous outcomes, \texttt{"diff"} requests the difference in means, but others are available for binary outcomes, including \texttt{"rr"} for the risk ratio, \texttt{"or"} for the odds ratio, and \texttt{"nnt"} for the number needed to treat, among others. If not specified, only AAPs will be computed if the variable named in \texttt{var} is categorical or specific values of the focal variable are specified in \texttt{var}. Ignored when the variable named in \texttt{var} is continuous and no specific values are specified because the AME is the only quantity computed. When \texttt{var} names a multi-category categorical variable, \texttt{contrast} cannot be used; see the section describing \texttt{transform()} for computing contrasts with them.
\item
  \texttt{outcome} -- a string containing the name of the outcome of interest when a multivariate (multiple outcome) model is supplied to \texttt{sim()} or the outcome category of interest when a multinomial model is supplied to \texttt{sim()}. For univariate (single outcome) and binary outcomes, this is ignored.
\item
  \texttt{type} -- a string containing the type of predicted value to return. In most cases, this can be left unspecified to request predictions on the scale of the outcome (e.g., probabilities for binary outcomes).
\item
  \texttt{eps} -- the value by which the observed values of the variable named in \texttt{var} are changed when it is continuous to compute the AME. This usually does not need to be specified.
\item
  \texttt{verbose} -- whether to display a progress bar.
\item
  \texttt{cl} -- an argument that controls parallel processing, which can be the number of cores to use or a cluster object resulting from \texttt{parallel::makeCluster()}.
\end{itemize}

Here, we'll use \texttt{sim\_ame()} to compute the AME of \texttt{treat} just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT (Greifer and Stuart 2023)). We'll request our estimate to be on the risk ratio scale.

\begin{verbatim}
est6 <- sim_ame(s,
                var = "treat",
                subset = treat == 1,
                contrast = "rr",
                verbose = FALSE)
\end{verbatim}

We can use \texttt{summary()} to display the estimates and their uncertainty intervals. Here, we'll also use \texttt{null} to include a test for the null hypothesis that the risk ratio is equal to 1.

\begin{verbatim}
summary(est6, null = c(`RR` = 1))
\end{verbatim}

\begin{verbatim}
#>         Estimate 2.5 % 97.5 % P-value
#> E[Y(0)]    0.687 0.610  0.759       .
#> E[Y(1)]    0.755 0.686  0.808       .
#> RR         1.100 0.949  1.255    0.21
\end{verbatim}

Here we see the estimates for the AAPs, \texttt{E{[}Y(0){]}} for the expected value of the outcome setting \texttt{treat} to 0 and \texttt{E{[}Y(1){]}} for the expected value of the outcome setting \texttt{treat} to 1, and the risk ratio \texttt{RR}. The p-value on the test for the risk ratio aligns with the uncertainty interval containing 1.

If we instead wanted the risk difference or odds ratio, we would not have to re-compute the AAPs. Instead, we can use \texttt{transform()} to compute a new derived quantity from the computed AAPs. The section on \texttt{transform()} demonstrates this.

We can compute the AME for a continuous predictor. Here, we'll consider \texttt{age} (just for demonstration; this analysis does not have a valid interpretation).

\begin{verbatim}
est7 <- sim_ame(s,
                var = "age",
                verbose = FALSE)
\end{verbatim}

We can use \texttt{summary()} to display the AME estimate and its uncertainty interval.

\begin{verbatim}
summary(est7)
\end{verbatim}

\begin{verbatim}
#>              Estimate    2.5 %   97.5 %
#> E[dY/d(age)] -0.00605 -0.00940 -0.00259
\end{verbatim}

The AME is named \texttt{E{[}dY/d(age){]}}, which signifies that a derivative has been computed (more precisely, the average of the unit-specific derivatives). This estimate can be interpreted like a slope in a linear regression model, but as a single summary of the effect of a predictor it is often too coarse to capture nonlinear relationships. The section below explains how to compute average dose-response functions for continuous predictors, which provide a more complete picture of their effects on an outcome.

Below, we'll examine effect modification of the ATT by the predictor \texttt{married} using the \texttt{by} argument to estimate AAPs and their ratio within levels of \texttt{married}:

\begin{verbatim}
est6b <- sim_ame(s,
                 var = "treat",
                 subset = treat == 1,
                 by = ~married,
                 contrast = "rr",
                 verbose = FALSE)

summary(est6b)
\end{verbatim}

\begin{verbatim}
#>           Estimate 2.5 % 97.5 %
#> E[Y(0)|0]    0.691 0.613  0.768
#> E[Y(1)|0]    0.733 0.655  0.796
#> RR[0]        1.061 0.911  1.232
#> E[Y(0)|1]    0.668 0.556  0.768
#> E[Y(1)|1]    0.848 0.677  0.940
#> RR[1]        1.270 0.952  1.579
\end{verbatim}

The presence of effect modification can be tested by testing the contrast between the effects computed within each level of the \texttt{by} variable; this demonstrated in the section on \texttt{transform()} below.

\hypertarget{sim_adrf-average-dose-response-functions}{%
\subsubsection{\texorpdfstring{\texttt{sim\_adrf()}: average dose-response functions}{sim\_adrf(): average dose-response functions}}\label{sim_adrf-average-dose-response-functions}}

A dose-response function for an individual is the relationship between the set value of a continuous focal predictor and the expected outcome. The average dose-response function (ADRF) is the average of the dose-response functions across all units. Essentially, it is a function that relates the value of the predictor to the corresponding AAP of the outcome, the average value of the outcome were all units to be set to that level of the predictor. ADRFs can be used to provide additional detail about the effect of a continuous predictor beyond a single AME.

A related quantity is the average marginal effect function (AMEF), which describes the relationship between a continuous focal predictor and the AME at that level of the predictor. That is, rather than describing how the outcome changes as a function of the predictor, it describes how the \emph{effect} of the predictor on the outcome changes as a function of the predictor. It is essentially the derivative of the ADRF and can be used to identify at which points along the ADRF the predictor has an effect.

The ADRF and AMEF can be computed using \texttt{sim\_adrf()}. The arguments are below:

\begin{verbatim}
sim_adrf(sim = , var = , subset = , by = , contrast = , at = ,
         n = , outcome = , type = , eps = , verbose = , cl = )
\end{verbatim}

\begin{itemize}
\item
  \texttt{sim} -- a \texttt{clarify\_sim} object; the output of a call to \texttt{sim()}.
\item
  \texttt{var} -- the name of focal variable over which to compute the ADRF or AMEF.
\item
  \texttt{subset} -- a logical vector, evaluated in the original dataset used to fit the model, defining a subset of units for which the ARDF or AMEF is to be computed.
\item
  \texttt{by} -- the name of one or more variables for which the ADRF or AMEF should be computed within subgroups. Can be supplied as a character vector of variable names or a one-sided formula.
\item
  \texttt{contrast} -- either \texttt{"adrf"} or \texttt{"amef"} to request the ADRF or AMEF, respectively. The default is to compute the ADRF.
\item
  \texttt{at} -- the values of the focal predictor at which to compute the ADRF or AMEF. This should be a vector of values that the focal predictor can take on. If unspecified, a vector of \texttt{n} (see below) equally-spaced values from the minimum to the maximum value of the predictor will be used. This should typically be used only if quantities are desired over a subset of the values of the focal predictor.
\item
  \texttt{n} -- if \texttt{at} is unspecified, the number of points along the range of the focal predictor at which to compute the ADRF or AMEF. More yields smoother functions, but will take longer and require more memory. The default is 21.
\item
  \texttt{outcome} -- a string containing the name of the outcome of interest when a multivariate (multiple outcome) model is supplied to \texttt{sim()} or the outcome category of interest when a multinomial model is supplied to \texttt{sim()}. For univariate (single outcome) and binary outcomes, this is ignored.
\item
  \texttt{type} -- a string containing the type of predicted value to return. In most cases, this can be left unspecified to request predictions on the scale of the outcome.
\item
  \texttt{eps} -- the value by which the observed values of the variable named in \texttt{var} are changed when it is continuous to compute the AMEF. This usually does not need to be specified.
\item
  \texttt{verbose} -- whether to display a progress bar.
\item
  \texttt{cl} -- an argument that controls parallel processing, which can be the number of cores to use or a cluster object resulting from \texttt{parallel::makeCluster()}.
\end{itemize}

Here, we'll consider \texttt{age} (just for demonstration; this analysis does not have a valid interpretation) and compute the ADRF and AMEF of \texttt{age} on the outcome. We'll only examine ages between 18 and 50, even though the range of \texttt{age} goes slightly beyond these values. First, we'll compute the ADRF of \texttt{age}, which examines how the outcome would vary on average if one set all unit's value of \texttt{age} to each value between 18 and 50 (here we only use even ages to speed up computation).

\begin{verbatim}
age_seq <- seq(18, 50, by = 2)

est8 <- sim_adrf(s,
                 var = "age",
                 contrast = "adrf",
                 at = age_seq,
                 verbose = FALSE)
\end{verbatim}

We can plot the ADRF using \texttt{plot()}.

\begin{verbatim}
plot(est8)
\end{verbatim}

\begin{center}\includegraphics{figures/unnamed-chunk-25-1} \end{center}

From the plot, we can see that as \texttt{age} increases, the expected outcome decreases.

We can also examine the AAPs at the requested ages using \texttt{summary()}, which will display all the estimated AAPs by default, so we will request just the first 4 (\texttt{age}s 18 to 24):

\begin{verbatim}
summary(est8, parm = 1:4)
\end{verbatim}

\begin{verbatim}
#>          Estimate 2.5 % 97.5 %
#> E[Y(18)]    0.821 0.771  0.858
#> E[Y(20)]    0.811 0.764  0.845
#> E[Y(22)]    0.800 0.757  0.831
#> E[Y(24)]    0.788 0.749  0.817
\end{verbatim}

Next we'll compute the AMEF, the effect of \texttt{age} at each level of \texttt{age}.

\begin{verbatim}
est9 <- sim_adrf(s,
                 var = "age",
                 contrast = "amef",
                 at = age_seq,
                 verbose = FALSE)
\end{verbatim}

We can plot the AMEF using \texttt{plot()}:

\begin{verbatim}
plot(est9)
\end{verbatim}

\begin{center}\includegraphics{figures/unnamed-chunk-28-1} \end{center}

From the plot, we can see the AME of \texttt{age} decreases slightly but is mostly constant across values of \texttt{age}, and the uncertainty intervals for the AMEs consistently exclude 0.

\hypertarget{transforming-and-combining-estimates}{%
\subsection{Transforming and combining estimates}\label{transforming-and-combining-estimates}}

Often, our quantities of interest are not just the outputs of the functions above, but comparisons between them. For example, to test for moderation of a treatment effect, we may want to compare AMEs in multiple groups defined by the moderator. Or, it might be that we are interested in an effect described using a different effect measure than the one originally produced; for example, we may decide we want the risk difference AME after computing the risk ratio AME. The functions \texttt{transform()} and \texttt{cbind()} allow users to transform quantities in a single \texttt{clarify\_est} object and combine two \texttt{clarify\_est} objects. These are essential for computing quantities that themselves are derived from the derived quantities computed by the \texttt{sim\_*()} functions.

\hypertarget{transform}{%
\subsubsection{\texorpdfstring{\texttt{transform()}}{transform()}}\label{transform}}

\texttt{transform()} is a generic function in R that is typically used to create a new variable in a data frame that is a function of other columns. For example, to compute the binary outcome we used in our model, we could have run the following\footnote{Users familiar with the \texttt{tidyverse} will note the similarities between \texttt{transform()} and \texttt{dplyr::mutate()}; only \texttt{transform()} can be used with \texttt{clarify\_est} objects.}:

\begin{verbatim}
lalonde <- transform(lalonde,
                     re78_0 = ifelse(re78 == 0, 1, 0))
\end{verbatim}

Similarly, to compute a derived or transformed quantity from a \texttt{clarify\_est} object, we can use \texttt{transform()}. Here, we'll compute the risk difference AME of \texttt{treat}; previously, we used \texttt{sim\_ame()} to compute the AAPs and the risk ratio.

\begin{verbatim}
est6 <- transform(est6,
                  RD = `E[Y(1)]` - `E[Y(0)]`)
\end{verbatim}

Note that we used tics (`) around the names of the AAPs; this is necessary when they contain special characters like parentheses or brackets.

When we run \texttt{summary()} on the output, the new quantity, which we named ``RD'', will be displayed along with the other estimates. We'll also set a null value for this quantity.

\begin{verbatim}
summary(est6, null = c(`RR` = 1, `RD` = 0))
\end{verbatim}

\begin{verbatim}
#>         Estimate   2.5 %  97.5 % P-value
#> E[Y(0)]   0.6866  0.6095  0.7590       .
#> E[Y(1)]   0.7551  0.6859  0.8081       .
#> RR        1.0998  0.9492  1.2553    0.21
#> RD        0.0685 -0.0380  0.1574    0.21
\end{verbatim}

One benefit of using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.

The same value would be computed if we were to have called \texttt{sim\_ame()} on the same \texttt{clarify\_sim} object and requested the risk difference using \texttt{contrast\ =\ "diff"}; using \texttt{transform()} saves time because the AAPs are already computed and stored in the \texttt{clarify\_est} object.

We can use \texttt{transform()} along with the \texttt{by} variable in \texttt{sim\_ame()} to compute the contrast between quantities computed within each subgroup of \texttt{married}. Previously we used \texttt{by} to compute the risk ratio ATT within levels of \texttt{married}; here we will compute the ratio of these risk ratios to assess the presence of effect modification.

\begin{verbatim}
est6b |>
  transform(RR_ratio = `RR[1]` / `RR[0]`) |>
  summary(parm = c("RR[0]", "RR[1]", "RR_ratio"),
          null = 1)
\end{verbatim}

\begin{verbatim}
#>          Estimate 2.5 % 97.5 % P-value  
#> RR[0]       1.061 0.911  1.232   0.434  
#> RR[1]       1.270 0.952  1.579   0.094 .
#> RR_ratio    1.196 0.910  1.514   0.174  
#> ---
#> Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\texttt{RR\_ratio} contains the ratio of the risk ratios for \texttt{married\ =\ 1} and \texttt{married\ =\ 0}. Here we also include a test for whether each of the risk ratios and their ratio differ from 1.

\hypertarget{cbind}{%
\subsubsection{\texorpdfstring{\texttt{cbind()}}{cbind()}}\label{cbind}}

\texttt{cbind()} is another generic R function that is typically used to combine two or more datasets columnwise (i.e., to widen a dataset). In \pkg{clarify}, \texttt{cbind()} can be used to combine two \texttt{clarify\_est} objects so that the estimates can be examined jointly and so that it is possible to compare them directly. For example, let's say we computed AMEs in two subgroups using \texttt{subset} and wanted to compare them. To do so, we call \texttt{sim\_ame()} twice, one for each subset (though in practice it is more effective to use \texttt{by}; this is just for illustration):

\begin{verbatim}
# AME of treat with race = "black"
est10b <- sim_ame(s, var = "treat", subset = race == "black",
                  contrast = "diff", verbose = FALSE)
summary(est10b)
\end{verbatim}

\begin{verbatim}
#>         Estimate   2.5 %  97.5 %
#> E[Y(0)]   0.6677  0.5814  0.7527
#> E[Y(1)]   0.7439  0.6663  0.8007
#> Diff      0.0762 -0.0353  0.1694
\end{verbatim}

\begin{verbatim}
# AME of treat with race = "hispan"
est10h <- sim_ame(s, var = "treat", subset = race == "hispan",
                  contrast = "diff", verbose = FALSE)
summary(est10h)
\end{verbatim}

\begin{verbatim}
#>         Estimate   2.5 %  97.5 %
#> E[Y(0)]   0.8266  0.7154  0.8972
#> E[Y(1)]   0.8971  0.7892  0.9526
#> Diff      0.0704 -0.0215  0.1382
\end{verbatim}

Here, we computed the risk difference for the subgroups \texttt{race\ =\ "black"} and \texttt{race\ =\ "hispan"}. If we wanted to compare the risk differences, we could combine them and compute a new quantity equal to their difference. We'll do that below.

First, we need to rename to quantities in each object so they don't overlap; we can do so using \texttt{names()}, which has a special method for \texttt{clarify\_est} objects.

\begin{verbatim}
names(est10b) <- paste(names(est10b), "b", sep = "_")
names(est10h) <- paste(names(est10h), "h", sep = "_")
\end{verbatim}

Next, we use \texttt{cbind()} to bind the objects together.

\begin{verbatim}
est10 <- cbind(est10b, est10h)
summary(est10)
\end{verbatim}

\begin{verbatim}
#>           Estimate   2.5 %  97.5 %
#> E[Y(0)]_b   0.6677  0.5814  0.7527
#> E[Y(1)]_b   0.7439  0.6663  0.8007
#> Diff_b      0.0762 -0.0353  0.1694
#> E[Y(0)]_h   0.8266  0.7154  0.8972
#> E[Y(1)]_h   0.8971  0.7892  0.9526
#> Diff_h      0.0704 -0.0215  0.1382
\end{verbatim}

Finally, we can use \texttt{transform()} to compute the difference between the risk differences:

\begin{verbatim}
est10 <- transform(est10,
                   `Dh - Db` = Diff_h - Diff_b)
summary(est10, parm = "Dh - Db")
\end{verbatim}

\begin{verbatim}
#>         Estimate    2.5 %   97.5 %
#> Dh - Db -0.00575 -0.06788  0.04102
\end{verbatim}

Importantly, \texttt{cbind()} can only be used to join together \texttt{clarify\_est} objects computed using the same simulated coefficients (i.e., resulting from the same call to \texttt{sim()}). This preserves the covariance among the estimated quantities, which is critical for valid inference. That is, \texttt{sim()} should only be called once per model, and all derived quantities should be computed using its output.

\hypertarget{using-with-multiply-imputed-data}{%
\subsection{\texorpdfstring{Using \pkg{clarify} with multiply imputed data}{Using  with multiply imputed data}}\label{using-with-multiply-imputed-data}}

Multiple imputation is a popular method of estimating quantities of interest in the presence of missing data and involves creating multiple versions of the original dataset each with the missing values imputed with estimates from an imputation model. Simulation-based inference in multiply imputed data is relatively straightforward. Simulated coefficients are drawn from the model estimated in each imputed dataset separately, and then the simulated coefficients are pooled into a single set of simulated coefficients. In Bayesian terms, this would be considered ``mixing draws'' and is the recommended approach for Bayesian analysis with multiply imputed data (Zhou and Reiter 2010).

Using \pkg{clarify} with multiply imputed data is simple. Rather than using \texttt{sim()}, we use the function \texttt{misim()}. \texttt{misim()} functions just like \texttt{sim()} except that it takes in a list of model fits (i.e., containing a model fit to each imputed dataset) or an object containing such a list (e.g., a \texttt{mira} object from \texttt{mice::with()} or a \texttt{mimira} object from \texttt{MatchThem::with()}). \texttt{misim()} simulates coefficient distributions within each imputed dataset and then appends them together to a form a single combined set of coefficient draws.

\texttt{sim\_apply()} and its wrappers accept the output of \texttt{misim()} and compute the desired quantity using each set of coefficients. When these function rely on using a dataset (e.g., \texttt{sim\_ame()}, which averages predicted outcomes across all units in the dataset used to fit the model), they automatically know to associate a given coefficient draw with the imputed dataset that was used to fit the model that produced that draw. In user-written functions supplied to the \texttt{FUN} argument of \texttt{sim\_apply()}, it is important to correctly extract the dataset from the model fit. This is demonstrated below.

The final estimates of the quantity of interest is computed as the mean of the estimates computed in each imputed dataset (i.e., using the original coefficients, not the simulated ones), which is the same quantity that would be computed using standard pooling rules. This is not always valid for noncollapsible estimates, like ratios, and so care should be taken to ensure the mean of the resulting estimates has a valid interpretation (this is related to the transformation-induced bias described by Rainey (2017)).

The arguments to \texttt{misim()} are as follows:

\begin{verbatim}
misim(fitlist = , n = , vcov = , coefs = , dist = )
\end{verbatim}

\begin{itemize}
\item
  \texttt{fitlist} -- a list of model fits or an accepted object containing them (e.g., a \texttt{mira} object from \texttt{mice::with()})
\item
  \texttt{n} -- the number of simulations to run \emph{for each imputed dataset}. The default is 1000, but fewer can be used because the total number of simulated quantities will be \texttt{m\ *\ n}, where \texttt{m} is the number of imputed datasets.
\item
  \texttt{vcov}, \texttt{coefs}, \texttt{dist} -- the same as with \texttt{sim()}, except that a list of such arguments can be supplied to be applied to each imputed dataset.
\end{itemize}

Below we illustrate using \texttt{misim()} and \texttt{sim\_apply()} with multiply imputed data. We'll use the \texttt{africa} dataset from the \pkg{Amelia} package.

\begin{verbatim}
library(Amelia)
data("africa", package = "Amelia")

# Multiple imputation
a.out <- amelia(x = africa, m = 10, cs = "country",
                ts = "year", logs = "gdp_pc", p2s = 0)

# Fit model to each dataset
model.list <- with(a.out, lm(gdp_pc ~ infl * trade))

# Simulate coefficients, 100 draws per imputation
si <- misim(model.list, n = 100)

si
\end{verbatim}

\begin{verbatim}
#> A `clarify_misim` object
#>  - 4 coefficients, 10 imputations with 100 simulated values each
#>  - sampled distributions: multivariate t(116)
\end{verbatim}

The function we'll be applying to each imputed dataset will be one that computes the average marginal effect of \texttt{infl}. (We'll run the same analysis afterward using \texttt{sim\_ame()}.)

\begin{verbatim}
sim_fun <- function(fit) {
  #Extract the original dataset using get_predictors()
  X <- insight::get_predictors(fit)

  p0 <- predict(fit)

  #Predictions after perturbing infl slightly
  p1 <- predict(fit, newdata = transform(X, infl = infl + 1e-5))

 c(AME = mean((p1 - p0) / 1e-5))
}

est_mi <- sim_apply(si, FUN = sim_fun, verbose = FALSE)

summary(est_mi)
\end{verbatim}

\begin{verbatim}
#>     Estimate 2.5 % 97.5 %
#> AME    -5.75 -8.82  -2.27
\end{verbatim}

Note that \texttt{sim\_apply()} ``knows'' which imputation produced each set of simulated coefficients, so using \texttt{insight::get\_predictors()} on the \texttt{fit} supplied to \texttt{sim\_fun()} will use the right dataset. Care should be taken when analyses restrict each imputed dataset in a different way (e.g.~when matching with a caliper in each one), as the resulting imputations may not refer to a specific target population and mixing the draws may be invalid.

Below, we can use \texttt{sim\_ame()}:

\begin{verbatim}
est_mi2 <- sim_ame(si, var = "infl", verbose = FALSE)

summary(est_mi2)
\end{verbatim}

\begin{verbatim}
#>               Estimate 2.5 % 97.5 %
#> E[dY/d(infl)]    -5.75 -8.82  -2.27
\end{verbatim}

We get the same results, as expected.

Note that \texttt{misim()} is compatible with model fit objects from \pkg{mice}, \pkg{Amelia}, \pkg{MatchThem}, and any other package that produces a list of model fit objects with each corresponding to the output of a model fit to an imputed dataset.

\hypertarget{comparison-to-other-packages}{%
\subsection{Comparison to other packages}\label{comparison-to-other-packages}}

Several packages offer methods for computing interpretable quantities form regression models, including \pkg{emmeans}, \pkg{margins}, \pkg{modelbased}, and \pkg{marginaleffects}. Many of the quantities computed by these packages can also be computed by \pkg{clarify}, the primary difference being that \pkg{clarify} uses simulation-based inference rather than delta method-based inference.

\pkg{marginaleffects} offers the most similar functionality to \pkg{clarify}, and \pkg{clarify} depends on functionality provided by \pkg{marginaleffects} to accommodate a wide variety of regression models. \pkg{marginaleffects} also offers simulation-based inference using \texttt{marginaleffects::inferences()} and support for arbitrary user-specified post-estimation functions using \texttt{marginaleffects::hypotheses()}. However, \pkg{clarify} and \texttt{marignalefefcts} differ in several ways. The largest difference is that \pkg{clarify} supports iterative building of more and more complex hypotheses through the \texttt{transform()} method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \pkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.

Because of \pkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing. \pkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.

There are areas and cases where \pkg{marginaleffects} may be the better choice than \pkg{clarify} or where the differences between the packages are of little consequence. \pkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \pkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience. In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \pkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \pkg{clarify} provides. For the quantities easily computed by \pkg{marginaleffects} that support simulation-based inference through \texttt{marginaleffects::inferences()}, using \pkg{marginaleffects} can provide a more familiar and flexible syntax than \pkg{clarify} might offer.

Note that as both packages continue to develop, these differences may grow or shrink. The differences above are meant to highlight the current differences and differences in philosophy and emphasis of the two packages. Ultimately, the user should use the package that supports their desired syntax and mode of inference.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

\pkg{clarify} provides utilities to facilitate simulation-based inference of deriving quantities form regression models. This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution fo the derived quantity is Normal. \pkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values. These enhance the utility and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-dehejiaCausalEffectsNonexperimental1999}{}}%
Dehejia, Rajeev H., and Sadek Wahba. 1999. {``Causal Effects in Nonexperimental Studies: Reevaluating the Evaluation of Training Programs.''} \emph{Journal of the American Statistical Association} 94 (448): 1053--62. \url{https://doi.org/10.1080/01621459.1999.10473858}.

\leavevmode\vadjust pre{\hypertarget{ref-greiferChoosingCausalEstimand2023}{}}%
Greifer, Noah, and Elizabeth A. Stuart. 2023. {``Choosing the Causal Estimand for Propensity Score Analysis of Observational Studies.''} \url{https://doi.org/10.48550/arXiv.2106.10577}.

\leavevmode\vadjust pre{\hypertarget{ref-JSSv042i08}{}}%
Ho, Daniel E., Kosuke Imai, Gary King, and Elizabeth A. Stuart. 2011. {``MatchIt: Nonparametric Preprocessing for Parametric Causal Inference.''} \emph{Journal of Statistical Software, Articles} 42 (8): 128. \url{https://doi.org/10.18637/jss.v042.i08}.

\leavevmode\vadjust pre{\hypertarget{ref-imaiCommonFrameworkStatistical2008a}{}}%
Imai, Kosuke, Gary King, and Olivia Lau. 2008. {``Toward a Common Framework for Statistical Analysis and Development.''} \emph{Journal of Computational and Graphical Statistics} 17 (4): 892--913. \url{https://doi.org/10.1198/106186008X384898}.

\leavevmode\vadjust pre{\hypertarget{ref-kingMakingMostStatistical2000}{}}%
King, Gary, Michael Tomz, and Jason Wittenberg. 2000. {``Making the Most of Statistical Analyses: Improving Interpretation and Presentation.''} \emph{American Journal of Political Science} 44 (2): 347--61. \url{https://doi.org/10.2307/2669316}.

\leavevmode\vadjust pre{\hypertarget{ref-rainey2017}{}}%
Rainey, Carlisle. 2017. {``Transformation-Induced Bias: Unbiased Coefficients Do Not Imply Unbiased Quantities of Interest.''} \emph{Political Analysis} 25 (3): 402--9. \url{https://doi.org/10.1017/pan.2017.11}.

\leavevmode\vadjust pre{\hypertarget{ref-raineyCarefulConsiderationCLARIFY2023}{}}%
---------. 2023. {``A Careful Consideration of {CLARIFY}: Simulation-Induced Bias in Point Estimates of Quantities of Interest.''} \emph{Political Science Research and Methods}, April, 1--10. \url{https://doi.org/10.1017/psrm.2023.8}.

\leavevmode\vadjust pre{\hypertarget{ref-tomzClarifySoftwareInterpreting2003}{}}%
Tomz, Michael, Jason Wittenberg, and Gary King. 2003. {``Clarify: Software for Interpreting and Presenting Statistical Results.''} \emph{Journal of Statistical Software} 8 (January): 1--30. \url{https://doi.org/10.18637/jss.v008.i01}.

\leavevmode\vadjust pre{\hypertarget{ref-zhouNoteBayesianInference2010}{}}%
Zhou, Xiang, and Jerome P. Reiter. 2010. {``A Note on Bayesian Inference After Multiple Imputation.''} \emph{The American Statistician} 64 (2): 159--63. \url{https://doi.org/10.1198/tast.2010.09109}.

\end{CSLReferences}

\bibliography{RJreferences.bib}

\address{%
Noah Greifer\\
Harvard University\\%
Institute for Quantitative Social Science\\ Cambridge, MA\\
%
ngreifer.github.io\\%
\textit{ORCiD: \href{https://orcid.org/0000-0003-3067-7154}{0000-0003-3067-7154}}\\%
\href{mailto:ngreifer@iq.harvard.edu}{\nolinkurl{ngreifer@iq.harvard.edu}}%
}

\address{%
Steven Worthington\\
Harvard University\\%
Institute for Quantitative Social Science\\ Cambridge, MA\\
%
%
\textit{ORCiD: \href{https://orcid.org/0000-0001-9550-5797}{0000-0001-9550-5797}}\\%
\href{mailto:sworthington@iq.harvard.edu}{\nolinkurl{sworthington@iq.harvard.edu}}%
}

\address{%
Stefano Iacus\\
Harvard University\\%
Institute for Quantitative Social Science\\ Cambridge, MA\\
%
%
\textit{ORCiD: \href{https://orcid.org/0000-0002-4884-0047}{0000-0002-4884-0047}}\\%
\href{mailto:siacus@iq.harvard.edu}{\nolinkurl{siacus@iq.harvard.edu}}%
}

\address{%
Gary King\\
Harvard University\\%
Institute for Quantitative Social Science\\ Cambridge, MA\\
%
%
\textit{ORCiD: \href{https://orcid.org/0000-0002-5327-7631}{0000-0002-5327-7631}}\\%
\href{mailto:king@harvard.edu}{\nolinkurl{king@harvard.edu}}%
}

### 2023-09-19 clarify/clarify.Rmd

---
title: "clarify: Simulation-Based Inference for Regression Models"
date: "`r Sys.Date()`"
abstract: >
  Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects and adjusted predictions. It avoids several assumptions required by the delta method that are commonly violated, especially in nonlinear models, but does not require models to be refit as when using the bootstrap. It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form the sampling distribution of the quantity. \pkg{clarify} provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest. \pkg{clarify} supports a large and growing number of models through its interface with the \pkg{marginaleffects} package and provides native support for multiply imputed data.
draft: true
author:  
  # see ?rjournal_article for more information
  - name: Noah Greifer
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    url: ngreifer.github.io
    orcid: 0000-0003-3067-7154
    email:  ngreifer@iq.harvard.edu
  - name: Steven Worthington
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: sworthington@iq.harvard.edu
    orcid: 0000-0001-9550-5797
  - name: Stefano Iacus
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: siacus@iq.harvard.edu
    orcid: 0000-0002-4884-0047
  - name: Gary King
    affiliation: Harvard University
    address:
    - Institute for Quantitative Social Science
    - Cambridge, MA
    email: king@harvard.edu
    orcid: 0000-0002-5327-7631
type: package
output: 
  rjtools::rjournal_web_article:
    self_contained: yes
    toc: no
bibliography: RJreferences.bib
---

```{r setup,include=FALSE}
knitr::opts_chunk$set(
  fig.path = "figures/",
  fig.align='center',
  fig.height = 2
)
```

## Introduction

Although regression models are frequently used in empirical research to study relationships among variables, often the quantity of substantive interest is not one of the coefficients of the model, but rather a quantity derived from the coefficients, such as predicted values or average marginal effects. The usual method for estimating the uncertainty of the derived quantities is known as the "delta method", which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the resulting estimate is normally distributed[^1]. In many cases, especially with nonlinear models, these approximation can fail badly. \pkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.

[^1]: In addition, most software that uses the delta method uses numerical differentiation, which also involves an approximation.

The methodology \pkg{clarify} relies on is described in @kingMakingMostStatistical2000 and @raineyCarefulConsiderationCLARIFY2023. Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a "posterior" distribution, which is taken to be the sampling distribution of the derived quantity, and from which uncertainty measures (standard errors and confidence intervals) can be computed. This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values. Arriving at the posterior distribution does not require taking any derivatives or making any approximations except those used to define the sampling distribution of the parameter estimates. The delta method makes these same approximation in addition to the approximations of the variance and the shape of the sampling distribution of the estimates.

More formally, we fit a regression model $y_i = f(x_i; \beta)$, such a linear or generalized linear model with model coefficients $\beta$. We assume$$
\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})
$$where $\hat{\beta}$ is the vector of estimates of $\beta$ and $\Sigma_{\hat{\beta}}$ is their asymptotic covariance matrix. We define a function $\tau(\beta)$ that represents a quantity of interest derived from the model parameters, and compute its estimate $\hat{\tau}(\beta)$ as $\tau(\hat{\beta})$. Next, we take $M$ draws $\tilde{\beta}^{(j)}$ for $j\in(1, \dots, M)$ from a multivariate Normal distribution with mean vector $\boldsymbol{\mu} = \hat{\beta}$ and covariance $\Sigma = \hat{\Sigma}_{\hat{\beta}}$, where $\hat{\Sigma}_{\hat{\beta}}$ is an estimate of the asymptotic covariance matrix of the parameter estimates. We use the distribution of $\tilde{\tau}=\tau(\tilde{\theta})$ as the "posterior" sampling distribution of $\hat{\tau}(\beta)$, and compute its variance as$$
\sigma^2_{\hat{\tau}(\theta)} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
$$and quantile $100(1-\alpha)\%$ confidence interval limits as $\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]$ where $\tilde{\tau}_{(k)}$ is the $k$th value of $\tilde{\tau}$ when arranged in ascending order.

Similar functionality exists in the \pkg{CLARIFY} package in Stata [@tomzClarifySoftwareInterpreting2003][^2] and used to be available in the `Zelig` R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations. \pkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below). \pkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).

[^2]: Despite the similar name, the R package \pkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \pkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution. The R implementation avoids the "simulation-induced bias" described by @raineyCarefulConsiderationCLARIFY2023.

## Using \pkg{clarify}

There are four steps to using \pkg{clarify}:

1.  Fit the model to the data using modeling functions in supported packages.

2.  Use `sim()` to take draws from the sampling distribution of the estimated model coefficients.

3.  Use `sim_apply()` or its wrappers `sim_setx()`, `sim_ame()`, and `sim_adrf()` to compute derived quantities using each simulated set of coefficients.

4.  Use `summary()` and `plot()` to summarize and visualize the distribution of the derived quantities and perform inference on them.

In the sections below, we'll describe how to implement these steps in detail. First, we'll load \pkg{clarify} using `library()`.

```{r}
library(clarify)
```

For a running example, we'll use the `lalonde` dataset in the \pkg{MatchIt} package [@JSSv042i08], which contains data on 614 participants enrolled in a job training program or sampled from a survey [@dehejiaCausalEffectsNonexperimental1999]. The treatment variable is `treat` and the outcome is `re78`, and all other variables are confounders. Although the original use of this dataset was to estimate the effect of `treat` on `re78`, we'll use it more generally to demonstrate all of \pkg{clarify}'s capabilities. In addition, we'll use a transformation of the outcome variable to demonstrate applications to nonlinear models, for which the benefits of simulation-based inference are more apparent.

```{r}
data("lalonde", package = "MatchIt")

lalonde$re78_0 <- ifelse(lalonde$re78 > 0, 1, 0)

head(lalonde)
```

### 1. Fitting the model

The first step is to fit the model. \pkg{clarify} can operate on a large set of models (those supported by \pkg{marginaleffects}), including generalized linear models, multinomial models, multivariate models, and instrumental variable models, many of which are available in other R packages. Even if \pkg{clarify} does not offer direct support for a given model, there are ways to use its functionality regardless (explained in more detail below).

Because we are computing derived quantities, it is not critical to parameterize the model in such a way that the coefficients are interpretable, e.g., by using a model with interpretable coefficients or centering predictors. Below, we'll fit a probit regression model for the outcome given the treatment and confounders. Coefficients in probit regression do not have a straightforward interpretation, but that's okay; our quantities of interest can be expressed as derived quantities---functions of the model parameters, such as predictions, counterfactual predictions, and averages and contrasts of them.

```{r}
fit <- glm(re78_0 ~ treat * married + age + educ + race +
             nodegree + re74 + re75, data = lalonde,
           family = binomial("probit"))
```

### 2. Drawing from the coefficient distribution

After fitting the model, we will use `sim()` to draw coefficients from their sampling distribution. The sampling distribution is assumed to be multivariate Normal or multivariate T with appropriate degrees of freedom, with a mean vector equal to the estimated coefficients and a covariance matrix equal to the asymptotic covariance matrix extracted from the model. The arguments to `sim()` are listed below:

``` r
sim(fit = , n = , vcov = , coefs = , dist = )
```

-   `fit` -- the fitted model object, the output of the call to the fitting function (e.g., `glm()`)

-   `n` -- the number of simulated values to draw; by default, 1000. More values will yield more replicable and precise results at the cost of speed.

-   `vcov` -- either the covariance matrix of the estimated coefficients, a function used to extract it from the model (e.g., `sandwich::vcovHC()` for the robust covariance matrix), or a string or formula giving a code for extracting the covariance matrix, which is passed to `marginaleffects::get_vcov()`. If left unspecified, the default covariance matrix will be extracted from the model.

-   `coefs` -- either a vector of coefficients to be sampled or a function to extract them from the fitted model. If left unspecified, the default coefficients will be extracted from the model. Typically this does not need to be specified.

-   `dist` -- the name of the distribution from which to draw the sampled coefficients. Can be `"normal"` for a Normal distribution or `t(#)` for a t-distribution, where `#` represents the degrees of freedom. If left unspecified, `sim()` will decide on which distribution makes sense given the characteristics of the model (the decision is made by `insight::get_df()` with `type = "wald"`). Typically this does not need to be specified.

If one's model is not supported by \pkg{clarify}, one can omit the `fit` argument and just specify the `vcov` and `coefs` argument, which will draw the coefficients from the distribution named in `dist` (`"normal"` by default).

`sim()` uses a random number generator to draw the sampled coefficients from the sampling distribution, so a seed should be set using `set.seed()` to ensure results are replicable across sessions.

The output of the call to `sim()` is a `clarify_sim` object, which contains the sampled coefficients, the original model fit object if supplied, and the coefficients and covariance matrix used to sample.

```{r}
set.seed(1234)

# Drawing 1000 simulated coefficients using an HC2 robust
# covariance matrix
s <- sim(fit, n = 1000,
         vcov = "HC2")

s
```

### 3. Computing derived quantities

After sampling the coefficients, we will compute derived quantities on each set of sampled coefficients and store the result, which represents the "posterior" distribution of the derived quantity, as well as on the original coefficients, which are used as the final estimates. The core functionality is provided by `sim_apply()`, which accepts a `clarify_sim` object from `sim()` and a function to compute and return one or more derived quantities, then applies that function to each set of simulated coefficients. The arguments to `sim_apply()` are below:

``` r
sim_apply(sim = , FUN = , verbose = , cl = , ...)
```

-   `sim` -- a `clarify_sim` object; the output of a call to `sim()`.

-   `FUN` -- a function that takes in either a model fit object or a vector of coefficients and returns one or more derived quantities. The first argument should be named `fit` to take in a model fit object or `coefs` to take in coefficients.

-   `verbose` -- whether to display a progress bar.

-   `cl` -- an argument that controls parallel processing, which can be the number of cores to use or a cluster object resulting from `parallel::makeCluster()`.

-   `...` - further arguments to `FUN`.

The `FUN` argument can be specified in one of two ways: either as a function that takes in a model fit object (e.g., a `glm` or `lm` object, the output of a call to `glm()` or `lm()`) or a function that takes in a vector of coefficients. The latter will always work but the former only works for supported models. When the function takes in a model fit object, `sim_apply()` will first insert each set of sampled coefficients into the model fit object and then supply the modified model to `FUN`.

For example, let's say our derived quantity of interest is the predicted probability of the outcome for participant PSID1. We would specified our `FUN` function as follows:

```{r}
sim_fun1 <- function(fit) {
  predict(fit, newdata = lalonde["PSID1",], type = "response")
}
```

The `fit` object supplied to this function will be one in which the coefficients have been set to their values in a draw from their sampling distribution as generated by `sim()`. We then supply the function to `sim_apply()` to simulate the sampling distribution of the predicted value of interest:

```{r}
est1 <- sim_apply(s, FUN = sim_fun1, verbose = FALSE)

est1
```

The resulting `clarify_est` object contains the simulated estimates in matrix form as well as the estimate computed on the original coefficients. We'll examine the sampling distribution shortly, but first we'll demonstrate computing a derived quantity from the coefficients directly.

The `race` variable is a factor, and the `black` category is used as the reference level, so it is not immediately clear whether there is a difference between the coefficients `racehispan` and `racewhite`, which represent the non-reference categories `hispan` and `white`. To compare these two directly, we can use `sim_apply()` to compute a derived quantity that corresponds to the difference between them.

```{r}
sim_fun2 <- function(coefs) {
  hispan <- unname(coefs["racehispan"])
  white <- unname(coefs["racewhite"])

  c("w - h" = white - hispan)
}

est2 <- sim_apply(s, FUN = sim_fun2, verbose = FALSE)

est2
```

The function supplied to `FUN` can be arbitrarily complicated and return as many derived quantities as one wants, though the slower each run of `FUN` is, the longer it will take to simulate the derived quantities. Using parallel processing by supplying an argument to `cl` can sometimes dramatically speed up evaluation.

There are several functions in \pkg{clarify} that serve as convenience wrappers for `sim_apply()` to automate some common derived quantities of interest. These include

-   `sim_setx()` -- computing predicted values and first differences at representative or user-specified values of the predictors

-   `sim_ame()` -- computing average adjusted predictions, contrasts of average adjusted predictions, and average marginal effects

-   `sim_adrf()` -- computing average dose-response functions and average marginal effects functions

These are described in their own sections below. In addition, there are functions that have methods for `clarify_est` objects, including `cbind()` for combining two `clarify_est` objects together and `transform()` for computing quantities that are derived from the already-computed derived quantities. These are also described in their own sections below.

### 4. Summarize and visualize the simulated distribution

To examine the uncertainty around and perform inference on our estimated quantities, we can use `plot()` and `summary()` on the `clarify_est` object.

`plot()` displays a density plot of the resulting estimates across the simulations, with markers identifying the point estimate (computed using the original model coefficients as recommended by @raineyCarefulConsiderationCLARIFY2023) and, optionally, uncertainty bounds (which function like confidence or credible interval bounds). The arguments to `plot()` are below:

``` r
plot(x = , parm = , ci = , level = , method = , reference =)
```

-   `x` -- the `clarify_est` object (the output of a call to `sim_apply()`).

-   `parm` -- the names or indices of the quantities to be plotted if more than one was estimated in `sim_apply()`; if unspecified, all will be plotted.

-   `ci` -- whether to display lines at the uncertainty bounds. The default is `TRUE` to display them.

-   `level` -- if `ci` is `TRUE`, the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when `method` (see below) is `"quantile"`.

-   `method` -- if `ci` is `TRUE`, the method used to compute the bounds. Allowable methods include a Normal approximation (`"wald"`) or using the quantiles of the resulting distribution (`"quantile"`). The Normal approximation involves multiplying the standard deviation of the estimates (i.e., which functions like the standard error of the sampling distribution) by the critical Z-statistic computed using `(1-level)/2` to create a symmetric margin of error around the point estimate. The default is `"quantile"` to instead use quantile-based bounds, which are more appropriate when the distribution is non-Normal. However, quantile-based bounds may require more simulations to stabilize.

-   `reference` -- whether to display a normal density over the plot for each estimate. The default is `FALSE` to omit them.

Below, we plot the first estimate we computed above, the predicted probability for participant PSID1:

```{r, fig.width=4}
plot(est1, reference = TRUE, ci = FALSE)
```

From the plot, one can see that the distribution of simulated values is non-Normal, asymmetrical, and not centered around the estimate, with no values falling above 1 because the outcome is a predicted probability. Given its non-Normality, the quantile-based bounds are clearly more appropriate than those resulting from the Normal approximation, as the bounds computed from the Normal approximation would be outside the bounds of the estimate. The plot itself is a `ggplot` object that can be modified using `ggplot2` syntax.

We can use `summary()` to display the value of the point estimate, the uncertainty bounds, and other statistics that describe the distribution of estimates. The arguments to `summary()` are below:

``` r
summary(object = , parm = , level = , method = , null = )
```

-   `object` -- the `clarify_est` object (the output of a call to `sim_apply()`).

-   `parm` -- the names or indices of the quantities to be displayed if more than one was estimated in `sim_apply()`; if unspecified, all will be displayed.

-   `level` -- the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when method (see below) is `"quantile"`.

-   `method` -- the method used to compute the uncertainty bounds. Allowable methods include a Normal approximation (`"wald"`) or using the quantiles of the resulting distribution (`"quantile"`). See `plot()` above.

-   `null` -- an optional argument specifying the null value in a hypothesis test for the estimates. If specified, a p-value will be computed using either a standard Z-test (if `method` is `"wald"`) or an inversion of the uncertainty interval (described below). The default is not to display any p-values.

Inverting the uncertainty interval involves finding the smallest confidence level such that the null value is within the confidence bounds. The p-value for the test is one minus this level. It is only valid as a p-value when the simulated distribution of the estimates differs from its true sampling distribution under the null value by a location shift (which can be violated when the distribution of the estimates is asymmetric). However, because the p-values are invariant to monotonic transformations of the estimates and null value, as long as the distribution of *some* monotonic transformation of the estimate is a location shift from its sampling distribution under the null hypothesis, the p-values will be valid.

We'll use `summary()` with the default arguments on our first `clarify_est` object to view the point estimate and quantile-based uncertainty bounds.

```{r}
summary(est1)
```

A benefit of quantile-based confidence bounds is that the bounds will always be in the domain of the quantity of interest, e.g., bounds for probabilities will not be above 1 or below 0 if the model always generates predicted probabilities between 0 and 1. In contrast, Wald-type symmetric confidence intervals can include values outside the domain of the quantity of interest. While it is possible to compute Wald-type confidence interval bounds that respect the domain boundaries, e.g., by computing the confidence interval around the logit of the predicted probability and using the inverse logit of the bounds as the bound on the probability, quantile confidence intervals do not require the user to know which transformation of the quantity of interest will yield appropriate bounds.

Our second estimated quantity, the difference between two regression coefficients, is closer to Normally distributed, as the plot below demonstrates (and would be expected theoretically), so we'll use the Normal approximation to test the hypothesis that difference differs from 0.

```{r, fig.width=4}
plot(est2, reference = TRUE, ci = FALSE)

summary(est2, method = "wald", null = 0)
```

The uncertainty intervals and p-values in the `summary()` output are computed using the Normal approximation because we set `method = "wald"`, and the p-value for the test that our estimate is equal to 0 is returned because we set `null = 0`. Note that the Normal approximation should be used only when the simulated sampling distribution is both close to Normally distributed and centered around the estimate (i.e., when the mean of the simulated values [red vertical line] coincides with the estimate computed on the original coefficients [black vertical line]).

## `sim_apply()` wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`

`sim_apply()` can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \pkg{clarify} provides shortcut functions to make computing these quantities simple. These functions include `sim_setx()`, `sim_ame()`, and `sim_adrf()`. Each of these can be used only when regression models compatible with \pkg{clarify} are supplied to the original call to `sim()`.

Like `sim_apply()`, each of these functions is named `sim_*()`, which signifies that they are to be used on an object produced by `sim()` (i.e., a `clarify_sim` object). (Multiple calls to these functions can be applied to the same `clarify_sim` object and combined; see the `cbind()` section below.) These functions are described below.

### `sim_setx()`: predictions at representative values

`sim_setx()` provides an interface to compute predictions at representative and user-supplied values of the predictors. For example, we might want to know what the effect of treatment is for a "typical" individual, which corresponds to the contrast between two model-based predictions (i.e., one under treatment and one under control for a unit with "typical" covariate values). This functionality mirrors the `setx()` and `setx1()` functionality of `Zelig` (which is where its name originates) and provides similar functionality to functions in \pkg{modelbased}, \pkg{emmeans}, \pkg{effects}, and \pkg{ggeffects}.

For each predictor, the user can specify whether they want predictions at specific values or at "typical" values, which are defined in \pkg{clarify} as the mode for unordered categorical and binary variables, the median for ordered categorical variables, and the mean for continuous variables. Predictions for multiple predictor combinations can be requested by specifying values that will be used to create a grid of predictor values, or the grid itself can be supplied as a data frame of desired predictor profiles. In addition, the "first difference", defined here as the difference between predictions for two predictor combinations, can be computed.

The arguments to `sim_setx()` are as follows:

``` r
sim_setx(sim = , x = , x1 = , outcome = , type = , verbose = , cl = )
```

-   `sim` -- a `clarify_sim` object; the output of a call to `sim()`.

-   `x` -- a named list containing the requested values of the predictors, e.g., `list(v1 = 1:4, v2 = "A")`, or a data frame containing the desired profiles. Any predictors not included will be set at their "typical" value as defined above.

-   `x1` -- an optional named list or data frame similar to `x` except with the value of one predictor changed. When specified, the first difference is computed between the covariate combination defined in `x` (and only one combination is allowed when `x1` is specified) and the covariate combination defined in `x1`.

-   `outcome` -- a string containing the name of the outcome of interest when a multivariate (multiple outcome) model is supplied to `sim()` or the outcome category of interest when a multinomial model is supplied to `sim()`. For univariate (single outcome) and binary outcomes, this is ignored.

-   `type` -- a string containing the type of predicted value to return. In most cases, this can be left unspecified to request predictions on the scale of the outcome.

-   `verbose` -- whether to display a progress bar.

-   `cl` -- an argument that controls parallel processing, which can be the number of cores to use or a cluster object resulting from `parallel::makeCluster()`.

Here, we'll use `sim_setx()` to examine predicted values of the outcome for control and treated units, at `re75` set to 0 and 20000, and `race` set to "black".

```{r}
est3 <- sim_setx(s,
                 x = list(treat = 0:1,
                          re75 = c(0, 20000),
                          race = "black"),
                 verbose = FALSE)
```

When we use `summary()` on the resulting output, we can see the estimates and their uncertainty intervals (calculated using quantiles by default).

```{r}
summary(est3)
```

To see the complete grid of the predictor values used in the predictions, which helps to identify the "typical" values of the other predictors, we can access the `"setx"` attribute of the object:

```{r}
attr(est3, "setx")
```

We can plot the distributions of the simulated values using `plot()`, which also separates the predictions by the predictor values (it's often clearer without the uncertainty bounds). The `var` argument controls which variable is used for faceting the plots.

```{r, fig.width=5}
plot(est3, var = "re75", ci = FALSE)
```

One can see again how a delta method or Normal approximation may not have yielded valid uncertainty intervals given the non-Normality of the distributions.

If a continuous variable with many levels is included in the grid of the predictors, something like a dose-response function for a typical unit can be generated. Below, we set `re75` to vary from 0 to 20000 in steps of 2000.

```{r}
est4 <- sim_setx(s,
                 x = list(treat = 0:1,
                          re75 = seq(0, 20000, by = 2000),
                          race = "black"),
                 verbose = FALSE)
```

When we plot the output, we can see how the predictions varies across the levels of `re75`:

```{r, fig.width=5}
plot(est4)
```

We'll return to display average dose-response functions using `sim_adrf()` later.

Finally, we can use `sim_setx()` to compute first differences, the contrast between two covariate combinations. We supply one covariate profile to `x` and another to `x1`, and `sim_setx()` simulates the two predicted values and their difference. Below, we simulate first difference for a treated and control unit who have `re75` of 0 and typical values of all other covariates:

```{r}
est5 <- sim_setx(s,
                 x = list(treat = 0, re75 = 0),
                 x1 = list(treat = 1, re75 = 0),
                 verbose = FALSE)
```

When we use `summary()`, we see the estimates for the predicted values and their first difference ("FD"):

```{r}
summary(est5)
```

It is possible to compute first differences without using `x1` using `transform()`, which we describe later.

### `sim_ame()`: average adjusted predictions and average marginal effects

Using predicted values and effects at representative values is one way to summarize regression models, but another way is to compute average adjusted predictions (AAPs), contrasts of AAPs, and average marginal effects (AMEs). The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units[^3].

[^3]: In \pkg{marginaleffects}, AAPs are computed using `avg_predictions()`, AMEs for binary variables are computed using `avg_comparisons()`, and AMEs for continuous variables are computed using `avg_slopes()`. AAPs are sometimes known as average "counterfactual" predictions.

The arguments to `sim_ame()` are as follows:

``` r
sim_ame(sim = , var = , subset = , by = , contrast = , outcome = ,
        type = , eps = , verbose = , cl = )
```

-   `sim` -- a `clarify_sim` object; the output of a call to `sim()`.

-   `var` -- the name of focal variable over which to compute the AAPs or AMEs, or a list containing the values for which AAPs should be computed.

-   `subset` -- a logical vector, evaluated in the original dataset used to fit the model, defining a subset of units for which the AAPs or AMEs are to be computed.

-   `by` -- the name of one or more variables for which AAPs should be computed within subgroups. Can be supplied as a character vector of variable names or a one-sided formula.

-   `contrast` -- the name of an effect measure used to contrast AAPs. For continuous outcomes, `"diff"` requests the difference in means, but others are available for binary outcomes, including `"rr"` for the risk ratio, `"or"` for the odds ratio, and `"nnt"` for the number needed to treat, among others. If not specified, only AAPs will be computed if the variable named in `var` is categorical or specific values of the focal variable are specified in `var`. Ignored when the variable named in `var` is continuous and no specific values are specified because the AME is the only quantity computed. When `var` names a multi-category categorical variable, `contrast` cannot be used; see the section describing `transform()` for computing contrasts with them.

-   `outcome` -- a string containing the name of the outcome of interest when a multivariate (multiple outcome) model is supplied to `sim()` or the outcome category of interest when a multinomial model is supplied to `sim()`. For univariate (single outcome) and binary outcomes, this is ignored.

-   `type` -- a string containing the type of predicted value to return. In most cases, this can be left unspecified to request predictions on the scale of the outcome (e.g., probabilities for binary outcomes).

-   `eps` -- the value by which the observed values of the variable named in `var` are changed when it is continuous to compute the AME. This usually does not need to be specified.

-   `verbose` -- whether to display a progress bar.

-   `cl` -- an argument that controls parallel processing, which can be the number of cores to use or a cluster object resulting from `parallel::makeCluster()`.

Here, we'll use `sim_ame()` to compute the AME of `treat` just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT [@greiferChoosingCausalEstimand2023]). We'll request our estimate to be on the risk ratio scale.

```{r}
est6 <- sim_ame(s,
                var = "treat",
                subset = treat == 1,
                contrast = "rr",
                verbose = FALSE)
```

We can use `summary()` to display the estimates and their uncertainty intervals. Here, we'll also use `null` to include a test for the null hypothesis that the risk ratio is equal to 1.

```{r}
summary(est6, null = c(`RR` = 1))
```

Here we see the estimates for the AAPs, `E[Y(0)]` for the expected value of the outcome setting `treat` to 0 and `E[Y(1)]` for the expected value of the outcome setting `treat` to 1, and the risk ratio `RR`. The p-value on the test for the risk ratio aligns with the uncertainty interval containing 1.

If we instead wanted the risk difference or odds ratio, we would not have to re-compute the AAPs. Instead, we can use `transform()` to compute a new derived quantity from the computed AAPs. The section on `transform()` demonstrates this.

We can compute the AME for a continuous predictor. Here, we'll consider `age` (just for demonstration; this analysis does not have a valid interpretation).

```{r}
est7 <- sim_ame(s,
                var = "age",
                verbose = FALSE)
```

We can use `summary()` to display the AME estimate and its uncertainty interval.

```{r}
summary(est7)
```

The AME is named `E[dY/d(age)]`, which signifies that a derivative has been computed (more precisely, the average of the unit-specific derivatives). This estimate can be interpreted like a slope in a linear regression model, but as a single summary of the effect of a predictor it is often too coarse to capture nonlinear relationships. The section below explains how to compute average dose-response functions for continuous predictors, which provide a more complete picture of their effects on an outcome.

Below, we'll examine effect modification of the ATT by the predictor `married` using the `by` argument to estimate AAPs and their ratio within levels of `married`:

```{r}
est6b <- sim_ame(s,
                 var = "treat",
                 subset = treat == 1,
                 by = ~married,
                 contrast = "rr",
                 verbose = FALSE)

summary(est6b)
```

The presence of effect modification can be tested by testing the contrast between the effects computed within each level of the `by` variable; this demonstrated in the section on `transform()` below.

### `sim_adrf()`: average dose-response functions

A dose-response function for an individual is the relationship between the set value of a continuous focal predictor and the expected outcome. The average dose-response function (ADRF) is the average of the dose-response functions across all units. Essentially, it is a function that relates the value of the predictor to the corresponding AAP of the outcome, the average value of the outcome were all units to be set to that level of the predictor. ADRFs can be used to provide additional detail about the effect of a continuous predictor beyond a single AME.

A related quantity is the average marginal effect function (AMEF), which describes the relationship between a continuous focal predictor and the AME at that level of the predictor. That is, rather than describing how the outcome changes as a function of the predictor, it describes how the *effect* of the predictor on the outcome changes as a function of the predictor. It is essentially the derivative of the ADRF and can be used to identify at which points along the ADRF the predictor has an effect.

The ADRF and AMEF can be computed using `sim_adrf()`. The arguments are below:

``` r
sim_adrf(sim = , var = , subset = , by = , contrast = , at = ,
         n = , outcome = , type = , eps = , verbose = , cl = )
```

-   `sim` -- a `clarify_sim` object; the output of a call to `sim()`.

-   `var` -- the name of focal variable over which to compute the ADRF or AMEF.

-   `subset` -- a logical vector, evaluated in the original dataset used to fit the model, defining a subset of units for which the ARDF or AMEF is to be computed.

-   `by` -- the name of one or more variables for which the ADRF or AMEF should be computed within subgroups. Can be supplied as a character vector of variable names or a one-sided formula.

-   `contrast` -- either `"adrf"` or `"amef"` to request the ADRF or AMEF, respectively. The default is to compute the ADRF.

-   `at` -- the values of the focal predictor at which to compute the ADRF or AMEF. This should be a vector of values that the focal predictor can take on. If unspecified, a vector of `n` (see below) equally-spaced values from the minimum to the maximum value of the predictor will be used. This should typically be used only if quantities are desired over a subset of the values of the focal predictor.

-   `n` -- if `at` is unspecified, the number of points along the range of the focal predictor at which to compute the ADRF or AMEF. More yields smoother functions, but will take longer and require more memory. The default is 21.

-   `outcome` -- a string containing the name of the outcome of interest when a multivariate (multiple outcome) model is supplied to `sim()` or the outcome category of interest when a multinomial model is supplied to `sim()`. For univariate (single outcome) and binary outcomes, this is ignored.

-   `type` -- a string containing the type of predicted value to return. In most cases, this can be left unspecified to request predictions on the scale of the outcome.

-   `eps` -- the value by which the observed values of the variable named in `var` are changed when it is continuous to compute the AMEF. This usually does not need to be specified.

-   `verbose` -- whether to display a progress bar.

-   `cl` -- an argument that controls parallel processing, which can be the number of cores to use or a cluster object resulting from `parallel::makeCluster()`.

Here, we'll consider `age` (just for demonstration; this analysis does not have a valid interpretation) and compute the ADRF and AMEF of `age` on the outcome. We'll only examine ages between 18 and 50, even though the range of `age` goes slightly beyond these values. First, we'll compute the ADRF of `age`, which examines how the outcome would vary on average if one set all unit's value of `age` to each value between 18 and 50 (here we only use even ages to speed up computation).

```{r}
age_seq <- seq(18, 50, by = 2)

est8 <- sim_adrf(s,
                 var = "age",
                 contrast = "adrf",
                 at = age_seq,
                 verbose = FALSE)
```

We can plot the ADRF using `plot()`.

```{r, fig.width=5}
plot(est8)
```

From the plot, we can see that as `age` increases, the expected outcome decreases.

We can also examine the AAPs at the requested ages using `summary()`, which will display all the estimated AAPs by default, so we will request just the first 4 (`age`s 18 to 24):

```{r}
summary(est8, parm = 1:4)
```

Next we'll compute the AMEF, the effect of `age` at each level of `age`.

```{r}
est9 <- sim_adrf(s,
                 var = "age",
                 contrast = "amef",
                 at = age_seq,
                 verbose = FALSE)
```

We can plot the AMEF using `plot()`:

```{r, fig.width=5}
plot(est9)
```

From the plot, we can see the AME of `age` decreases slightly but is mostly constant across values of `age`, and the uncertainty intervals for the AMEs consistently exclude 0.

## Transforming and combining estimates

Often, our quantities of interest are not just the outputs of the functions above, but comparisons between them. For example, to test for moderation of a treatment effect, we may want to compare AMEs in multiple groups defined by the moderator. Or, it might be that we are interested in an effect described using a different effect measure than the one originally produced; for example, we may decide we want the risk difference AME after computing the risk ratio AME. The functions `transform()` and `cbind()` allow users to transform quantities in a single `clarify_est` object and combine two `clarify_est` objects. These are essential for computing quantities that themselves are derived from the derived quantities computed by the `sim_*()` functions.

### `transform()`

`transform()` is a generic function in R that is typically used to create a new variable in a data frame that is a function of other columns. For example, to compute the binary outcome we used in our model, we could have run the following[^4]:

[^4]: Users familiar with the `tidyverse` will note the similarities between `transform()` and `dplyr::mutate()`; only `transform()` can be used with `clarify_est` objects.

```{r}
lalonde <- transform(lalonde,
                     re78_0 = ifelse(re78 == 0, 1, 0))
```

Similarly, to compute a derived or transformed quantity from a `clarify_est` object, we can use `transform()`. Here, we'll compute the risk difference AME of `treat`; previously, we used `sim_ame()` to compute the AAPs and the risk ratio.

```{r}
est6 <- transform(est6,
                  RD = `E[Y(1)]` - `E[Y(0)]`)
```

Note that we used tics (\`) around the names of the AAPs; this is necessary when they contain special characters like parentheses or brackets.

When we run `summary()` on the output, the new quantity, which we named "RD", will be displayed along with the other estimates. We'll also set a null value for this quantity.

```{r}
summary(est6, null = c(`RR` = 1, `RD` = 0))
```

One benefit of using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.

The same value would be computed if we were to have called `sim_ame()` on the same `clarify_sim` object and requested the risk difference using `contrast = "diff"`; using `transform()` saves time because the AAPs are already computed and stored in the `clarify_est` object.

We can use `transform()` along with the `by` variable in `sim_ame()` to compute the contrast between quantities computed within each subgroup of `married`. Previously we used `by` to compute the risk ratio ATT within levels of `married`; here we will compute the ratio of these risk ratios to assess the presence of effect modification.

```{r}
est6b |>
  transform(RR_ratio = `RR[1]` / `RR[0]`) |>
  summary(parm = c("RR[0]", "RR[1]", "RR_ratio"),
          null = 1)
```

`RR_ratio` contains the ratio of the risk ratios for `married = 1` and `married = 0`. Here we also include a test for whether each of the risk ratios and their ratio differ from 1.

### `cbind()`

`cbind()` is another generic R function that is typically used to combine two or more datasets columnwise (i.e., to widen a dataset). In \pkg{clarify}, `cbind()` can be used to combine two `clarify_est` objects so that the estimates can be examined jointly and so that it is possible to compare them directly. For example, let's say we computed AMEs in two subgroups using `subset` and wanted to compare them. To do so, we call `sim_ame()` twice, one for each subset (though in practice it is more effective to use `by`; this is just for illustration):

```{r}
# AME of treat with race = "black"
est10b <- sim_ame(s, var = "treat", subset = race == "black",
                  contrast = "diff", verbose = FALSE)
summary(est10b)

# AME of treat with race = "hispan"
est10h <- sim_ame(s, var = "treat", subset = race == "hispan",
                  contrast = "diff", verbose = FALSE)
summary(est10h)
```

Here, we computed the risk difference for the subgroups `race = "black"` and `race = "hispan"`. If we wanted to compare the risk differences, we could combine them and compute a new quantity equal to their difference. We'll do that below.

First, we need to rename to quantities in each object so they don't overlap; we can do so using `names()`, which has a special method for `clarify_est` objects.

```{r}
names(est10b) <- paste(names(est10b), "b", sep = "_")
names(est10h) <- paste(names(est10h), "h", sep = "_")
```

Next, we use `cbind()` to bind the objects together.

```{r}
est10 <- cbind(est10b, est10h)
summary(est10)
```

Finally, we can use `transform()` to compute the difference between the risk differences:

```{r}
est10 <- transform(est10,
                   `Dh - Db` = Diff_h - Diff_b)
summary(est10, parm = "Dh - Db")
```

Importantly, `cbind()` can only be used to join together `clarify_est` objects computed using the same simulated coefficients (i.e., resulting from the same call to `sim()`). This preserves the covariance among the estimated quantities, which is critical for valid inference. That is, `sim()` should only be called once per model, and all derived quantities should be computed using its output.

## Using \pkg{clarify} with multiply imputed data

```{r, include=F}
amelia_ok <- requireNamespace("Amelia", quietly = TRUE)
knitr::opts_chunk$set(
  eval = amelia_ok
)
if (amelia_ok) library(Amelia)
```

Multiple imputation is a popular method of estimating quantities of interest in the presence of missing data and involves creating multiple versions of the original dataset each with the missing values imputed with estimates from an imputation model. Simulation-based inference in multiply imputed data is relatively straightforward. Simulated coefficients are drawn from the model estimated in each imputed dataset separately, and then the simulated coefficients are pooled into a single set of simulated coefficients. In Bayesian terms, this would be considered "mixing draws" and is the recommended approach for Bayesian analysis with multiply imputed data [@zhouNoteBayesianInference2010].

Using \pkg{clarify} with multiply imputed data is simple. Rather than using `sim()`, we use the function `misim()`. `misim()` functions just like `sim()` except that it takes in a list of model fits (i.e., containing a model fit to each imputed dataset) or an object containing such a list (e.g., a `mira` object from `mice::with()` or a `mimira` object from `MatchThem::with()`). `misim()` simulates coefficient distributions within each imputed dataset and then appends them together to a form a single combined set of coefficient draws.

`sim_apply()` and its wrappers accept the output of `misim()` and compute the desired quantity using each set of coefficients. When these function rely on using a dataset (e.g., `sim_ame()`, which averages predicted outcomes across all units in the dataset used to fit the model), they automatically know to associate a given coefficient draw with the imputed dataset that was used to fit the model that produced that draw. In user-written functions supplied to the `FUN` argument of `sim_apply()`, it is important to correctly extract the dataset from the model fit. This is demonstrated below.

The final estimates of the quantity of interest is computed as the mean of the estimates computed in each imputed dataset (i.e., using the original coefficients, not the simulated ones), which is the same quantity that would be computed using standard pooling rules. This is not always valid for noncollapsible estimates, like ratios, and so care should be taken to ensure the mean of the resulting estimates has a valid interpretation (this is related to the transformation-induced bias described by @rainey2017).

The arguments to `misim()` are as follows:

``` r
misim(fitlist = , n = , vcov = , coefs = , dist = )
```

-   `fitlist` -- a list of model fits or an accepted object containing them (e.g., a `mira` object from `mice::with()`)

-   `n` -- the number of simulations to run *for each imputed dataset*. The default is 1000, but fewer can be used because the total number of simulated quantities will be `m * n`, where `m` is the number of imputed datasets.

-   `vcov`, `coefs`, `dist` -- the same as with `sim()`, except that a list of such arguments can be supplied to be applied to each imputed dataset.

Below we illustrate using `misim()` and `sim_apply()` with multiply imputed data. We'll use the `africa` dataset from the \pkg{Amelia} package.

```{r, message=F}
library(Amelia)
data("africa", package = "Amelia")

# Multiple imputation
a.out <- amelia(x = africa, m = 10, cs = "country",
                ts = "year", logs = "gdp_pc", p2s = 0)

# Fit model to each dataset
model.list <- with(a.out, lm(gdp_pc ~ infl * trade))

# Simulate coefficients, 100 draws per imputation
si <- misim(model.list, n = 100)

si
```

The function we'll be applying to each imputed dataset will be one that computes the average marginal effect of `infl`. (We'll run the same analysis afterward using `sim_ame()`.)

```{r}
sim_fun <- function(fit) {
  #Extract the original dataset using get_predictors()
  X <- insight::get_predictors(fit)

  p0 <- predict(fit)

  #Predictions after perturbing infl slightly
  p1 <- predict(fit, newdata = transform(X, infl = infl + 1e-5))

 c(AME = mean((p1 - p0) / 1e-5))
}

est_mi <- sim_apply(si, FUN = sim_fun, verbose = FALSE)

summary(est_mi)
```

Note that `sim_apply()` "knows" which imputation produced each set of simulated coefficients, so using `insight::get_predictors()` on the `fit` supplied to `sim_fun()` will use the right dataset. Care should be taken when analyses restrict each imputed dataset in a different way (e.g. when matching with a caliper in each one), as the resulting imputations may not refer to a specific target population and mixing the draws may be invalid.

Below, we can use `sim_ame()`:

```{r}
est_mi2 <- sim_ame(si, var = "infl", verbose = FALSE)

summary(est_mi2)
```

We get the same results, as expected.

Note that `misim()` is compatible with model fit objects from \pkg{mice}, \pkg{Amelia}, \pkg{MatchThem}, and any other package that produces a list of model fit objects with each corresponding to the output of a model fit to an imputed dataset.

## Comparison to other packages

Several packages offer methods for computing interpretable quantities form regression models, including \pkg{emmeans}, \pkg{margins}, \pkg{modelbased}, and \pkg{marginaleffects}. Many of the quantities computed by these packages can also be computed by \pkg{clarify}, the primary difference being that \pkg{clarify} uses simulation-based inference rather than delta method-based inference.

\pkg{marginaleffects} offers the most similar functionality to \pkg{clarify}, and \pkg{clarify} depends on functionality provided by \pkg{marginaleffects} to accommodate a wide variety of regression models. \pkg{marginaleffects} also offers simulation-based inference using `marginaleffects::inferences()` and support for arbitrary user-specified post-estimation functions using `marginaleffects::hypotheses()`. However, \pkg{clarify} and `marignalefefcts` differ in several ways. The largest difference is that \pkg{clarify} supports iterative building of more and more complex hypotheses through the `transform()` method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \pkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.

Because of \pkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing. \pkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.

There are areas and cases where \pkg{marginaleffects} may be the better choice than \pkg{clarify} or where the differences between the packages are of little consequence. \pkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \pkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience. In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \pkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \pkg{clarify} provides. For the quantities easily computed by \pkg{marginaleffects} that support simulation-based inference through `marginaleffects::inferences()`, using \pkg{marginaleffects} can provide a more familiar and flexible syntax than \pkg{clarify} might offer.

Note that as both packages continue to develop, these differences may grow or shrink. The differences above are meant to highlight the current differences and differences in philosophy and emphasis of the two packages. Ultimately, the user should use the package that supports their desired syntax and mode of inference.

## Conclusion

\pkg{clarify} provides utilities to facilitate simulation-based inference of deriving quantities form regression models. This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution fo the derived quantity is Normal. \pkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values. These enhance the utility and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.

### 2024-03-08 R/sim_ame.R
No longer weighting predictions to compute average marginal means

@@ -19,8 +19,6 @@
 #'
 #' Continuous calculations involve computing the average of marginal effects of `var` across units. A marginal effect is the instantaneous rate of change corresponding to changing a unit's observed value of `var` by a tiny amount and considering to what degree the predicted outcome changes. The ratio of the change in the predicted outcome to the change in the value of `var` is the marginal effect; these are averaged across the sample to arrive at an average marginal effect. The "tiny amount" used is `eps` times the standard deviation of the focal variable.
 #'
-#' If unit-level weights are included in the model fit (and discoverable using [insight::get_weights()]), all means will be computed as weighted means.
-#'
 #' ## Effect measures
 #'
 #' The effect measures specified in `contrast` are defined below. Typically only `"diff"` is appropriate for continuous outcomes and `"diff"` or `"irr"` are appropriate for count outcomes; the rest are appropriate for binary outcomes. For a focal variable with two levels, `0` and `1`, and an outcome `Y`, the average marginal means will be denoted in the below formulas as `E[Y(0)]` and `E[Y(1)]`, respectively.
@@ -51,7 +49,7 @@
 #'   output of a call to `sim_ame()`; [summary.clarify_est()] for computing
 #'   p-values and confidence intervals for the estimated quantities.
 #'
-#' `marginaleffects::marginaleffects()`, `marginaleffects::comparisons()`, and `margins::margins()` for delta method-based implementations of computing average marginal effects.
+#'  [marginaleffects::avg_predictions()], [marginaleffects::avg_comparisons()] and `[marginaleffects::avg_slopes()]` for delta method-based implementations of computing average marginal effects.
 #'
 #' @examples
 #' data("lalonde", package = "MatchIt")
@@ -248,7 +246,7 @@ sim_ame <- function(sim,
         pred <- clarify_predict(fit, newdata = dat2, group = outcome, type = type)
         p <- .get_p(pred)
         vapply(seq_along(vals), function(i) {
-          weighted.mean(p[seq_len(m) + (i - 1) * m], attr(fit, "weights"))
+          mean(p[seq_len(m) + (i - 1) * m])
         }, numeric(1L))
       }
 
@@ -288,9 +286,8 @@ sim_ame <- function(sim,
 
[…]

### 2024-03-08 R/clarify_predict.R
Minor fixes

@@ -6,8 +6,8 @@ clarify_predict <- function(x, newdata = NULL, group = NULL, type = NULL) {
     group <- NULL
   }
 
-  args <- list(x, newdata = newdata, vcov = FALSE, type = type)
-
+  args <- list(model = x, newdata = newdata, vcov = FALSE)
+  args$type <- type
 
   p <- try(do.call(marginaleffects::get_predict, args), silent = TRUE)
 

### 2024-03-08 clarify/clarify.Rmd
Manuscript updates

@@
 ---
-title: "clarify: Simulation-Based Inference for Regression Models"
+title: "`clarify`: Simulation-Based Inference for Regression Models"
 date: "`r Sys.Date()`"
@@
 It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form the sampling distribution of the quantity.
-\pkg{clarify} provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
-\pkg{clarify} supports a large and growing number of models through its interface with the \pkg{marginaleffects} package and provides native support for multiply imputed data.
+`clarify` provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
+`clarify` supports a large and growing number of models through its interface with the `marginaleffects` package and provides native support for multiply imputed data.
 draft: true
 author:  
-  # see ?rjournal_article for more information
   - name: Noah Greifer
@@
 )
+
+if (!requireNamespace("clarify")) {
+  install.packages("clarify")
+}
+
+if (!requireNamespace("MatchIt")) {
+  install.packages("MatchIt")
+}
+
+if (!requireNamespace("Amelia")) {
+  install.packages("Amelia")
+}
 ```
@@
 Although regression models are frequently used in empirical research to study relationships among variables, often the quantity of substantive interest is not one of the coefficients of the model, but rather a quantity derived from the coefficients, such as predicted values or average marginal effects.
-The usual method for estimating the uncertainty of the derived quantities is known as the "delta method", which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the resulting estimate is normally distributed[^1].
+The usual method for estimating the uncertainty of the derived quantities is known as the "delta method", which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the estimate of the derived quantity is normally distributed[^1].
 In many cases, especially with nonlinear models, these approximation can fail badly.
-\pkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.
+For example, predicted probabilities close to 0 or 1 or ratios of coefficients or probabilities typically do not have normal (or even symmetrical) distributions in finite samples, and the usual Wald-type confidence interval limits produced from delta method standard errors can include values outside the domain of the quantity of interest.
 
@@
 
-The methodology \pkg{clarify} relies on is described in @kingMakingMostStatistical2000 and @raineyCarefulConsiderationCLARIFY2023.
+\CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.
+Simulation-based inference is not only often more accurate than using the delta method, it is also simpler to understand and implement, as it does not require understanding Taylor series or the calculus that underlies it.
+This makes it more palatable to nontechnical audiences and easier to learn for students without sacrificing statistical performance.
+
+The methodology \CRANpkg{clarify} relies on is described in @kingMakingMostStatistical2000 and @raineyCarefulConsiderationCLARIFY2023.
 Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a "posterior" distribution, which is taken to be the sampling distribution of the derived quantity, and from which uncertainty measures (standard errors and confidence intervals) can be computed.
-This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values.
-Arriving at the posterior distribution does not require taking any derivatives or making any approximations except those used to define the sampling distribution of the parameter estimates.
-The delta method makes these same approximation in addition to the approximations of the variance and the shape of the sampling distribution of the estimates.
+This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values, a standard assumption motivated by the central limit theorem that underlies usual inference on the original model parameters.
+Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates.
+The delta method makes these same assumptions in addition to the approximations about the variance and the shape of the sampling distribution of the estimates of the derived quantities.
 
-More formally, we fit a regression model $y_i = f(x_i; \beta)$, such a linear or generalized linear model with model coefficients $\beta$. We assume$$
+The nonparametric bootstrap is another alternative to the delta method for inference that does not require these approximations; it typically involves re-sampling individuals from the sample, fitting the model in each sample, and computing the quantity of interest from each model.
+Although bootstrapping tends to work well in practice, especially for complex and non-Normal estimators, refitting the model repeatedly can be prohibitively time-consuming and computationally expensive, especially for complicated models or large datasets.
+Simulation-based inference only requires the model to be fit once, and the simulations involve taking draws from a distribution produced from the single set of estimated parameters, making it much quicker in practice and allowing the user to capitalize on the already valid estimation of the model parameters.
+
+More formally, we fit a regression model $y_i = f(x_i; \beta)$, such as a linear or other generalized linear model with model coefficients $\beta$. We assume$$
 \hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})
 $$where $\hat{\beta}$ is the vector of estimates of $\beta$ and $\Sigma_{\hat{\beta}}$ is their asymptotic covariance matrix.
-We define a function $\tau(\beta)$ that represents a quantity of interest derived from the model parameters, and compute its estimate $\hat{\tau}(\beta)$ as $\tau(\hat{\beta})$.
-Next, we take $M$ draws $\tilde{\beta}^{(j)}$ for $j\in(1, \dots, M)$ from a multivariate Normal distribution with mean vector $\boldsymbol{\mu} = \hat{\beta}$ and covariance $\Sigma = \hat{\Sigma}_{\hat{\beta}}$, where $\hat{\Sigma}_{\hat{\beta}}$ is an estimate of the asymptotic covariance matrix of the parameter estimates.
-We use the distribution of $\tilde{\tau}=\tau(\tilde{\theta})$ as the "posterior" sampling distribution of $\hat{\tau}(\beta)$, and compute its variance as$$
-\sigma^2_{\hat{\tau}(\theta)} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
+We define a function $\tau(\beta)$ that represents a quantity of interest derived from the model parameters, and compute its estimate $\widehat{\tau(\beta)}$ as $\tau(\hat{\beta})$.
+Next, we take $M$ draws $\tilde{\beta}^{(j)}$ for $j\in(1, \dots, M)$ from a multivariate Normal distribution with mean vector $\mu = \hat{\beta}$ and covariance $\Sigma = \hat{\Sigma}_{\hat{\beta}}$, where $\hat{\Sigma}_{\hat{\beta}}$ is an estimate of the asymptotic covariance matrix of the parameter estimates.
+We use the distribution of $\tilde{\tau}=\tau(\tilde{\theta})$ as the "posterior" sampling distribution of $\widehat{\tau(\beta)}$, and compute its variance as$$
+\sigma^2_{\widehat{\tau(\theta)}} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
 $$and quantile $100(1-\alpha)\%$ confidence interval limits as $\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]$ where $\tilde{\tau}_{(k)}$ is the $k$th value of $\tilde{\tau}$ when arranged in ascending order.
 
-Similar functionality exists in the \pkg{CLARIFY} package in Stata [@tomzClarifySoftwareInterpreting2003][^2] and used to be available in the `Zelig` R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations.
-\pkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
-\pkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
+Similar functionality exists in the \pkg{CLARIFY} package in Stata[^2] [@tomzClarifySoftwareInterpreting2003] and used to be available in the `Zelig` R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations.
+\CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
+\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
 
-[^2]: Despite the similar name, the R package \pkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \pkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution.
+[^2]: Despite the similar name, the R package \CRANpkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \CRANpkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution.
 The R implementation avoids the "simulation-induced bias" described by @raineyCarefulConsiderationCLARIFY2023.
 
-## Using \pkg{clarify}
+## Using \CRANpkg{clarify}
 
-There are four steps to using \pkg{clarify}:
+There are four steps to using \CRANpkg{clarify}:
 
@@
 
-In the sections below, we'll describe how to implement these steps in detail. First, we'll load \pkg{clarify} using `library()`.
+In the sections below, we will describe how to implement these steps in detail. First, we will load \CRANpkg{clarify} using `library()`.
 
@@
 
-For a running example, we'll use the `lalonde` dataset in the \pkg{MatchIt} package [@JSSv042i08], which contains data on 614 participants enrolled in a job training program or sampled from a survey [@dehejiaCausalEffectsNonexperimental1999].
+For a running example, we will use the `lalonde` dataset in the \CRANpkg{MatchIt} package [@JSSv042i08], which contains data on 614 participants enrolled in a job training program or sampled from a survey [@dehejiaCausalEffectsNonexperimental1999].
 The treatment variable is `treat` and the outcome is `re78`, and all other variables are confounders.
-Although the original use of this dataset was to estimate the effect of `treat` on `re78`, we'll use it more generally to demonstrate all of \pkg{clarify}'s capabilities.
-In addition, we'll use a transformation of the outcome variable to demonstrate applications to nonlinear models, for which the benefits of simulation-based inference are more apparent.
+Although the original use of this dataset was to estimate the effect of `treat` on `re78`, we will use it more generally to demonstrate all of \CRANpkg{clarify}'s capabilities.
+In addition, we will use a transformation of the outcome variable to demonstrate applications to nonlinear models, for which the benefits of simulation-based inference are more apparent.
 
@@
 The first step is to fit the model.
-\pkg{clarify} can operate on a large set of models (those supported by \pkg{marginaleffects}), including generalized linear models, multinomial models, multivariate models, and instrumental variable models, many of which are available in other R packages.
-Even if \pkg{clarify} does not offer direct support for a given model, there are ways to use its functionality regardless (explained in more detail below).
+\CRANpkg{clarify} can operate on a large set of models (those supported by \CRANpkg{marginaleffects}), including generalized linear models, multinomial models, multivariate models, and instrumental variable models, many of which are available in other R packages.
+Even if \CRANpkg{clarify} does not offer direct support for a given model, there are ways to use its functionality regardless (explained in more detail below).
 
 Because we are computing derived quantities, it is not critical to parameterize the model in such a way that the coefficients are interpretable, e.g., by using a model with interpretable coefficients or centering predictors.
-Below, we'll fit a probit regression model for the outcome given the treatment and confounders.
-Coefficients in probit regression do not have a straightforward interpretation, but that's okay; our quantities of interest can be expressed as derived quantities---functions of the model parameters, such as predictions, counterfactual predictions, and averages and contrasts of them.
+Below, we will fit a probit regression model for the outcome given the treatment and confounders.
+Coefficients in probit regression do not have a straightforward interpretation, but that does not matter; our quantities of interest can be expressed as derived quantities---functions of the model parameters, such as predictions, counterfactual predictions, and averages and contrasts of them.
 
@@
 
-If one's model is not supported by \pkg{clarify}, one can omit the `fit` argument and just specify the `vcov` and `coefs` argument, which will draw the coefficients from the distribution named in `dist` (`"normal"` by default).
+If one's model is not supported by \CRANpkg{clarify}, one can omit the `fit` argument and just specify the `vcov` and `coefs` argument, which will draw the coefficients from the distribution named in `dist` (`"normal"` by default).
 
@@
 
-For example, let's say our derived quantity of interest is the predicted probability of the outcome for participant PSID1. We would specified our `FUN` function as follows:
+For example, we will let our derived quantity of interest be the predicted probability of the outcome for participant PSID1. We would specified our `FUN` function as follows:
 
@@
 The resulting `clarify_est` object contains the simulated estimates in matrix form as well as the estimate computed on the original coefficients.
-We'll examine the sampling distribution shortly, but first we'll demonstrate computing a derived quantity from the coefficients directly.
+We will examine the sampling distribution shortly, but first we will demonstrate computing a derived quantity from the coefficients directly.
 
@@
 
-There are several functions in \pkg{clarify} that serve as convenience wrappers for `sim_apply()` to automate some common derived quantities of interest. These include
+There are several functions in \CRANpkg{clarify} that serve as convenience wrappers for `sim_apply()` to automate some common derived quantities of interest. These include
 
@@
 
--   `reference` -- whether to display a normal density over the plot for each estimate. The default is `FALSE` to omit them.
+-   `reference` -- whether to display a normal density over the plot for each estimate. The default is `FALSE` to omit it.
 
@@
 
+Overlaid on the plot in red is a Normal distribution with the same mean and standard deviation as the simulated values; this is requested by setting `reference = TRUE`.
 From the plot, one can see that the distribution of simulated values is non-Normal, asymmetrical, and not centered around the estimate, with no values falling above 1 because the outcome is a predicted probability.
@@
 
-We'll use `summary()` with the default arguments on our first `clarify_est` object to view the point estimate and quantile-based uncertainty bounds.
+We can use `summary()` with the default arguments on our first `clarify_est` object to view the point estimate and quantile-based uncertainty bounds.
 
@@
 A benefit of quantile-based confidence bounds is that the bounds will always be in the domain of the quantity of interest, e.g., bounds for probabilities will not be above 1 or below 0 if the model always generates predicted probabilities between 0 and 1.
-In contrast, Wald-type symmetric confidence intervals can include values outside the domain of the quantity of interest.
+In contrast, Wald-type symmetric confidence intervals (including those produced by the delta method) can include values outside the domain of the quantity of interest.
 While it is possible to compute Wald-type confidence interval bounds that respect the domain boundaries, e.g., by computing the confidence interval around the logit of the predicted probability and using the inverse logit of the bounds as the bound on the probability, quantile confidence intervals do not require the user to know which transformation of the quantity of interest will yield appropriate bounds.
 
-Our second estimated quantity, the difference between two regression coefficients, is closer to Normally distributed, as the plot below demonstrates (and would be expected theoretically), so we'll use the Normal approximation to test the hypothesis that difference differs from 0.
+Our second estimated quantity, the difference between two regression coefficients, is closer to Normally distributed, as the plot below demonstrates (and would be expected theoretically), so we will use the Normal approximation to test the hypothesis that difference differs from 0.
 
@@
 
-## `sim_apply()` wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`
+## `sim_apply()` Wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`
 
-`sim_apply()` can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \pkg{clarify} provides shortcut functions to make computing these quantities simple.
+`sim_apply()` can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \CRANpkg{clarify} provides shortcut functions to make computing these quantities simple.
 These functions include `sim_setx()`, `sim_ame()`, and `sim_adrf()`.
-Each of these can be used only when regression models compatible with \pkg{clarify} are supplied to the original call to `sim()`.
+Each of these can be used only when regression models compatible with \CRANpkg{clarify} are supplied to the original call to `sim()`.
 
@@
 For example, we might want to know what the effect of treatment is for a "typical" individual, which corresponds to the contrast between two model-based predictions (i.e., one under treatment and one under control for a unit with "typical" covariate values).
-This functionality mirrors the `setx()` and `setx1()` functionality of `Zelig` (which is where its name originates) and provides similar functionality to functions in \pkg{modelbased}, \pkg{emmeans}, \pkg{effects}, and \pkg{ggeffects}.
+This functionality mirrors the `setx()` and `setx1()` functionality of `Zelig` (which is where its name originates) and provides similar functionality to functions in \CRANpkg{modelbased}, \CRANpkg{emmeans}, \CRANpkg{effects}, and \CRANpkg{ggeffects}.
 
-For each predictor, the user can specify whether they want predictions at specific values or at "typical" values, which are defined in \pkg{clarify} as the mode for unordered categorical and binary variables, the median for ordered categorical variables, and the mean for continuous variables.
+For each predictor, the user can specify whether they want predictions at specific values or at "typical" values, which are defined in \CRANpkg{clarify} as the mode for unordered categorical and binary variables, the median for ordered categorical variables, and the mean for continuous variables.
 Predictions for multiple predictor combinations can be requested by specifying values that will be used to create a grid of predictor values, or the grid itself can be supplied as a data frame of desired predictor profiles.
@@
 
-Here, we'll use `sim_setx()` to examine predicted values of the outcome for control and treated units, at `re75` set to 0 and 20000, and `race` set to "black".
+Here, we will use `sim_setx()` to examine predicted values of the outcome for control and treated units, at `re75` set to 0 and 20000, and `race` set to "black".
 
@@
 
-We can plot the distributions of the simulated values using `plot()`, which also separates the predictions by the predictor values (it's often clearer without the uncertainty bounds).
+We can plot the distributions of the simulated values using `plot()`, which also separates the predictions by the predictor values (it is often clearer without the uncertainty bounds).
 The `var` argument controls which variable is used for faceting the plots.
@@
 
-We'll return to display average dose-response functions using `sim_adrf()` later.
+We will return to display average dose-response functions using `sim_adrf()` later.
 
@@
 Using predicted values and effects at representative values is one way to summarize regression models, but another way is to compute average adjusted predictions (AAPs), contrasts of AAPs, and average marginal effects (AMEs).
-The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units[^3].
+The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units[^3] [@longRegressionModelsCategorical2014].
 
-[^3]: In \pkg{marginaleffects}, AAPs are computed using `avg_predictions()`, AMEs for binary variables are computed using `avg_comparisons()`, and AMEs for continuous variables are computed using `avg_slopes()`.
+[^3]: In \CRANpkg{marginaleffects}, AAPs are computed using `avg_predictions()`, AMEs for binary variables are computed using `avg_comparisons()`, and AMEs for continuous variables are computed using `avg_slopes()`.
 AAPs are sometimes known as average "counterfactual" predictions.
@@
 
-Here, we'll use `sim_ame()` to compute the AME of `treat` just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT [@greiferChoosingCausalEstimand2023]).
-We'll request our estimate to be on the risk ratio scale.
+Here, we will use `sim_ame()` to compute the AME of `treat` just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT [@greiferChoosingCausalEstimand2023]).
+We will request our estimate to be on the risk ratio scale.
 
@@
 
-We can use `summary()` to display the estimates and their uncertainty intervals. Here, we'll also use `null` to include a test for the null hypothesis that the risk ratio is equal to 1.
+We can use `summary()` to display the estimates and their uncertainty intervals. Here, we will also use `null` to include a test for the null hypothesis that the risk ratio is equal to 1.
 
@@
 
-We can compute the AME for a continuous predictor. Here, we'll consider `age` (just for demonstration; this analysis does not have a valid interpretation).
+We can compute the AME for a continuous predictor. Here, we will consider `age` (just for demonstration; this analysis does not have a valid interpretation).
 
@@
 
-Below, we'll examine effect modification of the ATT by the predictor `married` using the `by` argument to estimate AAPs and their ratio within levels of `married`:
+Below, we will examine effect modification of the ATT by the predictor `married` using the `by` argument to estimate AAPs and their ratio within levels of `married`:
 
@@
 
-Here, we'll consider `age` (just for demonstration; this analysis does not have a valid interpretation) and compute the ADRF and AMEF of `age` on the outcome.
-We'll only examine ages between 18 and 50, even though the range of `age` goes slightly beyond these values.
-First, we'll compute the ADRF of `age`, which examines how the outcome would vary on average if one set all unit's value of `age` to each value between 18 and 50 (here we only use even ages to speed up computation).
+Here, we will consider `age` (just for demonstration; this analysis does not have a valid interpretation) and compute the ADRF and AMEF of `age` on the outcome.
+We will only examine ages between 18 and 50, even though the range of `age` goes slightly beyond these values.
+First, we will compute the ADRF of `age`, which examines how the outcome would vary on average if one set all unit's value of `age` to each value between 18 and 50 (here we only use even ages to speed up computation).
 
@@
 
-Next we'll compute the AMEF, the effect of `age` at each level of `age`.
+Next we will compute the AMEF, the effect of `age` at each level of `age`.
 
@@
 
-## Transforming and combining estimates
+## Transforming and Combining Estimates
 
@@
 Similarly, to compute a derived or transformed quantity from a `clarify_est` object, we can use `transform()`.
-Here, we'll compute the risk difference AME of `treat`; previously, we used `sim_ame()` to compute the AAPs and the risk ratio.
+Here, we will compute the risk difference AME of `treat`; previously, we used `sim_ame()` to compute the AAPs and the risk ratio.
 
@@
 
-When we run `summary()` on the output, the new quantity, which we named "RD", will be displayed along with the other estimates. We'll also set a null value for this quantity.
+When we run `summary()` on the output, the new quantity, which we named "RD", will be displayed along with the other estimates. We will also set a null value for this quantity.
 
@@
 One benefit of using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.
+In contrast, Wald-type inference (based either on the simulation-derived standard error or the delta method) is not invariant to transformations of the quantity of interest.
 
@@
 `cbind()` is another generic R function that is typically used to combine two or more datasets columnwise (i.e., to widen a dataset).
-In \pkg{clarify}, `cbind()` can be used to combine two `clarify_est` objects so that the estimates can be examined jointly and so that it is possible to compare them directly.
-For example, let's say we computed AMEs in two subgroups using `subset` and wanted to compare them.
-To do so, we call `sim_ame()` twice, one for each subset (though in practice it is more effective to use `by`; this is just for illustration):
+In \CRANpkg{clarify}, `cbind()` can be used to combine two `clarify_est` objects so that the estimates can be examined jointly and so that it is possible to compare them directly.
+For example, if we were to compute AMEs in two subgroups using `subset` and wanted to compare them, we would call `sim_ame()` twice, one for each subset (though in practice it is more effective to use `by`; this is just for illustration), as demonstrated below:
 
@@
 If we wanted to compare the risk differences, we could combine them and compute a new quantity equal to their difference.
-We'll do that below.
+We will do that below.
 
-First, we need to rename to quantities in each object so they don't overlap; we can do so using `names()`, which has a special method for `clarify_est` objects.
+First, we need to rename to quantities in each object so they do not overlap; we can do so using `names()`, which has a special method for `clarify_est` objects.
 
@@
 
-## Using \pkg{clarify} with multiply imputed data
+## Using \CRANpkg{clarify} with Multiply Imputed Data
 
@@
 
-Using \pkg{clarify} with multiply imputed data is simple.
+Using \CRANpkg{clarify} with multiply imputed data is simple.
 Rather than using `sim()`, we use the function `misim()`.
@@
 `sim_apply()` and its wrappers accept the output of `misim()` and compute the desired quantity using each set of coefficients.
-When these function rely on using a dataset (e.g., `sim_ame()`, which averages predicted outcomes across all units in the dataset used to fit the model), they automatically know to associate a given coefficient draw with the imputed dataset that was used to fit the model that produced that draw.
+When these functions rely on using a dataset (e.g., `sim_ame()`, which averages predicted outcomes across all units in the dataset used to fit the model), they automatically know to associate a given coefficient draw with the imputed dataset that was used to fit the model that produced that draw.
 In user-written functions supplied to the `FUN` argument of `sim_apply()`, it is important to correctly extract the dataset from the model fit.
@@
 
-Below we illustrate using `misim()` and `sim_apply()` with multiply imputed data. We'll use the `africa` dataset from the \pkg{Amelia} package.
+Below we illustrate using `misim()` and `sim_apply()` with multiply imputed data. We will use the `africa` dataset from the \CRANpkg{Amelia} package.
 
@@
 
-The function we'll be applying to each imputed dataset will be one that computes the average marginal effect of `infl`. (We'll run the same analysis afterward using `sim_ame()`.)
+The function we will be applying to each imputed dataset will be one that computes the average marginal effect of `infl`. (We will run the same analysis afterward using `sim_ame()`.)
 
@@
 
-Note that `misim()` is compatible with model fit objects from \pkg{mice}, \pkg{Amelia}, \pkg{MatchThem}, and any other package that produces a list of model fit objects with each corresponding to the output of a model fit to an imputed dataset.
+Note that `misim()` is compatible with model fit objects from \CRANpkg{mice}, \CRANpkg{Amelia}, \CRANpkg{MatchThem}, and any other package that produces a list of model fit objects with each corresponding to the output of a model fit to an imputed dataset.
 
-## Comparison to other packages
+## Comparison to Other Packages
 
-Several packages offer methods for computing interpretable quantities form regression models, including \pkg{emmeans}, \pkg{margins}, \pkg{modelbased}, and \pkg{marginaleffects}.
-Many of the quantities computed by these packages can also be computed by \pkg{clarify}, the primary difference being that \pkg{clarify} uses simulation-based inference rather than delta method-based inference.
+Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans}, \CRANpkg{margins}, \CRANpkg{modelbased}, and \CRANpkg{marginaleffects}.
+Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.
 
-\pkg{marginaleffects} offers the most similar functionality to \pkg{clarify}, and \pkg{clarify} depends on functionality provided by \pkg{marginaleffects} to accommodate a wide variety of regression models.
-\pkg{marginaleffects} also offers simulation-based inference using `marginaleffects::inferences()` and support for arbitrary user-specified post-estimation functions using `marginaleffects::hypotheses()`.
-However, \pkg{clarify} and `marignalefefcts` differ in several ways.
-The largest difference is that \pkg{clarify} supports iterative building of more and more complex hypotheses through the `transform()` method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \pkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.
+\CRANpkg{marginaleffects} offers the most similar functionality to \CRANpkg{clarify}, and \CRANpkg{clarify} depends on functionality provided by \CRANpkg{marginaleffects} to accommodate a wide variety of regression models.
+\CRANpkg{marginaleffects} also offers simulation-based inference using `marginaleffects::inferences()` and support for arbitrary user-specified post-estimation functions using `marginaleffects::hypotheses()`.
+However, \CRANpkg{clarify} and `marignalefefcts` differ in several ways.
+The largest difference is that \CRANpkg{clarify} supports iterative building of more and more complex hypotheses through the `transform()` method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \CRANpkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.
 
-Because of \pkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing.
-\pkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.
+Because of \CRANpkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing.
+\CRANpkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.
 
-There are areas and cases where \pkg{marginaleffects} may be the better choice than \pkg{clarify} or where the differences between the packages are of little consequence.
-\pkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \pkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience.
-In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \pkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \pkg{clarify} provides.
-For the quantities easily computed by \pkg{marginaleffects} that support simulation-based inference through `marginaleffects::inferences()`, using \pkg{marginaleffects} can provide a more familiar and flexible syntax than \pkg{clarify} might offer.
-
-Note that as both packages continue to develop, these differences may grow or shrink.
-The differences above are meant to highlight the current differences and differences in philosophy and emphasis of the two packages.
+There are areas and cases where \CRANpkg{marginaleffects} may be the better choice than \CRANpkg{clarify} or where the differences between the packages are of little consequence.
+\CRANpkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \CRANpkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience.
+In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \CRANpkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \CRANpkg{clarify} provides.
+For the quantities easily computed by \CRANpkg{marginaleffects} that support simulation-based inference through `marginaleffects::inferences()`, using \CRANpkg{marginaleffects} can provide a more familiar and flexible syntax than \CRANpkg{clarify} might offer.
 Ultimately, the user should use the package that supports their desired syntax and mode of inference.
@@
 
-\pkg{clarify} provides utilities to facilitate simulation-based inference of deriving quantities form regression models.
-This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution fo the derived quantity is Normal.
-\pkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values.
-These enhance the utility and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.
+\CRANpkg{clarify} provides functionality to facilitate simulation-based inference of deriving quantities from regression models.
+This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution of the derived quantity is Normal.
+\CRANpkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values.
+These enhance the usefulness and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.

### 2024-03-08 clarify/clarify.R

@@ -8,6 +8,18 @@ knitr::opts_chunk$set(
   fig.height = 2
 )
 
+if (!requireNamespace("clarify")) {
+  install.packages("clarify")
+}
+
+if (!requireNamespace("MatchIt")) {
+  install.packages("MatchIt")
+}
+
+if (!requireNamespace("Amelia")) {
+  install.packages("Amelia")
+}
+
 
 ## -----------------------------------------------------------------------------
 library(clarify)

### 2024-03-08 R/summary.clarify_est.R
Doc updates

@@ -28,7 +28,7 @@
 #' * [sim_apply()] for applying a function to each set of simulated coefficients
 #'
 #' @references
-#' Rainey, C. (2023). A careful consideration of CLARIFY: Simulation-induced bias in point estimates of quantities of interest. *Political Science Research and Methods*, 1–10. \doi{doi.org/10.1017/psrm.2023.8}
+#' Rainey, C. (2023). A careful consideration of CLARIFY: Simulation-induced bias in point estimates of quantities of interest. *Political Science Research and Methods*, 1–10. \doi{10.1017/psrm.2023.8}
 #'
 #' @examples
 #' data("lalonde", package = "MatchIt")

### 2024-03-08 tests/testthat/test-misim.R
Test updates

@@ -1,4 +1,6 @@
 test_that("misim() works with lists of regressions", {
+  skip_if(!file.exists(test_path("fixtures", "model_list.rds")))
+
   m <- readRDS(test_path("fixtures", "model_list.rds"))
 
   s <- misim(m, n = 5)
@@ -58,6 +60,8 @@ test_that("misim() works with lists of regressions", {
 })
 
 test_that("misim() works with mira objects", {
+  skip_if(!file.exists(test_path("fixtures", "mira.rds")))
+
   m <- readRDS(test_path("fixtures", "mira.rds"))
 
   s <- misim(m, n = 5)
@@ -117,6 +121,8 @@ test_that("misim() works with mira objects", {
 })
 
 test_that("misim() works with mimira objects", {
+  skip_if(!file.exists(test_path("fixtures", "mimira.rds")))
+
   m <- readRDS(test_path("fixtures", "mimira.rds"))
 
   s <- misim(m, n = 5)
@@ -177,6 +183,8 @@ test_that("misim() works with mimira objects", {
 })
 
 test_that("sim_ame() works with misim() and glm()", {
+  skip_if(!file.exists(test_path("fixtures", "model_list.rds")))
+
   m <- readRDS(test_path("fixtures", "model_list.rds"))
 
   s <- misim(m, n = 5)

### 2024-03-08 tests/testthat/test-sim_ame.R

@@ -1,3 +1,5 @@
+Sys.setenv(`_R_S3_METHOD_REGISTRATION_NOTE_OVERWRITES_` = "false")
+
 test_that("sim_ame() doesn't work with coefs and vcov", {
   mdata <- readRDS(test_path("fixtures", "mdata.rds"))
 

### 2024-05-30 R/clarify_est_methods.R
Updates to prep for resubmission

@@ -1,74 +1,3 @@
-#' @exportS3Method cbind clarify_est
-cbind.clarify_est <- function(..., deparse.level = 1) {
-  if (...length() == 0) return(NULL)
-
-  for (i in seq_len(...length())) {
-    if (!inherits(...elt(i), "clarify_est")) {
-      .err("all supplied objects must be `clarify_est` objects, the output of calls to `sim_apply()` or its wrappers")
-    }
-  }
-
-  obj <- list(...)
-  hashes <- lapply(obj, attr, "sim_hash")
-
-  if (any(lengths(hashes) == 0) || any(!vapply(hashes, chk::vld_string, logical(1L)))) {
-    .err("all supplied objects must be unmodified `clarify_est` objects")
-  }
-  if (!all_the_same(unlist(hashes)) || !all_the_same(unlist(lapply(obj, nrow)))) {
-    .err("all supplied objects must be calls of `sim_apply()` or its wrappers on the same `clarify_sim` object")
-  }
-
-  out <- do.call("cbind", lapply(obj, drop_sim_class))
-
-  attr(out, "original") <- do.call("c", lapply(obj, attr, "original"))
-  attr(out, "sim_hash") <- hashes[[1]]
-  class(out) <- c("clarify_est", class(out))
-
-  out
-}
-
-#' @exportS3Method transform clarify_est
-transform.clarify_est <- function(`_data`, ...) {
-  e <- eval(substitute(list(...)), as.data.frame(`_data`), parent.frame())
-
-  n <- nrow(`_data`)
-  if (!all(vapply(e, function(e.) length(e.) == 0 || (length(e.) == n && is.numeric(e.)), logical(1L)))) {
-    .err("all transformations must be vector operations of the variables in the original `clarify_est` object")
-  }
-
-  e_original <- eval(substitute(list(...)), as.list(attr(`_data`, "original")), parent.frame())
-
-  inx <- match(names(e), names(`_data`))
-  matched <- !is.na(inx)
-
-  if (any(matched)) {
-    nulls <- lengths(e[matched]) == 0
-
-    if (any(!nulls)) {
-      for (i in seq_along(e)[matched][!nulls]) {
-        `_data`[, inx[i]] <- e[[i]]
-        attr(`_data`, "original")[inx[i]] <- as.numeric(e_original[i])
-      }
-    }
-
-    if (any(nulls)) {
[…]

### 2024-05-30 R/sim_ame.R

@@ -1,55 +1,114 @@
 #' Compute average marginal effects
 #'
 #' @description
-#' `sim_ame()` is a wrapper for [sim_apply()] that computes average marginal effects, the average effect of changing a single variable from one value to another (i.e., from one category to another for categorical variables or a tiny change for continuous variables).
+#' `sim_ame()` is a wrapper for [sim_apply()] that computes average
+#' marginal effects, the average effect of changing a single variable from one
+#' value to another (i.e., from one category to another for categorical
+#' variables or a tiny change for continuous variables).
 #'
 #' @inheritParams sim_apply
-#' @param var either the name of a variable for which marginal effects are to be computed or a named list of length one containing the values the variable should take. If a list is supplied or the named variables is categorical (factor, character, or having two values), categorical calculations will be triggered. Otherwise, continuous calculations will be triggered. See Details.
-#' @param subset optional; a vector used to subset the data used to compute the marginal effects. This will be evaluated within the original dataset used to fit the model using [subset()], so nonstandard evaluation is allowed.
-#' @param by a one-sided formula or character vector containing the names of variables for which to stratify the estimates. Each quantity will be computed within each level of the complete cross of the variables specified in `by`.
-#' @param contrast a string containing the name of a contrast between the average marginal means when the variable named in `var` is categorical and takes on two values. Allowed options include `"diff"` for the difference in means (also `"rd"`), `"rr"` for the risk ratio (also `"irr"`), `"log(rr):` for the log risk ratio (also `"log(irr)"`), `"sr"` for the survival ratio, `"log(sr):` for the log survival ratio, `"srr"` for the switch relative risk (also `"grrr"`), `"or"` for the odds ratio, `"log(or)"` for the log odds ratio, and `"nnt"` for the number needed to treat. These options are not case sensitive, but the parentheses must be included if present.
-#' @param outcome a string containing the name of the outcome or outcome level for multivariate (multiple outcomes) or multi-category outcomes. Ignored for univariate (single outcome) and binary outcomes.
[…]

### 2024-05-30 R/summary.clarify_est.R

@@ -22,7 +22,7 @@
 #'
 #' When `method = "wald"`, the standard deviation of the simulation estimates is used as the standard error, which is used in the z-statistics and the confidence intervals. The p-values and confidence intervals are valid only when the sampling distribution of the resulting statistic is normal (which can be assessed using `plot()`). When `method = "quantile"`, the confidence interval is calculated using the quantiles of the simulation estimates corresponding to `level`, and the p-value is calculated as twice the proportion of simulation estimates less than or greater than `null`, whichever is smaller; this is equivalent to inverting the confidence interval but is only truly valid when the true sampling distribution is only a location shift from the sampling distribution under the null hypothesis and should therefore be interpreted with caution. Using `"method = "quantile"` (the default) is recommended because the confidence intervals will be valid even if the sampling distribution is not Normally distributed. The precision of the p-values and confidence intervals depends on the number of simulations requested (the value of `n` supplied to [sim()]).
 #'
-#' The plots are produced using [ggplot2::geom_density()] and can be customized with \pkg{ggplot2} functions.
+#' The plots are produced using [ggplot2::geom_density()] and can be customized with \pkg{ggplot2} functions. When `reference = TRUE`, a reference Normal distribution is produced using the empirical mean and standard deviation of the simulated values. A blue references line is plotted at the median of the simulated values. For Wald-based inference to be valid, the reference distribution should overlap with the empirical distribution, in which case the quantile-based and Wald-based intervals should be similar. For quantile-based inference to be valid, the median of the estimates should overlap with the estimated value; this is a necessary but not sufficient condition, though.
 #'
 #' @seealso
 #' * [sim_apply()] for applying a function to each set of simulated coefficients
@@ -85,6 +85,10 @@ summary.clarify_est <- function(object,
     .err("`parm` must be a numeric or character vector identifying the estimates to summarize")
   }
 
+  chk::chk_string(method)
+  method <- match_arg(method, c("quantile", "wald"))
+  # method <- match_arg(method, c("quantile", "wald", "optimal"))
+
[…]

### 2024-05-30 R/transform.clarify_est.R

@@ -1,0 +1,156 @@
+#' #' Transform and combine `clarify_est` objects
+#'
+#' @description
+#' `transform()` modifies a `clarify_est` object by allowing for the calculation of new quantities from the existing quantities without re-simulating them. `cbind()` binds two `clarify_est` objects together.
+#'
+#' @param _data the `clarify_est` object to be transformed.
+#' @param ... for `transform()`, arguments in the form `name = value`, where `name` is the name of a new quantity to be computed and `value` is an expression that is a function of the existing quantities corresponding to the new quantity to be computed. See Details. For `cbind()`, `clarify_est` objects to be combined.
+#' @param deparse.level ignored.
+#'
+#' @details
+#' For `transform()`, the expression on the right side of the `=` should use the names of the existing quantities (e.g., `` `E[Y(1)]` - `E[Y(1)]` ``), with `` ` `` appropriately included when the quantity name include parentheses or brackets. Alternatively, it can use indexes prefixed by `.b`, e.g., `.b2 - .b1`, to refer to the corresponding quantity by position. This can aid in computing derived quantities of quantities with complicated names. (Note that if a quantity is named something like `.b1`, it will need to be referred to by position rather than name, as the position-based label takes precedence). See examples. Setting an existing value to `NULL` will remove that quantity from the object.
+#'
+#' `cbind()` does not rename the quanities or check for uniqueness of the names, so it is important to rename them yourself prior to combining the objects.
+#'
+#' @return
+#' A `clarify_est` object, either with new columns added (when using `transform()`) or combining two `clarify_est` objects. Note that any type attributes corresponding to the `sim_apply()` wrapper used (e.g., `sim_ame()`) is lost when using either function. This can affect any helper functions (e.g., `plot()`) designed to work with the output of specific wrappers.
+#'
+#' @seealso [transform()], [cbind()], [sim()]
+#'
+#' @examples
+#' data("lalonde", package = "MatchIt")
+#'
+#' # Fit the model
[…]

### 2024-05-30 tests/testthat/test-misim.R

@@ -196,7 +196,7 @@ test_that("sim_ame() works with misim() and glm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 2)
   expect_identical(names(e), c("E[Y(0)]", "E[Y(1)]"))
-  expect_identical(attr(e, "var"), "treat")
+  expect_identical(attr(e, "var"), list(treat = 0:1))
 
   e <- sim_ame(s, "treat", contrast = "log(rr)", verbose = FALSE)
 
@@ -205,7 +205,7 @@ test_that("sim_ame() works with misim() and glm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
   expect_identical(names(e), c("E[Y(0)]", "E[Y(1)]", "log(RR)"))
-  expect_identical(attr(e, "var"), "treat")
+  expect_identical(attr(e, "var"), list(treat = 0:1))
 
   expect_warning(sim_ame(s, "race", contrast = "diff", verbose = FALSE),
                  "`contrast` is ignored")
@@ -216,7 +216,7 @@ test_that("sim_ame() works with misim() and glm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
   expect_identical(names(e), c("E[Y(black)]", "E[Y(hispan)]", "E[Y(white)]"))
-  expect_identical(attr(e, "var"), "race")
+  expect_identical(attr(e, "var"), list(race = c("black", "hispan", "white")))
 
   e <- sim_ame(s, list(race = c("black", "white")), contrast = "nnt", verbose = FALSE)
   expect_good_clarify_est(e)
@@ -224,7 +224,7 @@ test_that("sim_ame() works with misim() and glm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
   expect_identical(names(e), c("E[Y(black)]", "E[Y(white)]", "NNT"))
-  expect_identical(attr(e, "var"), "race")
+  expect_identical(attr(e, "var"), list(race = c("black", "white")))
 
   #Continuous variable
   e <- sim_ame(s, "age", verbose = FALSE)
@@ -233,7 +233,7 @@ test_that("sim_ame() works with misim() and glm()", {
[…]

### 2024-05-30 tests/testthat/test-sim_ame.R

@@ -28,7 +28,7 @@ test_that("sim_ame() works with lm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 2)
   expect_identical(names(e), c("E[Y(0)]", "E[Y(1)]"))
-  expect_identical(attr(e, "var"), "treat")
+  expect_identical(attr(e, "var"), list(treat = 0:1))
 
   e <- sim_ame(s, "treat", contrast = "diff", verbose = FALSE)
 
@@ -37,7 +37,7 @@ test_that("sim_ame() works with lm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
   expect_identical(names(e), c("E[Y(0)]", "E[Y(1)]", "Diff"))
-  expect_identical(attr(e, "var"), "treat")
+  expect_identical(attr(e, "var"), list(treat = 0:1))
 
   expect_warning(sim_ame(s, "race", contrast = "diff", verbose = FALSE),
                  "`contrast` is ignored")
@@ -48,7 +48,7 @@ test_that("sim_ame() works with lm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
   expect_identical(names(e), c("E[Y(black)]", "E[Y(hispan)]", "E[Y(white)]"))
-  expect_identical(attr(e, "var"), "race")
+  expect_identical(attr(e, "var"), list(race = c("black", "hispan", "white")))
 
   e <- sim_ame(s, list(race = c("black", "white")), contrast = "diff", verbose = FALSE)
   expect_good_clarify_est(e)
@@ -56,7 +56,7 @@ test_that("sim_ame() works with lm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 3)
   expect_identical(names(e), c("E[Y(black)]", "E[Y(white)]", "Diff"))
-  expect_identical(attr(e, "var"), "race")
+  expect_identical(attr(e, "var"), list(race = c("black", "white")))
 
   #Continuous variable
   e <- sim_ame(s, "age", verbose = FALSE)
@@ -65,7 +65,7 @@ test_that("sim_ame() works with lm()", {
   expect_equal(attr(e, "sim_hash"), attr(s, "sim_hash"))
   expect_equal(ncol(e), 1)
   expect_identical(names(e), "E[dY/d(age)]")
[…]

### 2024-05-30 clarify/Submission 2/response_to_reviewers.Rmd
Reorganized for resubmission

---
title: "Response to Reviewers"
author:  
  - name: Noah Greifer
  - name: Steven Worthington
  - name: Stefano Iacus
  - name: Gary King
date: "`r Sys.Date()`"
output: html_document
---

We are extremely grateful to the reviewers for providing feedback on our article, "`clarify`: Simulation-Based Inference for Regression Models". We are honored to have received positive feedback and have made efforts to incorporate their suggestions into the article, which we believe have strengthened it. We will respond to the reviewers' points in turn.

## Reviewer 1

> A bit of background on my perspective as a reviewer. As the paper notes, there is some “disagreement” in practice (and maybe in theory) about the relative value of the delta-method versus simulation-based inference. I fall into the delta-method camp. As such, I’m slightly skeptical of the method the paper proposes. That said, I don’t have a huge problem with the approach that the authors propose—I would never suggest that a researcher should switch from {clarify} to {marginaleffects}, for example. That said, I’m going to make an argument for publication, and that argument is from the perspective of a skeptic. Others might make stronger arguments for publication.

We appreciate the reviewer's candidness and support for our article despite their reservations.

> ### Strengths
>
> First, the paper is extremely clear about both the software and the method. I sometimes find modern software frustrating because it’s not always clear what the software is doing. I assume that it’s doing good things, but I’m not always sure what it’s doing. That is not the case with this paper. The authors describe the software interface clearly, but also the method that the software is implementing.

We appreciate the reviewer's kind words about our article.

> Second, this package is important for historical reasons. CLARIFY was (is?) an immensely popular Stata package among political scientists. {Zelig} never took off, but was widely known among political scientists. In my opinion, {clarify} is an excellent, smart replacement for {Zelig}. This paper is worth publishing because of the historical importance of CLARIFY and Zelig among political scientists. Will {clarify} be as popular as {marginaleffects}? I don’t think so. Will it help political scientists trained in and around 2003 to 2018? Absolutely. King, Tomz, and Wittenberg (2000) is one of the most cited political science papers ever, so it would be a real shame to not have a well-documented R package to implement those ideas. (I’m not sure how popular this method was/is outside political science; perhaps it’s also important in some adjacent social sciences.)

We thank the reviewer for acknowledging this. Indeed, the development of `clarify` was motivated by `Zelig`'s removal from CRAN and decreased support. We are aware of its historical impact and hope that `clarify` will not only allow users to continue to access some of `Zelig`'s most useful features, but also make those features easier to use without compromising the ability to maintain the package. We recognize that much of `Zelig`'s influence has been within the field of political science, but we hope that `clarify` can be a seen as a general-purpose package for researchers in any discipline. In our extended literature review, we found an independent literature in psychological methods that uses simulation-based inference for derived quantities in mediation analysis.

> This two points seem uncontroversial and should weigh heavily in favor of publication.

> ### A (Minor) Weakness
>
> I would gently push back on a few stronger claims in the paper regarding the performance of the simulation-based intervals over the delta intervals. Here are a few examples:
>
> 1.  “often more accurate than using the delta method” (p. 1)
> 2.  “Given its non-Normality, the quantile-based bounds are clearly more appropriate than those resulting from the Normal approximation, as the bounds computed from the Normal approximation would be outside the bounds of the estimate.” (p. 6)
> 3.  “Inverting the uncertainty interval involves finding the smallest confidence level such that the null value is within the confidence bounds. The p-value for the test is one minus this level.” (p. 6)
> 4.  “including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid)” (p. 16)
>
> I think the authors would agree with this summary of their position: When the simulations of the quantity of interest is not normal, then simulation-based inference should be preferred.”
>
> It isn’t clear to me why this summary would be true.
>
> For example, if I knew the sampling distribution was skewed to the right, then I would want a CI with a longer arm to the left and a shorter arm to the right, else the CI will misses won’t be symmetric (e.g., 2.5% low, 2.5% high). To make this concrete, suppose you get a point estimate at the 97.5th percentile of a right-skewed sampling distribution. Then you have to go really far back to the left to capture the truth. If you get a point estimate at the 2.5th percentile of this same sampling distribution, then you only need to go a little bit to the right to capture the truth. Thus, the CI with the nominal behavior would seem to require a short arm to the right and a long arm to the left. Simulation-based inference does the opposite of this. It’s my intuition that equal-armed CIs would work better than CIs with a long and short arm on the “wrong” side. This is merely my intuition.
>
> The quote from p. 1 is stated as a matter of fact, but it’s not clear what the authors mean by “more accurate” or what conception of “accurate” would make this statement true. Similarly for “valid” on p. 16.
>
> The most natural reading of “more accurate” seems to be “closer to nominal coverage” (e.g., 95% capture rate). The authors suggest that the delta method will not approximately achieve this coverage when the sampling distribution is far from symmetric. This seems non-controversial. But it seems to me (based on intuition/theory and simulations) that the simulation-based intervals will also behave poorly in these same scenarios (with this poor behavior translating to the p-values). Claims 1, 2, and 4 above seem to assume that simulation-based inference will meaningfully improve on the delta method when the sampling distribution is non-normal, but I can’t quite see why that should be (see discussion above). Claim 3 depends on claims 1, 2, and 4.
>
> If they are able, I suggest that the authors (1) clarify their usage of “accurate” and “valid” and (2) support these points with references and or brief justifications. It’s certainly beyond the scope of the paper to fully justify these claims, but given the matter-of-factness with which the authors make these claims, perhaps stating the claims more clearly or justifying them briefly would be helpful to readers.
>
> I should emphasize, though, that this is “small beans”—mostly theoretical navel gazing—because asymptotic results apply and simulation-based inference is easy to use and historically important and popular.

We thank the reviewer for this insightful point and nice example of how quantile-based intervals could be misleading in exactly the scenario we have recommended them. We are reminded of the difference between "basic" and "percentile" confidence intervals in the context of bootstrapping, where the "basic" interval seems to address the difficulties with skewness demonstrated by your example. While a similar idea could be implemented here, we prefer to wait until more research as been done before implementing and recommending it.

On the other hand, percentile confidence intervals for bootstrapping have an invariance property even for skewed distributions: as long as some transformation of the estimate would have a distribution symmetric about the transformed estimate, the untransformed percentile intervals will have the correct coverage. For this to be true, the median of the distribution of estimates should overlap with the point estimate. This property would be expected to apply for simulated quantile intervals, too, and we have implemented this as an additional diagnostic in the `plot()` method. We now mention this advantage in the paper; this also ties into the issue of back-transforming brought up by the other reviewer.

We have soften the language used throughout the paper, being sure to avoid unsupported claims about statistical performance, especially in comparison to the delta method. We performed a more extensive literature search and found several papers that empirically compared simulation-based intervals and the delta method. While in some cases performance (i.e., with respect to coverage) was similar, there were some specific cases, primarily in the context of mediation analysis, in which the quantile confidence intervals had slightly better coverage than the delta method-based Wald intervals. We have attempted to reframe simulation-based inference as an alternative to the delta method rather than a replacement, acknowledging that little empirical research has been done comparing the approaches for general statistical analysis.

## Reviewer 2

> Thank you for giving me the opportunity to review this interesting paper.
>
> I like the paper a lot. It is clear and well-written.
>
> The software is of high quality. I have tried it, read the documentation, and skimmed its code base. The authors follow modern best practices for development, including many unit tests, thorough documentation, and a nice website with a useful vignette and a migration guide for users of the older `Zelig` package. Well done!

We thank the reviewer for taking the time to review it and for their kind words about the paper and package.

> ### Motivation
>
> The motivation for simulation-based inference could be improved. For example, on page 1 the authors state that:
>
> > Simulation-based inference is not only often more accurate than using the delta method, it is also simpler to understand and implement, as it does not require understanding Taylor series or the calculus that underlies it. This makes it more palatable to nontechnical audiences and easier to learn for students without sacrificing statistical performance.
>
> This is a red herring. Easy to use software implements the delta method by default, and nontechnical audiences and students essentially never have to implement the delta method themselves.

We have clarified this in the paper, focusing on ease of understanding the method rather than ease of implementation, which we acknowledge has been greatly simplified since King et al. (2000) due to the development of modern packages including `marginaleffects`.

> Also, what does "accurate" mean, exactly? What does "often" mean? Under what conditions, exactly? This is a paper about software, so I don't expect a full theoretical investigation. But there should be at least be a little bit more discussion and breadcrumbs for users to follow. Are there good theoretical or simulation studies on the properties of this strategy, identifying when it works better or worse? Currently, the reader might leave the paper with the impression that simulation-based inference strictly dominates the delta method and bootstrapping in all cases, except along the computational cost dimension. Is that really true? I'll freely admit that I'm a bit skeptical, but I would love to see some references to authors who probe this question. I'm sure other readers would find this useful too in deciding whether they should use `clarify`.
>
> The flip side of this question is: If simulation-based inference is easier and more accurate, why isn't everyone using it already? What's the market failure?

Thank you for this comment. We have attempted to soften the language used and provide citations for studies that have compared the performance of the delta method and simulation-based inference. Unfortunately, there are few studies comparing the two for general inference of common quantities like average adjusted predictions or average marginal effects, but for the few quantities that have been studied, simulation-based inference has competitive performance. In general, by "accurate" and "valid" we mean achieving close to nominal coverage rates.

We highlight scenarios in which each of the three methods by be expected to perform better than the others, when they might fail, and when they might be expected to agree. However, there has been insufficient research done to make strong affirmative claims recommending any approach over the others universally, and we attempt to avoid making such claims.

Although simulation-based inference may be less common nowadays, it is worth noting that King et al. (2000), which introduced to method to political scientists, is among the most highly cited political methodology articles as noted by the other reviewer, and the software packages that implement its method, `Zelig` and `CLARIFY` for Stata, have been widely used. Modern tools that implement the delta method like `marginaleffects` and `margins` in Stata are certainly the standard nowadays, but we argue there has not been a general-purpose simulation-based inference package in R, which may have reduced its uptake. Additionally, researchers may be resistant to use a less-studied method, especially one that is computationally intensive and yields results that depend on a seed; we are sympathetic to these concerns but believe simulation-based inference should at least be available in an easy-to-use package, even if it is currently less commonly used than other methods.

> ### Approximations in simulation-based inference
>
> The authors write:
>
> > Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates.
>
> This may seem trivial, taking M random draws will lead to a different result than drawing a different M' set of coefficients. Clearly, there's a simulation-related approximation going on. This should be acknowledged early in the intro. The authors should revise the text to avoid saying that simulation-based inference requires no approximation.

We have noted the approximation due to Monte Carlo error and highlight that many replications may be required for results to stabilize. We highlight that this is a disadvantage for simulation-based inference relative to the delta method.

> ### Assumption or approximation?
>
> The abstract and introduction sell simulation-based inference as a way to relax "assumptions" of the delta method, but then goes on to talk about "approximations" that may fail:
>
> > The usual method for estimating the uncertainty of the derived quantities is known as the “delta method”, which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the estimate of the derived quantity is normally distributed.
>
> The classic textbook treatment of the delta method talks about two assumptions: continuity, and normality of the $\hat{\theta}$ --- not of derived quantities $h(\hat{\theta})$. Do the authors see a distinction between a violation of delta method assumptions and a "failure" of approximations in finite samples? If so, this should be cleared up in the abstract and intro to avoid confusion.

Normailty of $h(\hat\theta)$ is required for valid use of Normal quantile for Wald-based inference of the derived quantity. Of course both simulation-based inference and the delta method require joint Normality of $\hat\theta$. We have attempted to clarify this and soften the language around assumptions and their violation. We also cite a few studies that have compared their performance for derived quantities that explicitly do not have a Normal distribution.

> ### Backtransformation
>
> Quotes like these two feel misleading: because standard practice in such GLM models it to build confidence intervals by backtransformation, rather than by naively constructing symmetric intervals:
>
> > For example, predicted probabilities close to 0 or 1 or ratios of coefficients or probabilities typically do not have normal (or even symmetrical) distributions in finite samples, and the usual Wald-type confidence interval limits produced from delta method standard errors can include values outside the domain of the quantity of interest.
>
> > One can see again how a delta method or Normal approximation may not have yielded valid uncertainty intervals given the non-Normality of the distributions.
>
> Most of the alternative packages in `R` will automatically use backtransformation to build confidence intervals that do not stretch outside reasonable bounds. Of course, this is not possible or easy for all model types. But if they authors want to make a big deal out of that critique --- open with it on page 1 and reiterate it in the text --- they should probably show an example where this is a real problem

Thank you for this comment. We have attempted to clarify this and include a footnote acknowledging this. A benefit of simulation-based inference is that as long as there exists a transformation that yields a symmetric distribution, one does not need to know what that transformation is in order for the quantile-based interval to be valid; this has been described for quantile intervals for the bootstrap, which we now reference in the paper. To keep the paper focused on the software, we have chosen not to delve too deeply into a thorough empirical comparison between the methods to highlight when either might fail.

> ### Minor notes
>
> -   Why are all functions prefixed with `sim_`? I would argue that these prefixes are extraneous, and that this is what the namespace is for.
> -   Can `plot()` draw on more dimensions if more variables are included in `sim_setx()`?
> -   It is not clear to me from the documentation what `null` values are acceptable in `summary()`. I see RD and RR. What else?
>
> > The largest difference is that clarify supports iterative building of more and more complex hypotheses through the transform() method, which quickly computes new quantities and transformation from the existing computed quantities, whereas marginaleffects only supports a single transformation
>
> Or users can call `posterior_draws()` to manipulate the draws themselves, but this is admittedly less convenient.

We prefixed functions with `sim_` to highlight that these are specifically to be used after running `sim()`. Although the namespace and class checking accomplishes this as well, removing the `sim_` prefix would leave functions like `apply()`, `adrf()`, and `ame()`, suggetsing these functions are general-purpose functions for computing the relevant quantity, whereas they are specifically to be used in the context of simulation-based inference with `clarify`. This also avoid namespace clashes with other packagest hat might implement more general-purpose functions.

Yes, `plot()` can include other variable combinations as colors or facets when used with `sim_setx()`. In practice, varying too many variables will create cluttered plots, so we highlight simpler plots in the paper as example use cases.

The user can supply any value to `null` depending on the hypothesis they want to test, if any. Often, researchers are interested in tests of no effect, which needs to be defined differently for the contrast being used. For example, to test a hypothesis that two probabilities are equal, one can test whether their difference is 0, their ratio is 1, or their odds ratio is 1, etc. We do not specify which values the null should take to allow users to supply their own hypothesis. In some cases, hypothesis testing may not be of interest at all (e.g., for model predictions), so `null` can be omitted.

Although it is certainly possible to perform similar manipulations from the `marginaleffects` output, we would argue that because the focus of `clarify` is solely on simulation-based inference, its interface is more user-friendly for this analysis. `posterior_draws()` output needs to be reshaped and is better designed for expert users than casual users of the package, whereas `transform()` uses an existing base R function with a simple interface that yields an objects with the same properties as the object the user started with. We would like to think `transform()` is one of the biggest contributions of this package, as it supports iterative construction of more and more complicated quantities of interest without any increase in computational time.

------------------------------------------------------------------------

We thank both reviewers for their insightful comments and support for the paper and package. We hope to have improved the paper through their comments while maintain our position that `clarify` implements useful methodology for applied researchers, and therefore would benefit the R community.

### 2024-05-30 clarify/Submission 1/clarify.Rmd
Reorganized for resubmission

--- 2024-03-08 clarify/clarify.Rmd
@@
 It avoids several assumptions required by the delta method that are commonly violated, especially in nonlinear models, but does not require models to be refit as when using the bootstrap.
-It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form the sampling distribution of the quantity.
+It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form a simulated "posterior" distribution of the quantity.
 `clarify` provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
@@
 
-\CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.
+\CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating a "posterior" distributions of the derived quantities.
 Simulation-based inference is not only often more accurate than using the delta method, it is also simpler to understand and implement, as it does not require understanding Taylor series or the calculus that underlies it.
@@
 The methodology \CRANpkg{clarify} relies on is described in @kingMakingMostStatistical2000 and @raineyCarefulConsiderationCLARIFY2023.
-Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a "posterior" distribution, which is taken to be the sampling distribution of the derived quantity, and from which uncertainty measures (standard errors and confidence intervals) can be computed.
+Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a "posterior" distribution, from which uncertainty measures (standard errors and confidence intervals) can be computed.
 This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values, a standard assumption motivated by the central limit theorem that underlies usual inference on the original model parameters.
-Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates.
+Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates, except for the approximation due to Monte-Carlo error induced by sampling from a finite number of simulations.
 The delta method makes these same assumptions in addition to the approximations about the variance and the shape of the sampling distribution of the estimates of the derived quantities.
@@
 
+# Create a binary outcome variable
 lalonde$re78_0 <- ifelse(lalonde$re78 > 0, 1, 0)
@@
 
-For example, we will let our derived quantity of interest be the predicted probability of the outcome for participant PSID1. We would specified our `FUN` function as follows:
+For example, we will let our derived quantity of interest be the predicted probability of the outcome for participant PSID1. We specify our `FUN` function as follows:
 
@@
 The resulting `clarify_est` object contains the simulated estimates in matrix form as well as the estimate computed on the original coefficients.
-We will examine the sampling distribution shortly, but first we will demonstrate computing a derived quantity from the coefficients directly.
+We will examine the posterior distribution shortly, but first we will demonstrate computing a derived quantity from the coefficients directly.
 
@@
 The uncertainty intervals and p-values in the `summary()` output are computed using the Normal approximation because we set `method = "wald"`, and the p-value for the test that our estimate is equal to 0 is returned because we set `null = 0`.
-Note that the Normal approximation should be used only when the simulated sampling distribution is both close to Normally distributed and centered around the estimate (i.e., when the mean of the simulated values [red vertical line] coincides with the estimate computed on the original coefficients [black vertical line]).
+Note that the Normal approximation should be used only when the simulated posterior distribution is both close to Normal and centered around the estimate (i.e., when the mean of the simulated values [red vertical line] coincides with the estimate computed on the original coefficients [black vertical line]).
 
@@
 
-`sim_apply()` can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \CRANpkg{clarify} provides shortcut functions to make computing these quantities simple.
+`sim_apply()` can be used to compute the simulated posterior distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \CRANpkg{clarify} provides shortcut functions to make computing these quantities simple.
 These functions include `sim_setx()`, `sim_ame()`, and `sim_adrf()`.

### 2024-05-30 clarify/Submission 2/clarify.Rmd
Reorganized for resubmission

--- 2024-05-30 clarify/Submission 1/clarify.Rmd
@@
 abstract: >
-  Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects and adjusted predictions.
-It avoids several assumptions required by the delta method that are commonly violated, especially in nonlinear models, but does not require models to be refit as when using the bootstrap.
-It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form a simulated "posterior" distribution of the quantity.
+  Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects, average adjusted predictions, and other functions of model parameters.
+It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form a simulated "posterior" distribution of the quantity from which confidence intervals can be computed.
 `clarify` provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
@@
 Although regression models are frequently used in empirical research to study relationships among variables, often the quantity of substantive interest is not one of the coefficients of the model, but rather a quantity derived from the coefficients, such as predicted values or average marginal effects.
-The usual method for estimating the uncertainty of the derived quantities is known as the "delta method", which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the estimate of the derived quantity is normally distributed[^1].
-In many cases, especially with nonlinear models, these approximation can fail badly.
-For example, predicted probabilities close to 0 or 1 or ratios of coefficients or probabilities typically do not have normal (or even symmetrical) distributions in finite samples, and the usual Wald-type confidence interval limits produced from delta method standard errors can include values outside the domain of the quantity of interest.
+Quantifying the uncertainty of these derived quantities (i.e., computing standard errors, confidence intervals, and p-values) requires additional processing.
+Several methods of doing so exist, including the delta method, the bootstrap, and simulation-based inference.
+\CRANpkg{clarify} implements simulation-based inference, which we describe below along with these other methods.
 
-[^1]: In addition, most software that uses the delta method uses numerical differentiation, which also involves an approximation.
+The delta method involves computing a first-order Taylor series approximation to the variance of the derived quantity, and standard Wald-based inference relies on computing quantiles based on the Normal distribution and using them to compute p-values and confidence intervals.
+\CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating a "posterior" distribution of the derived quantities.
+Simulation-based inference does not require understanding Taylor series or the calculus that underlies it, which can make it more palatable to nontechnical audiences and easier to learn for students without necessarily sacrificing statistical performance [@kingMakingMostStatistical2000; @zelnerUsingSimulationInterpret2009].
+Some studies have found that simulation-based inference performs as well or better than the delta method for computing derived quantities (i.e., with respect to achieving close to nominal coverage for confidence intervals), especially for complicated derived quantities and in smaller samples [@mackinnonConfidenceLimitsIndirect2004; @holeComparisonApproachesEstimating2007; @herronPostestimationUncertaintyLimited1999].
+Its empirical performance has been particularly well studied in the context of mediation analysis, in which the quantities of interest are products and ratios of regression coefficients, where it has been shown to perform well relative to the delta method due to the non-Normality of these quantities [@tofighiMonteCarloConfidence2016; @preacherAdvantagesMonteCarlo2012].
 
-\CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating a "posterior" distributions of the derived quantities.
-Simulation-based inference is not only often more accurate than using the delta method, it is also simpler to understand and implement, as it does not require understanding Taylor series or the calculus that underlies it.
-This makes it more palatable to nontechnical audiences and easier to learn for students without sacrificing statistical performance.
-
-The methodology \CRANpkg{clarify} relies on is described in @kingMakingMostStatistical2000 and @raineyCarefulConsiderationCLARIFY2023.
+The methodology \CRANpkg{clarify} relies on was developed by @krinsky1986 and is described in @kingMakingMostStatistical2000 and @herronPostestimationUncertaintyLimited1999.
 Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a "posterior" distribution, from which uncertainty measures (standard errors and confidence intervals) can be computed.
 This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values, a standard assumption motivated by the central limit theorem that underlies usual inference on the original model parameters.
-Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates, except for the approximation due to Monte-Carlo error induced by sampling from a finite number of simulations.
-The delta method makes these same assumptions in addition to the approximations about the variance and the shape of the sampling distribution of the estimates of the derived quantities.
+Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates, except for the approximation due to Monte Carlo error induced by sampling from a finite number of simulations (which can always be reduced by increasing the number of draws at the cost of increased computing time).
 
-The nonparametric bootstrap is another alternative to the delta method for inference that does not require these approximations; it typically involves re-sampling individuals from the sample, fitting the model in each sample, and computing the quantity of interest from each model.
+The nonparametric bootstrap is another alternative to the delta method for inference that does not require its analytic approximations [@efronBootstrapMethodsStandard1986]; bootstrapping typically involves re-sampling individuals from the sample, fitting the model in each bootstrap sample, and computing the quantity of interest from each model.
 Although bootstrapping tends to work well in practice, especially for complex and non-Normal estimators, refitting the model repeatedly can be prohibitively time-consuming and computationally expensive, especially for complicated models or large datasets.
 Simulation-based inference only requires the model to be fit once, and the simulations involve taking draws from a distribution produced from the single set of estimated parameters, making it much quicker in practice and allowing the user to capitalize on the already valid estimation of the model parameters.
+Methods for computing valid confidence intervals in cases when the quantity of interest has a complicated distribution are better developed when bootstrapping, however [@efronBootstrapMethodsStandard1986].
 
@@
 We define a function $\tau(\beta)$ that represents a quantity of interest derived from the model parameters, and compute its estimate $\widehat{\tau(\beta)}$ as $\tau(\hat{\beta})$.
-Next, we take $M$ draws $\tilde{\beta}^{(j)}$ for $j\in(1, \dots, M)$ from a multivariate Normal distribution with mean vector $\mu = \hat{\beta}$ and covariance $\Sigma = \hat{\Sigma}_{\hat{\beta}}$, where $\hat{\Sigma}_{\hat{\beta}}$ is an estimate of the asymptotic covariance matrix of the parameter estimates.
-We use the distribution of $\tilde{\tau}=\tau(\tilde{\theta})$ as the "posterior" sampling distribution of $\widehat{\tau(\beta)}$, and compute its variance as$$
-\sigma^2_{\widehat{\tau(\theta)}} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
-$$and quantile $100(1-\alpha)\%$ confidence interval limits as $\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]$ where $\tilde{\tau}_{(k)}$ is the $k$th value of $\tilde{\tau}$ when arranged in ascending order.
+To perform simulation-based inference, we take $M$ draws $\tilde{\beta}^{(j)}$ for $j\in(1, \dots, M)$ from a multivariate Normal distribution with mean vector $\mu = \hat{\beta}$ and covariance $\Sigma = \hat{\Sigma}_{\hat{\beta}}$, where $\hat{\Sigma}_{\hat{\beta}}$ is an estimate of the asymptotic covariance matrix of the parameter estimates.
+We use the distribution of $\tilde{\tau}=\tau(\tilde{\beta})$ as the "posterior" distribution of $\widehat{\tau(\beta)}$, and compute its variance as$$
+\hat\sigma^2_{\widehat{\tau(\beta)}} = \frac{1}{M-1}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
+$$and quantile $100(1-\alpha)\%$ confidence interval limits as $\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]$ where $\tilde{\tau}_{(q)}$ is the $q$th value of $\tilde{\tau}$ when arranged in ascending order (i.e., the $q$th quantile of the empirical cumulative distribution function).
+Simulation-based Wald-type confidence intervals can be computed as $\left[\tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{\frac{\alpha}{2}}, \tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{1-\frac{\alpha}{2}} \right]$, where $Z_q$ is the $q$th quantile of a standard Normal distribution.
+The delta method-based Wald-type confidence intervals use this formula but with the first-order Taylor approximation to the asymptotic variance: $\hat\sigma^2_{\widehat{\tau(\beta)}}=\nabla\tau(\hat{\beta}) \Sigma_{\hat{\beta}} \nabla\tau'(\hat{\beta})$, where $\nabla\tau(\hat{\beta})$ is the gradient of $\tau(\beta)$ with respect to $\beta$ evaluated at $\hat{\beta}$.
+
+To compute a p-value for a hypothesis test involving the quantity of interest, i.e., $\text{H}_0: \tau (\beta) = \tau_0$ with a given null value $\tau_0$, we can invert the confidence interval [@thulinModernStatisticsWrangling2021]; that is, we find the largest value of $\alpha$ such that $\tau_0$ is within the confidence interval and use that $\alpha$ as the p-value for the test.
+For Wald-based inference (either using the simulation-based variance or delta method-based variance), this is equivalent to performing a standard two-sided Z-test using the test statistic $Z=\left(\tau(\hat\beta)-\tau_0\right) / \hat\sigma_{\widehat{\tau(\beta)}}$.
+One benefit of using the quantile p-values for inference is that equivalent tests of the same hypothesis will always yield identical p-values; for example, testing the equality of two derived quantities will yield the same p-value when comparing the difference between the quantities against a null hypothesis of 0 and the ratio of the quantities against a null hypothesis of 1, as each of these hypothesis is true if and only if the other is true.
+
+One would expect simulation-based quantile inference, simulation-based Wald inference, and delta method-based Wald inference to align when the posterior is Normally distributed around the estimate, in which case any discrepancies would be due to Monte Carlo error in the simulated values (and therefore would shrink with increasing draws).
+However, for low values of $\alpha$, it may require many draws for the simulation-based intervals to stabilize; delta method-based intervals are not subject to this error.
+There are a few cases in which the results might diverge: in some cases, the first-order Taylor series approximation to the variance may be poor, though in practice the approximation error is small and shrinks quickly with increasing sample size.
+When the posterior distribution is non-Normal but symmetric around the estimate, the quantile intervals may be more accurate (i.e., in the sense of achieving closer to nominal coverage) because they do not rely on quantiles from the Normal distribution [@tofighiMonteCarloConfidence2016].
+
+Another potential advantage quantile intervals can have over Wald-intervals is that when *some* monotonic transformation of the estimate has a symmetric distribution centered around the transformed estimate, the quantile intervals can achieve correct coverage without requiring knowledge of *which* transformation is required [@efronBootstrapMethodsStandard1986]; this is true of the quantile-based p-values as well.
+When the distribution is not centered around the estimate and no monotonic transformation will make it so, though, neither quantile-based nor Wald-based intervals would be expected to perform well, and quantile intervals could yield even worse coverage than Wald-based intervals, a phenomenon that occurs in the context of bootstrapping [@efronBootstrapMethodsStandard1986][^1].
+An informal falsification test for whether such a monotonic transformation exists is whether the median of the simulated estimates is aligned with the point estimate; if it is not, there is no monotonic transformation that will yield a symmetric quantile interval with the desired coverage.
+
+[^1]: We thank an anonymous reviewer for pointing out a scenario in which this could occur: for a quantity of interest with a right-skewed sampling distribution, one would prefer an estimate to the right of the quantity's true value to have a confidence interval skewed to left to capture the bulk of the sampling distribution, but in practice a quantile confidence interval would also be skewed to the right.
+While a symmetric Wald-based interval may not have adequate coverage, the quantile-based interval could perform even worse.
+
+## Related Software
 
@@
 \CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
-\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
+\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package [@arel-bundockMarginaleffectsPredictionsComparisons2024], which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
 
@@
 
-2.  Use `sim()` to take draws from the sampling distribution of the estimated model coefficients.
+2.  Use `sim()` to take draws from the multivariate distribution of the estimated model coefficients.
 
@@
 
-```{r}
+```{r library}
 library(clarify)
@@
 
-```{r}
+```{r data}
 data("lalonde", package = "MatchIt")
@@
 
-```{r}
+```{r fit}
 fit <- glm(re78_0 ~ treat * married + age + educ + race +
@@
 -   `dist` -- the name of the distribution from which to draw the sampled coefficients.
-Can be `"normal"` for a Normal distribution or `t(#)` for a t-distribution, where `#` represents the degrees of freedom.
+Can be `"normal"` for a Normal distribution or `t(#)` for a T-distribution, where `#` represents the degrees of freedom.
 If left unspecified, `sim()` will decide on which distribution makes sense given the characteristics of the model (the decision is made by `insight::get_df()` with `type = "wald"`).
@@
 `sim()` uses a random number generator to draw the sampled coefficients from the sampling distribution, so a seed should be set using `set.seed()` to ensure results are replicable across sessions.
+Using more iterations (i.e., increasing `n`) yields results that will be more stable across runs even when a seed is not set.
 
@@
 
-```{r}
+```{r sim}
 set.seed(1234)
@@
 
-After sampling the coefficients, we will compute derived quantities on each set of sampled coefficients and store the result, which represents the "posterior" distribution of the derived quantity, as well as on the original coefficients, which are used as the final estimates.
+After sampling the coefficients, one can compute derived quantities on each set of sampled coefficients and store the result, which represents the "posterior" distribution of the derived quantity, as well as on the original coefficients, which are used as the final estimates.
 The core functionality is provided by `sim_apply()`, which accepts a `clarify_sim` object from `sim()` and a function to compute and return one or more derived quantities, then applies that function to each set of simulated coefficients.
@@
 
-```{r}
+```{r sim_fun1}
 sim_fun1 <- function(fit) {
@@
 
-```{r}
+```{r est1}
 est1 <- sim_apply(s, FUN = sim_fun1, verbose = FALSE)
@@
 
-```{r}
+```{r sim_fun2}
 sim_fun2 <- function(coefs) {
@@
 -   `method` -- if `ci` is `TRUE`, the method used to compute the bounds.
-Allowable methods include a Normal approximation (`"wald"`) or using the quantiles of the resulting distribution (`"quantile"`).
+Allowable methods include thea Normal approximation (`"wald"`) or using the quantiles of the resulting distribution (`"quantile"`).
 The Normal approximation involves multiplying the standard deviation of the estimates (i.e., which functions like the standard error of the sampling distribution) by the critical Z-statistic computed using `(1-level)/2` to create a symmetric margin of error around the point estimate.
-The default is `"quantile"` to instead use quantile-based bounds, which are more appropriate when the distribution is non-Normal.
-However, quantile-based bounds may require more simulations to stabilize.
+The default is `"quantile"` to instead use quantile-based bounds.
 
--   `reference` -- whether to display a normal density over the plot for each estimate. The default is `FALSE` to omit it.
+-   `reference` -- whether to display a normal density over the plot for each estimate and an indicator line for the median of the estimate. The default is `FALSE` to omit them.
 
@@
 
-```{r, fig.width=4}
+```{r plot1, fig.width=4}
 plot(est1, reference = TRUE, ci = FALSE)
@@
 From the plot, one can see that the distribution of simulated values is non-Normal, asymmetrical, and not centered around the estimate, with no values falling above 1 because the outcome is a predicted probability.
-Given its non-Normality, the quantile-based bounds are clearly more appropriate than those resulting from the Normal approximation, as the bounds computed from the Normal approximation would be outside the bounds of the estimate.
+Given its non-Normality, the quantile-based bounds may be more appropriate than those resulting from the Normal approximation, as the bounds computed from the Normal approximation would be outside the bounds of the estimate.
+The blue reference line for the median of the estimates is close to the point estimate, suggesting it is possible for a monotonic transformation to have a symmetric distribution around the estimate[^3].
 The plot itself is a `ggplot` object that can be modified using `ggplot2` syntax.
+
+[^3]: In fact, we know the inverse link function for the model (i.e., the Normal distribution function `qnorm()`) is such a transformation in this case; \CRANpkg{marginaleffects} and other packages that implement the delta method for confidence intervals around model predictions typically automatically compute confidence intervals on the transformed predictions before transforming the intervals back using the model's link function.
+As long as such a transformation exists, the quantile intervals will be as valid as those that rely on transforming and back-transforming.
 
@@
 
--   `null` -- an optional argument specifying the null value in a hypothesis test for the estimates.
+-   `null` -- an optional argument specifying the desired null value in a hypothesis test for the estimates.
 If specified, a p-value will be computed using either a standard Z-test (if `method` is `"wald"`) or an inversion of the uncertainty interval (described below).
@@
 
-Inverting the uncertainty interval involves finding the smallest confidence level such that the null value is within the confidence bounds.
-The p-value for the test is one minus this level.
-It is only valid as a p-value when the simulated distribution of the estimates differs from its true sampling distribution under the null value by a location shift (which can be violated when the distribution of the estimates is asymmetric).
-However, because the p-values are invariant to monotonic transformations of the estimates and null value, as long as the distribution of *some* monotonic transformation of the estimate is a location shift from its sampling distribution under the null hypothesis, the p-values will be valid.
-
 We can use `summary()` with the default arguments on our first `clarify_est` object to view the point estimate and quantile-based uncertainty bounds.
 
-```{r}
+```{r summary1}
 summary(est1)
@@
 
-A benefit of quantile-based confidence bounds is that the bounds will always be in the domain of the quantity of interest, e.g., bounds for probabilities will not be above 1 or below 0 if the model always generates predicted probabilities between 0 and 1.
-In contrast, Wald-type symmetric confidence intervals (including those produced by the delta method) can include values outside the domain of the quantity of interest.
-While it is possible to compute Wald-type confidence interval bounds that respect the domain boundaries, e.g., by computing the confidence interval around the logit of the predicted probability and using the inverse logit of the bounds as the bound on the probability, quantile confidence intervals do not require the user to know which transformation of the quantity of interest will yield appropriate bounds.
-
 Our second estimated quantity, the difference between two regression coefficients, is closer to Normally distributed, as the plot below demonstrates (and would be expected theoretically), so we will use the Normal approximation to test the hypothesis that difference differs from 0.
 
-```{r, fig.width=4}
+```{r plot2, fig.width=4}
 plot(est2, reference = TRUE, ci = FALSE)
@@
 Note that the Normal approximation should be used only when the simulated posterior distribution is both close to Normal and centered around the estimate (i.e., when the mean of the simulated values [red vertical line] coincides with the estimate computed on the original coefficients [black vertical line]).
+In such cases, however, the delta method will likely perform as well, if not better, and all of its other benefits apply (i.e., it is computationally quicker and not subject to Monte Carlo error).
 
@@
 
-```{r}
+```{r setx3}
 est3 <- sim_setx(s,
@@
 
-```{r}
+```{r summary3}
 summary(est3)
@@
 
-```{r}
+```{r attr3}
 attr(est3, "setx")
@@
 
-```{r, fig.width=5}
+```{r plot3, fig.width=5}
 plot(est3, var = "re75", ci = FALSE)
@@
 
-One can see again how a delta method or Normal approximation may not have yielded valid uncertainty intervals given the non-Normality of the distributions.
+One can see again how a delta method or Normal approximation may have yielded uncertainty intervals outside the plausible range of the estimate without applying knowledge of the correct transformation to use to avoid doing so.
 
@@
 
-```{r}
+```{r setx4}
 est4 <- sim_setx(s,
@@
 
-```{r, fig.width=5}
+```{r plot4, fig.width=5}
 plot(est4)
@@
 
-```{r}
+```{r setx5}
 est5 <- sim_setx(s,
@@
 
-```{r}
+```{r summary5}
 summary(est5)
@@
 Using predicted values and effects at representative values is one way to summarize regression models, but another way is to compute average adjusted predictions (AAPs), contrasts of AAPs, and average marginal effects (AMEs).
-The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units[^3] [@longRegressionModelsCategorical2014].
+The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units[^4] [@longRegressionModelsCategorical2014].
 
-[^3]: In \CRANpkg{marginaleffects}, AAPs are computed using `avg_predictions()`, AMEs for binary variables are computed using `avg_comparisons()`, and AMEs for continuous variables are computed using `avg_slopes()`.
+[^4]: In \CRANpkg{marginaleffects}, AAPs are computed using `avg_predictions()`, AMEs for binary variables are computed using `avg_comparisons()`, and AMEs for continuous variables are computed using `avg_slopes()`.
 AAPs are sometimes known as average "counterfactual" predictions.
@@
 
-```{r}
+```{r ame6}
 est6 <- sim_ame(s,
@@
 
-```{r}
+```{r summary6}
 summary(est6, null = c(`RR` = 1))
@@
 
-```{r}
+```{r ame7}
 est7 <- sim_ame(s,
@@
 
-```{r}
+```{r summary7}
 summary(est7)
@@
 
-```{r}
+```{r ame6b}
 est6b <- sim_ame(s,
@@
 
-```{r}
+```{r adrf8}
 age_seq <- seq(18, 50, by = 2)
@@
 
-```{r, fig.width=5}
+```{r plot8, fig.width=5}
 plot(est8)
@@
 
-```{r}
+```{r summary8}
 summary(est8, parm = 1:4)
@@
 
-```{r}
+```{r adrf9}
 est9 <- sim_adrf(s,
@@
 
-```{r, fig.width=5}
+```{r plot9, fig.width=5}
 plot(est9)
@@
 `transform()` is a generic function in R that is typically used to create a new variable in a data frame that is a function of other columns.
-For example, to compute the binary outcome we used in our model, we could have run the following[^4]:
+For example, to compute the binary outcome we used in our model, we could have run the following[^5]:
 
-[^4]: Users familiar with the `tidyverse` will note the similarities between `transform()` and `dplyr::mutate()`; only `transform()` can be used with `clarify_est` objects.
+[^5]: Users familiar with the `tidyverse` will note the similarities between `transform()` and `dplyr::mutate()`; only `transform()` can be used with `clarify_est` objects.
 
-```{r}
+```{r transform_demo}
 lalonde <- transform(lalonde,
@@
 
-```{r}
+```{r transform6}
 est6 <- transform(est6,
@@
 
-Note that we used tics (\`) around the names of the AAPs; this is necessary when they contain special characters like parentheses or brackets.
+Note that we used tics (`` ` ``) around the names of the AAPs; this is necessary when they contain special characters like parentheses or brackets.
+An alternative is to use the shortcut names `.b#`, where `#` is replaced with a number (e.g., as `.b1`, `.b2`, etc.) corresponding to the index of the quantity referenced.
+For example, because `E[Y(1)]`and`E[Y(0)]` are the second and first computed quantities, respectively, the above code could be replaced with
+
+```{r transform6b, eval = FALSE}
+est6 <- transform(est6,
+                  RD = .b2 - .b1)
+```
+
+which will yield identical results[^6].
+
+[^6]: Note that if a quantity is named `.b#`, e.g., `.b1`, it can only be referred to using the positional shortcut and not its named.
+That is, the positional shortcut takes precedence over the names of the quantities.
 
@@
 
-```{r}
+```{r summary6_transform}
 summary(est6, null = c(`RR` = 1, `RD` = 0))
@@
 
-One benefit of using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.
-In contrast, Wald-type inference (based either on the simulation-derived standard error or the delta method) is not invariant to transformations of the quantity of interest.
+As mentioned previously, one benefit of using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for testing the same hypothesis with the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.
+In contrast, Wald-type inference (based on either the simulation-derived or delta method standard error) is not invariant to transformations of the quantity of interest.
 
@@
 
-```{r}
+```{r summary6b_transform}
 est6b |>
-  transform(RR_ratio = `RR[1]` / `RR[0]`) |>
-  summary(parm = c("RR[0]", "RR[1]", "RR_ratio"),
+  transform(`RR[1]/RR[0]` = `RR[1]` / `RR[0]`) |>
+  summary(parm = c("RR[0]", "RR[1]", "RR[1]/RR[0]"),
           null = 1)
@@
 
-`RR_ratio` contains the ratio of the risk ratios for `married = 1` and `married = 0`. Here we also include a test for whether each of the risk ratios and their ratio differ from 1.
+`RR[1]/RR[0]` contains the ratio of the risk ratios for `married = 1` and `married = 0`.
+Here we also include a test for whether each of the risk ratios and their ratio differ from 1, which is equivalent to testing whether the risk ratios differ across levels of `married`.
 
@@
 
-```{r}
+```{r ame_by_race}
 # AME of treat with race = "black"
@@
 
-First, we need to rename to quantities in each object so they do not overlap; we can do so using `names()`, which has a special method for `clarify_est` objects.
+First, we need to rename the quantities in each object so they do not overlap; we can do so using `names()`, which has a special method for `clarify_est` objects.
 
-```{r}
+```{r names}
 names(est10b) <- paste(names(est10b), "b", sep = "_")
@@
 
-```{r}
+```{r cbind10}
 est10 <- cbind(est10b, est10h)
@@
 
-```{r}
+```{r summary10}
 est10 <- transform(est10,
@@
 Importantly, `cbind()` can only be used to join together `clarify_est` objects computed using the same simulated coefficients (i.e., resulting from the same call to `sim()`).
-This preserves the covariance among the estimated quantities, which is critical for valid inference.
+This preserves the covariance among the estimated quantities, which is critical for maintaining valid inference.
 That is, `sim()` should only be called once per model, and all derived quantities should be computed using its output.
@@
 
-```{r, include=F}
+```{r amelia_load, include=F}
 amelia_ok <- requireNamespace("Amelia", quietly = TRUE)
@@
 
-```{r, message=F}
+```{r misim, message=F}
 library(Amelia)
@@
 
-The function we will be applying to each imputed dataset will be one that computes the average marginal effect of `infl`. (We will run the same analysis afterward using `sim_ame()`.)
+The function we will be applying to each imputed dataset will be one that computes the AME of `infl`. (We will run the same analysis afterward using `sim_ame()`.)
 
-```{r}
+```{r esi_mi}
 sim_fun <- function(fit) {
@@
 
-```{r}
+```{r est_mi2}
 est_mi2 <- sim_ame(si, var = "infl", verbose = FALSE)
@@
 
-Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans}, \CRANpkg{margins}, \CRANpkg{modelbased}, and \CRANpkg{marginaleffects}.
+Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} [@lenthEmmeansEstimatedMarginal2024], \CRANpkg{margins} [@leeperMarginsMarginalEffects2024], \CRANpkg{modelbased} [@makowskiEstimationModelbasedPredictions2020], and \CRANpkg{marginaleffects} [@arel-bundockMarginaleffectsPredictionsComparisons2024].
 Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.
@@
 However, \CRANpkg{clarify} and `marignalefefcts` differ in several ways.
-The largest difference is that \CRANpkg{clarify} supports iterative building of more and more complex hypotheses through the `transform()` method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \CRANpkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.
+The largest difference is that \CRANpkg{clarify} supports iterative building of more and more complex hypotheses through the `transform()` method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \CRANpkg{marginaleffects} only supports a single transformation and, as of version 0.20.0, cannot use simulation-based inference for these quantities.
 
-Because of \CRANpkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing.
-\CRANpkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.
+Because of \CRANpkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to view the distributions of simulated values and support for parallel processing.
+\CRANpkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules.
 
@@
 \CRANpkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \CRANpkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience.
-In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \CRANpkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \CRANpkg{clarify} provides.
+In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately Normally distributed in finite samples), using the delta method through \CRANpkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \CRANpkg{clarify} provides.
 For the quantities easily computed by \CRANpkg{marginaleffects} that support simulation-based inference through `marginaleffects::inferences()`, using \CRANpkg{marginaleffects} can provide a more familiar and flexible syntax than \CRANpkg{clarify} might offer.
@@
 \CRANpkg{clarify} provides functionality to facilitate simulation-based inference of deriving quantities from regression models.
-This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution of the derived quantity is Normal.
-\CRANpkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values.
-These enhance the usefulness and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.
+This framework provides an alternative to the delta method that can yield confidence intervals with closer to nominal coverage for some quantities of interest.
+While we do not claim simulation-based inference should be universally preferred over delta method-based inference, there are cases in which it can retain some advantageous properties, and we hope the availability of these methods in \CRANpkg{clarify} encourages additional research on when those properties can be realized and facilitates empirical work that takes advantages of these properties.

### 2024-05-30 clarify/Submission 2/clarify.tex
Reorganized for resubmission

--- 2023-09-19 clarify/clarify.tex
@@
 % !TeX root = RJwrapper.tex
-\title{clarify: Simulation-Based Inference for Regression Models}
+\title{\texttt{clarify}: Simulation-Based Inference for Regression Models}
 
@@
 It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form the sampling distribution of the quantity.
-\pkg{clarify} provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
-\pkg{clarify} supports a large and growing number of models through its interface with the \pkg{marginaleffects} package and provides native support for multiply imputed data.
+\texttt{clarify} provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
+\texttt{clarify} supports a large and growing number of models through its interface with the \texttt{marginaleffects} package and provides native support for multiply imputed data.
 }
@@
 Although regression models are frequently used in empirical research to study relationships among variables, often the quantity of substantive interest is not one of the coefficients of the model, but rather a quantity derived from the coefficients, such as predicted values or average marginal effects.
-The usual method for estimating the uncertainty of the derived quantities is known as the ``delta method'', which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the resulting estimate is normally distributed\footnote{In addition, most software that uses the delta method uses numerical differentiation, which also involves an approximation.}.
+The usual method for estimating the uncertainty of the derived quantities is known as the ``delta method'', which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the estimate of the derived quantity is normally distributed\footnote{In addition, most software that uses the delta method uses numerical differentiation, which also involves an approximation.}.
 In many cases, especially with nonlinear models, these approximation can fail badly.
-\pkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.
-
-The methodology \pkg{clarify} relies on is described in King, Tomz, and Wittenberg (2000) and Rainey (2023).
+For example, predicted probabilities close to 0 or 1 or ratios of coefficients or probabilities typically do not have normal (or even symmetrical) distributions in finite samples, and the usual Wald-type confidence interval limits produced from delta method standard errors can include values outside the domain of the quantity of interest.
+
+\CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.
+Simulation-based inference is not only often more accurate than using the delta method, it is also simpler to understand and implement, as it does not require understanding Taylor series or the calculus that underlies it.
+This makes it more palatable to nontechnical audiences and easier to learn for students without sacrificing statistical performance.
+
+The methodology \CRANpkg{clarify} relies on is described in King, Tomz, and Wittenberg (2000) and Rainey (2023).
 Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a ``posterior'' distribution, which is taken to be the sampling distribution of the derived quantity, and from which uncertainty measures (standard errors and confidence intervals) can be computed.
-This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values.
-Arriving at the posterior distribution does not require taking any derivatives or making any approximations except those used to define the sampling distribution of the parameter estimates.
-The delta method makes these same approximation in addition to the approximations of the variance and the shape of the sampling distribution of the estimates.
-
-More formally, we fit a regression model \(y_i = f(x_i; \beta)\), such a linear or generalized linear model with model coefficients \(\beta\). We assume\[
+This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values, a standard assumption motivated by the central limit theorem that underlies usual inference on the original model parameters.
+Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates.
+The delta method makes these same assumptions in addition to the approximations about the variance and the shape of the sampling distribution of the estimates of the derived quantities.
+
+The nonparametric bootstrap is another alternative to the delta method for inference that does not require these approximations; it typically involves re-sampling individuals from the sample, fitting the model in each sample, and computing the quantity of interest from each model.
+Although bootstrapping tends to work well in practice, especially for complex and non-Normal estimators, refitting the model repeatedly can be prohibitively time-consuming and computationally expensive, especially for complicated models or large datasets.
+Simulation-based inference only requires the model to be fit once, and the simulations involve taking draws from a distribution produced from the single set of estimated parameters, making it much quicker in practice and allowing the user to capitalize on the already valid estimation of the model parameters.
+
+More formally, we fit a regression model \(y_i = f(x_i; \beta)\), such as a linear or other generalized linear model with model coefficients \(\beta\). We assume\[
 \hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})
 \]where \(\hat{\beta}\) is the vector of estimates of \(\beta\) and \(\Sigma_{\hat{\beta}}\) is their asymptotic covariance matrix.
-We define a function \(\tau(\beta)\) that represents a quantity of interest derived from the model parameters, and compute its estimate \(\hat{\tau}(\beta)\) as \(\tau(\hat{\beta})\).
-Next, we take \(M\) draws \(\tilde{\beta}^{(j)}\) for \(j\in(1, \dots, M)\) from a multivariate Normal distribution with mean vector \(\boldsymbol{\mu} = \hat{\beta}\) and covariance \(\Sigma = \hat{\Sigma}_{\hat{\beta}}\), where \(\hat{\Sigma}_{\hat{\beta}}\) is an estimate of the asymptotic covariance matrix of the parameter estimates.
-We use the distribution of \(\tilde{\tau}=\tau(\tilde{\theta})\) as the ``posterior'' sampling distribution of \(\hat{\tau}(\beta)\), and compute its variance as\[
-\sigma^2_{\hat{\tau}(\theta)} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
+We define a function \(\tau(\beta)\) that represents a quantity of interest derived from the model parameters, and compute its estimate \(\widehat{\tau(\beta)}\) as \(\tau(\hat{\beta})\).
+Next, we take \(M\) draws \(\tilde{\beta}^{(j)}\) for \(j\in(1, \dots, M)\) from a multivariate Normal distribution with mean vector \(\mu = \hat{\beta}\) and covariance \(\Sigma = \hat{\Sigma}_{\hat{\beta}}\), where \(\hat{\Sigma}_{\hat{\beta}}\) is an estimate of the asymptotic covariance matrix of the parameter estimates.
+We use the distribution of \(\tilde{\tau}=\tau(\tilde{\theta})\) as the ``posterior'' sampling distribution of \(\widehat{\tau(\beta)}\), and compute its variance as\[
+\sigma^2_{\widehat{\tau(\theta)}} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
 \]and quantile \(100(1-\alpha)\%\) confidence interval limits as \(\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]\) where \(\tilde{\tau}_{(k)}\) is the \(k\)th value of \(\tilde{\tau}\) when arranged in ascending order.
 
-Similar functionality exists in the \pkg{CLARIFY} package in Stata {[}Tomz, Wittenberg, and King (2003){]}\footnote{Despite the similar name, the R package \pkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \pkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution.
-The R implementation avoids the ``simulation-induced bias'' described by Rainey (2023).} and used to be available in the \texttt{Zelig} R package (Imai, King, and Lau 2008), though there are differences in these implementations.
-\pkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
-\pkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
+Similar functionality exists in the \pkg{CLARIFY} package in Stata\footnote{Despite the similar name, the R package \CRANpkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \CRANpkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution.
+The R implementation avoids the ``simulation-induced bias'' described by Rainey (2023).} (Tomz, Wittenberg, and King 2003) and used to be available in the \texttt{Zelig} R package (Imai, King, and Lau 2008), though there are differences in these implementations.
+\CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
+\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
 
 \hypertarget{using}{%
-\subsection{\texorpdfstring{Using \pkg{clarify}}{Using }}\label{using}}
-
-There are four steps to using \pkg{clarify}:
+\subsection{\texorpdfstring{Using \CRANpkg{clarify}}{Using }}\label{using}}
+
+There are four steps to using \CRANpkg{clarify}:
 
@@
 
-In the sections below, we'll describe how to implement these steps in detail. First, we'll load \pkg{clarify} using \texttt{library()}.
+In the sections below, we will describe how to implement these steps in detail. First, we will load \CRANpkg{clarify} using \texttt{library()}.
 
@@
 
-For a running example, we'll use the \texttt{lalonde} dataset in the \pkg{MatchIt} package (Ho et al.
+For a running example, we will use the \texttt{lalonde} dataset in the \CRANpkg{MatchIt} package (Ho et al.
 2011), which contains data on 614 participants enrolled in a job training program or sampled from a survey (Dehejia and Wahba 1999).
 The treatment variable is \texttt{treat} and the outcome is \texttt{re78}, and all other variables are confounders.
-Although the original use of this dataset was to estimate the effect of \texttt{treat} on \texttt{re78}, we'll use it more generally to demonstrate all of \pkg{clarify}'s capabilities.
-In addition, we'll use a transformation of the outcome variable to demonstrate applications to nonlinear models, for which the benefits of simulation-based inference are more apparent.
+Although the original use of this dataset was to estimate the effect of \texttt{treat} on \texttt{re78}, we will use it more generally to demonstrate all of \CRANpkg{clarify}'s capabilities.
+In addition, we will use a transformation of the outcome variable to demonstrate applications to nonlinear models, for which the benefits of simulation-based inference are more apparent.
 
@@
 
-If one's model is not supported by \pkg{clarify}, one can omit the \texttt{fit} argument and just specify the \texttt{vcov} and \texttt{coefs} argument, which will draw the coefficients from the distribution named in \texttt{dist} (\texttt{"normal"} by default).
+If one's model is not supported by \CRANpkg{clarify}, one can omit the \texttt{fit} argument and just specify the \texttt{vcov} and \texttt{coefs} argument, which will draw the coefficients from the distribution named in \texttt{dist} (\texttt{"normal"} by default).
 
@@
 
-For example, let's say our derived quantity of interest is the predicted probability of the outcome for participant PSID1. We would specified our \texttt{FUN} function as follows:
+For example, we will let our derived quantity of interest be the predicted probability of the outcome for participant PSID1. We would specified our \texttt{FUN} function as follows:
 
@@
 The resulting \texttt{clarify\_est} object contains the simulated estimates in matrix form as well as the estimate computed on the original coefficients.
-We'll examine the sampling distribution shortly, but first we'll demonstrate computing a derived quantity from the coefficients directly.
+We will examine the sampling distribution shortly, but first we will demonstrate computing a derived quantity from the coefficients directly.
 
@@
 
-There are several functions in \pkg{clarify} that serve as convenience wrappers for \texttt{sim\_apply()} to automate some common derived quantities of interest. These include
+There are several functions in \CRANpkg{clarify} that serve as convenience wrappers for \texttt{sim\_apply()} to automate some common derived quantities of interest. These include
 
@@
 \item
-  \texttt{reference} -- whether to display a normal density over the plot for each estimate. The default is \texttt{FALSE} to omit them.
+  \texttt{reference} -- whether to display a normal density over the plot for each estimate. The default is \texttt{FALSE} to omit it.
 \end{itemize}
@@
 
+Overlaid on the plot in red is a Normal distribution with the same mean and standard deviation as the simulated values; this is requested by setting \texttt{reference\ =\ TRUE}.
 From the plot, one can see that the distribution of simulated values is non-Normal, asymmetrical, and not centered around the estimate, with no values falling above 1 because the outcome is a predicted probability.
@@
 
-We'll use \texttt{summary()} with the default arguments on our first \texttt{clarify\_est} object to view the point estimate and quantile-based uncertainty bounds.
+We can use \texttt{summary()} with the default arguments on our first \texttt{clarify\_est} object to view the point estimate and quantile-based uncertainty bounds.
 
@@
 \hypertarget{sim_apply-wrappers-sim_setx-sim_ame-sim_adrf}{%
-\subsection{\texorpdfstring{\texttt{sim\_apply()} wrappers: \texttt{sim\_setx()}, \texttt{sim\_ame()}, \texttt{sim\_adrf()}}{sim\_apply() wrappers: sim\_setx(), sim\_ame(), sim\_adrf()}}\label{sim_apply-wrappers-sim_setx-sim_ame-sim_adrf}}
-
-\texttt{sim\_apply()} can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \pkg{clarify} provides shortcut functions to make computing these quantities simple.
+\subsection{\texorpdfstring{\texttt{sim\_apply()} Wrappers: \texttt{sim\_setx()}, \texttt{sim\_ame()}, \texttt{sim\_adrf()}}{sim\_apply() Wrappers: sim\_setx(), sim\_ame(), sim\_adrf()}}\label{sim_apply-wrappers-sim_setx-sim_ame-sim_adrf}}
+
+\texttt{sim\_apply()} can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \CRANpkg{clarify} provides shortcut functions to make computing these quantities simple.
 These functions include \texttt{sim\_setx()}, \texttt{sim\_ame()}, and \texttt{sim\_adrf()}.
-Each of these can be used only when regression models compatible with \pkg{clarify} are supplied to the original call to \texttt{sim()}.
+Each of these can be used only when regression models compatible with \CRANpkg{clarify} are supplied to the original call to \texttt{sim()}.
 
@@
 For example, we might want to know what the effect of treatment is for a ``typical'' individual, which corresponds to the contrast between two model-based predictions (i.e., one under treatment and one under control for a unit with ``typical'' covariate values).
-This functionality mirrors the \texttt{setx()} and \texttt{setx1()} functionality of \texttt{Zelig} (which is where its name originates) and provides similar functionality to functions in \pkg{modelbased}, \pkg{emmeans}, \pkg{effects}, and \pkg{ggeffects}.
-
-For each predictor, the user can specify whether they want predictions at specific values or at ``typical'' values, which are defined in \pkg{clarify} as the mode for unordered categorical and binary variables, the median for ordered categorical variables, and the mean for continuous variables.
+This functionality mirrors the \texttt{setx()} and \texttt{setx1()} functionality of \texttt{Zelig} (which is where its name originates) and provides similar functionality to functions in \CRANpkg{modelbased}, \CRANpkg{emmeans}, \CRANpkg{effects}, and \CRANpkg{ggeffects}.
+
+For each predictor, the user can specify whether they want predictions at specific values or at ``typical'' values, which are defined in \CRANpkg{clarify} as the mode for unordered categorical and binary variables, the median for ordered categorical variables, and the mean for continuous variables.
 Predictions for multiple predictor combinations can be requested by specifying values that will be used to create a grid of predictor values, or the grid itself can be supplied as a data frame of desired predictor profiles.
@@
 
-Here, we'll use \texttt{sim\_setx()} to examine predicted values of the outcome for control and treated units, at \texttt{re75} set to 0 and 20000, and \texttt{race} set to ``black''.
+Here, we will use \texttt{sim\_setx()} to examine predicted values of the outcome for control and treated units, at \texttt{re75} set to 0 and 20000, and \texttt{race} set to ``black''.
 
@@
 
-We can plot the distributions of the simulated values using \texttt{plot()}, which also separates the predictions by the predictor values (it's often clearer without the uncertainty bounds).
+We can plot the distributions of the simulated values using \texttt{plot()}, which also separates the predictions by the predictor values (it is often clearer without the uncertainty bounds).
 The \texttt{var} argument controls which variable is used for faceting the plots.
@@
 
-We'll return to display average dose-response functions using \texttt{sim\_adrf()} later.
+We will return to display average dose-response functions using \texttt{sim\_adrf()} later.
 
@@
 Using predicted values and effects at representative values is one way to summarize regression models, but another way is to compute average adjusted predictions (AAPs), contrasts of AAPs, and average marginal effects (AMEs).
-The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units\footnote{In \pkg{marginaleffects}, AAPs are computed using \texttt{avg\_predictions()}, AMEs for binary variables are computed using \texttt{avg\_comparisons()}, and AMEs for continuous variables are computed using \texttt{avg\_slopes()}.
-AAPs are sometimes known as average ``counterfactual'' predictions.}.
+The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units\footnote{In \CRANpkg{marginaleffects}, AAPs are computed using \texttt{avg\_predictions()}, AMEs for binary variables are computed using \texttt{avg\_comparisons()}, and AMEs for continuous variables are computed using \texttt{avg\_slopes()}.
+AAPs are sometimes known as average ``counterfactual'' predictions.} (Long and Freese 2014).
 
@@
 
-Here, we'll use \texttt{sim\_ame()} to compute the AME of \texttt{treat} just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT (Greifer and Stuart 2023)).
-We'll request our estimate to be on the risk ratio scale.
+Here, we will use \texttt{sim\_ame()} to compute the AME of \texttt{treat} just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT (Greifer and Stuart 2023)).
+We will request our estimate to be on the risk ratio scale.
 
@@
 
-We can use \texttt{summary()} to display the estimates and their uncertainty intervals. Here, we'll also use \texttt{null} to include a test for the null hypothesis that the risk ratio is equal to 1.
+We can use \texttt{summary()} to display the estimates and their uncertainty intervals.
+Here, we will also use \texttt{null} to include a test for the null hypothesis that the risk ratio is equal to 1.
 
@@
 
-We can compute the AME for a continuous predictor. Here, we'll consider \texttt{age} (just for demonstration; this analysis does not have a valid interpretation).
+We can compute the AME for a continuous predictor. Here, we will consider \texttt{age} (just for demonstration; this analysis does not have a valid interpretation).
 
@@
 
-Below, we'll examine effect modification of the ATT by the predictor \texttt{married} using the \texttt{by} argument to estimate AAPs and their ratio within levels of \texttt{married}:
+Below, we will examine effect modification of the ATT by the predictor \texttt{married} using the \texttt{by} argument to estimate AAPs and their ratio within levels of \texttt{married}:
 
@@
 
-Here, we'll consider \texttt{age} (just for demonstration; this analysis does not have a valid interpretation) and compute the ADRF and AMEF of \texttt{age} on the outcome.
-We'll only examine ages between 18 and 50, even though the range of \texttt{age} goes slightly beyond these values.
-First, we'll compute the ADRF of \texttt{age}, which examines how the outcome would vary on average if one set all unit's value of \texttt{age} to each value between 18 and 50 (here we only use even ages to speed up computation).
+Here, we will consider \texttt{age} (just for demonstration; this analysis does not have a valid interpretation) and compute the ADRF and AMEF of \texttt{age} on the outcome.
+We will only examine ages between 18 and 50, even though the range of \texttt{age} goes slightly beyond these values.
+First, we will compute the ADRF of \texttt{age}, which examines how the outcome would vary on average if one set all unit's value of \texttt{age} to each value between 18 and 50 (here we only use even ages to speed up computation).
 
@@
 
-Next we'll compute the AMEF, the effect of \texttt{age} at each level of \texttt{age}.
+Next we will compute the AMEF, the effect of \texttt{age} at each level of \texttt{age}.
 
@@
 \hypertarget{transforming-and-combining-estimates}{%
-\subsection{Transforming and combining estimates}\label{transforming-and-combining-estimates}}
+\subsection{Transforming and Combining Estimates}\label{transforming-and-combining-estimates}}
 
@@
 Similarly, to compute a derived or transformed quantity from a \texttt{clarify\_est} object, we can use \texttt{transform()}.
-Here, we'll compute the risk difference AME of \texttt{treat}; previously, we used \texttt{sim\_ame()} to compute the AAPs and the risk ratio.
+Here, we will compute the risk difference AME of \texttt{treat}; previously, we used \texttt{sim\_ame()} to compute the AAPs and the risk ratio.
 
@@
 
-When we run \texttt{summary()} on the output, the new quantity, which we named ``RD'', will be displayed along with the other estimates. We'll also set a null value for this quantity.
+When we run \texttt{summary()} on the output, the new quantity, which we named ``RD'', will be displayed along with the other estimates. We will also set a null value for this quantity.
 
@@
 \texttt{cbind()} is another generic R function that is typically used to combine two or more datasets columnwise (i.e., to widen a dataset).
-In \pkg{clarify}, \texttt{cbind()} can be used to combine two \texttt{clarify\_est} objects so that the estimates can be examined jointly and so that it is possible to compare them directly.
-For example, let's say we computed AMEs in two subgroups using \texttt{subset} and wanted to compare them.
-To do so, we call \texttt{sim\_ame()} twice, one for each subset (though in practice it is more effective to use \texttt{by}; this is just for illustration):
+In \CRANpkg{clarify}, \texttt{cbind()} can be used to combine two \texttt{clarify\_est} objects so that the estimates can be examined jointly and so that it is possible to compare them directly.
+For example, if we were to compute AMEs in two subgroups using \texttt{subset} and wanted to compare them, we would call \texttt{sim\_ame()} twice, one for each subset (though in practice it is more effective to use \texttt{by}; this is just for illustration), as demonstrated below:
 
@@
 If we wanted to compare the risk differences, we could combine them and compute a new quantity equal to their difference.
-We'll do that below.
-
-First, we need to rename to quantities in each object so they don't overlap; we can do so using \texttt{names()}, which has a special method for \texttt{clarify\_est} objects.
+We will do that below.
+
+First, we need to rename to quantities in each object so they do not overlap; we can do so using \texttt{names()}, which has a special method for \texttt{clarify\_est} objects.
 
@@
 \hypertarget{using-with-multiply-imputed-data}{%
-\subsection{\texorpdfstring{Using \pkg{clarify} with multiply imputed data}{Using  with multiply imputed data}}\label{using-with-multiply-imputed-data}}
+\subsection{\texorpdfstring{Using \CRANpkg{clarify} with Multiply Imputed Data}{Using  with Multiply Imputed Data}}\label{using-with-multiply-imputed-data}}
 
@@
 
-Using \pkg{clarify} with multiply imputed data is simple.
+Using \CRANpkg{clarify} with multiply imputed data is simple.
 Rather than using \texttt{sim()}, we use the function \texttt{misim()}.
@@
 \texttt{sim\_apply()} and its wrappers accept the output of \texttt{misim()} and compute the desired quantity using each set of coefficients.
-When these function rely on using a dataset (e.g., \texttt{sim\_ame()}, which averages predicted outcomes across all units in the dataset used to fit the model), they automatically know to associate a given coefficient draw with the imputed dataset that was used to fit the model that produced that draw.
+When these functions rely on using a dataset (e.g., \texttt{sim\_ame()}, which averages predicted outcomes across all units in the dataset used to fit the model), they automatically know to associate a given coefficient draw with the imputed dataset that was used to fit the model that produced that draw.
 In user-written functions supplied to the \texttt{FUN} argument of \texttt{sim\_apply()}, it is important to correctly extract the dataset from the model fit.
@@
 
-Below we illustrate using \texttt{misim()} and \texttt{sim\_apply()} with multiply imputed data. We'll use the \texttt{africa} dataset from the \pkg{Amelia} package.
+Below we illustrate using \texttt{misim()} and \texttt{sim\_apply()} with multiply imputed data. We will use the \texttt{africa} dataset from the \CRANpkg{Amelia} package.
 
@@
 
-The function we'll be applying to each imputed dataset will be one that computes the average marginal effect of \texttt{infl}. (We'll run the same analysis afterward using \texttt{sim\_ame()}.)
+The function we will be applying to each imputed dataset will be one that computes the average marginal effect of \texttt{infl}. (We will run the same analysis afterward using \texttt{sim\_ame()}.)
 
@@
 
-Note that \texttt{misim()} is compatible with model fit objects from \pkg{mice}, \pkg{Amelia}, \pkg{MatchThem}, and any other package that produces a list of model fit objects with each corresponding to the output of a model fit to an imputed dataset.
+Note that \texttt{misim()} is compatible with model fit objects from \CRANpkg{mice}, \CRANpkg{Amelia}, \CRANpkg{MatchThem}, and any other package that produces a list of model fit objects with each corresponding to the output of a model fit to an imputed dataset.
 
 \hypertarget{comparison-to-other-packages}{%
-\subsection{Comparison to other packages}\label{comparison-to-other-packages}}
-
-Several packages offer methods for computing interpretable quantities form regression models, including \pkg{emmeans}, \pkg{margins}, \pkg{modelbased}, and \pkg{marginaleffects}.
-Many of the quantities computed by these packages can also be computed by \pkg{clarify}, the primary difference being that \pkg{clarify} uses simulation-based inference rather than delta method-based inference.
-
-\pkg{marginaleffects} offers the most similar functionality to \pkg{clarify}, and \pkg{clarify} depends on functionality provided by \pkg{marginaleffects} to accommodate a wide variety of regression models.
-\pkg{marginaleffects} also offers simulation-based inference using \texttt{marginaleffects::inferences()} and support for arbitrary user-specified post-estimation functions using \texttt{marginaleffects::hypotheses()}.
-However, \pkg{clarify} and \texttt{marignalefefcts} differ in several ways.
-The largest difference is that \pkg{clarify} supports iterative building of more and more complex hypotheses through the \texttt{transform()} method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \pkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.
-
-Because of \pkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing.
-\pkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.
-
-There are areas and cases where \pkg{marginaleffects} may be the better choice than \pkg{clarify} or where the differences between the packages are of little consequence.
-\pkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \pkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience.
-In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \pkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \pkg{clarify} provides.
-For the quantities easily computed by \pkg{marginaleffects} that support simulation-based inference through \texttt{marginaleffects::inferences()}, using \pkg{marginaleffects} can provide a more familiar and flexible syntax than \pkg{clarify} might offer.
-
-Note that as both packages continue to develop, these differences may grow or shrink.
-The differences above are meant to highlight the current differences and differences in philosophy and emphasis of the two packages.
+\subsection{Comparison to Other Packages}\label{comparison-to-other-packages}}
+
+Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans}, \CRANpkg{margins}, \CRANpkg{modelbased}, and \CRANpkg{marginaleffects}.
+Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.
+
+\CRANpkg{marginaleffects} offers the most similar functionality to \CRANpkg{clarify}, and \CRANpkg{clarify} depends on functionality provided by \CRANpkg{marginaleffects} to accommodate a wide variety of regression models.
+\CRANpkg{marginaleffects} also offers simulation-based inference using \texttt{marginaleffects::inferences()} and support for arbitrary user-specified post-estimation functions using \texttt{marginaleffects::hypotheses()}.
+However, \CRANpkg{clarify} and \texttt{marignalefefcts} differ in several ways.
+The largest difference is that \CRANpkg{clarify} supports iterative building of more and more complex hypotheses through the \texttt{transform()} method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \CRANpkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.
+
+Because of \CRANpkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing.
+\CRANpkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.
+
+There are areas and cases where \CRANpkg{marginaleffects} may be the better choice than \CRANpkg{clarify} or where the differences between the packages are of little consequence.
+\CRANpkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \CRANpkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience.
+In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \CRANpkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \CRANpkg{clarify} provides.
+For the quantities easily computed by \CRANpkg{marginaleffects} that support simulation-based inference through \texttt{marginaleffects::inferences()}, using \CRANpkg{marginaleffects} can provide a more familiar and flexible syntax than \CRANpkg{clarify} might offer.
 Ultimately, the user should use the package that supports their desired syntax and mode of inference.
@@
 
-\pkg{clarify} provides utilities to facilitate simulation-based inference of deriving quantities form regression models.
-This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution fo the derived quantity is Normal.
-\pkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values.
-These enhance the utility and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.
+\CRANpkg{clarify} provides functionality to facilitate simulation-based inference of deriving quantities from regression models.
+This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution of the derived quantity is Normal.
+\CRANpkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values.
+These enhance the usefulness and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.
 
@@
 \url{https://doi.org/10.2307/2669316}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-longRegressionModelsCategorical2014}{}}%
+Long, J. Scott, and Jeremy Freese. 2014. \emph{Regression Models for Categorical Dependent Variables Using Stata}. Third edition. College Station, Texas: Stata Press Publication, StataCorp LP.
 

### 2024-05-30 clarify/Submission 2/clarify.R

@@ -1,0 +1,294 @@
+# Generated by `rjournal_pdf_article()` using `knitr::purl()`: do not edit by hand
+# Please edit clarify.Rmd to modify this file
+
+## ----setup,include=FALSE------------------------------------------------------
+knitr::opts_chunk$set(
+  fig.path = "figures/",
+  fig.align='center',
+  fig.height = 2
+)
+
+if (!requireNamespace("clarify")) {
+  install.packages("clarify")
+}
+
+if (!requireNamespace("MatchIt")) {
+  install.packages("MatchIt")
+}
+
+if (!requireNamespace("Amelia")) {
+  install.packages("Amelia")
+}
+
+
+## -----------------------------------------------------------------------------
+library(clarify)
+
+
+## -----------------------------------------------------------------------------
+data("lalonde", package = "MatchIt")
+
+lalonde$re78_0 <- ifelse(lalonde$re78 > 0, 1, 0)
+
+head(lalonde)
+
+
+## -----------------------------------------------------------------------------
+fit <- glm(re78_0 ~ treat * married + age + educ + race +
+             nodegree + re74 + re75, data = lalonde,
+           family = binomial("probit"))
+
+
+## -----------------------------------------------------------------------------
+set.seed(1234)
+
+# Drawing 1000 simulated coefficients using an HC2 robust
+# covariance matrix
+s <- sim(fit, n = 1000,
+         vcov = "HC2")
+
+s
+
+
+## -----------------------------------------------------------------------------
+sim_fun1 <- function(fit) {
+  predict(fit, newdata = lalonde["PSID1",], type = "response")
+}
+
+
+## -----------------------------------------------------------------------------
+est1 <- sim_apply(s, FUN = sim_fun1, verbose = FALSE)
+
+est1
+
+
+## -----------------------------------------------------------------------------
+sim_fun2 <- function(coefs) {
+  hispan <- unname(coefs["racehispan"])
+  white <- unname(coefs["racewhite"])
+  
+  c("w - h" = white - hispan)
+}
+
+est2 <- sim_apply(s, FUN = sim_fun2, verbose = FALSE)
+
+est2
+
+
+## ---- fig.width=4-------------------------------------------------------------
+plot(est1, reference = TRUE, ci = FALSE)
+
+
+## -----------------------------------------------------------------------------
+summary(est1)
+
+
+## ---- fig.width=4-------------------------------------------------------------
+plot(est2, reference = TRUE, ci = FALSE)
+
[…]

### 2024-05-30 README.Rmd
README updates

@@
 # Fit the model
-fit <- glm(I(re78 == 0) ~ treat * (age + educ + race + married +
-                                     nodegree + re74 + re75),
+fit <- glm(I(re78 > 0) ~ treat + age + educ + race + married +
+             nodegree + re74 + re75,
            data = lalonde, family = binomial)
@@
 
-Next, to estimate the ATT risk ratio, we simulate coefficients from their implied distribution and compute the effects of interest in each simulation, yielding a distribution of estimates that was can summarize and use for inference:
+Next, to estimate the ATT risk ratio, we simulate coefficients from their implied distribution and compute the effects of interest in each simulation, yielding a distribution of estimates that we can summarize and use for inference:
 
@@
 Simulation-based inference is an alternative to the delta method and bootstrapping for performing inference on quantities that are functions of model parameters.
-The delta method involves multiple assumptions: 1) the model coefficients are normally distributed, 2) the resulting quantity of interest is normally distributed, and 3) the first-order approximation to the variance of the desired estimator is equal to the true variance.
-When these assumptions are incorrect, which is especially likely when the quantity of interest is a complicated nonlinear function of the model coefficients, the resulting inferences can be inaccurate.
-Bootstrapping is one solution to this problem that does not require any of the above assumptions for valid nonparametric inference (though other assumptions are required); however, it is computationally intensive because the original model needs to be fit many times, and any problems with the model that are only apparent in some bootstrap samples (e.g., failure to converge, perfect prediction) can make using bootstrapping challenging.
-
-Simulation-based inference provides a compromise to these two methods: it is more accurate than the delta method because it does not require assumptions 2) and 3) (though it still relies on the central limit theorem to assume the coefficients are normally distributed), and it is faster and more stable than bootstrapping because the model only needs to be fit once.
-Simulation-based inference involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution.
+It involves simulating model coefficients from their multivariate distribution using their estimated values and covariance from a single model fit to the original data, computing the quantities of interest from each set of model coefficients, and then performing inference using the resulting distribution of the estimates as their sampling distribution.
 Confidence intervals can be computed using the percentiles of the resulting sampling distribution, and p-values can be computed by inverting the confidence intervals.
@@
 
-There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::comparisons()` and `marginaleffects::marginaleffects()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions.
+There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::avg_predictions()` and `marginaleffects::avg_slopes()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions.
 `clarify` also offers support for models fit to multiply imputed data with the `misim()` function.

### 2024-05-30 clarify/Submission 2/response_to_reviewers.Rmd
Paper upates

@@
 (2000), which introduced to method to political scientists, is among the most highly cited political methodology articles as noted by the other reviewer, and the software packages that implement its method, `Zelig` and `CLARIFY` for Stata, have been widely used.
-Modern tools that implement the delta method like `marginaleffects` and `margins` in Stata are certainly the standard nowadays, but we argue there has not been a general-purpose simulation-based inference package in R, which may have reduced its uptake.
+Modern tools that implement the delta method like `marginaleffects` and `margins` in Stata are certainly the standard nowadays, but we would argue there has not been a general-purpose simulation-based inference package in R, which may have reduced its uptake.
 Additionally, researchers may be resistant to use a less-studied method, especially one that is computationally intensive and yields results that depend on a seed; we are sympathetic to these concerns but believe simulation-based inference should at least be available in an easy-to-use package, even if it is currently less commonly used than other methods.
@@
 
-Normailty of $h(\hat\theta)$ is required for valid use of Normal quantile for Wald-based inference of the derived quantity.
+Normality of $h(\hat\theta)$ is required for valid use of Normal quantiles for Wald-based inference of the derived quantity.
 Of course both simulation-based inference and the delta method require joint Normality of $\hat\theta$.
@@
 We prefixed functions with `sim_` to highlight that these are specifically to be used after running `sim()`.
-Although the namespace and class checking accomplishes this as well, removing the `sim_` prefix would leave functions like `apply()`, `adrf()`, and `ame()`, suggetsing these functions are general-purpose functions for computing the relevant quantity, whereas they are specifically to be used in the context of simulation-based inference with `clarify`.
-This also avoid namespace clashes with other packagest hat might implement more general-purpose functions.
+Although the namespace and class checking accomplishes this as well, removing the `sim_` prefix would leave functions like `apply()`, `adrf()`, and `ame()`, suggesting these functions are general-purpose functions for computing the relevant quantity, whereas they are specifically to be used in the context of simulation-based inference with `clarify`.
+This also avoid namespace clashes with other packages that might implement more general-purpose functions.
 
@@
 The user can supply any value to `null` depending on the hypothesis they want to test, if any.
-Often, researchers are interested in tests of no effect, which needs to be defined differently for the contrast being used.
+Often, researchers are interested in tests of no effect, which need to be defined differently for the contrast being used.
 For example, to test a hypothesis that two probabilities are equal, one can test whether their difference is 0, their ratio is 1, or their odds ratio is 1, etc.
@@
 Although it is certainly possible to perform similar manipulations from the `marginaleffects` output, we would argue that because the focus of `clarify` is solely on simulation-based inference, its interface is more user-friendly for this analysis.
-`posterior_draws()` output needs to be reshaped and is better designed for expert users than casual users of the package, whereas `transform()` uses an existing base R function with a simple interface that yields an objects with the same properties as the object the user started with.
+`posterior_draws()` output needs to be reshaped and is better designed for expert users than casual users of the package, whereas `transform()` uses an existing base R function with a simple interface that yields an object with the same properties as the object the user started with.
 We would like to think `transform()` is one of the biggest contributions of this package, as it supports iterative construction of more and more complicated quantities of interest without any increase in computational time.
@@
 We thank both reviewers for their insightful comments and support for the paper and package.
-We hope to have improved the paper through their comments while maintain our position that `clarify` implements useful methodology for applied researchers, and therefore would benefit the R community.
+We hope to have improved the paper through their comments while maintaining our position that `clarify` implements useful methodology for applied researchers, and therefore would benefit the R community.

### 2025-01-23 clarify/Final version/clarify.Rmd
Package cleaning and prep for final submission

--- 2024-05-30 clarify/Submission 2/clarify.Rmd
@@
 output: 
-  rjtools::rjournal_web_article:
+  rjtools::rjournal_pdf_article:
     self_contained: yes
@@
 
-## Introduction
+# Introduction
 
@@
 
-## Related Software
+# Related Software
 
@@
 \CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
-\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package [@arel-bundockMarginaleffectsPredictionsComparisons2024], which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
+\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package [@marginaleffectsforthcoming], which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
 
@@
 
-## Using \CRANpkg{clarify}
+# Using \CRANpkg{clarify}
 
@@
 
-### 1. Fitting the model
+## 1. Fitting the model
 
@@
 
-### 2. Drawing from the coefficient distribution
+## 2. Drawing from the coefficient distribution
 
@@
 
-### 3. Computing derived quantities
+## 3. Computing derived quantities
 
@@
 
--   `...` - further arguments to `FUN`.
+-   `...` -- further arguments to `FUN`.
 
@@
 
-### 4. Summarize and visualize the simulated distribution
+## 4. Summarize and visualize the simulated distribution
 
@@
 
-## `sim_apply()` Wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`
+# `sim_apply()` Wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`
 
@@
 
-### `sim_setx()`: predictions at representative values
+## `sim_setx()`: predictions at representative values
 
@@
 
-### `sim_ame()`: average adjusted predictions and average marginal effects
+## `sim_ame()`: average adjusted predictions and average marginal effects
 
@@
 
-### `sim_adrf()`: average dose-response functions
+## `sim_adrf()`: average dose-response functions
 
@@
 
-## Transforming and Combining Estimates
+# Transforming and Combining Estimates
 
@@
 
-### `transform()`
+## `transform()`
 
@@
 
-### `cbind()`
+## `cbind()`
 
@@
 
-## Using \CRANpkg{clarify} with Multiply Imputed Data
+# Using \pkg{clarify} with Multiply Imputed Data
 
@@
 
-## Comparison to Other Packages
+# Comparison to Other Packages
 
-Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} [@lenthEmmeansEstimatedMarginal2024], \CRANpkg{margins} [@leeperMarginsMarginalEffects2024], \CRANpkg{modelbased} [@makowskiEstimationModelbasedPredictions2020], and \CRANpkg{marginaleffects} [@arel-bundockMarginaleffectsPredictionsComparisons2024].
+Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} [@emmeans2024], \pkg{margins} [@margins2021], \CRANpkg{modelbased} [@modelbased2020], and \CRANpkg{marginaleffects} [@marginaleffectsforthcoming].
 Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.
@@
 
-## Conclusion
+# Conclusion
 

### 2025-09-18 R/clarify_est_methods.R
Code cleaning and updates; support for simultaneous inference

@@ -12,15 +12,15 @@ names.clarify_est <- function(x) {
   names(attr(x, "original")) <- value
 
   for (i in names(attributes(x))) {
-    if (identical(names(attr(x, i, TRUE)), original_names)) {
+    if (identical(names(.attr(x, i)), original_names)) {
       names(attr(x, i)) <- value
     }
 
-    if (identical(rownames(attr(x, i)), original_names)) {
+    if (identical(rownames(.attr(x, i)), original_names)) {
       rownames(attr(x, i)) <- value
     }
 
-    if (identical(colnames(attr(x, i)), original_names)) {
+    if (identical(colnames(.attr(x, i)), original_names)) {
       colnames(attr(x, i)) <- value
     }
   }
@@ -43,7 +43,7 @@ Ops.clarify_est <- function(e1, e2 = NULL) {
     left <- drop_sim_class(e1)
     e1[] <- eval(f)
 
-    left <- attr(e1, "original", TRUE)
+    left <- .attr(e1, "original")
     attr(e1, "original")[] <- eval(f)
     return(e1)
   }
@@ -59,17 +59,17 @@ Ops.clarify_est <- function(e1, e2 = NULL) {
                    .Generic))
     }
 
-    if (!identical(attr(e1, "hash"), attr(e2, "hash"))) {
+    if (!identical(.attr(e1, "hash"), .attr(e2, "hash"))) {
       .err(sprintf("`%s` can only be used on `clarify_est` objects originating from calls applied to the same `clarify-sim` object",
                    .Generic))
     }
 
-    if (any(dim(e2) != dim(e1))) {
+    if (!all(dim(e2) == dim(e1))) {
       .err(sprintf("`%s` can only be used on `clarify_est` objects with an equal number of estimated quantities",
                    .Generic))
     }
 
-    if (!identical(attr(e1, "at"), attr(e2, "at"))) {
+    if (!identical(.attr(e1, "at"), .attr(e2, "at"))) {
       .err(sprintf("`%s` can only be used on `clarify_adrf` objects with the same values of `at`",
                    .Generic))
     }
@@ -81,12 +81,12 @@ Ops.clarify_est <- function(e1, e2 = NULL) {
   if (e1_clarify_est)
     e1[] <- eval(f)
   else
-    e2[] < eval(f)
+    e2[] <- eval(f)
 
[…]

### 2025-09-18 R/get_model_components.R

@@ -1,27 +1,27 @@
 #Functions for extracting information from models
 
 # Get the coefficients from a model as a vector
-get_coefs <- function(fit) {
-
-  b <- try(marginaleffects::get_coef(fit), silent = TRUE)
-
-  if (!check_valid_coef(b)) {
-    .err("`sim()` was unable to extract a valid set of coefficients from the model fit; please supply coefficients to the `coefs` argument and a covariance matrix to the `vcov` argument")
-  }
-
-  b
-}
+# get_coefs <- function(fit) {
+#
+#   b <- try(marginaleffects::get_coef(fit), silent = TRUE)
+#
+#   if (!check_valid_coef(b)) {
+#     .err("`sim()` was unable to extract a valid set of coefficients from the model fit; please supply coefficients to the `coefs` argument and a covariance matrix to the `vcov` argument")
+#   }
+#
+#   b
+# }
 
 # Get the covariance from a model
-get_vcov <- function(fit, vcov = NULL) {
-  v <- try(marginaleffects::get_vcov(fit, vcov), silent = TRUE)
-
-  if (!check_valid_vcov(v)) {
-    .err("`sim()` was unable to extract a valid covariance matrix from the model fit; please supply a covariance matrix to the `vcov` argument")
-  }
-
-  v
-}
+# get_vcov <- function(fit, vcov = NULL) {
+#   v <- try(marginaleffects::get_vcov(fit, vcov), silent = TRUE)
+#
+#   if (!check_valid_vcov(v)) {
+#     .err("`sim()` was unable to extract a valid covariance matrix from the model fit; please supply a covariance matrix to the `vcov` argument")
+#   }
+#
+#   v
+# }
 
 # Get the model degrees of freedom
 ## Assesses whether the model is linear and fit with OLS; if not,

### 2025-09-18 R/misim.R

@@ -1,6 +1,6 @@
-#' @title Simulate model coefficients after multiple imputation
+#' Simulate model coefficients after multiple imputation
 #'
-#' @description `misim()` simulates model parameters from multivariate normal or t distributions after multiple imputation that are then used by [sim_apply()] to calculate quantities of interest.
+#' `misim()` simulates model parameters from multivariate normal or t distributions after multiple imputation that are then used by [sim_apply()] to calculate quantities of interest.
 #'
 #' @param fitlist a list of model fits, one for each imputed dataset, or a `mira` object (the output of a call to `with()` applied to a `mids` object in `mice`).
 #' @param n the number of simulations to run for each imputed dataset; default is 1000. More is always better but resulting calculations will take longer.
@@ -8,7 +8,7 @@
 #' @param coefs a vector of coefficient estimates, a function to use to extract it from `fit`, or a list thereof with an element for each imputed dataset. By default, uses [stats::coef()] or [insight::get_parameters()] if that doesn't work.
 #' @param dist a character vector containing the name of the multivariate distribution(s) to use to draw simulated coefficients. Should be one of `"normal"` (multivariate normal distribution) or `"t_{#}"` (multivariate t distribution), where `{#}` corresponds to the desired degrees of freedom (e.g., `"t_100"`). If `NULL`, the right distributions to use will be determined based on heuristics; see [sim()] for details.
 #'
-#' @return
+#' @returns
 #' A `clarify_misim` object, which inherits from `clarify_sim` and has the following components:
 #'  \item{sim.coefs}{a matrix containing the simulated coefficients with a column for each coefficient and a row for each simulation for each imputation}
 #'  \item{coefs}{a matrix containing the original coefficients extracted from `fitlist` or supplied to `coefs`, with a row per imputation.}
@@ -20,8 +20,13 @@
[…]

### 2025-09-18 R/plot.clarify_adrf.R

@@ -8,42 +8,49 @@
 #' @param method the method used to compute confidence bands. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See [summary.clarify_est()] for details. Abbreviations allowed.
 #' @param baseline `logical`; whether to include a horizontal line at `y = 0` on the plot. Default is `FALSE` for the ADRF (since 0 might not be in the range of the outcome) and `TRUE` for the AMEF.
 #' @param color the color of the line and confidence band in the plot.
+#' @param simultaneous `logical`; whether confidence bands should be simultaneous or not (i.e., for nominal coverage of the whole effect curve); default is `FALSE`, but `TRUE` is recommended. See Details at [summary.clarify_est()] for details.
 #'
-#' @return A `ggplot` object.
+#' @returns
+#' A `ggplot` object.
 #'
-#' @details These plots are produced using [ggplot2::geom_line()] and [ggplot2::geom_ribbon()]. The confidence bands should be interpreted pointwise (i.e., they do not account for simultaneous inference).
+#' @details
+#' These plots are produced using [ggplot2::geom_line()] and [ggplot2::geom_ribbon()]. The confidence bands should be interpreted pointwise (i.e., they do not account for simultaneous inference) unless `simultaneous = TRUE`.
 #'
-#' @seealso [summary.clarify_est()] for computing p-values and confidence intervals for the estimated quantities.
+#' @seealso
+#' [summary.clarify_est()] for computing p-values and confidence intervals for the estimated quantities.
 #'
 #' @examples
 #' ## See help("sim_adrf") for examples
-#'
+
 #' @exportS3Method plot clarify_adrf
 plot.clarify_adrf <- function(x,
                               ci = TRUE,
                               level = .95,
                               method = "quantile",
-                              baseline,
+                              baseline = NULL,
                               color = "black",
+                              simultaneous = FALSE,
                               ...) {
 
-  at <- attr(x, "at", TRUE)
-  var <- attr(x, "var", TRUE)
-  contrast <- attr(x, "contrast", TRUE)
-  by <- attr(x, "by", TRUE)
+  at <- .attr(x, "at")
+  var <- .attr(x, "var")
+  contrast <- .attr(x, "contrast")
[…]

### 2025-09-18 R/plot.clarify_est.R

@@ -7,6 +7,7 @@ plot.clarify_est <- function(x,
                              method = "quantile",
                              reference = FALSE,
                              ncol = 3L,
+                             simultaneous = FALSE,
                              ...) {
 
   chk::chk_flag(ci)
@@ -22,10 +23,13 @@ plot.clarify_est <- function(x,
 
   est_names <- est_names[parm]
 
-  est_long <- setNames(utils::stack(as.data.frame(as.matrix(x))[est_names]),
-                       c("val", "est"))
-  original_est_long <- setNames(utils::stack(original_est[est_names]),
-                                c("val", "est"))
+  est_long <- as.data.frame(as.matrix(x))[est_names] |>
+    stack() |>
+    setNames(c("val", "est"))
+
+  original_est_long <- original_est[est_names] |>
+    stack() |>
+    setNames(c("val", "est"))
 
   p <- ggplot() +
     geom_density(data = est_long, mapping = aes(x = .data$val),
@@ -36,10 +40,13 @@ plot.clarify_est <- function(x,
     facet_wrap(vars(.data$est), scales = "free", ncol = min(ncol, nlevels(original_est_long$est)))
 
   if (ci) {
-    ci <- confint(x, parm = parm, level = level,
-                  method = method)
+    ci_long <- confint(x, parm = parm, level = level,
+                       method = method, simultaneous = simultaneous) |>
+      t() |>
+      as.data.frame() |>
+      stack() |>
+      setNames(c("val", "est"))
 
-    ci_long <- setNames(utils::stack(as.data.frame(t(ci))), c("val", "est"))
     p <- p + geom_vline(data = ci_long, mapping = aes(xintercept = .data$val),
                         linetype = 2)
   }
@@ -52,8 +59,9 @@ plot.clarify_est <- function(x,
       height = dnorm(0, 0, tapply(est_long$val, est_long$est, sd)),
       median = tapply(est_long$val, est_long$est, median))
 
-    p <- p + geom_density(data = est_long, mapping = aes(x = .data$val),
-                          stat = StatNormal, color = "red") +
+    p <- p +
+      geom_density(data = est_long, mapping = aes(x = .data$val),
+                   stat = StatNormal, color = "red") +
       geom_segment(aes(x = .data$mean, xend = .data$mean,
                        y = 0, yend = .data$height),
                    data = ref_means_and_medians, color = "red") +
@@ -62,8 +70,7 @@ plot.clarify_est <- function(x,
[…]

### 2025-09-18 R/plot.clarify_setx.R

@@ -8,30 +8,35 @@
 #' @param ci `logical`; whether to display confidence intervals or bands for the estimates. Default is `TRUE`.
 #' @param method the method used to compute confidence intervals or bands. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See [summary.clarify_est()] for details. Abbreviations allowed.
 #' @param reference `logical`; whether to overlay a normal density reference distribution over the plots. Default is `FALSE`. Ignored when variables other than the focal varying predictor vary.
+#' @param simultaneous `logical`; whether confidence bands should be simultaneous or not (i.e., for nominal coverage of the whole effect curve); default is `FALSE`, but `TRUE` is recommended. See Details at [summary.clarify_est()] for details.
 #'
-#' @return A `ggplot` object.
+#' @returns
+#' A `ggplot` object.
 #'
-#' @details `plot()` creates one of two kinds of plots depending on how the reference grid was specified in the call to `sim_setx()` and what `var` is set to. When the focal varying predictor (i.e., the one set in `var`) is numeric and takes on three or more unique values in the reference grid, the produced plot is a line graph displaying the value of the marginal prediction (denoted as `E[Y|X]`) across values of the focal varying predictor, with confidence bands displayed when `ci = TRUE`. If other predictors also vary, lines for different values will be displayed in different colors. These plots are produced using [ggplot2::geom_line()] and [ggplot2::geom_ribbon()]
+#' @details
+#' `plot()` creates one of two kinds of plots depending on how the reference grid was specified in the call to `sim_setx()` and what `var` is set to. When the focal varying predictor (i.e., the one set in `var`) is numeric and takes on three or more unique values in the reference grid, the produced plot is a line graph displaying the value of the marginal prediction (denoted as `E[Y|X]`) across values of the focal varying predictor, with confidence bands displayed when `ci = TRUE`. If other predictors also vary, lines for different values will be displayed in different colors. These plots are produced using [ggplot2::geom_line()] and [ggplot2::geom_ribbon()]
 #'
[…]

### 2025-09-18 R/sim.R

@@ -1,6 +1,6 @@
 #' Simulate model parameters
 #'
-#' @description `sim()` simulates model parameters from a multivariate normal or t distribution that are then used by [sim_apply()] to calculate quantities of interest.
+#' `sim()` simulates model parameters from a multivariate normal or t distribution that are then used by [sim_apply()] to calculate quantities of interest.
 #'
 #' @param fit a model fit, such as the output of a call to [lm()] or [glm()]. Can be left unspecified if `coefs` and `vcov` are not functions.
 #' @param n the number of simulations to run; default is 1000. More is always better but resulting calculations will take longer.
@@ -8,7 +8,7 @@
 #' @param coefs either a vector of coefficient estimates or a function to use to extract it from `fit`. By default, uses [stats::coef()] or [insight::get_parameters()] if that doesn't work.
 #' @param dist a string containing the name of the multivariate distribution to use to draw simulated coefficients. Should be one of `"normal"` (multivariate normal distribution) or `"t({#})"` (multivariate t distribution), where `{#}` corresponds to the desired degrees of freedom (e.g., `"t(100)"`). If `NULL`, the right distribution to use will be determined based on heuristics; see Details.
 #'
-#' @return
+#' @returns
 #' A `clarify_sim` object, which has the following components:
 #'  \item{sim.coefs}{a matrix containing the simulated coefficients with a column for each coefficient and a row for each simulation}
 #'  \item{coefs}{the original coefficients extracted from `fit` or supplied to `coefs`.}
@@ -16,9 +16,8 @@
 #'  \item{fit}{the original model fit supplied to `fit`}
 #' The `"dist"` attribute contains `"normal"` if the coefficients were sampled from a multivariate normal distribution and `"t(df)"` if sampled from a multivariate t distribution. The `"clarify_hash"` attribute contains a unique hash generated by [rlang::hash()].
 #'
[…]

### 2025-09-18 R/sim_adrf.R

@@ -1,6 +1,5 @@
 #' Compute an average dose-response function
 #'
-#' @description
 #' `sim_adrf()` is a wrapper for [sim_apply()] that computes average dose-response functions (ADRFs) and average marginal effect functions (AMEFs). An ADRF describes the relationship between values a focal variable can take and the expected value of the outcome were all units to be given each value of the variable. An AMEF describes the relationship between values a focal variable can take and the derivative of ADRF at each value.
 #'
 #' @inheritParams sim_apply
@@ -14,26 +13,26 @@
 #' @param type a string containing the type of predicted values (e.g., the link or the response). Passed to [marginaleffects::get_predict()] and eventually to `predict()` in most cases. The default and allowable option depend on the type of model supplied, but almost always corresponds to the response scale (e.g., predicted probabilities for binomial models).
 #' @param eps when `contrast = "amef"`, the value by which to shift the value of `var` to approximate the derivative. See Details.
 #' @param \dots for `sim_adrf()`, additional arguments passed to [marginaleffects::get_predict()] (and eventually to `predict()`) to compute predictions. For `print()`, ignored.
+#' @param x a `clarify_adrf` object.
 #'
 #' @details
 #' The ADRF is composed of average marginal means across levels of the focal predictor. For each level of the focal predictor, predicted values of the outcome are computed after setting the value of the predictor to that level, and those values of the outcome are averaged across all units in the sample to arrive at an average marginal mean. Thus, the ADRF represent the relationship between the "dose" (i.e., the level of the focal predictor) and the average "response" (i.e., the outcome variable). It is the continuous analog to the average marginal effect computed for a binary predictor, e.g., using [sim_ame()]. Although inference can be at each level of the predictor or between two levels of the predictor, typically a plot of the ADRF is the most useful relevant quantity. These can be requested using [plot.clarify_adrf()].
 #'
[…]

### 2025-09-18 R/sim_setx.R

@@ -1,12 +1,6 @@
 #' Compute predictions and first differences at set values
 #'
-#' `sim_setx()` is a wrapper for [sim_apply()] that computes predicted values of
-#' the outcome at specified values of the predictors, sometimes called marginal
-#' predictions. One can also compute the difference between two marginal
-#' predictions (the "first difference"). Although any function that accepted
-#' `clarify_est` objects can be used with `sim_setx()` output objects, a
-#' special plotting function, [plot.clarify_setx()], can be used to plot marginal
-#' predictions.
+#' `sim_setx()` is a wrapper for [sim_apply()] that computes predicted values of the outcome at specified values of the predictors, sometimes called marginal predictions. One can also compute the difference between two marginal predictions (the "first difference"). Although any function that accepted `clarify_est` objects can be used with `sim_setx()` output objects, a special plotting function, [plot.clarify_setx()], can be used to plot marginal predictions.
 #'
 #' @inheritParams sim_apply
 #' @param x a data.frame containing a reference grid of predictor values or a named list of values each predictor should take defining such a reference grid, e.g., `list(v1 = 1:4, v2 = c("A", "B"))`. Any omitted predictors are fixed at a "typical" value. See Details. When `x1` is specified, `x` should identify a single reference unit.
@@ -18,12 +12,16 @@
 #' @param outcome a string containing the name of the outcome or outcome level for multivariate (multiple outcomes) or multi-category outcomes. Ignored for univariate (single outcome) and binary outcomes.
 #' @param type a string containing the type of predicted values (e.g., the link or the response). Passed to [marginaleffects::get_predict()] and eventually to `predict()` in most cases. The default and allowable option depend on the type of model supplied, but almost always corresponds to the response scale (e.g., predicted probabilities for binomial models).
 #' @param \dots for `sim_setx()`, additional arguments passed to [marginaleffects::get_predict()] (and eventually to `predict()`) to compute predictions. For `print()`, ignored.
[…]

### 2025-09-18 R/summary.clarify_est.R

@@ -7,20 +7,25 @@
 #' @param level the confidence level desired. Default is .95 for 95% confidence intervals.
 #' @param method the method used to compute p-values and confidence intervals. Can be `"wald"` to use a Normal approximation or `"quantile"` to use the simulated sampling distribution (default). See Details. Abbreviations allowed.
 #' @param null the values of the parameters under the null hypothesis for the p-value calculations. Should have length equal to the number of quantities estimated, or one, in which case it will be recycled, or it can be a named vector with just the names of quantities for which null values are to be set. Set values to `NA` to omit p-values for those quantities. When all values are `NA`, the default, no p-values are produced.
+#' @param simultaneous `logical`; whether confidence intervals and p-values should be simultaneous or not (i.e., adjusted for multiple comparisons); default is `FALSE`. See Details.
 #' @param ci `logical`; whether to display confidence interval limits for the estimates. Default is `TRUE`.
 #' @param reference `logical`; whether to overlay a normal density reference distribution over the plots. Default is `FALSE`.
 #' @param ncol the number of columns used when wrapping multiple plots; default is 3.
 #' @param ... for `plot()`, further arguments passed to [ggplot2::geom_density()].
 #'
-#' @return For `summary()`, a `summary.clarify_est` object, which is a matrix containing the coefficient estimates, standard errors, test statistics, p-values, and confidence intervals. Not all columns will be present depending on the arguments supplied to `summary()`.
+#' @returns
+#' For `summary()`, a `summary.clarify_est` object, which is a matrix containing the coefficient estimates, standard errors, test statistics, p-values, and confidence intervals. Not all columns will be present depending on the arguments supplied to `summary()`.
 #'
 #' For `confint()`, a matrix containing the confidence intervals for the requested quantities.
 #'
 #' For `plot()`, a `ggplot` object.
 #'
-#' @details `summary()` uses the estimates computed from the original model as its estimates and uses the simulated parameters for inference only, in line with the recommendations of Rainey (2023).
+#' @details
[…]

### 2025-09-18 R/utils.R

@@ -26,7 +26,7 @@ word_list <- function(word.list = NULL, and.or = "and", is.are = FALSE, quotes =
   }
 
   if (is_null(and.or) || isFALSE(and.or)) {
-    out <- paste(word.list, collapse = ", ")
+    out <- toString(word.list)
   }
   else {
     and.or <- match_arg(and.or, c("and", "or"))
@@ -39,7 +39,7 @@ word_list <- function(word.list = NULL, and.or = "and", is.are = FALSE, quotes =
     }
     else {
       out <- sprintf("%s, %s %s",
-                     paste(word.list[-L], collapse = ", "),
+                     toString(word.list[-L]),
                      and.or,
                      word.list[L])
     }
@@ -66,16 +66,16 @@ add_quotes <- function(x, quotes = 2L) {
     return(paste0(quotes, x, str_rev(quotes)))
   }
 
-  if (!chk::vld_count(quotes) || quotes > 2) {
+  if (!chk::vld_count(quotes) || quotes > 2L) {
     stop("`quotes` must be boolean, 1, 2, or a string.")
   }
 
-  if (quotes == 0) {
+  if (quotes == 0L) {
     return(x)
   }
 
   x <- {
-    if (quotes == 1) sprintf("'%s'", x)
+    if (quotes == 1L) sprintf("'%s'", x)
     else sprintf('"%s"', x)
   }
 
@@ -98,7 +98,8 @@ match_arg <- function(arg, choices, several.ok = FALSE) {
   arg.name <- deparse1(substitute(arg), width.cutoff = 500L)
 
   if (missing(choices)) {
-    formal.args <- formals(sys.function(sysP <- sys.parent()))
+    sysP <- sys.parent()
+    formal.args <- formals(sys.function(sysP))
     choices <- eval(formal.args[[as.character(substitute(arg))]],
                     envir = sys.frame(sysP))
   }
@@ -118,11 +119,14 @@ match_arg <- function(arg, choices, several.ok = FALSE) {
   }
 
   i <- pmatch(arg, choices, nomatch = 0L, duplicates.ok = TRUE)
-  if (all(i == 0L))
+
+  if (all(i == 0L)) {
     .err(sprintf("the argument to `%s` should be %s%s",
                  arg.name,
[…]

### 2025-09-18 rjournal_paper/Final version/clarify.tex
File management

--- 2024-05-30 clarify/Submission 2/clarify.tex
@@
 \abstract{%
-Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects and adjusted predictions.
-It avoids several assumptions required by the delta method that are commonly violated, especially in nonlinear models, but does not require models to be refit as when using the bootstrap.
-It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form the sampling distribution of the quantity.
-\texttt{clarify} provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
-\texttt{clarify} supports a large and growing number of models through its interface with the \texttt{marginaleffects} package and provides native support for multiply imputed data.
+Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects, average adjusted predictions, and other functions of model parameters.
+It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form a simulated ``posterior'' distribution of the quantity from which confidence intervals can be computed.
+clarify provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
+clarify supports a large and growing number of models through its interface with the marginaleffects package and provides native support for multiply imputed data.
 }
 
-\hypertarget{introduction}{%
-\subsection{Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}
 
 Although regression models are frequently used in empirical research to study relationships among variables, often the quantity of substantive interest is not one of the coefficients of the model, but rather a quantity derived from the coefficients, such as predicted values or average marginal effects.
-The usual method for estimating the uncertainty of the derived quantities is known as the ``delta method'', which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the estimate of the derived quantity is normally distributed\footnote{In addition, most software that uses the delta method uses numerical differentiation, which also involves an approximation.}.
-In many cases, especially with nonlinear models, these approximation can fail badly.
-For example, predicted probabilities close to 0 or 1 or ratios of coefficients or probabilities typically do not have normal (or even symmetrical) distributions in finite samples, and the usual Wald-type confidence interval limits produced from delta method standard errors can include values outside the domain of the quantity of interest.
-
-\CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.
-Simulation-based inference is not only often more accurate than using the delta method, it is also simpler to understand and implement, as it does not require understanding Taylor series or the calculus that underlies it.
-This makes it more palatable to nontechnical audiences and easier to learn for students without sacrificing statistical performance.
-
-The methodology \CRANpkg{clarify} relies on is described in King, Tomz, and Wittenberg (2000) and Rainey (2023).
-Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a ``posterior'' distribution, which is taken to be the sampling distribution of the derived quantity, and from which uncertainty measures (standard errors and confidence intervals) can be computed.
+Quantifying the uncertainty of these derived quantities (i.e., computing standard errors, confidence intervals, and p-values) requires additional processing.
+Several methods of doing so exist, including the delta method, the bootstrap, and simulation-based inference.
+\CRANpkg{clarify} implements simulation-based inference, which we describe below along with these other methods.
+
+The delta method involves computing a first-order Taylor series approximation to the variance of the derived quantity, and standard Wald-based inference relies on computing quantiles based on the Normal distribution and using them to compute p-values and confidence intervals.
+\CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating a ``posterior'' distribution of the derived quantities.
+Simulation-based inference does not require understanding Taylor series or the calculus that underlies it, which can make it more palatable to nontechnical audiences and easier to learn for students without necessarily sacrificing statistical performance \citep{kingMakingMostStatistical2000, zelnerUsingSimulationInterpret2009}.
+Some studies have found that simulation-based inference performs as well or better than the delta method for computing derived quantities (i.e., with respect to achieving close to nominal coverage for confidence intervals), especially for complicated derived quantities and in smaller samples \citep{mackinnonConfidenceLimitsIndirect2004, holeComparisonApproachesEstimating2007, herronPostestimationUncertaintyLimited1999}.
+Its empirical performance has been particularly well studied in the context of mediation analysis, in which the quantities of interest are products and ratios of regression coefficients, where it has been shown to perform well relative to the delta method due to the non-Normality of these quantities \citep{tofighiMonteCarloConfidence2016, preacherAdvantagesMonteCarlo2012}.
+
+The methodology \CRANpkg{clarify} relies on was developed by \citet{krinsky1986} and is described in \citet{kingMakingMostStatistical2000} and \citet{herronPostestimationUncertaintyLimited1999}.
+Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a ``posterior'' distribution, from which uncertainty measures (standard errors and confidence intervals) can be computed.
 This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values, a standard assumption motivated by the central limit theorem that underlies usual inference on the original model parameters.
-Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates.
-The delta method makes these same assumptions in addition to the approximations about the variance and the shape of the sampling distribution of the estimates of the derived quantities.
-
-The nonparametric bootstrap is another alternative to the delta method for inference that does not require these approximations; it typically involves re-sampling individuals from the sample, fitting the model in each sample, and computing the quantity of interest from each model.
+Arriving at the posterior distribution does not require taking any derivatives or making any approximations beyond those usually used for inference on model parameter estimates, except for the approximation due to Monte Carlo error induced by sampling from a finite number of simulations (which can always be reduced by increasing the number of draws at the cost of increased computing time).
+
+The nonparametric bootstrap is another alternative to the delta method for inference that does not require its analytic approximations \citep{efronBootstrapMethodsStandard1986}; bootstrapping typically involves re-sampling individuals from the sample, fitting the model in each bootstrap sample, and computing the quantity of interest from each model.
 Although bootstrapping tends to work well in practice, especially for complex and non-Normal estimators, refitting the model repeatedly can be prohibitively time-consuming and computationally expensive, especially for complicated models or large datasets.
 Simulation-based inference only requires the model to be fit once, and the simulations involve taking draws from a distribution produced from the single set of estimated parameters, making it much quicker in practice and allowing the user to capitalize on the already valid estimation of the model parameters.
-
-More formally, we fit a regression model \(y_i = f(x_i; \beta)\), such as a linear or other generalized linear model with model coefficients \(\beta\). We assume\[
-\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})
-\]where \(\hat{\beta}\) is the vector of estimates of \(\beta\) and \(\Sigma_{\hat{\beta}}\) is their asymptotic covariance matrix.
+Methods for computing valid confidence intervals in cases when the quantity of interest has a complicated distribution are better developed when bootstrapping, however \citep{efronBootstrapMethodsStandard1986}.
+
+More formally, we fit a regression model \(y_i = f(x_i; \beta)\), such as a linear or other generalized linear model with model coefficients \(\beta\).
+We assume \(\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})\) where \(\hat{\beta}\) is the vector of estimates of \(\beta\) and \(\Sigma_{\hat{\beta}}\) is their asymptotic covariance matrix.
 We define a function \(\tau(\beta)\) that represents a quantity of interest derived from the model parameters, and compute its estimate \(\widehat{\tau(\beta)}\) as \(\tau(\hat{\beta})\).
-Next, we take \(M\) draws \(\tilde{\beta}^{(j)}\) for \(j\in(1, \dots, M)\) from a multivariate Normal distribution with mean vector \(\mu = \hat{\beta}\) and covariance \(\Sigma = \hat{\Sigma}_{\hat{\beta}}\), where \(\hat{\Sigma}_{\hat{\beta}}\) is an estimate of the asymptotic covariance matrix of the parameter estimates.
-We use the distribution of \(\tilde{\tau}=\tau(\tilde{\theta})\) as the ``posterior'' sampling distribution of \(\widehat{\tau(\beta)}\), and compute its variance as\[
-\sigma^2_{\widehat{\tau(\theta)}} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
-\]and quantile \(100(1-\alpha)\%\) confidence interval limits as \(\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]\) where \(\tilde{\tau}_{(k)}\) is the \(k\)th value of \(\tilde{\tau}\) when arranged in ascending order.
+
+To perform simulation-based inference, we take \(M\) draws \(\tilde{\beta}^{(j)}\) for \(j\in(1, \dots, M)\) from a multivariate Normal distribution with mean vector \(\mu = \hat{\beta}\) and covariance \(\Sigma = \hat{\Sigma}_{\hat{\beta}}\), where \(\hat{\Sigma}_{\hat{\beta}}\) is an estimate of the asymptotic covariance matrix of the parameter estimates.
+We use the distribution of \(\tilde{\tau}=\tau(\tilde{\beta})\) as the ``posterior'' distribution of \(\widehat{\tau(\beta)}\), and compute its variance as
+\begin{equation}
+\hat\sigma^2_{\widehat{\tau(\beta)}} = \frac{1}{M-1}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
+\label{eq:posteriorvariance}
+\end{equation}
+and quantile \(100(1-\alpha)\%\) confidence interval limits as \(\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]\) where \(\tilde{\tau}_{(q)}\) is the \(q\)th value of \(\tilde{\tau}\) when arranged in ascending order (i.e., the \(q\)th quantile of the empirical cumulative distribution function of \(\tilde{\tau}\)).
+Simulation-based Wald-type confidence intervals can be computed as
+\begin{equation}
+\left[\tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{\frac{\alpha}{2}}, \tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{1-\frac{\alpha}{2}} \right]
+\label{eq:siminterval}
+\end{equation}
+where \(Z_q\) is the \(q\)th quantile of a standard Normal distribution.
+The delta method-based Wald-type confidence intervals use this formula but with the first-order Taylor approximation to the asymptotic variance:
+\begin{equation}
+\hat\sigma^2_{\widehat{\tau(\beta)}}=\nabla\tau(\hat{\beta}) \Sigma_{\hat{\beta}} \nabla\tau'(\hat{\beta})
+\label{eq:deltavariance}
+\end{equation}
+where \(\nabla\tau(\hat{\beta})\) is the gradient of \(\tau(\beta)\) with respect to \(\beta\) evaluated at \(\hat{\beta}\).
+
+To compute a p-value for a hypothesis test involving the quantity of interest, i.e., \(\text{H}_0: \tau (\beta) = \tau_0\) with a given null value \(\tau_0\), we can invert the confidence interval \citep{thulinModernStatisticsWrangling2021}; that is, we find the largest value of \(\alpha\) such that \(\tau_0\) is within the confidence interval and use that \(\alpha\) as the p-value for the test.
+For Wald-based inference (either using the simulation-based variance or delta method-based variance), this is equivalent to performing a standard two-sided Z-test using the test statistic
+\begin{equation}
+Z=\frac{\tau(\hat\beta)-\tau_0}{\hat\sigma_{\widehat{\tau(\beta)}}}
+\label{eq:waldz}
+\end{equation}
+One benefit of using the quantile p-values for inference is that equivalent tests of the same hypothesis will always yield identical p-values; for example, testing the equality of two derived quantities will yield the same p-value when comparing the difference between the quantities against a null hypothesis of 0 and the ratio of the quantities against a null hypothesis of 1, as each of these hypothesis is true if and only if the other is true.
+
+One would expect simulation-based quantile inference, simulation-based Wald inference, and delta method-based Wald inference to align when the posterior is Normally distributed around the estimate, in which case any discrepancies would be due to Monte Carlo error in the simulated values (and therefore would shrink with increasing draws).
+However, for low values of \(\alpha\), it may require many draws for the simulation-based intervals to stabilize; delta method-based intervals are not subject to this error.
+There are a few cases in which the results might diverge: in some cases, the first-order Taylor series approximation to the variance may be poor, though in practice the approximation error is small and shrinks quickly with increasing sample size.
+When the posterior distribution is non-Normal but symmetric around the estimate, the quantile intervals may be more accurate (i.e., in the sense of achieving closer to nominal coverage) because they do not rely on quantiles from the Normal distribution \citep{tofighiMonteCarloConfidence2016}.
+
+Another potential advantage quantile intervals can have over Wald-intervals is that when \emph{some} monotonic transformation of the estimate has a symmetric distribution centered around the transformed estimate, the quantile intervals can achieve correct coverage without requiring knowledge of \emph{which} transformation is required \citep{efronBootstrapMethodsStandard1986}; this is true of the quantile-based p-values as well.
+When the distribution is not centered around the estimate and no monotonic transformation will make it so, though, neither quantile-based nor Wald-based intervals would be expected to perform well, and quantile intervals could yield even worse coverage than Wald-based intervals, a phenomenon that occurs in the context of bootstrapping \citep{efronBootstrapMethodsStandard1986}\footnote{We thank an anonymous reviewer for pointing out a scenario in which this could occur: for a quantity of interest with a right-skewed sampling distribution, one would prefer an estimate to the right of the quantity's true value to have a confidence interval skewed to left to capture the bulk of the sampling distribution, but in practice a quantile confidence interval would also be skewed to the right.
+While a symmetric Wald-based interval may not have adequate coverage, the quantile-based interval could perform even worse.}.
+An informal falsification test for whether such a monotonic transformation exists is whether the median of the simulated estimates is aligned with the point estimate; if it is not, there is no monotonic transformation that will yield a symmetric quantile interval with the desired coverage.
+
+\section{Related software}\label{related-software}
 
 Similar functionality exists in the \pkg{CLARIFY} package in Stata\footnote{Despite the similar name, the R package \CRANpkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \CRANpkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution.
-The R implementation avoids the ``simulation-induced bias'' described by Rainey (2023).} (Tomz, Wittenberg, and King 2003) and used to be available in the \texttt{Zelig} R package (Imai, King, and Lau 2008), though there are differences in these implementations.
+The R implementation avoids the ``simulation-induced bias'' described by \citet{raineyCarefulConsiderationCLARIFY2023}.} \citep{tomzClarifySoftwareInterpreting2003} and used to be available in the \pkg{Zelig} R package \citep{imaiCommonFrameworkStatistical2008a}, though there are differences in these implementations.
 \CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
-\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
-
-\hypertarget{using}{%
-\subsection{\texorpdfstring{Using \CRANpkg{clarify}}{Using }}\label{using}}
+\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package \citep{marginaleffectsforthcoming}, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
+
+\section{\texorpdfstring{Using \CRANpkg{clarify}}{Using }}\label{using}
 
@@
 \item
-  Use \texttt{sim()} to take draws from the sampling distribution of the estimated model coefficients.
+  Use \texttt{sim()} to take draws from the multivariate distribution of the estimated model coefficients.
 \item
@@
 
-For a running example, we will use the \texttt{lalonde} dataset in the \CRANpkg{MatchIt} package (Ho et al.
-2011), which contains data on 614 participants enrolled in a job training program or sampled from a survey (Dehejia and Wahba 1999).
+For a running example, we will use the \texttt{lalonde} dataset in the \CRANpkg{MatchIt} package \citep{JSSv042i08}, which contains data on 614 participants enrolled in a job training program or sampled from a survey \citep{dehejiaCausalEffectsNonexperimental1999}.
 The treatment variable is \texttt{treat} and the outcome is \texttt{re78}, and all other variables are confounders.
@@
 
-\hypertarget{fitting-the-model}{%
-\subsubsection{1. Fitting the model}\label{fitting-the-model}}
+\subsection{1. Fitting the model}\label{fitting-the-model}
 
@@
 
-\hypertarget{drawing-from-the-coefficient-distribution}{%
-\subsubsection{2. Drawing from the coefficient distribution}\label{drawing-from-the-coefficient-distribution}}
+\subsection{2. Drawing from the coefficient distribution}\label{drawing-from-the-coefficient-distribution}
 
@@
   \texttt{dist} -- the name of the distribution from which to draw the sampled coefficients.
-Can be \texttt{"normal"} for a Normal distribution or \texttt{t(\#)} for a t-distribution, where \texttt{\#} represents the degrees of freedom.
+Can be \texttt{"normal"} for a Normal distribution or \texttt{t(\#)} for a T-distribution, where \texttt{\#} represents the degrees of freedom.
 If left unspecified, \texttt{sim()} will decide on which distribution makes sense given the characteristics of the model (the decision is made by \texttt{insight::get\_df()} with \texttt{type\ =\ "wald"}).
@@
 \texttt{sim()} uses a random number generator to draw the sampled coefficients from the sampling distribution, so a seed should be set using \texttt{set.seed()} to ensure results are replicable across sessions.
+Using more iterations (i.e., increasing \texttt{n}) yields results that will be more stable across runs even when a seed is not set.
 
@@
 
-\hypertarget{computing-derived-quantities}{%
-\subsubsection{3. Computing derived quantities}\label{computing-derived-quantities}}
-
-After sampling the coefficients, we will compute derived quantities on each set of sampled coefficients and store the result, which represents the ``posterior'' distribution of the derived quantity, as well as on the original coefficients, which are used as the final estimates.
+\subsection{3. Computing derived quantities}\label{computing-derived-quantities}
+
+After sampling the coefficients, one can compute derived quantities on each set of sampled coefficients and store the result, which represents the ``posterior'' distribution of the derived quantity, as well as on the original coefficients, which are used as the final estimates.
 The core functionality is provided by \texttt{sim\_apply()}, which accepts a \texttt{clarify\_sim} object from \texttt{sim()} and a function to compute and return one or more derived quantities, then applies that function to each set of simulated coefficients.
@@
 \item
-  \texttt{...} - further arguments to \texttt{FUN}.
+  \texttt{...} -- further arguments to \texttt{FUN}.
 \end{itemize}
@@
 
-For example, we will let our derived quantity of interest be the predicted probability of the outcome for participant PSID1. We would specified our \texttt{FUN} function as follows:
+For example, we will let our derived quantity of interest be the predicted probability of the outcome for participant PSID1. We specify our \texttt{FUN} function as follows:
 
@@
 The resulting \texttt{clarify\_est} object contains the simulated estimates in matrix form as well as the estimate computed on the original coefficients.
-We will examine the sampling distribution shortly, but first we will demonstrate computing a derived quantity from the coefficients directly.
+We will examine the posterior distribution shortly, but first we will demonstrate computing a derived quantity from the coefficients directly.
 
@@
 
-\hypertarget{summarize-and-visualize-the-simulated-distribution}{%
-\subsubsection{4. Summarize and visualize the simulated distribution}\label{summarize-and-visualize-the-simulated-distribution}}
+\subsection{4. Summarize and visualize the simulated distribution}\label{summarize-and-visualize-the-simulated-distribution}
 
@@
 
-\texttt{plot()} displays a density plot of the resulting estimates across the simulations, with markers identifying the point estimate (computed using the original model coefficients as recommended by Rainey (2023)) and, optionally, uncertainty bounds (which function like confidence or credible interval bounds).
+\texttt{plot()} displays a density plot of the resulting estimates across the simulations, with markers identifying the point estimate (computed using the original model coefficients as recommended by \citet{raineyCarefulConsiderationCLARIFY2023}) and, optionally, uncertainty bounds (which function like confidence or credible interval bounds).
 The arguments to \texttt{plot()} are below:
@@
   \texttt{method} -- if \texttt{ci} is \texttt{TRUE}, the method used to compute the bounds.
-Allowable methods include a Normal approximation (\texttt{"wald"}) or using the quantiles of the resulting distribution (\texttt{"quantile"}).
+Allowable methods include the Normal approximation (\texttt{"wald"}) or using the quantiles of the resulting distribution (\texttt{"quantile"}).
 The Normal approximation involves multiplying the standard deviation of the estimates (i.e., which functions like the standard error of the sampling distribution) by the critical Z-statistic computed using \texttt{(1-level)/2} to create a symmetric margin of error around the point estimate.
-The default is \texttt{"quantile"} to instead use quantile-based bounds, which are more appropriate when the distribution is non-Normal.
-However, quantile-based bounds may require more simulations to stabilize.
-\item
-  \texttt{reference} -- whether to display a normal density over the plot for each estimate. The default is \texttt{FALSE} to omit it.
+The default is \texttt{"quantile"} to instead use quantile-based bounds.
+\item
+  \texttt{reference} -- whether to display a normal density over the plot for each estimate and an indicator line for the median of the estimate. The default is \texttt{FALSE} to omit them.
 \end{itemize}
@@
 
-\begin{center}\includegraphics{figures/unnamed-chunk-8-1} \end{center}
+\begin{center}\includegraphics[alt={A plot of the density of the simulated predicted probability for participant PSID1, overlaid with a Normal distribution and a reference line for the median of the estimates}]{figures/plot1-1} \end{center}
 
@@
 From the plot, one can see that the distribution of simulated values is non-Normal, asymmetrical, and not centered around the estimate, with no values falling above 1 because the outcome is a predicted probability.
-Given its non-Normality, the quantile-based bounds are clearly more appropriate than those resulting from the Normal approximation, as the bounds computed from the Normal approximation would be outside the bounds of the estimate.
+Given its non-Normality, the quantile-based bounds may be more appropriate than those resulting from the Normal approximation, as the bounds computed from the Normal approximation would be outside the bounds of the estimate.
+The blue reference line for the median of the estimates is close to the point estimate, suggesting it is possible for a monotonic transformation to have a symmetric distribution around the estimate\footnote{In fact, we know the inverse link function for the model (i.e., the Normal distribution function \texttt{qnorm()}) is such a transformation in this case; \CRANpkg{marginaleffects} and other packages that implement the delta method for confidence intervals around model predictions typically automatically compute confidence intervals on the transformed predictions before transforming the intervals back using the model's link function.
+As long as such a transformation exists, the quantile intervals will be as valid as those that rely on transforming and back-transforming.}.
 The plot itself is a \texttt{ggplot} object that can be modified using \texttt{ggplot2} syntax.
@@
 \item
-  \texttt{level} -- the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when method (see below) is \texttt{"quantile"}.
+  \texttt{level} -- the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when \texttt{method} (see below) is \texttt{"quantile"}.
 \item
@@
 \item
-  \texttt{null} -- an optional argument specifying the null value in a hypothesis test for the estimates.
+  \texttt{null} -- an optional argument specifying the desired null value in a hypothesis test for the estimates.
 If specified, a p-value will be computed using either a standard Z-test (if \texttt{method} is \texttt{"wald"}) or an inversion of the uncertainty interval (described below).
@@
 
-Inverting the uncertainty interval involves finding the smallest confidence level such that the null value is within the confidence bounds.
-The p-value for the test is one minus this level.
-It is only valid as a p-value when the simulated distribution of the estimates differs from its true sampling distribution under the null value by a location shift (which can be violated when the distribution of the estimates is asymmetric).
-However, because the p-values are invariant to monotonic transformations of the estimates and null value, as long as the distribution of \emph{some} monotonic transformation of the estimate is a location shift from its sampling distribution under the null hypothesis, the p-values will be valid.
-
 We can use \texttt{summary()} with the default arguments on our first \texttt{clarify\_est} object to view the point estimate and quantile-based uncertainty bounds.
@@
 #>       Estimate 2.5 % 97.5 %
-#> PSID1    0.976 0.891  0.996
-\end{verbatim}
-
-A benefit of quantile-based confidence bounds is that the bounds will always be in the domain of the quantity of interest, e.g., bounds for probabilities will not be above 1 or below 0 if the model always generates predicted probabilities between 0 and 1.
-In contrast, Wald-type symmetric confidence intervals (including those produced by the delta method) can include values outside the domain of the quantity of interest.
-While it is possible to compute Wald-type confidence interval bounds that respect the domain boundaries, e.g., by computing the confidence interval around the logit of the predicted probability and using the inverse logit of the bounds as the bound on the probability, quantile confidence intervals do not require the user to know which transformation of the quantity of interest will yield appropriate bounds.
+#> PSID1    0.976 0.890  0.996
+\end{verbatim}
 
@@
 
-\begin{center}\includegraphics{figures/unnamed-chunk-10-1} \end{center}
+\begin{center}\includegraphics[alt={A plot of the density of the simulated difference between two regression coefficients, overlaid with a Normal distribution and a reference line for the median of the estimates.}]{figures/plot2-1} \end{center}
 
@@
 The uncertainty intervals and p-values in the \texttt{summary()} output are computed using the Normal approximation because we set \texttt{method\ =\ "wald"}, and the p-value for the test that our estimate is equal to 0 is returned because we set \texttt{null\ =\ 0}.
-Note that the Normal approximation should be used only when the simulated sampling distribution is both close to Normally distributed and centered around the estimate (i.e., when the mean of the simulated values {[}red vertical line{]} coincides with the estimate computed on the original coefficients {[}black vertical line{]}).
-
-\hypertarget{sim_apply-wrappers-sim_setx-sim_ame-sim_adrf}{%
-\subsection{\texorpdfstring{\texttt{sim\_apply()} Wrappers: \texttt{sim\_setx()}, \texttt{sim\_ame()}, \texttt{sim\_adrf()}}{sim\_apply() Wrappers: sim\_setx(), sim\_ame(), sim\_adrf()}}\label{sim_apply-wrappers-sim_setx-sim_ame-sim_adrf}}
-
-\texttt{sim\_apply()} can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \CRANpkg{clarify} provides shortcut functions to make computing these quantities simple.
+Note that the Normal approximation should be used only when the simulated posterior distribution is both close to Normal and centered around the estimate (i.e., when the mean of the simulated values {[}red vertical line{]} coincides with the estimate computed on the original coefficients {[}black vertical line{]}).
+In such cases, however, the delta method will likely perform as well, if not better, and all of its other benefits apply (i.e., it is computationally quicker and not subject to Monte Carlo error).
+
+\section{\texorpdfstring{Wrappers for \texttt{sim\_apply()}: \texttt{sim\_setx()}, \texttt{sim\_ame()}, and \texttt{sim\_adrf()}}{Wrappers for sim\_apply(): sim\_setx(), sim\_ame(), and sim\_adrf()}}\label{wrappers-for-sim_apply-sim_setx-sim_ame-and-sim_adrf}
+
+\texttt{sim\_apply()} can be used to compute the simulated posterior distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \CRANpkg{clarify} provides shortcut functions to make computing these quantities simple.
 These functions include \texttt{sim\_setx()}, \texttt{sim\_ame()}, and \texttt{sim\_adrf()}.
@@
 
-\hypertarget{sim_setx-predictions-at-representative-values}{%
-\subsubsection{\texorpdfstring{\texttt{sim\_setx()}: predictions at representative values}{sim\_setx(): predictions at representative values}}\label{sim_setx-predictions-at-representative-values}}
+\subsection{\texorpdfstring{\texttt{sim\_setx()}: predictions at representative values}{sim\_setx(): predictions at representative values}}\label{sim_setx-predictions-at-representative-values}
 
@@
 For example, we might want to know what the effect of treatment is for a ``typical'' individual, which corresponds to the contrast between two model-based predictions (i.e., one under treatment and one under control for a unit with ``typical'' covariate values).
-This functionality mirrors the \texttt{setx()} and \texttt{setx1()} functionality of \texttt{Zelig} (which is where its name originates) and provides similar functionality to functions in \CRANpkg{modelbased}, \CRANpkg{emmeans}, \CRANpkg{effects}, and \CRANpkg{ggeffects}.
+This functionality mirrors the \texttt{setx()} and \texttt{setx1()} functionality of \pkg{Zelig} (which is where its name originates) and provides similar functionality to functions in \CRANpkg{modelbased}, \CRANpkg{emmeans}, \CRANpkg{effects}, and \CRANpkg{ggeffects}.
 
@@
 #>                         Estimate 2.5 % 97.5 %
-#> treat = 0, re75 = 0        0.667 0.558  0.771
-#> treat = 1, re75 = 0        0.712 0.618  0.790
-#> treat = 0, re75 = 20000    0.938 0.701  0.993
-#> treat = 1, re75 = 20000    0.953 0.751  0.996
+#> treat = 0, re75 = 0        0.667 0.558  0.772
+#> treat = 1, re75 = 0        0.712 0.617  0.790
+#> treat = 0, re75 = 20000    0.938 0.700  0.994
+#> treat = 1, re75 = 20000    0.953 0.747  0.996
 \end{verbatim}
@@
 
-\begin{center}\includegraphics{figures/unnamed-chunk-14-1} \end{center}
-
-One can see again how a delta method or Normal approximation may not have yielded valid uncertainty intervals given the non-Normality of the distributions.
+\begin{center}\includegraphics[alt={Two plots of the densities of the simulated predictions of the outcome for control and treated units, one corresponding to re74 = 0 and the other to re75 = 20000.}]{figures/plot3-1} \end{center}
+
+One can see again how a delta method or Normal approximation may have yielded uncertainty intervals outside the plausible range of the estimate without applying knowledge of the correct transformation to use to avoid doing so.
 
@@
 
-\begin{center}\includegraphics{figures/unnamed-chunk-16-1} \end{center}
+\begin{center}\includegraphics[alt={A plot of the predicted values of the outcome across levels of re75 from 0 to 20000 with a line for control units and a line for treated units.
+Each line has an uncertainty band around it.}]{figures/plot4-1} \end{center}
 
@@
 #>           Estimate   2.5 %  97.5 %
-#> treat = 0   0.7856  0.7041  0.8557
-#> treat = 1   0.8213  0.7114  0.8989
-#> FD          0.0357 -0.0592  0.1187
+#> treat = 0   0.7856  0.7039  0.8558
+#> treat = 1   0.8213  0.7111  0.8995
+#> FD          0.0357 -0.0598  0.1188
 \end{verbatim}
@@
 
-\hypertarget{sim_ame-average-adjusted-predictions-and-average-marginal-effects}{%
-\subsubsection{\texorpdfstring{\texttt{sim\_ame()}: average adjusted predictions and average marginal effects}{sim\_ame(): average adjusted predictions and average marginal effects}}\label{sim_ame-average-adjusted-predictions-and-average-marginal-effects}}
+\subsection{\texorpdfstring{\texttt{sim\_ame()}: average adjusted predictions and average marginal effects}{sim\_ame(): average adjusted predictions and average marginal effects}}\label{sim_ame-average-adjusted-predictions-and-average-marginal-effects}
 
@@
 The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units\footnote{In \CRANpkg{marginaleffects}, AAPs are computed using \texttt{avg\_predictions()}, AMEs for binary variables are computed using \texttt{avg\_comparisons()}, and AMEs for continuous variables are computed using \texttt{avg\_slopes()}.
-AAPs are sometimes known as average ``counterfactual'' predictions.} (Long and Freese 2014).
+AAPs are sometimes known as average ``counterfactual'' predictions.} \citep{longRegressionModelsCategorical2014}.
 
@@
 
-Here, we will use \texttt{sim\_ame()} to compute the AME of \texttt{treat} just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT (Greifer and Stuart 2023)).
+Here, we will use \texttt{sim\_ame()} to compute the AME of \texttt{treat} just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT \citep{greiferChoosingCausalEstimand2023}).
 We will request our estimate to be on the risk ratio scale.
@@
 #>         Estimate 2.5 % 97.5 % P-value
-#> E[Y(0)]    0.687 0.610  0.759       .
-#> E[Y(1)]    0.755 0.686  0.808       .
+#> E[Y(0)]    0.687 0.608  0.760       .
+#> E[Y(1)]    0.755 0.685  0.809       .
 #> RR         1.100 0.949  1.255    0.21
@@
 #>           Estimate 2.5 % 97.5 %
-#> E[Y(0)|0]    0.691 0.613  0.768
+#> E[Y(0)|0]    0.691 0.612  0.768
 #> E[Y(1)|0]    0.733 0.655  0.796
-#> RR[0]        1.061 0.911  1.232
-#> E[Y(0)|1]    0.668 0.556  0.768
-#> E[Y(1)|1]    0.848 0.677  0.940
-#> RR[1]        1.270 0.952  1.579
+#> RR[0]        1.061 0.909  1.234
+#> E[Y(0)|1]    0.668 0.556  0.769
+#> E[Y(1)|1]    0.848 0.676  0.940
+#> RR[1]        1.270 0.948  1.583
 \end{verbatim}
@@
 
-\hypertarget{sim_adrf-average-dose-response-functions}{%
-\subsubsection{\texorpdfstring{\texttt{sim\_adrf()}: average dose-response functions}{sim\_adrf(): average dose-response functions}}\label{sim_adrf-average-dose-response-functions}}
+\subsection{\texorpdfstring{\texttt{sim\_adrf()}: average dose-response functions}{sim\_adrf(): average dose-response functions}}\label{sim_adrf-average-dose-response-functions}
 
@@
 
-\begin{center}\includegraphics{figures/unnamed-chunk-25-1} \end{center}
+\begin{center}\includegraphics[alt={A plot of the average dose-response function for the outcome against age. The line has an uncertainty band around it.}]{figures/plot8-1} \end{center}
 
@@
 #> E[Y(20)]    0.811 0.764  0.845
-#> E[Y(22)]    0.800 0.757  0.831
+#> E[Y(22)]    0.800 0.757  0.832
 #> E[Y(24)]    0.788 0.749  0.817
@@
 
-\begin{center}\includegraphics{figures/unnamed-chunk-28-1} \end{center}
+\begin{center}\includegraphics[alt={A plot of the average marginal effect function for the outcome against age. The line has an uncertainty band around it.}]{figures/plot9-1} \end{center}
 
@@
 
-\hypertarget{transforming-and-combining-estimates}{%
-\subsection{Transforming and Combining Estimates}\label{transforming-and-combining-estimates}}
+\section{Transforming and combining estimates}\label{transforming-and-combining-estimates}
 
@@
 
-\hypertarget{transform}{%
-\subsubsection{\texorpdfstring{\texttt{transform()}}{transform()}}\label{transform}}
+\subsection{\texorpdfstring{\texttt{transform()}}{transform()}}\label{transform}
 
@@
 
-Note that we used tics (`) around the names of the AAPs; this is necessary when they contain special characters like parentheses or brackets.
+Note that we used tics (\texttt{\textasciigrave{}}) around the names of the AAPs; this is necessary when they contain special characters like parentheses or brackets.
+An alternative is to use the shortcut names \texttt{.b\#}, where \texttt{\#} is replaced with a number (e.g., as \texttt{.b1}, \texttt{.b2}, etc.) corresponding to the index of the quantity referenced.
+For example, because \texttt{E{[}Y(1){]}}and\texttt{E{[}Y(0){]}} are the second and first computed quantities, respectively, the above code could be replaced with
+
+\begin{verbatim}
+est6 <- transform(est6,
+                  RD = .b2 - .b1)
+\end{verbatim}
+
+which will yield identical results\footnote{Note that if a quantity is named \texttt{.b\#}, e.g., \texttt{.b1}, it can only be referred to using the positional shortcut and not its named.
+That is, the positional shortcut takes precedence over the names of the quantities.}.
 
@@
 #>         Estimate   2.5 %  97.5 % P-value
-#> E[Y(0)]   0.6866  0.6095  0.7590       .
-#> E[Y(1)]   0.7551  0.6859  0.8081       .
-#> RR        1.0998  0.9492  1.2553    0.21
-#> RD        0.0685 -0.0380  0.1574    0.21
-\end{verbatim}
-
-One benefit of using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.
-In contrast, Wald-type inference (based either on the simulation-derived standard error or the delta method) is not invariant to transformations of the quantity of interest.
+#> E[Y(0)]   0.6866  0.6081  0.7596       .
+#> E[Y(1)]   0.7551  0.6850  0.8088       .
+#> RR        1.0998  0.9485  1.2554    0.21
+#> RD        0.0685 -0.0382  0.1580    0.21
+\end{verbatim}
+
+As mentioned previously, one benefit of using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for testing the same hypothesis with the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.
+In contrast, Wald-type inference (based on either the simulation-derived or delta method standard error) is not invariant to transformations of the quantity of interest.
 
@@
 est6b |>
-  transform(RR_ratio = `RR[1]` / `RR[0]`) |>
-  summary(parm = c("RR[0]", "RR[1]", "RR_ratio"),
+  transform(`RR[1]/RR[0]` = `RR[1]` / `RR[0]`) |>
+  summary(parm = c("RR[0]", "RR[1]", "RR[1]/RR[0]"),
           null = 1)
@@
 #>             Estimate 2.5 % 97.5 % P-value  
-#> RR[0]       1.061 0.911  1.232   0.434  
-#> RR[1]       1.270 0.952  1.579   0.094 .
-#> RR_ratio    1.196 0.910  1.514   0.174  
+#> RR[0]          1.061 0.909  1.234   0.434  
+#> RR[1]          1.270 0.948  1.583   0.094 .
+#> RR[1]/RR[0]    1.196 0.908  1.516   0.174  
 #> ---
@@
 
-\texttt{RR\_ratio} contains the ratio of the risk ratios for \texttt{married\ =\ 1} and \texttt{married\ =\ 0}.
-Here we also include a test for whether each of the risk ratios and their ratio differ from 1.
-
-\hypertarget{cbind}{%
-\subsubsection{\texorpdfstring{\texttt{cbind()}}{cbind()}}\label{cbind}}
+\texttt{RR{[}1{]}/RR{[}0{]}} contains the ratio of the risk ratios for \texttt{married\ =\ 1} and \texttt{married\ =\ 0}.
+Here we also include a test for whether each of the risk ratios and their ratio differ from 1, which is equivalent to testing whether the risk ratios differ across levels of \texttt{married}.
+
+\subsection{\texorpdfstring{\texttt{cbind()}}{cbind()}}\label{cbind}
 
@@
 #>         Estimate   2.5 %  97.5 %
-#> E[Y(0)]   0.6677  0.5814  0.7527
-#> E[Y(1)]   0.7439  0.6663  0.8007
-#> Diff      0.0762 -0.0353  0.1694
+#> E[Y(0)]   0.6677  0.5813  0.7529
+#> E[Y(1)]   0.7439  0.6661  0.8016
+#> Diff      0.0762 -0.0359  0.1700
 \end{verbatim}
@@
 #>         Estimate   2.5 %  97.5 %
-#> E[Y(0)]   0.8266  0.7154  0.8972
-#> E[Y(1)]   0.8971  0.7892  0.9526
-#> Diff      0.0704 -0.0215  0.1382
+#> E[Y(0)]   0.8266  0.7146  0.8990
+#> E[Y(1)]   0.8971  0.7888  0.9527
+#> Diff      0.0704 -0.0223  0.1387
 \end{verbatim}
@@
 
-First, we need to rename to quantities in each object so they do not overlap; we can do so using \texttt{names()}, which has a special method for \texttt{clarify\_est} objects.
+First, we need to rename the quantities in each object so they do not overlap; we can do so using \texttt{names()}, which has a special method for \texttt{clarify\_est} objects.
 
@@
 #>           Estimate   2.5 %  97.5 %
-#> E[Y(0)]_b   0.6677  0.5814  0.7527
-#> E[Y(1)]_b   0.7439  0.6663  0.8007
-#> Diff_b      0.0762 -0.0353  0.1694
-#> E[Y(0)]_h   0.8266  0.7154  0.8972
-#> E[Y(1)]_h   0.8971  0.7892  0.9526
-#> Diff_h      0.0704 -0.0215  0.1382
+#> E[Y(0)]_b   0.6677  0.5813  0.7529
+#> E[Y(1)]_b   0.7439  0.6661  0.8016
+#> Diff_b      0.0762 -0.0359  0.1700
+#> E[Y(0)]_h   0.8266  0.7146  0.8990
+#> E[Y(1)]_h   0.8971  0.7888  0.9527
+#> Diff_h      0.0704 -0.0223  0.1387
 \end{verbatim}
@@
 #>         Estimate    2.5 %   97.5 %
-#> Dh - Db -0.00575 -0.06788  0.04102
+#> Dh - Db -0.00575 -0.06833  0.04103
 \end{verbatim}
@@
 Importantly, \texttt{cbind()} can only be used to join together \texttt{clarify\_est} objects computed using the same simulated coefficients (i.e., resulting from the same call to \texttt{sim()}).
-This preserves the covariance among the estimated quantities, which is critical for valid inference.
+This preserves the covariance among the estimated quantities, which is critical for maintaining valid inference.
 That is, \texttt{sim()} should only be called once per model, and all derived quantities should be computed using its output.
 
-\hypertarget{using-with-multiply-imputed-data}{%
-\subsection{\texorpdfstring{Using \CRANpkg{clarify} with Multiply Imputed Data}{Using  with Multiply Imputed Data}}\label{using-with-multiply-imputed-data}}
+\section{\texorpdfstring{Using \CRANpkg{clarify} with multiply imputed data}{Using  with multiply imputed data}}\label{using-with-multiply-imputed-data}
 
@@
 Simulated coefficients are drawn from the model estimated in each imputed dataset separately, and then the simulated coefficients are pooled into a single set of simulated coefficients.
-In Bayesian terms, this would be considered ``mixing draws'' and is the recommended approach for Bayesian analysis with multiply imputed data (Zhou and Reiter 2010).
+In Bayesian terms, this would be considered ``mixing draws'' and is the recommended approach for Bayesian analysis with multiply imputed data \citep{zhouNoteBayesianInference2010}.
 
@@
 The final estimates of the quantity of interest is computed as the mean of the estimates computed in each imputed dataset (i.e., using the original coefficients, not the simulated ones), which is the same quantity that would be computed using standard pooling rules.
-This is not always valid for noncollapsible estimates, like ratios, and so care should be taken to ensure the mean of the resulting estimates has a valid interpretation (this is related to the transformation-induced bias described by Rainey (2017)).
+This is not always valid for noncollapsible estimates, like ratios, and so care should be taken to ensure the mean of the resulting estimates has a valid interpretation (this is related to the transformation-induced bias described by \citet{rainey2017}).
 
@@
 
-The function we will be applying to each imputed dataset will be one that computes the average marginal effect of \texttt{infl}. (We will run the same analysis afterward using \texttt{sim\_ame()}.)
+The function we will be applying to each imputed dataset will be one that computes the AME of \texttt{infl}. (We will run the same analysis afterward using \texttt{sim\_ame()}.)
 
@@
 #>     Estimate 2.5 % 97.5 %
-#> AME    -5.75 -8.82  -2.27
+#> AME    -5.75 -8.82  -2.26
 \end{verbatim}
@@
 #>               Estimate 2.5 % 97.5 %
-#> E[dY/d(infl)]    -5.75 -8.82  -2.27
+#> E[dY/d(infl)]    -5.75 -8.82  -2.26
 \end{verbatim}
@@
 
-\hypertarget{comparison-to-other-packages}{%
-\subsection{Comparison to Other Packages}\label{comparison-to-other-packages}}
-
-Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans}, \CRANpkg{margins}, \CRANpkg{modelbased}, and \CRANpkg{marginaleffects}.
+\section{Comparison to other packages}\label{comparison-to-other-packages}
+
+Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} \citep{emmeans2024}, \CRANpkg{margins} \citep{margins2021}, \CRANpkg{modelbased} \citep{modelbased2020}, and \CRANpkg{marginaleffects} \citep{marginaleffectsforthcoming}.
 Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.
@@
 However, \CRANpkg{clarify} and \texttt{marignalefefcts} differ in several ways.
-The largest difference is that \CRANpkg{clarify} supports iterative building of more and more complex hypotheses through the \texttt{transform()} method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \CRANpkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.
-
-Because of \CRANpkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing.
-\CRANpkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.
+The largest difference is that \CRANpkg{clarify} supports iterative building of more and more complex hypotheses through the \texttt{transform()} method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \CRANpkg{marginaleffects} only supports a single transformation and, as of version 0.20.0, cannot use simulation-based inference for these quantities.
+
+Because of \CRANpkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to view the distributions of simulated values and support for parallel processing.
+\CRANpkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules.
 
@@
 \CRANpkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \CRANpkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience.
-In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \CRANpkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \CRANpkg{clarify} provides.
+In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately Normally distributed in finite samples), using the delta method through \CRANpkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \CRANpkg{clarify} provides.
 For the quantities easily computed by \CRANpkg{marginaleffects} that support simulation-based inference through \texttt{marginaleffects::inferences()}, using \CRANpkg{marginaleffects} can provide a more familiar and flexible syntax than \CRANpkg{clarify} might offer.
@@
 
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
+\section{Conclusion}\label{conclusion}
 
 \CRANpkg{clarify} provides functionality to facilitate simulation-based inference of deriving quantities from regression models.
-This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution of the derived quantity is Normal.
-\CRANpkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values.
-These enhance the usefulness and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-dehejiaCausalEffectsNonexperimental1999}{}}%
-Dehejia, Rajeev H., and Sadek Wahba.
-1999.
-{``Causal Effects in Nonexperimental Studies: Reevaluating the Evaluation of Training Programs.''} \emph{Journal of the American Statistical Association} 94 (448): 1053--62.
-\url{https://doi.org/10.1080/01621459.1999.10473858}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-greiferChoosingCausalEstimand2023}{}}%
-Greifer, Noah, and Elizabeth A. Stuart. 2023. {``Choosing the Causal Estimand for Propensity Score Analysis of Observational Studies.''} \url{https://doi.org/10.48550/arXiv.2106.10577}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-JSSv042i08}{}}%
-Ho, Daniel E., Kosuke Imai, Gary King, and Elizabeth A.
-Stuart.
-2011.
-{``MatchIt: Nonparametric Preprocessing for Parametric Causal Inference.''} \emph{Journal of Statistical Software, Articles} 42 (8): 128.
-\url{https://doi.org/10.18637/jss.v042.i08}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-imaiCommonFrameworkStatistical2008a}{}}%
-Imai, Kosuke, Gary King, and Olivia Lau.
-2008.
-{``Toward a Common Framework for Statistical Analysis and Development.''} \emph{Journal of Computational and Graphical Statistics} 17 (4): 892--913.
-\url{https://doi.org/10.1198/106186008X384898}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-kingMakingMostStatistical2000}{}}%
-King, Gary, Michael Tomz, and Jason Wittenberg.
-2000.
-{``Making the Most of Statistical Analyses: Improving Interpretation and Presentation.''} \emph{American Journal of Political Science} 44 (2): 347--61.
-\url{https://doi.org/10.2307/2669316}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-longRegressionModelsCategorical2014}{}}%
-Long, J. Scott, and Jeremy Freese. 2014. \emph{Regression Models for Categorical Dependent Variables Using Stata}. Third edition. College Station, Texas: Stata Press Publication, StataCorp LP.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rainey2017}{}}%
-Rainey, Carlisle.
-2017.
-{``Transformation-Induced Bias: Unbiased Coefficients Do Not Imply Unbiased Quantities of Interest.''} \emph{Political Analysis} 25 (3): 402--9.
-\url{https://doi.org/10.1017/pan.2017.11}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-raineyCarefulConsiderationCLARIFY2023}{}}%
----------.
-2023.
-{``A Careful Consideration of {CLARIFY}: Simulation-Induced Bias in Point Estimates of Quantities of Interest.''} \emph{Political Science Research and Methods}, April, 1--10.
-\url{https://doi.org/10.1017/psrm.2023.8}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-tomzClarifySoftwareInterpreting2003}{}}%
-Tomz, Michael, Jason Wittenberg, and Gary King.
-2003.
-{``Clarify: Software for Interpreting and Presenting Statistical Results.''} \emph{Journal of Statistical Software} 8 (January): 1--30.
-\url{https://doi.org/10.18637/jss.v008.i01}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-zhouNoteBayesianInference2010}{}}%
-Zhou, Xiang, and Jerome P. Reiter. 2010. {``A Note on Bayesian Inference After Multiple Imputation.''} \emph{The American Statistician} 64 (2): 159--63. \url{https://doi.org/10.1198/tast.2010.09109}.
-
-\end{CSLReferences}
+This framework provides an alternative to the delta method that can yield confidence intervals with closer to nominal coverage for some quantities of interest.
+While we do not claim simulation-based inference should be universally preferred over delta method-based inference, there are cases in which it can retain some advantageous properties, and we hope the availability of these methods in \CRANpkg{clarify} encourages additional research on when those properties can be realized and facilitates empirical work that takes advantages of these properties.
 

### 2025-09-18 rjournal_paper/Submission 2/clarify.tex
File management

--- 2025-09-18 rjournal_paper/Final version/clarify.tex
@@
 It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form a simulated ``posterior'' distribution of the quantity from which confidence intervals can be computed.
-clarify provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
-clarify supports a large and growing number of models through its interface with the marginaleffects package and provides native support for multiply imputed data.
+\texttt{clarify} provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
+\texttt{clarify} supports a large and growing number of models through its interface with the \texttt{marginaleffects} package and provides native support for multiply imputed data.
 }
@@
 \CRANpkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating a ``posterior'' distribution of the derived quantities.
-Simulation-based inference does not require understanding Taylor series or the calculus that underlies it, which can make it more palatable to nontechnical audiences and easier to learn for students without necessarily sacrificing statistical performance \citep{kingMakingMostStatistical2000, zelnerUsingSimulationInterpret2009}.
-Some studies have found that simulation-based inference performs as well or better than the delta method for computing derived quantities (i.e., with respect to achieving close to nominal coverage for confidence intervals), especially for complicated derived quantities and in smaller samples \citep{mackinnonConfidenceLimitsIndirect2004, holeComparisonApproachesEstimating2007, herronPostestimationUncertaintyLimited1999}.
-Its empirical performance has been particularly well studied in the context of mediation analysis, in which the quantities of interest are products and ratios of regression coefficients, where it has been shown to perform well relative to the delta method due to the non-Normality of these quantities \citep{tofighiMonteCarloConfidence2016, preacherAdvantagesMonteCarlo2012}.
-
-The methodology \CRANpkg{clarify} relies on was developed by \citet{krinsky1986} and is described in \citet{kingMakingMostStatistical2000} and \citet{herronPostestimationUncertaintyLimited1999}.
+Simulation-based inference does not require understanding Taylor series or the calculus that underlies it, which can make it more palatable to nontechnical audiences and easier to learn for students without necessarily sacrificing statistical performance (King, Tomz, and Wittenberg 2000; Zelner 2009).
+Some studies have found that simulation-based inference performs as well or better than the delta method for computing derived quantities (i.e., with respect to achieving close to nominal coverage for confidence intervals), especially for complicated derived quantities and in smaller samples (MacKinnon, Lockwood, and Williams 2004; Hole 2007; Herron 1999).
+Its empirical performance has been particularly well studied in the context of mediation analysis, in which the quantities of interest are products and ratios of regression coefficients, where it has been shown to perform well relative to the delta method due to the non-Normality of these quantities (Tofighi and MacKinnon 2016; Preacher and Selig 2012).
+
+The methodology \CRANpkg{clarify} relies on was developed by Krinsky and Robb (1986) and is described in King, Tomz, and Wittenberg (2000) and Herron (1999).
 Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a ``posterior'' distribution, from which uncertainty measures (standard errors and confidence intervals) can be computed.
@@
 
-The nonparametric bootstrap is another alternative to the delta method for inference that does not require its analytic approximations \citep{efronBootstrapMethodsStandard1986}; bootstrapping typically involves re-sampling individuals from the sample, fitting the model in each bootstrap sample, and computing the quantity of interest from each model.
+The nonparametric bootstrap is another alternative to the delta method for inference that does not require its analytic approximations (Efron and Tibshirani 1986); bootstrapping typically involves re-sampling individuals from the sample, fitting the model in each bootstrap sample, and computing the quantity of interest from each model.
 Although bootstrapping tends to work well in practice, especially for complex and non-Normal estimators, refitting the model repeatedly can be prohibitively time-consuming and computationally expensive, especially for complicated models or large datasets.
 Simulation-based inference only requires the model to be fit once, and the simulations involve taking draws from a distribution produced from the single set of estimated parameters, making it much quicker in practice and allowing the user to capitalize on the already valid estimation of the model parameters.
-Methods for computing valid confidence intervals in cases when the quantity of interest has a complicated distribution are better developed when bootstrapping, however \citep{efronBootstrapMethodsStandard1986}.
-
-More formally, we fit a regression model \(y_i = f(x_i; \beta)\), such as a linear or other generalized linear model with model coefficients \(\beta\).
-We assume \(\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})\) where \(\hat{\beta}\) is the vector of estimates of \(\beta\) and \(\Sigma_{\hat{\beta}}\) is their asymptotic covariance matrix.
+Methods for computing valid confidence intervals in cases when the quantity of interest has a complicated distribution are better developed when bootstrapping, however (Efron and Tibshirani 1986).
+
+More formally, we fit a regression model \(y_i = f(x_i; \beta)\), such as a linear or other generalized linear model with model coefficients \(\beta\). We assume\[
+\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})
+\]where \(\hat{\beta}\) is the vector of estimates of \(\beta\) and \(\Sigma_{\hat{\beta}}\) is their asymptotic covariance matrix.
 We define a function \(\tau(\beta)\) that represents a quantity of interest derived from the model parameters, and compute its estimate \(\widehat{\tau(\beta)}\) as \(\tau(\hat{\beta})\).
-
 To perform simulation-based inference, we take \(M\) draws \(\tilde{\beta}^{(j)}\) for \(j\in(1, \dots, M)\) from a multivariate Normal distribution with mean vector \(\mu = \hat{\beta}\) and covariance \(\Sigma = \hat{\Sigma}_{\hat{\beta}}\), where \(\hat{\Sigma}_{\hat{\beta}}\) is an estimate of the asymptotic covariance matrix of the parameter estimates.
-We use the distribution of \(\tilde{\tau}=\tau(\tilde{\beta})\) as the ``posterior'' distribution of \(\widehat{\tau(\beta)}\), and compute its variance as
-\begin{equation}
+We use the distribution of \(\tilde{\tau}=\tau(\tilde{\beta})\) as the ``posterior'' distribution of \(\widehat{\tau(\beta)}\), and compute its variance as\[
 \hat\sigma^2_{\widehat{\tau(\beta)}} = \frac{1}{M-1}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
-\label{eq:posteriorvariance}
-\end{equation}
-and quantile \(100(1-\alpha)\%\) confidence interval limits as \(\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]\) where \(\tilde{\tau}_{(q)}\) is the \(q\)th value of \(\tilde{\tau}\) when arranged in ascending order (i.e., the \(q\)th quantile of the empirical cumulative distribution function of \(\tilde{\tau}\)).
-Simulation-based Wald-type confidence intervals can be computed as
-\begin{equation}
-\left[\tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{\frac{\alpha}{2}}, \tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{1-\frac{\alpha}{2}} \right]
-\label{eq:siminterval}
-\end{equation}
-where \(Z_q\) is the \(q\)th quantile of a standard Normal distribution.
-The delta method-based Wald-type confidence intervals use this formula but with the first-order Taylor approximation to the asymptotic variance:
-\begin{equation}
-\hat\sigma^2_{\widehat{\tau(\beta)}}=\nabla\tau(\hat{\beta}) \Sigma_{\hat{\beta}} \nabla\tau'(\hat{\beta})
-\label{eq:deltavariance}
-\end{equation}
-where \(\nabla\tau(\hat{\beta})\) is the gradient of \(\tau(\beta)\) with respect to \(\beta\) evaluated at \(\hat{\beta}\).
-
-To compute a p-value for a hypothesis test involving the quantity of interest, i.e., \(\text{H}_0: \tau (\beta) = \tau_0\) with a given null value \(\tau_0\), we can invert the confidence interval \citep{thulinModernStatisticsWrangling2021}; that is, we find the largest value of \(\alpha\) such that \(\tau_0\) is within the confidence interval and use that \(\alpha\) as the p-value for the test.
-For Wald-based inference (either using the simulation-based variance or delta method-based variance), this is equivalent to performing a standard two-sided Z-test using the test statistic
-\begin{equation}
-Z=\frac{\tau(\hat\beta)-\tau_0}{\hat\sigma_{\widehat{\tau(\beta)}}}
-\label{eq:waldz}
-\end{equation}
+\]and quantile \(100(1-\alpha)\%\) confidence interval limits as \(\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]\) where \(\tilde{\tau}_{(q)}\) is the \(q\)th value of \(\tilde{\tau}\) when arranged in ascending order (i.e., the \(q\)th quantile of the empirical cumulative distribution function).
+Simulation-based Wald-type confidence intervals can be computed as \(\left[\tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{\frac{\alpha}{2}}, \tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{1-\frac{\alpha}{2}} \right]\), where \(Z_q\) is the \(q\)th quantile of a standard Normal distribution.
+The delta method-based Wald-type confidence intervals use this formula but with the first-order Taylor approximation to the asymptotic variance: \(\hat\sigma^2_{\widehat{\tau(\beta)}}=\nabla\tau(\hat{\beta}) \Sigma_{\hat{\beta}} \nabla\tau'(\hat{\beta})\), where \(\nabla\tau(\hat{\beta})\) is the gradient of \(\tau(\beta)\) with respect to \(\beta\) evaluated at \(\hat{\beta}\).
+
+To compute a p-value for a hypothesis test involving the quantity of interest, i.e., \(\text{H}_0: \tau (\beta) = \tau_0\) with a given null value \(\tau_0\), we can invert the confidence interval (Thulin 2021); that is, we find the largest value of \(\alpha\) such that \(\tau_0\) is within the confidence interval and use that \(\alpha\) as the p-value for the test.
+For Wald-based inference (either using the simulation-based variance or delta method-based variance), this is equivalent to performing a standard two-sided Z-test using the test statistic \(Z=\left(\tau(\hat\beta)-\tau_0\right) / \hat\sigma_{\widehat{\tau(\beta)}}\).
 One benefit of using the quantile p-values for inference is that equivalent tests of the same hypothesis will always yield identical p-values; for example, testing the equality of two derived quantities will yield the same p-value when comparing the difference between the quantities against a null hypothesis of 0 and the ratio of the quantities against a null hypothesis of 1, as each of these hypothesis is true if and only if the other is true.
@@
 There are a few cases in which the results might diverge: in some cases, the first-order Taylor series approximation to the variance may be poor, though in practice the approximation error is small and shrinks quickly with increasing sample size.
-When the posterior distribution is non-Normal but symmetric around the estimate, the quantile intervals may be more accurate (i.e., in the sense of achieving closer to nominal coverage) because they do not rely on quantiles from the Normal distribution \citep{tofighiMonteCarloConfidence2016}.
-
-Another potential advantage quantile intervals can have over Wald-intervals is that when \emph{some} monotonic transformation of the estimate has a symmetric distribution centered around the transformed estimate, the quantile intervals can achieve correct coverage without requiring knowledge of \emph{which} transformation is required \citep{efronBootstrapMethodsStandard1986}; this is true of the quantile-based p-values as well.
-When the distribution is not centered around the estimate and no monotonic transformation will make it so, though, neither quantile-based nor Wald-based intervals would be expected to perform well, and quantile intervals could yield even worse coverage than Wald-based intervals, a phenomenon that occurs in the context of bootstrapping \citep{efronBootstrapMethodsStandard1986}\footnote{We thank an anonymous reviewer for pointing out a scenario in which this could occur: for a quantity of interest with a right-skewed sampling distribution, one would prefer an estimate to the right of the quantity's true value to have a confidence interval skewed to left to capture the bulk of the sampling distribution, but in practice a quantile confidence interval would also be skewed to the right.
+When the posterior distribution is non-Normal but symmetric around the estimate, the quantile intervals may be more accurate (i.e., in the sense of achieving closer to nominal coverage) because they do not rely on quantiles from the Normal distribution (Tofighi and MacKinnon 2016).
+
+Another potential advantage quantile intervals can have over Wald-intervals is that when \emph{some} monotonic transformation of the estimate has a symmetric distribution centered around the transformed estimate, the quantile intervals can achieve correct coverage without requiring knowledge of \emph{which} transformation is required (Efron and Tibshirani 1986); this is true of the quantile-based p-values as well.
+When the distribution is not centered around the estimate and no monotonic transformation will make it so, though, neither quantile-based nor Wald-based intervals would be expected to perform well, and quantile intervals could yield even worse coverage than Wald-based intervals, a phenomenon that occurs in the context of bootstrapping {[}Efron and Tibshirani (1986){]}\footnote{We thank an anonymous reviewer for pointing out a scenario in which this could occur: for a quantity of interest with a right-skewed sampling distribution, one would prefer an estimate to the right of the quantity's true value to have a confidence interval skewed to left to capture the bulk of the sampling distribution, but in practice a quantile confidence interval would also be skewed to the right.
 While a symmetric Wald-based interval may not have adequate coverage, the quantile-based interval could perform even worse.}.
@@
 
-\section{Related software}\label{related-software}
+\section{Related Software}\label{related-software}
 
 Similar functionality exists in the \pkg{CLARIFY} package in Stata\footnote{Despite the similar name, the R package \CRANpkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \CRANpkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution.
-The R implementation avoids the ``simulation-induced bias'' described by \citet{raineyCarefulConsiderationCLARIFY2023}.} \citep{tomzClarifySoftwareInterpreting2003} and used to be available in the \pkg{Zelig} R package \citep{imaiCommonFrameworkStatistical2008a}, though there are differences in these implementations.
+The R implementation avoids the ``simulation-induced bias'' described by Rainey (2023).} (Tomz, Wittenberg, and King 2003) and used to be available in the \texttt{Zelig} R package (Imai, King, and Lau 2008), though there are differences in these implementations.
 \CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
-\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package \citep{marginaleffectsforthcoming}, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
+\CRANpkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package (Arel-Bundock, Greifer, and Heiss Forthcoming), which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
 
@@
 
-For a running example, we will use the \texttt{lalonde} dataset in the \CRANpkg{MatchIt} package \citep{JSSv042i08}, which contains data on 614 participants enrolled in a job training program or sampled from a survey \citep{dehejiaCausalEffectsNonexperimental1999}.
+For a running example, we will use the \texttt{lalonde} dataset in the \CRANpkg{MatchIt} package (Ho et al.
+2011), which contains data on 614 participants enrolled in a job training program or sampled from a survey (Dehejia and Wahba 1999).
 The treatment variable is \texttt{treat} and the outcome is \texttt{re78}, and all other variables are confounders.
@@
 
-\texttt{plot()} displays a density plot of the resulting estimates across the simulations, with markers identifying the point estimate (computed using the original model coefficients as recommended by \citet{raineyCarefulConsiderationCLARIFY2023}) and, optionally, uncertainty bounds (which function like confidence or credible interval bounds).
+\texttt{plot()} displays a density plot of the resulting estimates across the simulations, with markers identifying the point estimate (computed using the original model coefficients as recommended by Rainey (2023)) and, optionally, uncertainty bounds (which function like confidence or credible interval bounds).
 The arguments to \texttt{plot()} are below:
@@
   \texttt{method} -- if \texttt{ci} is \texttt{TRUE}, the method used to compute the bounds.
-Allowable methods include the Normal approximation (\texttt{"wald"}) or using the quantiles of the resulting distribution (\texttt{"quantile"}).
+Allowable methods include thea Normal approximation (\texttt{"wald"}) or using the quantiles of the resulting distribution (\texttt{"quantile"}).
 The Normal approximation involves multiplying the standard deviation of the estimates (i.e., which functions like the standard error of the sampling distribution) by the critical Z-statistic computed using \texttt{(1-level)/2} to create a symmetric margin of error around the point estimate.
@@
 
-\begin{center}\includegraphics[alt={A plot of the density of the simulated predicted probability for participant PSID1, overlaid with a Normal distribution and a reference line for the median of the estimates}]{figures/plot1-1} \end{center}
+\begin{center}\includegraphics{figures/plot1-1} \end{center}
 
@@
 \item
-  \texttt{level} -- the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when \texttt{method} (see below) is \texttt{"quantile"}.
+  \texttt{level} -- the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when method (see below) is \texttt{"quantile"}.
 \item
@@
 
-\begin{center}\includegraphics[alt={A plot of the density of the simulated difference between two regression coefficients, overlaid with a Normal distribution and a reference line for the median of the estimates.}]{figures/plot2-1} \end{center}
+\begin{center}\includegraphics{figures/plot2-1} \end{center}
 
@@
 
-\section{\texorpdfstring{Wrappers for \texttt{sim\_apply()}: \texttt{sim\_setx()}, \texttt{sim\_ame()}, and \texttt{sim\_adrf()}}{Wrappers for sim\_apply(): sim\_setx(), sim\_ame(), and sim\_adrf()}}\label{wrappers-for-sim_apply-sim_setx-sim_ame-and-sim_adrf}
+\section{\texorpdfstring{\texttt{sim\_apply()} Wrappers: \texttt{sim\_setx()}, \texttt{sim\_ame()}, \texttt{sim\_adrf()}}{sim\_apply() Wrappers: sim\_setx(), sim\_ame(), sim\_adrf()}}\label{sim_apply-wrappers-sim_setx-sim_ame-sim_adrf}
 
@@
 For example, we might want to know what the effect of treatment is for a ``typical'' individual, which corresponds to the contrast between two model-based predictions (i.e., one under treatment and one under control for a unit with ``typical'' covariate values).
-This functionality mirrors the \texttt{setx()} and \texttt{setx1()} functionality of \pkg{Zelig} (which is where its name originates) and provides similar functionality to functions in \CRANpkg{modelbased}, \CRANpkg{emmeans}, \CRANpkg{effects}, and \CRANpkg{ggeffects}.
+This functionality mirrors the \texttt{setx()} and \texttt{setx1()} functionality of \texttt{Zelig} (which is where its name originates) and provides similar functionality to functions in \CRANpkg{modelbased}, \CRANpkg{emmeans}, \CRANpkg{effects}, and \CRANpkg{ggeffects}.
 
@@
 \begin{verbatim}
-#>                         treat married      age     educ  race nodegree     re74
-#> treat = 0, re75 = 0         0       0 27.36319 10.26873 black        1 4557.547
-#> treat = 1, re75 = 0         1       0 27.36319 10.26873 black        1 4557.547
-#> treat = 0, re75 = 20000     0       0 27.36319 10.26873 black        1 4557.547
-#> treat = 1, re75 = 20000     1       0 27.36319 10.26873 black        1 4557.547
-#>                          re75
-#> treat = 0, re75 = 0         0
-#> treat = 1, re75 = 0         0
-#> treat = 0, re75 = 20000 20000
-#> treat = 1, re75 = 20000 20000
+#>                         treat married      age     educ  race nodegree     re74  re75
+#> treat = 0, re75 = 0         0       0 27.36319 10.26873 black        1 4557.547     0
+#> treat = 1, re75 = 0         1       0 27.36319 10.26873 black        1 4557.547     0
+#> treat = 0, re75 = 20000     0       0 27.36319 10.26873 black        1 4557.547 20000
+#> treat = 1, re75 = 20000     1       0 27.36319 10.26873 black        1 4557.547 20000
 \end{verbatim}
@@
 
-\begin{center}\includegraphics[alt={Two plots of the densities of the simulated predictions of the outcome for control and treated units, one corresponding to re74 = 0 and the other to re75 = 20000.}]{figures/plot3-1} \end{center}
+\begin{center}\includegraphics{figures/plot3-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[alt={A plot of the predicted values of the outcome across levels of re75 from 0 to 20000 with a line for control units and a line for treated units.
-Each line has an uncertainty band around it.}]{figures/plot4-1} \end{center}
+\begin{center}\includegraphics{figures/plot4-1} \end{center}
 
@@
 The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units\footnote{In \CRANpkg{marginaleffects}, AAPs are computed using \texttt{avg\_predictions()}, AMEs for binary variables are computed using \texttt{avg\_comparisons()}, and AMEs for continuous variables are computed using \texttt{avg\_slopes()}.
-AAPs are sometimes known as average ``counterfactual'' predictions.} \citep{longRegressionModelsCategorical2014}.
+AAPs are sometimes known as average ``counterfactual'' predictions.} (Long and Freese 2014).
 
@@
 
-Here, we will use \texttt{sim\_ame()} to compute the AME of \texttt{treat} just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT \citep{greiferChoosingCausalEstimand2023}).
+Here, we will use \texttt{sim\_ame()} to compute the AME of \texttt{treat} just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT (Greifer and Stuart 2023)).
 We will request our estimate to be on the risk ratio scale.
@@
 
-\begin{center}\includegraphics[alt={A plot of the average dose-response function for the outcome against age. The line has an uncertainty band around it.}]{figures/plot8-1} \end{center}
+\begin{center}\includegraphics{figures/plot8-1} \end{center}
 
@@
 
-\begin{center}\includegraphics[alt={A plot of the average marginal effect function for the outcome against age. The line has an uncertainty band around it.}]{figures/plot9-1} \end{center}
+\begin{center}\includegraphics{figures/plot9-1} \end{center}
 
@@
 
-\section{Transforming and combining estimates}\label{transforming-and-combining-estimates}
+\section{Transforming and Combining Estimates}\label{transforming-and-combining-estimates}
 
@@
 
-\section{\texorpdfstring{Using \CRANpkg{clarify} with multiply imputed data}{Using  with multiply imputed data}}\label{using-with-multiply-imputed-data}
+\section{\texorpdfstring{Using \pkg{clarify} with Multiply Imputed Data}{Using  with Multiply Imputed Data}}\label{using-with-multiply-imputed-data}
 
@@
 Simulated coefficients are drawn from the model estimated in each imputed dataset separately, and then the simulated coefficients are pooled into a single set of simulated coefficients.
-In Bayesian terms, this would be considered ``mixing draws'' and is the recommended approach for Bayesian analysis with multiply imputed data \citep{zhouNoteBayesianInference2010}.
+In Bayesian terms, this would be considered ``mixing draws'' and is the recommended approach for Bayesian analysis with multiply imputed data (Zhou and Reiter 2010).
 
@@
 The final estimates of the quantity of interest is computed as the mean of the estimates computed in each imputed dataset (i.e., using the original coefficients, not the simulated ones), which is the same quantity that would be computed using standard pooling rules.
-This is not always valid for noncollapsible estimates, like ratios, and so care should be taken to ensure the mean of the resulting estimates has a valid interpretation (this is related to the transformation-induced bias described by \citet{rainey2017}).
+This is not always valid for noncollapsible estimates, like ratios, and so care should be taken to ensure the mean of the resulting estimates has a valid interpretation (this is related to the transformation-induced bias described by Rainey (2017)).
 
@@
 
-\section{Comparison to other packages}\label{comparison-to-other-packages}
-
-Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} \citep{emmeans2024}, \CRANpkg{margins} \citep{margins2021}, \CRANpkg{modelbased} \citep{modelbased2020}, and \CRANpkg{marginaleffects} \citep{marginaleffectsforthcoming}.
+\section{Comparison to Other Packages}\label{comparison-to-other-packages}
+
+Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} (Lenth 2024), \pkg{margins} (Leeper 2021), \CRANpkg{modelbased} (Makowski et al.
+2020), and \CRANpkg{marginaleffects} (Arel-Bundock, Greifer, and Heiss Forthcoming).
 Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.
@@
 
-\bibliography{RJreferences.bib}
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-marginaleffectsforthcoming}{}}%
+Arel-Bundock, Vincent, Noah Greifer, and Andrew Heiss.
+Forthcoming.
+{``How to Intepret Statistical Models Using {marginaleffects} in {R} and {Python}.''} \emph{Journal of Statistical Software}, Forthcoming.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dehejiaCausalEffectsNonexperimental1999}{}}%
+Dehejia, Rajeev H., and Sadek Wahba.
+1999.
+{``Causal Effects in Nonexperimental Studies: Reevaluating the Evaluation of Training Programs.''} \emph{Journal of the American Statistical Association} 94 (448): 1053--62.
+\url{https://doi.org/10.1080/01621459.1999.10473858}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-efronBootstrapMethodsStandard1986}{}}%
+Efron, B., and R.
+Tibshirani.
+1986.
+{``Bootstrap Methods for Standard Errors, Confidence Intervals, and Other Measures of Statistical Accuracy.''} \emph{Statistical Science} 1 (1): 54--75.
+\url{https://www.jstor.org/stable/2245500}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-greiferChoosingCausalEstimand2023}{}}%
+Greifer, Noah, and Elizabeth A. Stuart. 2023. {``Choosing the Causal Estimand for Propensity Score Analysis of Observational Studies.''} \url{https://doi.org/10.48550/arXiv.2106.10577}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-herronPostestimationUncertaintyLimited1999}{}}%
+Herron, Michael C. 1999. {``Postestimation Uncertainty in Limited Dependent Variable Models.''} \emph{Political Analysis} 8 (1): 83--98. \url{https://doi.org/10.1093/oxfordjournals.pan.a029806}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-JSSv042i08}{}}%
+Ho, Daniel E., Kosuke Imai, Gary King, and Elizabeth A.
+Stuart.
+2011.
+{``MatchIt: Nonparametric Preprocessing for Parametric Causal Inference.''} \emph{Journal of Statistical Software, Articles} 42 (8): 128.
+\url{https://doi.org/10.18637/jss.v042.i08}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-holeComparisonApproachesEstimating2007}{}}%
+Hole, Arne Risa.
+2007.
+{``A Comparison of Approaches to Estimating Confidence Intervals for Willingness to Pay Measures.''} \emph{Health Economics} 16 (8): 827--40.
+\url{https://doi.org/10.1002/hec.1197}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-imaiCommonFrameworkStatistical2008a}{}}%
+Imai, Kosuke, Gary King, and Olivia Lau.
+2008.
+{``Toward a Common Framework for Statistical Analysis and Development.''} \emph{Journal of Computational and Graphical Statistics} 17 (4): 892--913.
+\url{https://doi.org/10.1198/106186008X384898}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kingMakingMostStatistical2000}{}}%
+King, Gary, Michael Tomz, and Jason Wittenberg.
+2000.
+{``Making the Most of Statistical Analyses: Improving Interpretation and Presentation.''} \emph{American Journal of Political Science} 44 (2): 347--61.
+\url{https://doi.org/10.2307/2669316}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-krinsky1986}{}}%
+Krinsky, Itzhak, and A.
+Leslie Robb.
+1986.
+{``On Approximating the Statistical Properties of Elasticities.''} \emph{The Review of Economics and Statistics} 68 (4): 715.
+\url{https://doi.org/10.2307/1924536}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-margins2021}{}}%
+Leeper, Thomas J. 2021. \emph{Margins: Marginal Effects for Model Objects}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-emmeans2024}{}}%
+Lenth, Russell V. 2024. \emph{Emmeans: Estimated Marginal Means, Aka Least-Squares Means}. \url{https://CRAN.R-project.org/package=emmeans}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-longRegressionModelsCategorical2014}{}}%
+Long, J. Scott, and Jeremy Freese. 2014. \emph{Regression Models for Categorical Dependent Variables Using Stata}. Third edition. College Station, Texas: Stata Press Publication, StataCorp LP.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mackinnonConfidenceLimitsIndirect2004}{}}%
+MacKinnon, David P., Chondra M.
+Lockwood, and Jason Williams.
+2004.
+{``Confidence Limits for the Indirect Effect: Distribution of the Product and Resampling Methods.''} \emph{Multivariate Behavioral Research} 39 (1): 99--128.
+\url{https://doi.org/10.1207/s15327906mbr3901_4}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-modelbased2020}{}}%
+Makowski, Dominique, Mattan S.
+Ben-Shachar, Indrajeet Patil, and Daniel Lüdecke.
+2020.
+{``Estimation of Model-Based Predictions, Contrasts and Means.''} \emph{CRAN}.
+\url{https://github.com/easystats/modelbased}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-preacherAdvantagesMonteCarlo2012}{}}%
+Preacher, Kristopher J., and James P.
+Selig.
+2012.
+{``Advantages of Monte Carlo Confidence Intervals for Indirect Effects.''} \emph{Communication Methods and Measures} 6 (2): 77--98.
+\url{https://doi.org/10.1080/19312458.2012.679848}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rainey2017}{}}%
+Rainey, Carlisle.
+2017.
+{``Transformation-Induced Bias: Unbiased Coefficients Do Not Imply Unbiased Quantities of Interest.''} \emph{Political Analysis} 25 (3): 402--9.
+\url{https://doi.org/10.1017/pan.2017.11}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-raineyCarefulConsiderationCLARIFY2023}{}}%
+---------.
+2023.
+{``A Careful Consideration of {CLARIFY}: Simulation-Induced Bias in Point Estimates of Quantities of Interest.''} \emph{Political Science Research and Methods}, April, 1--10.
+\url{https://doi.org/10.1017/psrm.2023.8}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-thulinModernStatisticsWrangling2021}{}}%
+Thulin, Måns. 2021. \emph{Modern Statistics with r: From Wrangling and Exploring Data to Inference and Predictive Modelling}. Uppsala, Sweden: Eos Chasma Press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tofighiMonteCarloConfidence2016}{}}%
+Tofighi, Davood, and David P.
+MacKinnon.
+2016.
+{``Monte Carlo Confidence Intervals for Complex Functions of Indirect Effects.''} \emph{Structural Equation Modeling: A Multidisciplinary Journal} 23 (2): 194205.
+\url{https://doi.org/10.1080/10705511.2015.1057284}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomzClarifySoftwareInterpreting2003}{}}%
+Tomz, Michael, Jason Wittenberg, and Gary King.
+2003.
+{``Clarify: Software for Interpreting and Presenting Statistical Results.''} \emph{Journal of Statistical Software} 8 (January): 1--30.
+\url{https://doi.org/10.18637/jss.v008.i01}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zelnerUsingSimulationInterpret2009}{}}%
+Zelner, Bennet A.
+2009.
+{``Using simulation to interpret results from logit, probit, and other nonlinear models.''} \emph{Strategic Management Journal} 30 (12): 1335--48.
+\url{https://doi.org/10.1002/smj.783}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-zhouNoteBayesianInference2010}{}}%
+Zhou, Xiang, and Jerome P. Reiter. 2010. {``A Note on Bayesian Inference After Multiple Imputation.''} \emph{The American Statistician} 64 (2): 159--63. \url{https://doi.org/10.1198/tast.2010.09109}.
+
+\end{CSLReferences}
 

### 2025-09-18 tests/testthat/test-sim_ame.R
Test updates to pass checks

@@ -359,6 +359,8 @@ test_that("sim_ame() works with MASS::polr()", {
 
 test_that("sim_ame() works with betareg::betareg()", {
   skip_if_not_installed("betareg")
+  skip_if_not_installed("marginaleffects", "0.30.0.2")
+
   mdata <- readRDS(test_path("fixtures", "mdata.rds"))
 
   fit <- betareg::betareg(propY ~ treat + age + educ + race + re74 | treat + age,

### 2025-09-18 README.Rmd

@@
 <!-- badges: start -->
-[![CRAN status](https://www.r-pkg.org/badges/version/clarify)](https://CRAN.R-project.org/package=clarify)
+[![](https://r-pkg.org/badges/version/clarify)](https://cran.rstudio.com/package=clarify)
+[![](https://cranlogs.r-pkg.org/badges/clarify)](https://cran.rstudio.com/package=clarify)
 <!-- badges: end -->
@@
 # Marginal risk ratio ATT, simulation-based
-sim_est <- sim_ame(sim_coefs, var = "treat", subset = treat == 1,
-                   contrast = "RR", verbose = FALSE)
+sim_est <- sim_ame(sim_coefs,
+                   var = "treat",
+                   subset = treat == 1,
+                   contrast = "RR",
+                   verbose = FALSE)
 
@@
 # of the other predictors
-sim_est <- sim_setx(sim_coefs, x = list(age = 20:50, treat = 0:1),
+sim_est <- sim_setx(sim_coefs,
+                    x = list(age = 20:50, treat = 0:1),
                     verbose = FALSE)

### 2025-09-18 _dev/clarify_old.Rmd

--- 2023-09-19 clarify/clarify.Rmd
@@
 ---
-title: "clarify: Simulation-Based Inference for Regression Models"
+title: "clarify"
+output: rmarkdown::html_vignette
 date: "`r Sys.Date()`"
-abstract: >
-  Simulation-based inference is an alternative to the delta method for computing the uncertainty around regression post-estimation (i.e., derived) quantities such as average marginal effects and adjusted predictions.
-It avoids several assumptions required by the delta method that are commonly violated, especially in nonlinear models, but does not require models to be refit as when using the bootstrap.
-It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form the sampling distribution of the quantity.
-\pkg{clarify} provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
-\pkg{clarify} supports a large and growing number of models through its interface with the \pkg{marginaleffects} package and provides native support for multiply imputed data.
-draft: true
-author:  
-  # see ?rjournal_article for more information
-  - name: Noah Greifer
-    affiliation: Harvard University
-    address:
-    - Institute for Quantitative Social Science
-    - Cambridge, MA
-    url: ngreifer.github.io
-    orcid: 0000-0003-3067-7154
-    email:  ngreifer@iq.harvard.edu
-  - name: Steven Worthington
-    affiliation: Harvard University
-    address:
-    - Institute for Quantitative Social Science
-    - Cambridge, MA
-    email: sworthington@iq.harvard.edu
-    orcid: 0000-0001-9550-5797
-  - name: Stefano Iacus
-    affiliation: Harvard University
-    address:
-    - Institute for Quantitative Social Science
-    - Cambridge, MA
-    email: siacus@iq.harvard.edu
-    orcid: 0000-0002-4884-0047
-  - name: Gary King
-    affiliation: Harvard University
-    address:
-    - Institute for Quantitative Social Science
-    - Cambridge, MA
-    email: king@harvard.edu
-    orcid: 0000-0002-5327-7631
-type: package
-output: 
-  rjtools::rjournal_web_article:
-    self_contained: yes
-    toc: no
-bibliography: RJreferences.bib
+vignette: >
+  %\VignetteIndexEntry{clarify}
+  %\VignetteEngine{knitr::rmarkdown}
+  %\VignetteEncoding{UTF-8}
+bibliography: references.bib
 ---
 
-```{r setup,include=FALSE}
+```{r, include = FALSE}
 knitr::opts_chunk$set(
-  fig.path = "figures/",
-  fig.align='center',
-  fig.height = 2
+  collapse = TRUE,
+  comment = "#>",
+  fig.width = 6.5,
+  fig.height = 2.75,
+  fig.align = "center"
 )
@@
 Although regression models are frequently used in empirical research to study relationships among variables, often the quantity of substantive interest is not one of the coefficients of the model, but rather a quantity derived from the coefficients, such as predicted values or average marginal effects.
-The usual method for estimating the uncertainty of the derived quantities is known as the "delta method", which involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the resulting estimate is normally distributed[^1].
-In many cases, especially with nonlinear models, these approximation can fail badly.
-\pkg{clarify} implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.
+The usual method for estimating the uncertainty of the derived quantities is an approximation known as the "delta method".
+The delta method involves two approximations: 1) that the variance of the derived quantity can be represented as a first-order Taylor series, and 2) that the resulting estimate is normally distributed[^1].In many cases, especially with nonlinear models, these approximation can fail badly.
+`clarify` implements an alternative to the delta method---simulation-based inference---which involves simulating the sampling distributions of the derived quantities.
 
@@
 
-The methodology \pkg{clarify} relies on is described in @kingMakingMostStatistical2000 and @raineyCarefulConsiderationCLARIFY2023.
-Simulation-based inference involves taking draws from a specified joint distribution of model parameters, computing derived quantities from these draws, and collecting the derived quantities in a "posterior" distribution, which is taken to be the sampling distribution of the derived quantity, and from which uncertainty measures (standard errors and confidence intervals) can be computed.
-This method assumes the model parameters are drawn from a multivariate Normal (or T) distribution with means at the estimated values and covariance equal to the asymptotic covariance matrix of the estimated values.
-Arriving at the posterior distribution does not require taking any derivatives or making any approximations except those used to define the sampling distribution of the parameter estimates.
-The delta method makes these same approximation in addition to the approximations of the variance and the shape of the sampling distribution of the estimates.
+The methodology `clarify` relies on is described in @kingMakingMostStatistical2000 and @raineyCarefulConsiderationCLARIFY2023.
+Similar functionality exists in the `CLARIFY` package in Stata [@tomzClarifySoftwareInterpreting2003][^2] and used to be available in the `Zelig` R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations.
+`clarify` provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
+`clarify` relies on and can be seen as a companion to the `marginaleffects` package, which offers similar functionality but primarily uses the delta method for calculating uncertainty.
 
-More formally, we fit a regression model $y_i = f(x_i; \beta)$, such a linear or generalized linear model with model coefficients $\beta$. We assume$$
-\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})
-$$where $\hat{\beta}$ is the vector of estimates of $\beta$ and $\Sigma_{\hat{\beta}}$ is their asymptotic covariance matrix.
-We define a function $\tau(\beta)$ that represents a quantity of interest derived from the model parameters, and compute its estimate $\hat{\tau}(\beta)$ as $\tau(\hat{\beta})$.
-Next, we take $M$ draws $\tilde{\beta}^{(j)}$ for $j\in(1, \dots, M)$ from a multivariate Normal distribution with mean vector $\boldsymbol{\mu} = \hat{\beta}$ and covariance $\Sigma = \hat{\Sigma}_{\hat{\beta}}$, where $\hat{\Sigma}_{\hat{\beta}}$ is an estimate of the asymptotic covariance matrix of the parameter estimates.
-We use the distribution of $\tilde{\tau}=\tau(\tilde{\theta})$ as the "posterior" sampling distribution of $\hat{\tau}(\beta)$, and compute its variance as$$
-\sigma^2_{\hat{\tau}(\theta)} = \frac{1}{M}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
-$$and quantile $100(1-\alpha)\%$ confidence interval limits as $\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]$ where $\tilde{\tau}_{(k)}$ is the $k$th value of $\tilde{\tau}$ when arranged in ascending order.
-
-Similar functionality exists in the \pkg{CLARIFY} package in Stata [@tomzClarifySoftwareInterpreting2003][^2] and used to be available in the `Zelig` R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations.
-\pkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
-\pkg{clarify} relies on and can be seen as a companion to the \CRANpkg{marginaleffects} package, which offers similar functionality but primarily uses the delta method for calculating uncertainty (though simulation-based inference is supported in a more limited capacity as well).
-
-[^2]: Despite the similar name, the R package \pkg{clarify} and the Stata package \pkg{CLARIFY} differ in several ways, one of which is that the estimates reported by \pkg{clarify} in R are those computed using the original model coefficients, whereas those reported by \pkg{CLARIFY} in Stata are those computed as the average of the simulated distribution.
+[^2]: Despite the similar name, the R package `clarify` and the Stata package `CLARIFY` differ in several ways, one of which is that the estimates reported by `clarify` in R are those computed using the original model coefficients, whereas those reported by `CLARIFY` in Stata are those computed as the average of the simulated distribution.
 The R implementation avoids the "simulation-induced bias" described by @raineyCarefulConsiderationCLARIFY2023.
 
-## Using \pkg{clarify}
+## Using `clarify`
 
-There are four steps to using \pkg{clarify}:
+There are four steps to using `clarify`:
 
-1.  Fit the model to the data using modeling functions in supported packages.
+1.  Fit the model to the data using modeling functions in supported packages
 
-2.  Use `sim()` to take draws from the sampling distribution of the estimated model coefficients.
+2.  Use `sim()` to take draws from the sampling distribution of the estimated model coefficients
 
-3.  Use `sim_apply()` or its wrappers `sim_setx()`, `sim_ame()`, and `sim_adrf()` to compute derived quantities using each simulated set of coefficients.
+3.  Use `sim_apply()` or its wrappers `sim_setx()`, `sim_ame()`, and `sim_adrf()` to compute derived quantities using each simulated set of coefficients
 
-4.  Use `summary()` and `plot()` to summarize and visualize the distribution of the derived quantities and perform inference on them.
+4.  Use `summary()` and `plot()` to summarize and visualize the distribution of the derived quantities and perform inference on them
 
-In the sections below, we'll describe how to implement these steps in detail. First, we'll load \pkg{clarify} using `library()`.
+In the sections below, we'll describe how to implement these steps in detail. First, we'll load `clarify` using `library()`.
 
-```{r}
+```{r setup}
 library(clarify)
@@
 
-For a running example, we'll use the `lalonde` dataset in the \pkg{MatchIt} package [@JSSv042i08], which contains data on 614 participants enrolled in a job training program or sampled from a survey [@dehejiaCausalEffectsNonexperimental1999].
+For a running example, we'll use the `lalonde` dataset in the `MatchIt` package, which contains data on 614 participants enrolled in a job training program or sampled from a survey.
 The treatment variable is `treat` and the outcome is `re78`, and all other variables are confounders.
-Although the original use of this dataset was to estimate the effect of `treat` on `re78`, we'll use it more generally to demonstrate all of \pkg{clarify}'s capabilities.
-In addition, we'll use a transformation of the outcome variable to demonstrate applications to nonlinear models, for which the benefits of simulation-based inference are more apparent.
+Although the original intent was to estimate the effect of `treat` on `re78`, we'll use it more generally to demonstrate all of `clarify`'s capabilities.
+In addition, we'll use a transformation of the outcome variable to demonstrate applications to nonlinear models.
 
@@
 
-### 1. Fitting the model
+## 1. Fitting the model
 
 The first step is to fit the model.
-\pkg{clarify} can operate on a large set of models (those supported by \pkg{marginaleffects}), including generalized linear models, multinomial models, multivariate models, and instrumental variable models, many of which are available in other R packages.
-Even if \pkg{clarify} does not offer direct support for a given model, there are ways to use its functionality regardless (explained in more detail below).
+`clarify` can operate on a large set of models (those supported by `marginaleffects`), including generalized linear models, multinomial models, multivariate models, and instrumental variable models, many of which are available in other R packages.
+Even if `clarify` does not offer direct support for a given model, there are ways to use its functionality regardless (explained in more detail below).
 
-Because we are computing derived quantities, it is not critical to parameterize the model in such a way that the coefficients are interpretable, e.g., by using a model with interpretable coefficients or centering predictors.
+Because we are computing derived quantities, it is not critical to parameterize the model in such a way that the coefficients are interpretable.
 Below, we'll fit a probit regression model for the outcome given the treatment and confounders.
-Coefficients in probit regression do not have a straightforward interpretation, but that's okay; our quantities of interest can be expressed as derived quantities---functions of the model parameters, such as predictions, counterfactual predictions, and averages and contrasts of them.
+Coefficients in probit regression do not have a straightforward interpretation, but that's okay; our quantities of interest can be expressed as derived quantities--functions of the model parameters, such as predictions, counterfactual predictions, and averages and contrasts of them.
 
@@
 
-### 2. Drawing from the coefficient distribution
+## 2. Drawing from the coefficient distribution
 
 After fitting the model, we will use `sim()` to draw coefficients from their sampling distribution.
-The sampling distribution is assumed to be multivariate Normal or multivariate T with appropriate degrees of freedom, with a mean vector equal to the estimated coefficients and a covariance matrix equal to the asymptotic covariance matrix extracted from the model.
+The sampling distribution is assumed to be multivariate normal or multivariate t with appropriate degrees of freedom, with a mean vector equal to the coefficient vector and a covariance matrix equal to the asymptotic covariance matrix extracted from the model.
 The arguments to `sim()` are listed below:
@@
 
--   `vcov` -- either the covariance matrix of the estimated coefficients, a function used to extract it from the model (e.g., `sandwich::vcovHC()` for the robust covariance matrix), or a string or formula giving a code for extracting the covariance matrix, which is passed to `marginaleffects::get_vcov()`.
+-   `vcov` -- either the covariance matrix of the estimated coefficients, a function used to extract it from the model (e.g., `sandwich::vcovHC()` for the robust covariance matrix), or a string or formula giving a code for extracting the covariance matrix (see `marginaleffects::get_vcov()` for details).
 If left unspecified, the default covariance matrix will be extracted from the model.
@@
 -   `dist` -- the name of the distribution from which to draw the sampled coefficients.
-Can be `"normal"` for a Normal distribution or `t(#)` for a t-distribution, where `#` represents the degrees of freedom.
+Can be `"normal"` for a normal distribution or `t(#)` for a t-distribution, where `#` represents the degrees of freedom.
 If left unspecified, `sim()` will decide on which distribution makes sense given the characteristics of the model (the decision is made by `insight::get_df()` with `type = "wald"`).
@@
 
-If one's model is not supported by \pkg{clarify}, one can omit the `fit` argument and just specify the `vcov` and `coefs` argument, which will draw the coefficients from the distribution named in `dist` (`"normal"` by default).
+If your model is not supported by `clarify`, you can omit the `fit` argument and just specify the `vcov` and `coefs` argument, which will draw the coefficients from the distribution named in `dist` (`"normal"` by default).
 
@@
 
-# Drawing 1000 simulated coefficients using an HC2 robust
+# Drawing simulated coefficients using an HC2 robust
 # covariance matrix
-s <- sim(fit, n = 1000,
-         vcov = "HC2")
+s <- sim(fit, vcov = "HC2")
 
@@
 
-### 3. Computing derived quantities
+## 3. Computing derived quantities
 
-After sampling the coefficients, we will compute derived quantities on each set of sampled coefficients and store the result, which represents the "posterior" distribution of the derived quantity, as well as on the original coefficients, which are used as the final estimates.
+After sampling the coefficients, we will compute derived quantities on each set of sampled coefficients and store the result, which represents a "posterior" distribution of the derived quantity, as well as on the original coefficients, which are used as the final estimates.
 The core functionality is provided by `sim_apply()`, which accepts a `clarify_sim` object from `sim()` and a function to compute and return one or more derived quantities, then applies that function to each set of simulated coefficients.
@@
 
-The `FUN` argument can be specified in one of two ways: either as a function that takes in a model fit object (e.g., a `glm` or `lm` object, the output of a call to `glm()` or `lm()`) or a function that takes in a vector of coefficients.
+The `FUN` argument can be specified in one of two ways: either as a function that takes in a model fit object or a function that takes in a vector of coefficients.
 The latter will always work but the former only works for supported models.
@@
 
-The `race` variable is a factor, and the `black` category is used as the reference level, so it is not immediately clear whether there is a difference between the coefficients `racehispan` and `racewhite`, which represent the non-reference categories `hispan` and `white`.
+The `race` variable is a factor, and the `black` category is used as the reference level, so it's not immediately clear whether there is a difference between the coefficients `racehispan` and `racewhite`, which represent the non-reference categories `hispan` and `white`.
 To compare these two directly, we can use `sim_apply()` to compute a derived quantity that corresponds to the difference between them.
@@
 
-The function supplied to `FUN` can be arbitrarily complicated and return as many derived quantities as one wants, though the slower each run of `FUN` is, the longer it will take to simulate the derived quantities.
+The function supplied to `FUN` can be arbitrarily complicated and return as many derived quantities as you want, though the slower each run of `FUN` is, the longer it will take to simulate the derived quantities.
 Using parallel processing by supplying an argument to `cl` can sometimes dramatically speed up evaluation.
 
-There are several functions in \pkg{clarify} that serve as convenience wrappers for `sim_apply()` to automate some common derived quantities of interest. These include
+There are several functions in `clarify` that serve as convenience wrappers for `sim_apply()` to automate some common derived quantities of interest. These include
 
@@
 
-```{r, fig.width=4}
+```{r}
 plot(est1, reference = TRUE, ci = FALSE)
@@
 
-From the plot, one can see that the distribution of simulated values is non-Normal, asymmetrical, and not centered around the estimate, with no values falling above 1 because the outcome is a predicted probability.
-Given its non-Normality, the quantile-based bounds are clearly more appropriate than those resulting from the Normal approximation, as the bounds computed from the Normal approximation would be outside the bounds of the estimate.
+From the plot, we can see that the distribution of simulated values is non-Normal, asymmetrical, and not centered around the estimate, with no values falling below 0 because the outcome is a predicted probability.
+Given its non-Normality, the quantile-based bounds are clearly more appropriate, as the bounds computed from the Normal approximation would be outside the bounds of the estimate.
 The plot itself is a `ggplot` object that can be modified using `ggplot2` syntax.
@@
 -   `null` -- an optional argument specifying the null value in a hypothesis test for the estimates.
-If specified, a p-value will be computed using either a standard Z-test (if `method` is `"wald"`) or an inversion of the uncertainty interval (described below).
+If specified, a p-value will be computed using either a standard Z-test (if `method` is `"quantile"`) or an inversion of the uncertainty interval.
 The default is not to display any p-values.
@@
 It is only valid as a p-value when the simulated distribution of the estimates differs from its true sampling distribution under the null value by a location shift (which can be violated when the distribution of the estimates is asymmetric).
-However, because the p-values are invariant to monotonic transformations of the estimates and null value, as long as the distribution of *some* monotonic transformation of the estimate is a location shift from its sampling distribution under the null hypothesis, the p-values will be valid.
+However, because the p-values are invariant to monotonic transformations of the estimates and null value, as long as the distribution of some monotonic transformation of the estimate is a location shift from its sampling distribution under the null hypothesis, the p-values will be valid.
 
@@
 
-A benefit of quantile-based confidence bounds is that the bounds will always be in the domain of the quantity of interest, e.g., bounds for probabilities will not be above 1 or below 0 if the model always generates predicted probabilities between 0 and 1.
-In contrast, Wald-type symmetric confidence intervals can include values outside the domain of the quantity of interest.
-While it is possible to compute Wald-type confidence interval bounds that respect the domain boundaries, e.g., by computing the confidence interval around the logit of the predicted probability and using the inverse logit of the bounds as the bound on the probability, quantile confidence intervals do not require the user to know which transformation of the quantity of interest will yield appropriate bounds.
-
 Our second estimated quantity, the difference between two regression coefficients, is closer to Normally distributed, as the plot below demonstrates (and would be expected theoretically), so we'll use the Normal approximation to test the hypothesis that difference differs from 0.
 
-```{r, fig.width=4}
+```{r}
 plot(est2, reference = TRUE, ci = FALSE)
@@
 The uncertainty intervals and p-values in the `summary()` output are computed using the Normal approximation because we set `method = "wald"`, and the p-value for the test that our estimate is equal to 0 is returned because we set `null = 0`.
+The computed bounds are very close to the quantile-based bound (displayed in the plot, and can be requested in `summary()` by setting `method = "quantile"`) because the simulated sampling distribution is close to Normal.
 Note that the Normal approximation should be used only when the simulated sampling distribution is both close to Normally distributed and centered around the estimate (i.e., when the mean of the simulated values [red vertical line] coincides with the estimate computed on the original coefficients [black vertical line]).
 
-## `sim_apply()` wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`
+# `sim_apply()` wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`
 
-`sim_apply()` can be used to compute the simulated sampling distribution for an arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program by hand, so \pkg{clarify} provides shortcut functions to make computing these quantities simple.
+`sim_apply()` can be used to compute the simulated sampling distribution for any arbitrary derived quantity of interest, but there are some quantities that are common in applied research and may otherwise be somewhat challenging to program on their own, so `clarify` provides shortcut functions to make computing these quantities simple.
 These functions include `sim_setx()`, `sim_ame()`, and `sim_adrf()`.
-Each of these can be used only when regression models compatible with \pkg{clarify} are supplied to the original call to `sim()`.
+Each of these can only be used when regression models compatible with `clarify` are supplied to the original call to `sim()`.
 
@@
 For example, we might want to know what the effect of treatment is for a "typical" individual, which corresponds to the contrast between two model-based predictions (i.e., one under treatment and one under control for a unit with "typical" covariate values).
-This functionality mirrors the `setx()` and `setx1()` functionality of `Zelig` (which is where its name originates) and provides similar functionality to functions in \pkg{modelbased}, \pkg{emmeans}, \pkg{effects}, and \pkg{ggeffects}.
+This functionality mirrors the `setx()` and `setx1()` functionality of `Zelig` (which is where its name originates) and provides similar functionality to functions in `modelbased`, `emmeans`, `effects`, and `ggeffects`.
 
-For each predictor, the user can specify whether they want predictions at specific values or at "typical" values, which are defined in \pkg{clarify} as the mode for unordered categorical and binary variables, the median for ordered categorical variables, and the mean for continuous variables.
+For each predictor, the user can specify whether they want predictions at specific values or at "typical" values, which are defined in `clarify` as the mode for unordered categorical and binary variables, the median for ordered categorical variables, and the mean for continuous variables.
 Predictions for multiple predictor combinations can be requested by specifying values that will be used to create a grid of predictor values, or the grid itself can be supplied as a data frame of desired predictor profiles.
@@
 
-```{r, fig.width=5}
+```{r}
 plot(est3, var = "re75", ci = FALSE)
@@
 
-One can see again how a delta method or Normal approximation may not have yielded valid uncertainty intervals given the non-Normality of the distributions.
+We can see again how a delta method or Normal approximation may not have yielded valid uncertainty intervals given the non-Normality of the distributions.
 
@@
 
-```{r, fig.width=5}
+```{r}
 plot(est4)
@@
 
-### `sim_ame()`: average adjusted predictions and average marginal effects
+## `sim_ame()`: average adjusted predictions and average marginal effects
 
-Using predicted values and effects at representative values is one way to summarize regression models, but another way is to compute average adjusted predictions (AAPs), contrasts of AAPs, and average marginal effects (AMEs).
+Using predicted values and effects at representative values is one way to summarize regression models, but another way is to compute average adjusted predictions (AAPs) and average marginal effects (AMEs).
 The definitions for these terms may vary and the names for these concepts differ across sources, but here we define AAPs as the average of the predicted values for all units after setting one predictor to a chosen value, and we define AMEs for binary predictors as the contrast of two AAPs and for continuous predictors as the average of instantaneous rate of change in the AAP corresponding to a small change in the predictor from its observed values across all units[^3].
 
-[^3]: In \pkg{marginaleffects}, AAPs are computed using `avg_predictions()`, AMEs for binary variables are computed using `avg_comparisons()`, and AMEs for continuous variables are computed using `avg_slopes()`.
+[^3]: In `marginaleffects`, AAPs are computed using `avg_predictions()`, AMEs for binary variables are computed using `avg_comparisons()`, and AMEs for continuous variables are computed using `avg_slopes()`.
 AAPs are sometimes known as average "counterfactual" predictions.
@@
 For continuous outcomes, `"diff"` requests the difference in means, but others are available for binary outcomes, including `"rr"` for the risk ratio, `"or"` for the odds ratio, and `"nnt"` for the number needed to treat, among others.
-If not specified, only AAPs will be computed if the variable named in `var` is categorical or specific values of the focal variable are specified in `var`.
-Ignored when the variable named in `var` is continuous and no specific values are specified because the AME is the only quantity computed.
-When `var` names a multi-category categorical variable, `contrast` cannot be used; see the section describing `transform()` for computing contrasts with them.
+If not specified, only AAPs will be computed if the variable named in `var` is binary.
+Ignored when the variable named in `var` is continuous because the AME is the only quantity computed.
+When `var` names a multi-category categorical variable, `contrast` cannot be used; see the section describing `transfom()` for computing contrasts with them.
 
@@
 
--   `type` -- a string containing the type of predicted value to return.
-In most cases, this can be left unspecified to request predictions on the scale of the outcome (e.g., probabilities for binary outcomes).
+-   `type` -- a string containing the type of predicted value to return. In most cases, this can be left unspecified to request predictions on the scale of the outcome.
 
@@
 
-Here, we'll use `sim_ame()` to compute the AME of `treat` just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT [@greiferChoosingCausalEstimand2023]).
+Here, we'll use `sim_ame()` to compute the AME of `treat` just among those who were treated (in causal inference, this is known as the average treatment effect in the treated, or ATT).
 We'll request our estimate to be on the risk ratio scale.
@@
 est6 <- sim_ame(s,
-                var = "treat",
-                subset = treat == 1,
-                contrast = "rr",
-                verbose = FALSE)
+                var = "treat", subset = treat == 1,
+                contrast = "RR", verbose = FALSE)
 ```
@@
 ```{r}
-est7 <- sim_ame(s,
-                var = "age",
-                verbose = FALSE)
+est7 <- sim_ame(s, var = "age", verbose = FALSE)
 ```
@@
 The AME is named `E[dY/d(age)]`, which signifies that a derivative has been computed (more precisely, the average of the unit-specific derivatives).
-This estimate can be interpreted like a slope in a linear regression model, but as a single summary of the effect of a predictor it is often too coarse to capture nonlinear relationships.
+This estimate can be interpreted like a slope in a linear regression model, but as a single summary of the effect of a predictor it is too coarse to capture nonlinear relationships.
 The section below explains how to compute average dose-response functions for continuous predictors, which provide a more complete picture of their effects on an outcome.
 
-Below, we'll examine effect modification of the ATT by the predictor `married` using the `by` argument to estimate AAPs and their ratio within levels of `married`:
+Below, we'll examine effect modification using the `by` argument to estimate AAPs and their ratio within levels of the predictor `married`:
 
@@
 est6b <- sim_ame(s,
-                 var = "treat",
-                 subset = treat == 1,
-                 by = ~married,
-                 contrast = "rr",
-                 verbose = FALSE)
+                 var = "treat", by = ~married,
+                 contrast = "RR", verbose = FALSE)
 
-summary(est6b)
+est6b
 ```
@@
 ``` r
-sim_adrf(sim = , var = , subset = , by = , contrast = , at = ,
-         n = , outcome = , type = , eps = , verbose = , cl = )
+sim_adrf(sim = , var = , subset = , contrast = , at = ,
+         n = , outcome = , type = , eps = , verbose = ,
+         cl = )
 ```
@@
 
-est8 <- sim_adrf(s,
-                 var = "age",
-                 contrast = "adrf",
-                 at = age_seq,
-                 verbose = FALSE)
+est8 <- sim_adrf(s, var = "age", contrast = "adrf",
+                 at = age_seq, verbose = FALSE)
 ```
@@
 
-```{r, fig.width=5}
+```{r}
 plot(est8)
@@
 
-From the plot, we can see that as `age` increases, the expected outcome decreases.
+From the plot, we can see that as `age` increases, the expected outcome also increases.
 
@@
 ```{r}
-est9 <- sim_adrf(s,
-                 var = "age",
-                 contrast = "amef",
-                 at = age_seq,
-                 verbose = FALSE)
+est9 <- sim_adrf(s, var = "age", contrast = "amef",
+                 at = age_seq, verbose = FALSE)
 ```
@@
 
-```{r, fig.width=5}
+```{r}
 plot(est9)
@@
 
-From the plot, we can see the AME of `age` decreases slightly but is mostly constant across values of `age`, and the uncertainty intervals for the AMEs consistently exclude 0.
+From the plot, we can see the AME of `age` increases slightly but is mostly constant across values of `age`, and the uncertainty intervals for the AMEs consistently exclude 0.
 
-## Transforming and combining estimates
+# Transforming and combining estimates
 
@@
 `transform()` is a generic function in R that is typically used to create a new variable in a data frame that is a function of other columns.
-For example, to compute the binary outcome we used in our model, we could have run the following[^4]:
-
-[^4]: Users familiar with the `tidyverse` will note the similarities between `transform()` and `dplyr::mutate()`; only `transform()` can be used with `clarify_est` objects.
+For example, to compute the binary outcome we used in our model, we could have run the following:
 
@@
 ```
+
+(Users familiar with the `tidyverse` will note the similarities between `transform()` and `dplyr::mutate()`; only `transform()` can be used with `clarify_est` objects.)
 
@@
 
-One benefit of using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.
+One nice thing about using simulation-based inference with p-values computed from inverting the confidence intervals is that the p-values for the risk difference and risk ratio (and any other effect measure for comparing a pair of values) will always exactly align, thereby ensuring inference does not depend on the effect measure used.
 
@@
 We can use `transform()` along with the `by` variable in `sim_ame()` to compute the contrast between quantities computed within each subgroup of `married`.
-Previously we used `by` to compute the risk ratio ATT within levels of `married`; here we will compute the ratio of these risk ratios to assess the presence of effect modification.
 
@@
 `cbind()` is another generic R function that is typically used to combine two or more datasets columnwise (i.e., to widen a dataset).
-In \pkg{clarify}, `cbind()` can be used to combine two `clarify_est` objects so that the estimates can be examined jointly and so that it is possible to compare them directly.
-For example, let's say we computed AMEs in two subgroups using `subset` and wanted to compare them.
+In `clarify`, `cbind()` can be used to combine two `clarify_est` objects so that the estimates can be examined jointly and so that it is possible to compare them directly.
+For example, let's say we computed AMEs in two subgroups using `subset`and wanted to compare them.
 To do so, we call `sim_ame()` twice, one for each subset (though in practice it is more effective to use `by`; this is just for illustration):
@@
 
-## Using \pkg{clarify} with multiply imputed data
+# Using `clarify` with multiply imputed data
 
@@
 amelia_ok <- requireNamespace("Amelia", quietly = TRUE)
-knitr::opts_chunk$set(
-  eval = amelia_ok
-)
-if (amelia_ok) library(Amelia)
 ```
 
-Multiple imputation is a popular method of estimating quantities of interest in the presence of missing data and involves creating multiple versions of the original dataset each with the missing values imputed with estimates from an imputation model.
 Simulation-based inference in multiply imputed data is relatively straightforward.
@@
 
-Using \pkg{clarify} with multiply imputed data is simple.
+Using `clarify` with multiply imputed data is simple.
 Rather than using `sim()`, we use the function `misim()`.
@@
 
--   `n` -- the number of simulations to run *for each imputed dataset*.
+-   `n` -- the number of simulations to run for each imputed dataset.
 The default is 1000, but fewer can be used because the total number of simulated quantities will be `m * n`, where `m` is the number of imputed datasets.
@@
 
-Below we illustrate using `misim()` and `sim_apply()` with multiply imputed data. We'll use the `africa` dataset from the \pkg{Amelia} package.
+Below we illustrate using `misim()` and `sim_apply()` with multiply imputed data. We'll use the `africa` dataset from the `Amelia` package.
 
-```{r, message=F}
+```{r, eval = amelia_ok}
 library(Amelia)
@@
 
-# Simulate coefficients, 100 draws per imputation
-si <- misim(model.list, n = 100)
+# Simulate coefficients
+si <- misim(model.list, n = 200)
 
@@
 
-```{r}
+```{r, eval = amelia_ok}
 sim_fun <- function(fit) {
@@
 
-  p0 <- predict(fit)
+  p0 <- predict(fit, newdata = X)
 
-  #Predictions after perturbing infl slightly
+  #Perturb infl slightly
   p1 <- predict(fit, newdata = transform(X, infl = infl + 1e-5))
@@
 
-```{r}
+```{r, eval = amelia_ok}
 est_mi2 <- sim_ame(si, var = "infl", verbose = FALSE)
@@
 
-Note that `misim()` is compatible with model fit objects from \pkg{mice}, \pkg{Amelia}, \pkg{MatchThem}, and any other package that produces a list of model fit objects with each corresponding to the output of a model fit to an imputed dataset.
+# Comparison to other packages
 
-## Comparison to other packages
+Several packages offer methods for computing interpretable quantities form regression models, including `emmeans`, `margins`, `modelbased`, and `marginaleffects`.
+Many of the quantities computed by these packages can also be computed by `clarify`, the primary difference being that `clarify` uses simulation-based inference rather than delta method-based inference.
 
-Several packages offer methods for computing interpretable quantities form regression models, including \pkg{emmeans}, \pkg{margins}, \pkg{modelbased}, and \pkg{marginaleffects}.
-Many of the quantities computed by these packages can also be computed by \pkg{clarify}, the primary difference being that \pkg{clarify} uses simulation-based inference rather than delta method-based inference.
+`marginaleffects` offers the most similar functionality to `clarify`, and `clarify` depends on functionality provided by `marginaleffects` to accommodate a wide variety of regression models.
+`marginaleffects` also offers simulation-based inference using `marginaleffects::inferences()` and support for arbitrary user-specified post-estimation functions using `marginaleffects::hypotheses()`.
+However, `clarify` and `marignalefefcts` differ in several ways.
+The largest difference is that `clarify` supports iterative building of more and more complex hypotheses through the `transform()` method, which quickly computes new quantities and transformation from the existing computed quantities, whereas `marginaleffects` only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.
 
-\pkg{marginaleffects} offers the most similar functionality to \pkg{clarify}, and \pkg{clarify} depends on functionality provided by \pkg{marginaleffects} to accommodate a wide variety of regression models.
-\pkg{marginaleffects} also offers simulation-based inference using `marginaleffects::inferences()` and support for arbitrary user-specified post-estimation functions using `marginaleffects::hypotheses()`.
-However, \pkg{clarify} and `marignalefefcts` differ in several ways.
-The largest difference is that \pkg{clarify} supports iterative building of more and more complex hypotheses through the `transform()` method, which quickly computes new quantities and transformation from the existing computed quantities, whereas \pkg{marginaleffects} only supports a single transformation and, as of version 0.13.0, cannot use simulation-based inference for these quantities.
+Because of `clarify`'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing.
+`clarify` also provides support for simulation-based inference of multiply imputed data, which does nto require any special pooling rules and does not require normality of the estimators.
 
-Because of \pkg{clarify}'s focus on simulation, it provides functionality directly aimed at improving simulation-based inference, including plots to assess the normality of the distributions of simulated values (important for assessing whether Wald-type confidence intervals and p-values are valid) and support for parallel processing.
-\pkg{clarify} also provides support for simulation-based inference of multiply imputed data, which does not require any special pooling rules and does not require normality of the derived quantities.
-
-There are areas and cases where \pkg{marginaleffects} may be the better choice than \pkg{clarify} or where the differences between the packages are of little consequence.
-\pkg{marginaleffects} focuses on providing a complete framework for post-estimation using model predictions, whereas \pkg{clarify} is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience.
-In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through \pkg{marginaleffects} will be much faster, more accurate, and more replicable than the simulation-based inference \pkg{clarify} provides.
-For the quantities easily computed by \pkg{marginaleffects} that support simulation-based inference through `marginaleffects::inferences()`, using \pkg{marginaleffects} can provide a more familiar and flexible syntax than \pkg{clarify} might offer.
+There are areas and cases where `marginaleffects` may be the better choice than `clarify` or where the differences between the packages are of smaller consequence.
+`marginaleffects` focuses on providing a complete framework for post-estimation using model predictions, whereas `clarify` is primarily focused on supporting user-defined functions, with commonly used estimators offered as a convenience.
+In cases where the delta method is an acceptable approximation (e.g., for quantities computed from linear models or other quantities known to be approximately normally distributed in finite samples), using the delta method through `marginaleffects` will be much faster, more accurate, and more replicable than the simulation-based inference `clarify` provides.
+For the quantities easily computed by `marginaleffects` and that support simulation-based inference through `marginaleffects::inferences()`, using `marginaleffects` can provide a more familiar and flexible syntax than `clarify` might offer.
 
 Note that as both packages continue to develop, these differences may grow or shrink.
-The differences above are meant to highlight the current differences and differences in philosophy and emphasis of the two packages.
+The difference above are meant to highlight the current differences and differences in philosophy and emphasis of the two packages.
 Ultimately, the user should use the package that supports their desired syntax and mode of inference.
 
-## Conclusion
-
-\pkg{clarify} provides utilities to facilitate simulation-based inference of deriving quantities form regression models.
-This framework avoids some of the approximations of the more common delta method, in particular the first-order approximation to the asymptotic variance and the approximation that the sampling distribution fo the derived quantity is Normal.
-\pkg{clarify} supports simulation-based inference of arbitrary derived quantities as well as common ones including average adjusted predictions, average marginal effects, and predictions at representative values.
-These enhance the utility and interpretability of regression models without requiring analysts to sacrifice parameterization for interpretability.
+# References

### 2025-09-18 rjournal_paper/Final version/clarify.Rmd

--- 2025-01-23 clarify/Final version/clarify.Rmd
@@
 title: "`clarify`: Simulation-Based Inference for Regression Models"
-date: "`r Sys.Date()`"
+date: "2025-02-11"
 abstract: >
@@
 It works by drawing model parameters from their joint distribution and estimating quantities of interest from each set of simulated values, which form a simulated "posterior" distribution of the quantity from which confidence intervals can be computed.
-`clarify` provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
-`clarify` supports a large and growing number of models through its interface with the `marginaleffects` package and provides native support for multiply imputed data.
+clarify provides a simple, unified interface for performing simulation-based inference for any user-specified derived quantities as well as wrappers for common quantities of interest.
+clarify supports a large and growing number of models through its interface with the marginaleffects package and provides native support for multiply imputed data.
 draft: true
@@
   rjtools::rjournal_pdf_article:
+    toc: no
+  rjtools::rjournal_web_article:
     self_contained: yes
@@
 
-More formally, we fit a regression model $y_i = f(x_i; \beta)$, such as a linear or other generalized linear model with model coefficients $\beta$. We assume$$
-\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})
-$$where $\hat{\beta}$ is the vector of estimates of $\beta$ and $\Sigma_{\hat{\beta}}$ is their asymptotic covariance matrix.
+More formally, we fit a regression model $y_i = f(x_i; \beta)$, such as a linear or other generalized linear model with model coefficients $\beta$.
+We assume $\hat{\beta} \sim \text{MVN}(\beta, \Sigma_{\hat{\beta}})$ where $\hat{\beta}$ is the vector of estimates of $\beta$ and $\Sigma_{\hat{\beta}}$ is their asymptotic covariance matrix.
 We define a function $\tau(\beta)$ that represents a quantity of interest derived from the model parameters, and compute its estimate $\widehat{\tau(\beta)}$ as $\tau(\hat{\beta})$.
+
 To perform simulation-based inference, we take $M$ draws $\tilde{\beta}^{(j)}$ for $j\in(1, \dots, M)$ from a multivariate Normal distribution with mean vector $\mu = \hat{\beta}$ and covariance $\Sigma = \hat{\Sigma}_{\hat{\beta}}$, where $\hat{\Sigma}_{\hat{\beta}}$ is an estimate of the asymptotic covariance matrix of the parameter estimates.
-We use the distribution of $\tilde{\tau}=\tau(\tilde{\beta})$ as the "posterior" distribution of $\widehat{\tau(\beta)}$, and compute its variance as$$
+We use the distribution of $\tilde{\tau}=\tau(\tilde{\beta})$ as the "posterior" distribution of $\widehat{\tau(\beta)}$, and compute its variance as
+\begin{equation}
 \hat\sigma^2_{\widehat{\tau(\beta)}} = \frac{1}{M-1}\sum^M_{j=1}{(\tilde{\tau}^{(j)} - \bar{\tilde{\tau}})^2}
-$$and quantile $100(1-\alpha)\%$ confidence interval limits as $\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]$ where $\tilde{\tau}_{(q)}$ is the $q$th value of $\tilde{\tau}$ when arranged in ascending order (i.e., the $q$th quantile of the empirical cumulative distribution function).
-Simulation-based Wald-type confidence intervals can be computed as $\left[\tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{\frac{\alpha}{2}}, \tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{1-\frac{\alpha}{2}} \right]$, where $Z_q$ is the $q$th quantile of a standard Normal distribution.
-The delta method-based Wald-type confidence intervals use this formula but with the first-order Taylor approximation to the asymptotic variance: $\hat\sigma^2_{\widehat{\tau(\beta)}}=\nabla\tau(\hat{\beta}) \Sigma_{\hat{\beta}} \nabla\tau'(\hat{\beta})$, where $\nabla\tau(\hat{\beta})$ is the gradient of $\tau(\beta)$ with respect to $\beta$ evaluated at $\hat{\beta}$.
+(\#eq:posteriorvariance)
+\end{equation} 
+and quantile $100(1-\alpha)\%$ confidence interval limits as $\left[\tilde{\tau}_{(\frac{\alpha}{2})}, \tilde{\tau}_{(1-\frac{\alpha}{2})}\right]$ where $\tilde{\tau}_{(q)}$ is the $q$th value of $\tilde{\tau}$ when arranged in ascending order (i.e., the $q$th quantile of the empirical cumulative distribution function of $\tilde{\tau}$).
+Simulation-based Wald-type confidence intervals can be computed as
+\begin{equation}
+\left[\tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{\frac{\alpha}{2}}, \tau(\hat{\beta}) + \hat\sigma_{\widehat{\tau(\beta)}} Z_{1-\frac{\alpha}{2}} \right]
+(\#eq:siminterval)
+\end{equation}
+where $Z_q$ is the $q$th quantile of a standard Normal distribution.
+The delta method-based Wald-type confidence intervals use this formula but with the first-order Taylor approximation to the asymptotic variance:
+\begin{equation}
+\hat\sigma^2_{\widehat{\tau(\beta)}}=\nabla\tau(\hat{\beta}) \Sigma_{\hat{\beta}} \nabla\tau'(\hat{\beta})
+(\#eq:deltavariance)
+\end{equation}
+where $\nabla\tau(\hat{\beta})$ is the gradient of $\tau(\beta)$ with respect to $\beta$ evaluated at $\hat{\beta}$.
 
 To compute a p-value for a hypothesis test involving the quantity of interest, i.e., $\text{H}_0: \tau (\beta) = \tau_0$ with a given null value $\tau_0$, we can invert the confidence interval [@thulinModernStatisticsWrangling2021]; that is, we find the largest value of $\alpha$ such that $\tau_0$ is within the confidence interval and use that $\alpha$ as the p-value for the test.
-For Wald-based inference (either using the simulation-based variance or delta method-based variance), this is equivalent to performing a standard two-sided Z-test using the test statistic $Z=\left(\tau(\hat\beta)-\tau_0\right) / \hat\sigma_{\widehat{\tau(\beta)}}$.
+For Wald-based inference (either using the simulation-based variance or delta method-based variance), this is equivalent to performing a standard two-sided Z-test using the test statistic
+\begin{equation}
+Z=\frac{\tau(\hat\beta)-\tau_0}{\hat\sigma_{\widehat{\tau(\beta)}}}
+(\#eq:waldz)
+\end{equation}
 One benefit of using the quantile p-values for inference is that equivalent tests of the same hypothesis will always yield identical p-values; for example, testing the equality of two derived quantities will yield the same p-value when comparing the difference between the quantities against a null hypothesis of 0 and the ratio of the quantities against a null hypothesis of 1, as each of these hypothesis is true if and only if the other is true.
@@
 
-# Related Software
+# Related software
 
-Similar functionality exists in the \pkg{CLARIFY} package in Stata[^2] [@tomzClarifySoftwareInterpreting2003] and used to be available in the `Zelig` R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations.
+Similar functionality exists in the \pkg{CLARIFY} package in Stata[^2] [@tomzClarifySoftwareInterpreting2003] and used to be available in the \pkg{Zelig} R package [@imaiCommonFrameworkStatistical2008a], though there are differences in these implementations.
 \CRANpkg{clarify} provides additional flexibility by allowing the user to request any derived quantity, in addition to providing shortcuts for common quantities, including predictions at representative values, average marginal effects, and average dose-response functions (described below).
@@
 -   `method` -- if `ci` is `TRUE`, the method used to compute the bounds.
-Allowable methods include thea Normal approximation (`"wald"`) or using the quantiles of the resulting distribution (`"quantile"`).
+Allowable methods include the Normal approximation (`"wald"`) or using the quantiles of the resulting distribution (`"quantile"`).
 The Normal approximation involves multiplying the standard deviation of the estimates (i.e., which functions like the standard error of the sampling distribution) by the critical Z-statistic computed using `(1-level)/2` to create a symmetric margin of error around the point estimate.
@@
 
-```{r plot1, fig.width=4}
+```{r plot1, fig.width=4, fig.alt="A plot of the density of the simulated predicted probability for participant PSID1, overlaid with a Normal distribution and a reference line for the median of the estimates"}
 plot(est1, reference = TRUE, ci = FALSE)
@@
 
--   `level` -- the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when method (see below) is `"quantile"`.
+-   `level` -- the desired two-sided confidence level. The default is .95 so that that the bounds are at the .025 and .975 quantiles when `method` (see below) is `"quantile"`.
 
@@
 
-```{r plot2, fig.width=4}
+```{r plot2, fig.width=4, fig.alt = "A plot of the density of the simulated difference between two regression coefficients, overlaid with a Normal distribution and a reference line for the median of the estimates."}
 plot(est2, reference = TRUE, ci = FALSE)
@@
 
-# `sim_apply()` Wrappers: `sim_setx()`, `sim_ame()`, `sim_adrf()`
+# Wrappers for `sim_apply()`: `sim_setx()`, `sim_ame()`, and `sim_adrf()`
 
@@
 For example, we might want to know what the effect of treatment is for a "typical" individual, which corresponds to the contrast between two model-based predictions (i.e., one under treatment and one under control for a unit with "typical" covariate values).
-This functionality mirrors the `setx()` and `setx1()` functionality of `Zelig` (which is where its name originates) and provides similar functionality to functions in \CRANpkg{modelbased}, \CRANpkg{emmeans}, \CRANpkg{effects}, and \CRANpkg{ggeffects}.
+This functionality mirrors the `setx()` and `setx1()` functionality of \pkg{Zelig} (which is where its name originates) and provides similar functionality to functions in \CRANpkg{modelbased}, \CRANpkg{emmeans}, \CRANpkg{effects}, and \CRANpkg{ggeffects}.
 
@@
 
-```{r plot3, fig.width=5}
+```{r plot3, fig.width=5, fig.alt = "Two plots of the densities of the simulated predictions of the outcome for control and treated units, one corresponding to re74 = 0 and the other to re75 = 20000."}
 plot(est3, var = "re75", ci = FALSE)
@@
 
-```{r plot4, fig.width=5}
+```{r plot4, fig.width=5, fig.alt = "A plot of the predicted values of the outcome across levels of re75 from 0 to 20000 with a line for control units and a line for treated units.
+Each line has an uncertainty band around it."}
 plot(est4)
@@
 
-```{r plot8, fig.width=5}
+```{r plot8, fig.width=5, fig.alt = "A plot of the average dose-response function for the outcome against age. The line has an uncertainty band around it."}
 plot(est8)
@@
 
-```{r plot9, fig.width=5}
+```{r plot9, fig.width=5, fig.alt = "A plot of the average marginal effect function for the outcome against age. The line has an uncertainty band around it."}
 plot(est9)
@@
 
-# Transforming and Combining Estimates
+# Transforming and combining estimates
 
@@
 
-# Using \pkg{clarify} with Multiply Imputed Data
+# Using \CRANpkg{clarify} with multiply imputed data
 
@@
 
-# Comparison to Other Packages
+# Comparison to other packages
 
-Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} [@emmeans2024], \pkg{margins} [@margins2021], \CRANpkg{modelbased} [@modelbased2020], and \CRANpkg{marginaleffects} [@marginaleffectsforthcoming].
+Several packages offer methods for computing interpretable quantities form regression models, including \CRANpkg{emmeans} [@emmeans2024], \CRANpkg{margins} [@margins2021], \CRANpkg{modelbased} [@modelbased2020], and \CRANpkg{marginaleffects} [@marginaleffectsforthcoming].
 Many of the quantities computed by these packages can also be computed by \CRANpkg{clarify}, the primary difference being that \CRANpkg{clarify} uses simulation-based inference rather than delta method-based inference.

### 2025-09-19 README.Rmd
Doc and site updates

--- 2024-05-30 README.Rmd
@@
 output: github_document
+bibliography: vignettes/references.bib
+link-citations: true
 ---
@@
 <!-- badges: start -->
-[![CRAN status](https://www.r-pkg.org/badges/version/clarify)](https://CRAN.R-project.org/package=clarify)
+
+[![](https://r-pkg.org/badges/version/clarify)](https://CRAN.R-project.org/package=clarify) [![](https://cranlogs.r-pkg.org/badges/clarify)](https://CRAN.R-project.org/package=clarify)
+
 <!-- badges: end -->
 
-`clarify` implements simulation-based inference for computing functions of model parameters, such as average marginal effects and predictions at representative values of the predictors.
-See the `clarify` [website](https://iqss.github.io/clarify/) for documentation and other examples.
-`clarify` was designed to replicate and expand on functionality previously provided by the `Zelig` package.
+*clarify* implements simulation-based inference for functions of model parameters, such as average marginal effects and predictions at representative values of the predictors.
+See the *clarify* [website](https://iqss.github.io/clarify/) for documentation and other examples, and see @greiferClarifySimulationBasedInference2025 for the paper describing the package (also available at `vignette("clarify")`).
+*clarify* was designed to replicate and expand on functionality previously provided by the *Zelig* package.
 
@@
 
-`clarify` can be installed from CRAN using
+*clarify* can be installed from [CRAN](https://CRAN.R-project.org/package=clarify) using
 
@@
 
-You can install the development version of `clarify` from [GitHub](https://github.com/iqss/clarify) with
+You can install the development version of *clarify* from [GitHub](https://github.com/iqss/clarify) with
 
@@
 Below is an example of performing g-computation for the average treatment effect on the treated (ATT) after logistic regression to compute the average causal risk ratio and its confidence interval.
-First we load the data (in this case the `lalonde` dataset from `MatchIt`) and fit a logistic regression using functions outside of `clarify`:
+First we load the data (in this case the `lalonde` dataset from *MatchIt*) and fit a logistic regression using functions outside of *clarify*:
 
@@
 
-Below, we provide information on the framework `clarify` uses and some other examples. For a complete vignette, see `vignette("clarify")`.
+Below, we provide information on the framework *clarify* uses and some other examples. For a complete vignette, see `vignette("clarify")`.
 
@@
 Alternatively, if the resulting sampling distribution is normally distributed, its standard error can be estimated as the standard deviation of the estimates and normal-theory Wald confidence intervals and p-values can be computed.
-The methodology of simulation-based inference is explained in King, Tomz, and Wittenberg (2000).
+The methodology of simulation-based inference is explained in @kingMakingMostStatistical2000 and @herronPostestimationUncertaintyLimited1999.
 
-`clarify` was designed to provide a simple, general interface for simulation-based inference and includes a few convenience functions to perform common tasks like computing average marginal effects.
-The primary functions of `clarify` are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
+*clarify* was designed to provide a simple, general interface for simulation-based inference and includes a few convenience functions to perform common tasks like computing average marginal effects.
+The primary functions of *clarify* are `sim()`, `sim_apply()`, `summary()`, and `plot()`.
 These work together to create a simple workflow for simulation-based inference.
 
-* `sim()` simulates model parameters from a fitted model
-* `sim_apply()` applies an estimator to the simulated coefficients, or to the original object but with the new coefficients inserted
-* `summary()` produces confidence intervals and p-values for the resulting estimates
-* `plot()` produces plots of the simulated sampling distribution of the resulting estimates
+-   `sim()` simulates model parameters from a fitted model
+-   `sim_apply()` applies an estimator to the simulated coefficients, or to the original object but with the new coefficients inserted
+-   `summary()` produces confidence intervals and p-values for the resulting estimates
+-   `plot()` produces plots of the simulated sampling distribution of the resulting estimates
 
 There are also some wrappers for `sim_apply()` for performing some common operations: `sim_ame()` computes the average marginal effect of a variable, mirroring `marginaleffects::avg_predictions()` and `marginaleffects::avg_slopes()`; `sim_setx()` computes predictions at typical values of the covariates and differences between them, mirroring `Zelig::setx()` and `Zelig::setx1()`; and `sim_adrf()` computes average dose-response functions.
-`clarify` also offers support for models fit to multiply imputed data with the `misim()` function.
+*clarify* also offers support for models fit to multiply imputed data with the `misim()` function.
 
@@
 The plot of the simulated sampling distribution indicates that the sampling distribution for the risk ratio is not normally distributed around the estimate, indicating that the delta method may be a poor approximation and the asymmetric confidence intervals produced using the simulation may be more valid.
-Note that the estimates are those computed from the original model coefficients; the distribution is used only for computing confidence intervals, in line with recommendations by Rainey (2023).
+Note that the estimates are those computed from the original model coefficients; the distribution is used only for computing confidence intervals, in line with recommendations by @raineyCarefulConsiderationCLARIFY2023.
 
@@
 sim_est <- transform(sim_est, `RD` = `E[Y(1)]` - `E[Y(0)]`)
+
 summary(sim_est, null = c(`RR` = 1, `RD` = 0))
@@
 
-We can also use `clarify` to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of `Zelig`'s `setx()` and `setx1()` functions, using `sim_setx()`:
+We can also use *clarify* to compute predictions and first differences at set and typical values of the predictors, mimicking the functionality of *Zelig*'s `setx()` and `setx1()` functions, using `sim_setx()`:
 
@@
 
-See `vignette("Zelig", package = "clarify")` for more examples of translating a `Zelig`-based workflow into one that uses `clarify` to estimate the same quantities of interest.
+See `vignette("Zelig", package = "clarify")` for more examples of translating a *Zelig*-based workflow into one that uses *clarify* to estimate the same quantities of interest.
 
-`clarify` offers parallel processing for all estimation functions to speed up computation.
+*clarify* offers parallel processing for all estimation functions to speed up computation.
 Functionality is also available for the analysis of models fit to multiply imputed data.
@@
 ## References
-
-King, G., Tomz, M., & Wittenberg, J.
-(2000).
-Making the Most of Statistical Analyses: Improving Interpretation and Presentation.
-*American Journal of Political Science*, 44(2), 347–361.
-https://doi.org/10.2307/2669316
-
-Rainey, C.
-(2023).
-A careful consideration of CLARIFY: Simulation-induced bias in point estimates of quantities of interest.
-*Political Science Research and Methods*, 1–10.
-https://doi.org/10.1017/psrm.2023.8
